### 2016-06-26 Main.Rmd
First Commit

---
title: "EBC2016"
author: "KeachMurakami"
date: "June 24, 2016"
bibliography: ~/Dropbox/R/List.bib
csl: new-phytologist.csl
output:
  html_document:
    toc: true
    # toc_float: true
    depth: 3
    theme: sandstone
    self_contained: TRUE
    fig_caption: true
    pandoc_args: [
    "--latexmathml"
    ]
  # word_document:
  #   toc: true
  #   fig_caption: true
  #   pandoc_args: [
  #   "--latexmathml"
  #   ]
---

```{r load, echo = F, message = F}
devtools::source_url("https://raw.githubusercontent.com/KeachMurakami/Sources/master/Startup.R")
opts_chunk$set(echo = FALSE, fig.width = 7.5, fig.height = 7.5, out.width = "100%",
               message = FALSE, warning = FALSE, cache = F, eval = T)

base_size_default <- 12

theme_bw2 <-
  function(base_size = 12, base_family = "", legend = "none"){
    theme_bw() %+replace%
      theme(legend.position = legend,
            panel.grid.minor = element_blank(),
            axis.ticks = element_line(colour = "grey50", size = rel(.75)),
            panel.margin = unit(0, units = "points")
      )
    }

options(warn = -1)
options(warn = 1)
```

Authors: Keach Murakami^1+^, Ryo Matsuda^1^, and Kazuhiro Fujiwara^1^

Affiliations: ^1^Graduate School of Agricultural and Life Sciences, The University of Tokyo

Address: ^1^Yayoi, Bunkyo, Tokyo, 113--8657, Japan

e-mail: keach.murakami@gmail.com

------

The photosynthetic rate is one of the most important and widely-used information for the plant sciences.
ダメージだとか、成長速度だとかを反映する。

なので、正しい値が知りたい。

でも、バイアスがよく入る。
弱光可でも

------

# References

### 2016-06-30 Main.Rmd
進捗。

@@
 ---
-title: "EBC2016"
+title: ""
 author: "KeachMurakami"
@@
 bibliography: ~/Dropbox/R/List.bib
-csl: new-phytologist.csl
+# csl: new-phytologist.csl
 output:
@@
 ```{r load, echo = F, message = F}
-devtools::source_url("https://raw.githubusercontent.com/KeachMurakami/Sources/master/Startup.R")
+# devtools::source_url("https://raw.githubusercontent.com/KeachMurakami/Sources/master/Startup.R")
+library(knitr)
 opts_chunk$set(echo = FALSE, fig.width = 7.5, fig.height = 7.5, out.width = "100%",
@@
 
-The photosynthetic rate is one of the most important and widely-used information for the plant sciences.
-ダメージだとか、成長速度だとかを反映する。
+# Introduction
 
-なので、正しい値が知りたい。
+  The photosynthetic rate is one of the most important and commonly reported phenotype for the plant sciences.
+  The rate represents the physiological and 
+  Considering the importance of the photosynthetic rate, the effects on the rates were evaluated, and.
+  Thus, the reliable measurements must be made prior to the evaluation.
+  文献間での比較 (scalable research)
 
-でも、バイアスがよく入る。
-弱光可でも
+  ステート遷移の話は小さくする。バランスするけど、やっぱりそれを超える時もある。だから重要よね。  
+  In the short term, the distribution of excitation energy is adjusted by the dynamic allocation of the light-harvesting antenna complex of PSII (LHCII) to PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].
+  When state transitions are insufficient to counterbalance the uneven distribution of excitation energy,
+
+  As for the plant cultivation under the controled environment, 
+  For this decade, a number of attempts have been made for plant growth with artificial lighting [e.g. ].
+  The impacts of the SPD of the growth light on the plant growth have been intensively investigated [].
+  In these papers, the photosynthetic rates were measured with an identical actinic light source, and subsequently the rates were compared and used for the key factor for the discussion of the plant growth.
+
+  Ideally, the photosynthetic rates should be measured under the in situ conditions.
+  If the SPD of light the leaves receive is predetermined, then measurements should be made under the same light conditions.
+  For instance, commercial transplants are sometimes raised in a closed system with artificial lighting [e.g.
+@Kozai2007POP], and subsequently transferred to a greenhouse and cultivated under sunlight.
+  Therefore, in comparisons of light sources with different SPDs for transplant production, *P*~n~ measurements should be made under sunlight to eliminate the need to consider the interaction.
+
+  If researchers aim to describe the photosynthetic characteristics or the SPD of light the leaves receive is not predetermined, then *P*~n~ should be measured under both PSII- and PSI-light and the interaction evaluated to detect any biases.
+  Such biases can result in spurious estimates of photosynthetic parameters (e.g.
+initial slopes and compensation points of CO~2~ and PFD photosynthetic rate curves) calculated from the measured *P*~n~ values using model-fitting methods [e.g.
+@Sharkey_et_al2007PCE].
+  Biases in quantum yields of photosynthetic oxygen evolution rates were reported in pioneering papers [@Chow_et_al1990PNAS; @Walters_Horton1995aPlanta].
+  When comparing values for such parameters among reports (i.e. in reviews and meta-analyses), particular care should be taken to consider the SPDs of ML.
+
+  群落を対象とする場合でも、同様だ。
+  栽培環境の異なる葉の光合成速度を比較している場合が結構ある。
+  たとえばHigashide さんの話など。
+
+  In this review, we mainly focus on the photosynthetic responses of the leaves to the spectral distribution of light during the measurements.
+  PSII-light PSI-light. FR.
+  In addition, we briefly discuss the potential significance of systemic regulation from a horticultural viewpoint.
+
+# The interaction in the
+
+  交互作用がある話。  
+  When the light use efficiency of the leaves were measured,
+
+  *Pisum sativum* plants were grown under PSII- and PSI-light (PSII- and PSI-leaves, respectively) and the photosynthetic quantum yield of O~2~ evolution was measured under PSII- and PSI-light.
+  When measured under PSII-light, the yield was higher in PSII-leaves; when measured under PSI-light, the yield was higher in PSI-leaves.
+  A similar trend was observed in other studies on *Arabidopsis thaliana* [@Walters_Horton1995aPlanta] and *Cucumis sativus* [@Hogewoning_et_al2012PC; @Murakami_et_al2016PhysiolPlant].
+  @Murakami_et_al2016PhysiolPlant reported that 
+  These studies indicated that comparisons of leaf photosynthetic rates between plants grown under different SPDs of light can be biased depending on the SPD of measuring light (ML), as @Walters2005JXB pointed out.
+  In other words, there must be an interaction between the SPDs of GL and ML in terms of the measured photosynthetic rate.
+  Adjustments in PS stoichiometry and the resulting changes in the distribution of excitation energy in response to the SPD of GL appeared to explain these observations.
+  On the basis of this idea, supplemental far-red (FR) light was expected to trigger the interaction because it drastically decreases the proportion of excitation energy distributed to PSII [@Evans1986PhotoPhoto; @Evans1987FPB; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA], and drastically induces imbalanced excitation.
+
+  In plants, the amounts of photosynthetic electron transport components in leaves change according to the relative spectral photon flux density distribution (SPD) of light during growth [@Chow_et_al1990PCE; @Chow_et_al1990PNAS; Anderson_et_al1995PR; Matsuda_et_al2004PCP; @Matsuda_et_al2007SSPN; @Matsuda_et_al2008PCP].
+  In particular, the stoichiometry between photosystem II and I complexes (PSII and PSI, respectively) responds sensitively to the SPD of growth light (GL) [@Chow_et_al1990PCE; @Chow_et_al1990PNAS; @Smith_et_al1993PCE; @Walters_Horton1994Planta; @Walters_Horton1995bPlanta; @Pfannschmidt_et_al1999Nature; Wagner_et_al2008Planta; Hogewoning_et_al2012PC].
+  Within the chlorophyll (chl) absorption band (approximately 350--750 nm), longer wavelengths of light (> 680-–690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [@Evans1986PhotoPhoto; @Evans1987FPB; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
+  Monochromatic light at shorter wavelengths (< 680--690 nm) is estimated to be preferentially absorbed by PSII (especially in the wavebands near 470 and 650 nm corresponding to the absorption peaks of chl *b*), or evenly absorbed by both PSs [@Evans1986PhotoPhoto; @Evans1987FPB; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
+  Thus, light with a given SPD can be categorized as either PSII or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI, respectively.
+  Because photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) is limited by the slowest step.
+  In this respect, any imbalance in the distribution of excitation energy between the two PSs results in decreased light-use efficiency of photosynthesis [@Pfannschmidt2005JP; @Walters2005JXB; @Hogewoning_et_al2012PC].
+  Moreover, such imbalances can harm leaves by generating reactive oxygen species, which cause oxidative damage to chloroplast components [@Asada1999AnnRev].
+
+  Under PSII-light, the relative amount of the reaction center complex of PSII (RCII) to that of PSI (RCI) (RCII/RCI ratio) in leaves decreases to balance the distribution of excitation energy between the two PSs.
+  Conversely, under PSI-light, the RCII/RCI ratio increases to achieve a balance [@Chow_et_al1990PCE; @Chow_et_al1990PNAS; @Smith_et_al1993PCE; @Walters_Horton1994Planta; @Walters_Horton1995bPlanta; @Pfannschmidt_et_al1999Nature; Wagner_et_al2008Planta; Hogewoning_et_al2012PC].
+  In this study, the terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context.
+  That is, we state which should be more PSII-biased when referring to two (or more) SPDs.
+  In their study on *Pisum sativum*, @Chow_et_al1990PNAS reported that adjustments in PS stoichiometry allowed the plant to maintain a high quantum efficiency of photosynthesis.
+  In that study, pea plants were grown under PSII- and PSI-light (PSII- and PSI-leaves, respectively) and the photosynthetic quantum yield of O~2~ evolution was measured under PSII- and PSI-light.
+  When measured under PSII-light, the yield was higher in PSII-leaves; when measured under PSI-light, the yield was higher in PSI-leaves.
+  A similar trend was observed in other studies on *Arabidopsis thaliana* [@Walters_Horton1995aPlanta] and *Cucumis sativus* [@Hogewoning_et_al2012PC; @Murakami_et_al2016PhysiolPlant].
+  These studies indicated that comparisons of leaf photosynthetic rates between plants grown under different SPDs of light can be biased depending on the SPD of measuring light (ML), as @Walters2005JXB pointed out.
+  In other words, there must be an interaction between the SPDs of GL and ML in terms of the measured photosynthetic rate.
+  Adjustments in PS stoichiometry and the resulting changes in the distribution of excitation energy in response to the SPD of GL appeared to explain these observations.
+  On the basis of this idea, supplemental far-red (FR) light was expected to trigger the interaction because it drastically decreases the proportion of excitation energy distributed to PSII [@Evans1986PhotoPhoto; @Evans1987FPB; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA], and drastically induces imbalanced excitation.
+  However, it has not been experimentally validated whether supplemental FR light during growth --- the simplest and clearest trigger --- induces the interaction between GL and ML that affects the measured photosynthetic rate.
+
+@Walters_Horton1995aPlanta
+
+# The prausible mechanism of the interaction
+
+# The importance and
 

### 2016-07-14 Main.Rmd
流れはできた。

--- 2016-06-26 Main.Rmd
@@
 ---
-title: "EBC2016"
+title: "Evaluating the leaf photosynthetic rates?"
 author: "KeachMurakami"
@@
 
-theme_bw2 <-
-  function(base_size = 12, base_family = "", legend = "none"){
-    theme_bw() %+replace%
-      theme(legend.position = legend,
-            panel.grid.minor = element_blank(),
-            axis.ticks = element_line(colour = "grey50", size = rel(.75)),
-            panel.margin = unit(0, units = "points")
-      )
-    }
-
 options(warn = -1)
 options(warn = 1)
+```
+
+```{r Spectra}
+HID_raw <-
+  fread("~/Dropbox/R/spectrum/HID.csv", skip = 13)
+
+HIDs <-
+  HID_raw %>%
+  setnames(., c("wavelength", paste0("ID", 1:(dim(HID_raw)[2] - 1)))) %>%
+  select(1, HPS = 12, MH = 21)
+
+# MH: M220FCELS-W/BUD; IWASAKI ELECTRIC CO., LTD.
+# HPS: NH220FLS; IWASAKI ELECTRIC CO., LTD.
+
+Absorptances <-
+  fread("~/Dropbox/materials/SpectrumCucumber.csv") %>%
+  filter(Trtm %in% c("W", "WFR", "FL")) %>%
+  mutate(wavelength = as.numeric(wavelength)) %>%
+  filter(variable == "absorption", Trtm == "W")
+
+Sun <-
+  fread("~/Dropbox/materials/Sunlight_JIS.csv") %>%
+  setnames(c("wavelength", "Sun")) %>%
+  left_join(., Absorptances, by = "wavelength") %>%
+  transmute(wavelength, Sun, TransSun = Sun * (100 - ave), Absorptance = ave)
+
+# Sun: JIS C8904-3
+
+# LEDs <-
+
+SPDs <-
+  left_join(HIDs, Sun, by = "wavelength") %>%
+    SPDnorm(from = 350, to = 750, integratedPFD = 100) %>%
+    select(-Absorptance) %>%
+    SPD + theme_bw2() +
+    xlab("Wavelength [nm]") + ylab(u_SPFD("Spectral photon flux density"))
+
+CapSPD <-
+  "Fig. 2 Spectral photon flux density distribution of light . The distributions at a PFD of 100 µmol m<sup>--2</sup> s<sup>--1</sup> within 400--750 nm are shown."
+```
+
+```{r InteractionPict}
+
+X_div <- 100
+X_range <- seq(0, 1, length.out = X_div)
+
+InteractionView <-
+  data_frame(X = rep(X_range, times = 2),
+             ETR = c(dbeta(X_range, 2, 4) * 1.2, dbeta(X_range, 3, 2)),
+             Trtm = rep(c("W", "WFR"), each = X_div)) %>%
+    ggplot(aes(X, ETR, col = Trtm, group = Trtm)) +
+    theme_bw2() +
+    geom_line()
+
+  geom_rect()
+
+  annotate()
+
 ```
@@
 
-------
-
-The photosynthetic rate is one of the most important and widely-used information for the plant sciences.
-ダメージだとか、成長速度だとかを反映する。
-
-なので、正しい値が知りたい。
-
-でも、バイアスがよく入る。
-弱光可でも
+Abbreviations
+ML
+Pg
+Pn
+ETR
+SPD
+PPFD
 
@@
 
+# Introduction
+
+  The photosynthetic rate is one of the most important and commonly reported phenotype for the plant sciences.
+  Considering the importance of the photosynthetic rate, the effects on the rates were measured, evaluated, and compared among the leaves cultivated under different conditions, typically control and treatment.
+  Based on the measured rates, the impacts of the treatments are discussed.
+  Thus, the reliable measurements must be made prior to the evaluation.
+
+  Several studies have reported that the SPD of the ML affected the *P*~n~ of leaves [e.g. @McCree1972AM; @Inada1976PCP; @Hogewoning_et_al2012PC].
+  To eliminate this direct effect, the photosynthetic parameters usually measured under identical SPD conditions in the agricultural and horticultural researches.
+  The most prevailing light source might be blue and red LED light sources.
+
+  However, our recent paper demonstrated that the light source cannot evaluate the instantaneous leaf photosynthetic properties in some cases [@Murakami_et_al2016PhysiolPlant].
+  @Murakami_et_al2016PhysiolPlant compared the photosynthetic rates of leaves grown under white LED light without and with supplemental far-red LED light (W- and WFR-leaves) using blue-red LED light source sunlight-like SPD of light.
+  The photosynthetic rate of W-leaves was greater than that of WFR-leaves under BR LED light (i.e.
+PSII-light), while the rates were comparable between the leaves, or slightly greater in the WFR-leaves, under sunlight (i.e.
+PSI-light).
+  In other words, the SPDs of light incident on the leaf during growth and the measurement interacts on the photosynthetic rates.
+  If the plants were evaluated without considering the interactions, the selection and decision might be distorted.
+  In this short review, we introduce the papers reportign the interaction and the likely causes of it, the light energy distribution between the photosystic electron transport.
+  Subsequently we discuss the practical situations where the interaction should be cared and the recomended measuring methods in the practical measurements of the photosynthetic rates.
+  It is known that the SPD of light affects the instantaneous photosynthetic rate through the other mechanisms, such as the stomatal response [@Shimazaki_et_al2007AnnRev], 光阻害のスペクトル and light penetrating depth within the leaf [@Terashima_et_al2009PCP].
+  These subjects are not referred in this review, *** review articles on these topics are available [@].
+
+# How the interactions are generated
+
+  Light energy absorbed by a leaf drives photosynthetic electron transport.
+  In higher plants, the photosynthetic electron transport chain is anchored by photochemical reactions that occur at two types of photosystems, PSII and PSI.
+  The electron transports are powered by photon energy transferred to the respective photosystems, thus enabling electron transfer against the redox potential (called the Z scheme).
+  Since the electron transport occurs in series, an imbalanced energy distribution between PSII and PSI should lower photosynthetic light use efficiency [e.g. @Hogewoning et al. 2012].
+  These photosystems represent different light absorption spectral distributions.
+  Within the chlorophyll (chl) absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [@Evans1986PhotoPhoto; @Evans1987FPB; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
+  Monochromatic light at shorter wavelengths (< 680--690 nm) is estimated to be preferentially absorbed by PSII (especially in the wavebands near 470 and 650 nm corresponding to the absorption peaks of chl *b*), or evenly absorbed by both PSs [@Evans1986PhotoPhoto; @Evans1987FPB; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
+  Because photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) is limited by the slowest step.
+
+  なので、偏った光を照射したときの電子伝達は、その律速側の光化学系の量が多い葉で高くなる。
+
+  Thus, light with a given SPD can be categorized as either PSII or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI, respectively.
+  In the short term, the distribution of excitation energy is adjusted by the dynamic allocation of the light-harvesting antenna complex of PSII (LHCII) to PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].
+  When state transitions are insufficient to counterbalance the uneven distribution of excitation energy, a long-term acclimation response occurs [@Dietzel_et_al2008FJ].
+Under PSII-light, the relative amount of the reaction center complex of PSII (RCII) to that of PSI (RCI) (RCII/RCI ratio) in leaves decreases to balance the distribution of excitation energy between the two PSs.
+  Conversely, under PSI-light, the RCII/RCI ratio increases to achieve a balance [@Chow_et_al1990PCE; @Chow_et_al1990PNAS; @Smith_et_al1993PCE; @Walters_Horton1994Planta; @Walters_Horton1995bPlanta; @Pfannschmidt_et_al1999Nature; @Wagner_et_al2008Planta; @Hogewoning_et_al2012PC].
+  In this study, the terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context.
+  That is, we state which should be more PSII-biased when referring to two (or more) SPDs.
+  In their study on *Pisum sativum*, @Chow_et_al1990PNAS reported that adjustments in PS stoichiometry allowed the plant to maintain a high quantum efficiency of photosynthesis.
+  In that study, pea plants were grown under **cool-white fluorescent lamps with yellow Plexglas and incandescent bulbs with red Plexglas** (PSII- and PSI-light, respectively) and the photosynthetic quantum yield of O~2~ evolution was measured under PSII- and PSI-light.
+  When measured under PSII-light, the yield was higher in PSII-light-grown leaves; when measured under PSI-light, the yield was higher in PSI-light-grown leaves.
+  A similar trend was observed in other studies on *Arabidopsis thaliana* [@Walters_Horton1995aPlanta] and *Cucumis sativus* [@Hogewoning_et_al2012PC; @Murakami_et_al2016PhysiolPlant] (Table. 1).
+  **@Walters_Horton1995aPlanta used halogen lamp and filters **
+  **@Hogewoning_et_al2012PC used an artificial sunlight [@Hogewoning_et_al2010aJXB] and blue LED light as PSII-light and an artificial shadelight as PSI-light.**
+  **@Murakami_et_al2016PhysiolPlant compared the photosynthetic rates of leaves grown under white LED light without and with supplemental far-red LED light (W- and WFR-leaves) using blue-red LED light source sunlight-like SPD of light.**
+  **The photosynthetic rate of W-leaves was greater than that of WFR-leaves under BR LED light (i.e.
+PSII-light), while the rates were comparable between the leaves, or slightly greater in the WFR-leaves, under sunlight (i.e.
+PSI-light).**
+  These studies indicated that comparisons of leaf photosynthetic rates between plants grown under different SPDs of light can be biased depending on the SPD of measuring light (ML).
+  @Walters2005JXB pointed out.
+
+One further issue, which is of importance not only for studies on acclimation but also more generally in the analysis of photosynthesis, is that actinic lights used for gas exchange or Chl fluorescence analyses are almost always spectrally distinct from sunlight and from lights used in growth chambers.
+This is very likely to result in an im- balance in the excitation of PSI and PSII: In the case of red or blue LEDs, light is preferentially absorbed by PSII so that PSI excitation is limiting for photosynthesis; con- versely, halogen light sources are rich in longer wave- lengths preferentially absorbed by PSI, so that PSII excitation is limiting (Walters et al., 1999).
+As a result of this mismatch between growth and experimental light sources, experimental determinations of photosynthetic efficiency can be appreciably lower than is the case under growth conditions.
+Indeed, whether PSI or PSII excitation is limiting, measurements of Chl fluorescence in situ routinely show PSII to be markedly more oxidized than is the case under experimental lights of similar irradiance (Walters et al., 2004).
+Therefore, while gas exchange and Chl fluorescence analyses are invaluable in making com- parisons between plants so as to monitor changes which result from acclimation, differences in the spectral quality of growth and experimental lights (as is often unavoidable for technical reasons) mean that such measurements do not necessarily reflect the functioning of the photosynthetic apparatus under growth conditions.
+This places limits on the extent to which such studies are useful in understand- ing the consequences of acclimation for photosynthetic function.
+
+# Where and When the interactions should be cared.
+
+  実際に測定してみないことには、どの程度生じているかは不明である。
+  The impacts of the interaction in these systems should be evaluated prior to the **decision**.
+
+  Since only light in the far-red waveband directs the balance to be PSI-biased, we had better to take special care for the interactions when the leaves grown under FR-poor and FR-rich light were comapred.
+
+  For instance, assimilation light provided by the most of the artificial light sources contains little FR (Fig. XXX).
+  Blue or red LEDs and most of fluorescent lamps, white LEDs, metal halide lamps, and high-pressure sodium lamps typical PSII-light.
+  On contrary, as sunlight, いくつかのメタハラ, and offcourse FR LEDs contains much FR (Fig. ), thus lights serves as PSI-light.
+  Therefore, comparing the photosynthetic rates of leaves using the blue and red LED light source might result in relative overestimation in the former group and *vice versa* in the latter group, as demonstrated in our previous report [@Murakami_et_al2016PhysiolPlant].
+
+  As for the plant cultivation under artificial light sources, 
+  For this decade, a number of attempts have been made for plant growth with artificial lighting [e.g. ].
+  The impacts of the SPD of light during growth on the plant **growth** have been intensively investigated [@].
+  In these papers, the photosynthetic rates were measured with an identical actinic light source, and subsequently the rates were compared and used for the key factor for the discussion of the plant growth.
+  When imitating natural environemt (i.e. sunlight), this might be strongly
+
+  The evaluation of the vertical profile of the photosynthetic properties of the leaves among the plant stand may be biased in the same manner.
+  While the leaves in the upper layers were acclimated to sunlight, those in the lower layers were acclimated to the leaf-penetrated light.
+  Due to the higher transmittance in the far-red waveband of a leaf, the leaf-penetrated light contains much FR, namely PSI-light (Fig. 1).
+  Subsequently, the upper and lower leaves can be considered to become PSII- and PSI-leaves.
+  Comparing the photosynthetic rates of these leaves with the blue and red LED light source should cause the interaction and concomittant biases.
+
+  Note that these interaction should be occur in the evaluations of the chlorophyll fluorescence and the photoinhibition.
+  The overexicitation of PSII should result in the lowered PSII photochemical yield, frequently measured as an .
+  In addition that, the photoinhibition experiments might also be affected the interaction.
+  Imbalance in the excitation balance between the photosystems is supposed to acceralate the photoinhibition [@].
+  Therefore, evaluating PSI-leaves under PSII-biased actinic light should underestimate ΦPSII and overestimate the photoinhibition in connection to those in the PSII-leaves.
+
+# How the photosynthetic responses should be measured?
+
+  If researchers aim to describe the photosynthetic characteristics or the SPD of light the leaves receive is not predetermined, then *P*~n~ should be measured under both PSII- and PSI-light and the interaction evaluated to detect any biases.
+  Such biases can result in spurious estimates of photosynthetic parameters (e.g.
+initial slopes and compensation points of CO~2~ and PFD photosynthetic rate curves) calculated from the measured *P*~n~ values using model-fitting methods [e.g.
+@Sharkey_et_al2007PCE].
+  Biases in quantum yields of photosynthetic oxygen evolution rates were reported in pioneering papers [@Chow_et_al1990PNAS; @Walters_Horton1995aPlanta].
+  When comparing values for such parameters among reports (i.e. in reviews and meta-analyses), particular care should be taken to consider the SPDs of ML.
+  If the SPD of light the leaves receive is predetermined, then measurements should be made under the same light conditions.
+  For instance, commercial transplants are sometimes raised in a closed system with artificial lighting [e.g.
+@Kozai2007POP], and subsequently transferred to a greenhouse and cultivated under sunlight.
+  栽培環境が決まっている場合、その光で測定するのが望ましいでしょう。
+  何でもかんでも赤青LED光でやるとPitfall.
+  太陽光光源なんかが役に立つかもね。
+  Therefore, in comparisons of light sources with different SPDs for transplant production, *P*~n~ measurements should be made under sunlight to eliminate the need to consider the interaction.
+  Ideally, the photosynthetic rates should be measured under the in situ conditions.
+  If the SPD of light the leaves receive is predetermined, then measurements should be made under the same light conditions.
+  For instance, commercial transplants are sometimes raised in a closed system with artificial lighting [e.g.
+@Kozai2007POP], and subsequently transferred to a greenhouse and cultivated under sunlight.
+  Therefore, in comparisons of light sources with different SPDs for transplant production, *P*~n~ measurements should be made under sunlight to eliminate the need to consider the interaction.
+
+  The effect of the interaction on the photosytnehtic rate was not prominent compared to those of the other factors such as PPFD, temperature, and CO~2~ concentrations.
+  Therefore, it is not 基本的には、同一の光源で測定することで十分である場合が多い。
+  PFDの影響は明らかにスペクトルの影響よりも大きい。
+  PFDが変動しやすい環境下で測定を行う場合には、光質応答を木にして太陽光下で測定を行うよりは、それを無視してでも人工光で再現性を担保するほうがいいだろう。
+  しかし、栽培光環境が葉の光合成特性に及ぼす影響を評価するような研究であれば、議論は慎重に行うべきである。
+  とくに、栽培時のFR強度が変わる場合には、交互作用の影響が大きく表れやすいと予想される。
+  The effect of the incteraction should be amplified in the comparison be the leaves with different photosystems stoichiometries.
+  Thus, the interaction should be taken special care when the 
+  When the photosynthetic rates of the leaves grown differently were compared, the responses of the rates to both PSII- and PSI-light had better to be measured, compared, and reported in the paper.
+  At least, the light source of ML must be described in the materials and methods section so that readers can follow its SPD.
+
+  Therefore, the *P*~n~ and photosynthetic characteristics of leaves must be discussed in connection with the SPD of ML.
+  The SPD of ML must always be considered when evaluating leaf and whole-plant photosynthesis.
+
+  Apparently, measuring the photosynthetic rates with plural levels of SPDs costs  
+  To omit the evaluation of the multi-levels of the SPDs in the descriptive evaluation of the leaf photosynthesis, the determinant parameters are required to be defined and to be quantified.
+  これらを避けるためには、交絡因子の数値化が必要であろう。
+
+  交互作用の解析をして交互作用が有意な場合、主効果の検討には統計的には意味がない。
+
+```{r FigOutput, fig.cap = CapSPD}
+SPDs
+```
+
 # References

### 2016-07-14 Main.Rmd
書き進め。

@@
 ```{r Spectra}
+
+# set integrate ranges
+PFD_integrate_min <- 350
+PFD_integrate_max <- 750
+
 HID_raw <-
@@
   setnames(., c("wavelength", paste0("ID", 1:(dim(HID_raw)[2] - 1)))) %>%
-  select(1, HPS = 12, MH = 21)
+  select(1, HPS_ = 12, MH_ = 21)
+
+HPS_Ocean_raw <-
+  fread("~/Dropbox/materials/SPD_HPS.txt", skip = 50, nrow = 2000) %>%
+  rename(wavelength = V1, value = V2)
+
+HPS_Ocean_PFD <-
+  smooth.spline(HPS_Ocean_raw$wavelength, HPS_Ocean_raw$value) %>%
+    predict(., seq(PFD_integrate_min, PFD_integrate_max)) %>%
+    .$y %>%
+  sum
+
+HPS_Ocean <-
+  HPS_Ocean_raw %>%
+  mutate(value = value * 100 / HPS_Ocean_PFD, variable = "HPS")
+
+MH_Ocean_raw <-
+  fread("~/Dropbox/materials/SPD_MH.txt", skip = 50, nrow = 2000) %>%
+  rename(wavelength = V1, value = V2)
+
+MH_Ocean_PFD <-
+  smooth.spline(MH_Ocean_raw$wavelength, MH_Ocean_raw$value) %>%
+    predict(., seq(PFD_integrate_min, PFD_integrate_max)) %>%
+    .$y %>%
+  sum
+
+MH_Ocean <-
+  MH_Ocean_raw %>%
+  mutate(value = value * 100 / MH_Ocean_PFD, variable = "MH")
 
@@
 SPDs <-
-  left_join(HIDs, Sun, by = "wavelength") %>%
+  # left_join(HIDs, Sun, by = "wavelength") %>%
+  Sun %>%
   SPDnorm(from = 350, to = 750, integratedPFD = 100) %>%
   select(-Absorptance) %>%
-    SPD + theme_bw2() +
+  gather(variable, value, -wavelength) %>%
+  bind_rows(., HPS_Ocean) %>%
+  bind_rows(., MH_Ocean) %>%
+  filter(between(wavelength, 350, 800)) %>%
+  ggplot(aes(x = wavelength, y = value, group = variable, col = variable)) +
+  theme_bw2(legend = "right") +
+  geom_line() +
   xlab("Wavelength [nm]") + ylab(u_SPFD("Spectral photon flux density"))
@@
 
-  geom_rect()
-
-  annotate()
-
+CapInteract <-
+  "Fig. 2 Spectral photon flux density distribution of light . The distributions at a PFD of 100 µmol m<sup>--2</sup> s<sup>--1</sup> within 400--750 nm are shown."
 ```
@@
 
-  Several studies have reported that the SPD of the ML affected the *P*~n~ of leaves [e.g. @McCree1972AM; @Inada1976PCP; @Hogewoning_et_al2012PC].
+  A number of studies have reported that the SPD of the ML affected the *P*~n~ of leaves [e.g. @McCree1972AM; @Inada1976PCP; @Hogewoning_et_al2012PC].
   To eliminate this direct effect, the photosynthetic parameters usually measured under identical SPD conditions in the agricultural and horticultural researches.
@@
 
-```{r FigOutput, fig.cap = CapSPD}
+```{r FigSPD, fig.cap = CapSPD}
 SPDs
@@
 
+```{r FigInteract, fig.cap = CapInteract}
+InteractionView
+```
 # References

### 2016-07-15 Main.Rmd
書き進め。

@@
   If the plants were evaluated without considering the interactions, the selection and decision might be distorted.
-  In this short review, we introduce the papers reportign the interaction and the likely causes of it, the light energy distribution between the photosystic electron transport.
-  Subsequently we discuss the practical situations where the interaction should be cared and the recomended measuring methods in the practical measurements of the photosynthetic rates.
-  It is known that the SPD of light affects the instantaneous photosynthetic rate through the other mechanisms, such as the stomatal response [@Shimazaki_et_al2007AnnRev], 光阻害のスペクトル and light penetrating depth within the leaf [@Terashima_et_al2009PCP].
-  These subjects are not referred in this review, *** review articles on these topics are available [@].
+
+  In this short review, we introduce the papers reporting the interaction and its likely causes, the light energy distribution between the photosystic electron transport.
+  Subsequently we discuss the practical situations where the interaction should be cared and the recomended measuring methods in the measurements of the photosynthetic rates.
+  It is known that the SPD of light affects the instantaneous photosynthetic rate through the other mechanisms, such as the stomatal response [@Shimazaki_et_al2007AnnRev], photo**inhibition** [@Zavafer_et_al2015JPP] and light penetrating depth within the leaf [@Terashima_et_al2009PCP].
+  Thought these subjects are not referred in this article, the cited review articles on these topics are available.
 
@@
 
-  Light energy absorbed by a leaf drives photosynthetic electron transport.
+  Light energy absorbed by a leaf drives photosynthetic electron transport, and thereby the photosynthetic carbon **fixation**.
   In higher plants, the photosynthetic electron transport chain is anchored by photochemical reactions that occur at two types of photosystems, PSII and PSI.
   The electron transports are powered by photon energy transferred to the respective photosystems, thus enabling electron transfer against the redox potential (called the Z scheme).
-  Since the electron transport occurs in series, an imbalanced energy distribution between PSII and PSI should lower photosynthetic light use efficiency [e.g. @Hogewoning et al. 2012].
-  These photosystems represent different light absorption spectral distributions.
+  Because photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) is limited by the slowest step.
+  Therefore, when the excess energy is distributed to PSII, the energy distribution to PSI limits the ETR and light use efficiency (i.e.
+photochemical quantum yield) of PSII is lowered (Fig.
+1A) and *vice versa* (Fig.
+1B).
+  Note that the balanced distribution should not be 50-50 basis because the rate-limiting photosystem does not always perform the photochemical reaction at a quantum yield of a 100%.
+  Even in a dark adapted helthy leaf, the yield of PSII cannot exceed 0.84 (i.e. chl fluorescence parameter *F*~v~/*F*~m~).
+  Although there is no clear consensus, the maximum yield of PSI seems to be greater than that of PSII.
+  A little bit greater distribution to PSII should be required to make maximum use of the absorbed photons.
+  Gentyに触れるか？
+
+  **AEFに言及**
+
+  **The imbalance between the photosystems ** can be caused by the SPD of light.
+  These photosystems represent different light absorption spectral distributions due to the difference in the compositions of binding pigments, mainly chlorophyll (chl) *a* and *b*.
   Within the chlorophyll (chl) absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [@Evans1986PhotoPhoto; @Evans1987FPB; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
-  Monochromatic light at shorter wavelengths (< 680--690 nm) is estimated to be preferentially absorbed by PSII (especially in the wavebands near 470 and 650 nm corresponding to the absorption peaks of chl *b*), or evenly absorbed by both PSs [@Evans1986PhotoPhoto; @Evans1987FPB; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
-  Because photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) is limited by the slowest step.
-
-  なので、偏った光を照射したときの電子伝達は、その律速側の光化学系の量が多い葉で高くなる。
-
-  Thus, light with a given SPD can be categorized as either PSII or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI, respectively.
-  In the short term, the distribution of excitation energy is adjusted by the dynamic allocation of the light-harvesting antenna complex of PSII (LHCII) to PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].
-  When state transitions are insufficient to counterbalance the uneven distribution of excitation energy, a long-term acclimation response occurs [@Dietzel_et_al2008FJ].
-Under PSII-light, the relative amount of the reaction center complex of PSII (RCII) to that of PSI (RCI) (RCII/RCI ratio) in leaves decreases to balance the distribution of excitation energy between the two PSs.
-  Conversely, under PSI-light, the RCII/RCI ratio increases to achieve a balance [@Chow_et_al1990PCE; @Chow_et_al1990PNAS; @Smith_et_al1993PCE; @Walters_Horton1994Planta; @Walters_Horton1995bPlanta; @Pfannschmidt_et_al1999Nature; @Wagner_et_al2008Planta; @Hogewoning_et_al2012PC].
+  Such an umbalanced distribution was caused by the facts that only chl *a* can absorb light within the longer waveband and that PSI contains a greater amount of chl *a* than PSII.
+  Monochromatic light at shorter wavelengths (< 680--690 nm) is estimated to be preferentially absorbed by PSII (especially in the wavebands near 470 and 650 nm corresponding to the absorption peaks of chl *b*---abundant in PSII), or evenly absorbed by both PSs [@Evans1986PhotoPhoto; @Evans1987FPB; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
+  These wavelength dependency of the distribution balance is a determinant of EED under a given SPD of light.
+  以降はPSIIとPSI-lightを使う。相対的なものだ。
   In this study, the terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context.
   That is, we state which should be more PSII-biased when referring to two (or more) SPDs.
+  Thus, light with a given SPD can be categorized as either PSII or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI, respectively.
+
+  Apparently, the distribution is affected by the stoichiometry of the membrane composition, vulneerable to the SPD of light during the leaf growth [@].
+  **In the short term, the distribution of excitation energy is adjusted by the dynamic allocation of the light-harvesting antenna complex of PSII (LHCII) to PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].**
+  **When state transitions are insufficient to counterbalance the uneven distribution of excitation energy, a long-term acclimation response occurs [@Dietzel_et_al2008FJ].**
+  Under PSII-light, the relative amount of the reaction center complex of PSII to that of PSI in leaves decreases.
+  Conversely, under PSI-light, the relative amount increases to achieve a balance [@Chow_et_al1990PCE; @Chow_et_al1990PNAS; @Smith_et_al1993PCE; @Walters_Horton1994Planta; @Walters_Horton1995bPlanta; @Pfannschmidt_et_al1999Nature; @Wagner_et_al2008Planta; @Hogewoning_et_al2012PC].
+  These reactions are believed to be induced so that balance the *excitation balance*.
+  簡単にいうと、leaves grown under PSII-light tend to distribute the photons to PSI and leaves grown under PSI-light tend to distribute the photons to PSII.
+
+  Expected interactions have been reported in several studies [@].
   In their study on *Pisum sativum*, @Chow_et_al1990PNAS reported that adjustments in PS stoichiometry allowed the plant to maintain a high quantum efficiency of photosynthesis.
-  In that study, pea plants were grown under **cool-white fluorescent lamps with yellow Plexglas and incandescent bulbs with red Plexglas** (PSII- and PSI-light, respectively) and the photosynthetic quantum yield of O~2~ evolution was measured under PSII- and PSI-light.
+  In that study, pea plants were grown under **cool-white fluorescent lamps with yellow Plexglas and incandescent bulbs with red Plexglas** (PSII- and PSI-light, respectively) and the photosynthetic quantum yield of O~2~ evolution---O~2~ evolution rate per absorbed photons by leaf---was measured under PSII- and PSI-light.
   When measured under PSII-light, the yield was higher in PSII-light-grown leaves; when measured under PSI-light, the yield was higher in PSI-light-grown leaves.
@@
 
+弱光下  
+  Under a higher PFDs, the photosynthetic rate is determined by the ETR and the selective PCO and PCC 
+  Ambient condition
+
 # Where and When the interactions should be cared.
 
-  実際に測定してみないことには、どの程度生じているかは不明である。
   The impacts of the interaction in these systems should be evaluated prior to the **decision**.
-
-  Since only light in the far-red waveband directs the balance to be PSI-biased, we had better to take special care for the interactions when the leaves grown under FR-poor and FR-rich light were comapred.
-
-  For instance, assimilation light provided by the most of the artificial light sources contains little FR (Fig. XXX).
-  Blue or red LEDs and most of fluorescent lamps, white LEDs, metal halide lamps, and high-pressure sodium lamps typical PSII-light.
-  On contrary, as sunlight, いくつかのメタハラ, and offcourse FR LEDs contains much FR (Fig. ), thus lights serves as PSI-light.
-  Therefore, comparing the photosynthetic rates of leaves using the blue and red LED light source might result in relative overestimation in the former group and *vice versa* in the latter group, as demonstrated in our previous report [@Murakami_et_al2016PhysiolPlant].
+  Since the PFD in the far-red waveband has strong impact on the **energy distribution**, we had better to take special care for the interactions when the leaves grown under FR-poor and FR-rich light were comapred.
 
@@
   In these papers, the photosynthetic rates were measured with an identical actinic light source, and subsequently the rates were compared and used for the key factor for the discussion of the plant growth.
-  When imitating natural environemt (i.e. sunlight), this might be strongly
+  For instance, assimilation light provided by the most of the artificial light sources contain little FR (Fig. 3).
+  Blue or red LEDs and most of fluorescent lamps, white LEDs, metal halide lamps, and high-pressure sodium lamps typical PSII-light.
+  On contrary, sunlight, いくつかのメタハラ, and offcourse FR LEDs contain much FR (Fig. 3), thus they serve as PSI-light.
+  Therefore, comparing the photosynthetic rates of leaves using the blue and red LED light source might result in relative overestimation in the former group and *vice versa* in the latter group, as demonstrated in our previous report [@Murakami_et_al2016PhysiolPlant].
+
+  模したつもりで模すことができてないな。When imitating natural environemt (i.e. sunlight), this might be strongly
 
@@
   While the leaves in the upper layers were acclimated to sunlight, those in the lower layers were acclimated to the leaf-penetrated light.
-  Due to the higher transmittance in the far-red waveband of a leaf, the leaf-penetrated light contains much FR, namely PSI-light (Fig. 1).
+  Due to the higher transmittance in the far-red waveband of a leaf, the leaf-penetrated light contains much FR, namely PSI-light (Fig. 3).
   Subsequently, the upper and lower leaves can be considered to become PSII- and PSI-leaves.
@@
 
-  If researchers aim to describe the photosynthetic characteristics or the SPD of light the leaves receive is not predetermined, then *P*~n~ should be measured under both PSII- and PSI-light and the interaction evaluated to detect any biases.
-  Such biases can result in spurious estimates of photosynthetic parameters (e.g.
-initial slopes and compensation points of CO~2~ and PFD photosynthetic rate curves) calculated from the measured *P*~n~ values using model-fitting methods [e.g.
-@Sharkey_et_al2007PCE].
-  Biases in quantum yields of photosynthetic oxygen evolution rates were reported in pioneering papers [@Chow_et_al1990PNAS; @Walters_Horton1995aPlanta].
-  When comparing values for such parameters among reports (i.e. in reviews and meta-analyses), particular care should be taken to consider the SPDs of ML.
   If the SPD of light the leaves receive is predetermined, then measurements should be made under the same light conditions.
@@
   Therefore, in comparisons of light sources with different SPDs for transplant production, *P*~n~ measurements should be made under sunlight to eliminate the need to consider the interaction.
+
+  If researchers aim to describe the photosynthetic characteristics or the SPD of light the leaves receive is not predetermined, then *P*~n~ should be measured under both PSII- and PSI-light and the interaction evaluated to detect any biases.
+  Such biases can result in spurious estimates of photosynthetic parameters (e.g.
+initial slopes and compensation points of CO~2~ and PFD photosynthetic rate curves) calculated from the measured *P*~n~ values using model-fitting methods [e.g.
+@Sharkey_et_al2007PCE].
+  When comparing values for such parameters among reports (i.e. in reviews and meta-analyses), particular care should be taken to consider the SPDs of ML.
+
   Ideally, the photosynthetic rates should be measured under the in situ conditions.
-  If the SPD of light the leaves receive is predetermined, then measurements should be made under the same light conditions.
-  For instance, commercial transplants are sometimes raised in a closed system with artificial lighting [e.g.
-@Kozai2007POP], and subsequently transferred to a greenhouse and cultivated under sunlight.
-  Therefore, in comparisons of light sources with different SPDs for transplant production, *P*~n~ measurements should be made under sunlight to eliminate the need to consider the interaction.
-
   The effect of the interaction on the photosytnehtic rate was not prominent compared to those of the other factors such as PPFD, temperature, and CO~2~ concentrations.
@@
   とくに、栽培時のFR強度が変わる場合には、交互作用の影響が大きく表れやすいと予想される。
+  一般性を持たないので、この測定光のもとでは、という但し書きが必要となる。
   The effect of the incteraction should be amplified in the comparison be the leaves with different photosystems stoichiometries.

### 2016-07-16 Main.Rmd
進め。

@@
 
-  The impacts of the interaction in these systems should be evaluated prior to the **decision**.
   Since the PFD in the far-red waveband has strong impact on the **energy distribution**, we had better to take special care for the interactions when the leaves grown under FR-poor and FR-rich light were comapred.
+  The impacts of the interaction on the photosynthetic rates should be concerned when the rates of leaves grown under different PFDs of FR.
 
-  As for the plant cultivation under artificial light sources, 
   For this decade, a number of attempts have been made for plant growth with artificial lighting [e.g. ].
-  The impacts of the SPD of light during growth on the plant **growth** have been intensively investigated [@].
-  In these papers, the photosynthetic rates were measured with an identical actinic light source, and subsequently the rates were compared and used for the key factor for the discussion of the plant growth.
-  For instance, assimilation light provided by the most of the artificial light sources contain little FR (Fig. 3).
+  The impacts of the SPD of light during growth on the plant traits, **such as the growth rate and resultant biomass**, have been intensively investigated [@].
+(Li Kubota, Shibuya, Jishi?
+Matsuda, Inada？なんかあるっけ)
+  In these papers, the photosynthetic rates were measured with an identical actinic light source, and subsequently the rates were compared and discussed as a key factor of the plant growth.
+  Assimilation light provided by the most of the artificial light sources contain little FR (Fig. 3).
   Blue or red LEDs and most of fluorescent lamps, white LEDs, metal halide lamps, and high-pressure sodium lamps typical PSII-light.
-  On contrary, sunlight, いくつかのメタハラ, and offcourse FR LEDs contain much FR (Fig. 3), thus they serve as PSI-light.
+  On contrary, いくつかのメタハラ and sunlight contain much FR (Fig. 3), thus they serve as PSI-light.
+  FR supplemented light also serve as PSI-light.
   Therefore, comparing the photosynthetic rates of leaves using the blue and red LED light source might result in relative overestimation in the former group and *vice versa* in the latter group, as demonstrated in our previous report [@Murakami_et_al2016PhysiolPlant].
-
-  模したつもりで模すことができてないな。When imitating natural environemt (i.e. sunlight), this might be strongly
 
@@
   Comparing the photosynthetic rates of these leaves with the blue and red LED light source should cause the interaction and concomittant biases.
+
+  The results from a chamber experiments, where PSII-light is usually used for the growth light, might not be comparable to the responses under sunlight.
+  We should conduct an experiment under sunlight, not a chamber experiments, when the response under sunlight is the interest of the experiment.
 
@@
 
-  If the SPD of light the leaves receive is predetermined, then measurements should be made under the same light conditions.
+  Ideally, the photosynthetic rates should be measured under the *in situ* conditions.
+  When the plant growth in the subsequent condition are focused, the rates should be measured under the SPD of light the plant will recieve.
   For instance, commercial transplants are sometimes raised in a closed system with artificial lighting [e.g.
 @Kozai2007POP], and subsequently transferred to a greenhouse and cultivated under sunlight.
-  栽培環境が決まっている場合、その光で測定するのが望ましいでしょう。
-  何でもかんでも赤青LED光でやるとPitfall.
-  太陽光光源なんかが役に立つかもね。
-  Therefore, in comparisons of light sources with different SPDs for transplant production, *P*~n~ measurements should be made under sunlight to eliminate the need to consider the interaction.
+  Therefore, in comparisons of light sources with different SPDs for transplant production, *P*~n~ measurements should be made under sunlight.
+  When the difference in the plant growth in the experiments are analyzed, the rates should be measured under the SPD of light the plant recieved.
+  These simple solutions may eliminate the problems caused by the interaction.
+
+  Note that the effect of the interaction on the photosytnehtic rate was not prominent compared to those of the other factors such as PPFD and CO~2~ concentration.
+  Accurate control of the PFD must be set above the regulation of the interaction.
+  Fluctuations in the PFD should be removed by using artificial light sources to ensure the reproductivity and reliability of the research.
 
@@
   When comparing values for such parameters among reports (i.e. in reviews and meta-analyses), particular care should be taken to consider the SPDs of ML.
-
-  Ideally, the photosynthetic rates should be measured under the in situ conditions.
-  The effect of the interaction on the photosytnehtic rate was not prominent compared to those of the other factors such as PPFD, temperature, and CO~2~ concentrations.
-  Therefore, it is not 基本的には、同一の光源で測定することで十分である場合が多い。
-  PFDの影響は明らかにスペクトルの影響よりも大きい。
-  PFDが変動しやすい環境下で測定を行う場合には、光質応答を木にして太陽光下で測定を行うよりは、それを無視してでも人工光で再現性を担保するほうがいいだろう。
   しかし、栽培光環境が葉の光合成特性に及ぼす影響を評価するような研究であれば、議論は慎重に行うべきである。
-  とくに、栽培時のFR強度が変わる場合には、交互作用の影響が大きく表れやすいと予想される。
   一般性を持たないので、この測定光のもとでは、という但し書きが必要となる。
@@
   Apparently, measuring the photosynthetic rates with plural levels of SPDs costs  
+  また太陽光あるいは葉の透過光だったりと複雑な分光分布を再現するのは現実には難しい。
   To omit the evaluation of the multi-levels of the SPDs in the descriptive evaluation of the leaf photosynthesis, the determinant parameters are required to be defined and to be quantified.
@@
   交互作用の解析をして交互作用が有意な場合、主効果の検討には統計的には意味がない。
+
+```{r FigETR, fig.cap = CapSPD}
+ETRs
+```
+
+```{r Fig, fig.cap = CapSPD}
+FigStructure
+```
 

### 2016-07-17 Main.Rmd
書き進め。Fig.1 (分配の模式図) を作成。

@@
 
-HID_raw <-
-  fread("~/Dropbox/R/spectrum/HID.csv", skip = 13)
+# HID_raw <-
+#   fread("~/Dropbox/R/spectrum/HID.csv", skip = 13)
+# 
+# HIDs <-
+#   HID_raw %>%
+#   setnames(., c("wavelength", paste0("ID", 1:(dim(HID_raw)[2] - 1)))) %>%
+#   select(1, HPS_ = 12, MH_ = 21)
+FL_Ocean_raw <-
+  fread("~/Dropbox/materials/SPD_FL.csv") %>%
+  transmute(wavelength = `Wavelength[nm]`, value = FL) %>%
+  na.omit
 
-HIDs <-
-  HID_raw %>%
-  setnames(., c("wavelength", paste0("ID", 1:(dim(HID_raw)[2] - 1)))) %>%
-  select(1, HPS_ = 12, MH_ = 21)
+FL_Ocean_PFD <-
+  smooth.spline(FL_Ocean_raw$wavelength, FL_Ocean_raw$value) %>%
+    predict(., seq(PFD_integrate_min, PFD_integrate_max)) %>%
+    .$y %>%
+  sum
+
+FL_Ocean <-
+  FL_Ocean_raw %>%
+  mutate(value = value * 100 / FL_Ocean_PFD, variable = "FL")
 
@@
   gather(variable, value, -wavelength) %>%
+  bind_rows(., FL_Ocean) %>%
   bind_rows(., HPS_Ocean) %>%
@@
 
-Abbreviations
-ML
-Pg
-Pn
-ETR
-SPD
-PPFD
+**Abbreviations**
+ETR: 
+ML: measuring light
+Pn: 
+PPFD: photosynthetic photon flux density
+SPD: spectral PFD distribution
 
@@
 
-  The photosynthetic rate is one of the most important and commonly reported phenotype for the plant sciences.
+  The net photosynthetic rate is one of the most important and commonly reported phenotype for the plant sciences.
   Considering the importance of the photosynthetic rate, the effects on the rates were measured, evaluated, and compared among the leaves cultivated under different conditions, typically control and treatment.
@@
 
-  Light energy absorbed by a leaf drives photosynthetic electron transport, and thereby the photosynthetic carbon **fixation**.
+  The knowledge about the photosynthetic electron transport is required to understand the mechanism of the interaction.
+  Light energy absorbed by a leaf drives the electron transport, and thereby the photosynthetic O~2~ evolution and CO~2~ uptake.
   In higher plants, the photosynthetic electron transport chain is anchored by photochemical reactions that occur at two types of photosystems, PSII and PSI.
   The electron transports are powered by photon energy transferred to the respective photosystems, thus enabling electron transfer against the redox potential (called the Z scheme).
-  Because photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) is limited by the slowest step.
-  Therefore, when the excess energy is distributed to PSII, the energy distribution to PSI limits the ETR and light use efficiency (i.e.
-photochemical quantum yield) of PSII is lowered (Fig.
-1A) and *vice versa* (Fig.
-1B).
+  Because photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) is limited by the slowest step (Fig. 1).
+  When the excess energy is distributed to PSII under the imbalanced energy distribution, the energy distribution to PSI limits the ETR and the photochemical quantum yield of PSII is lowered (Fig.
+1A).
+  When the excess energy is distributed to PSI, the energy distribution to PSII limits the ETR and the yield of PSI is lowered (Fig. 1D).
+  In both cases, a part of absorbed photons is dissipated as heat and fluorescence, and thus the entire photosynthetic quantum yield---the bulk ETR per absorbed photon---becomes smaller.
+
   Note that the balanced distribution should not be 50-50 basis because the rate-limiting photosystem does not always perform the photochemical reaction at a quantum yield of a 100%.
@@
   Gentyに触れるか？
-
   **AEFに言及**
@@
   **The imbalance between the photosystems ** can be caused by the SPD of light.
-  These photosystems represent different light absorption spectral distributions due to the difference in the compositions of binding pigments, mainly chlorophyll (chl) *a* and *b*.
+
+  PSII and PSI represent different light absorption spectral distributions due to the difference in the compositions of binding pigments, mainly chlorophyll (chl) *a* and *b*.
   Within the chlorophyll (chl) absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [@Evans1986PhotoPhoto; @Evans1987FPB; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
@@
   These wavelength dependency of the distribution balance is a determinant of EED under a given SPD of light.
-  以降はPSIIとPSI-lightを使う。相対的なものだ。
-  In this study, the terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context.
-  That is, we state which should be more PSII-biased when referring to two (or more) SPDs.
-  Thus, light with a given SPD can be categorized as either PSII or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI, respectively.
+  この分野の研究では, light with a given SPD is categorized as either PSII or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI, respectively.
+  この判断はおおむね主観で決められている。FRが増えればPSI-light。
 
-  Apparently, the distribution is affected by the stoichiometry of the membrane composition, vulneerable to the SPD of light during the leaf growth [@].
+  Apparently, the distribution is affected by the stoichiometry of the membrane composition, vulnerable to the SPD of light during the leaf growth [@].
   **In the short term, the distribution of excitation energy is adjusted by the dynamic allocation of the light-harvesting antenna complex of PSII (LHCII) to PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].**
@@
   These reactions are believed to be induced so that balance the *excitation balance*.
+
+  The terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context.
+  For instance, a SPD of light, which is in good balance for PSII-leaves, can overexcite PSII in PSI-leaves (Fig. 1AB).
+
   簡単にいうと、leaves grown under PSII-light tend to distribute the photons to PSI and leaves grown under PSI-light tend to distribute the photons to PSII. 
-
   Expected interactions have been reported in several studies [@].
@@
 
-  Apparently, measuring the photosynthetic rates with plural levels of SPDs costs  
+  Apparently, measuring the photosynthetic rates under multilevels of SPDs costs much more time, resource, and labor.
   また太陽光あるいは葉の透過光だったりと複雑な分光分布を再現するのは現実には難しい。
@@
 
-```{r FigETR, fig.cap = CapSPD}
-ETRs
-```
+![FigETR](FigETR.png)
 
-```{r Fig, fig.cap = CapSPD}
+```{r Fig, eval = F, fig.cap = CapSPD}
 FigStructure
@@
 
-```{r FigInteract, fig.cap = CapInteract}
+```{r FigInteract, fifig.cap = CapInteract}
 InteractionView

### 2016-07-18 Main.Rmd
書き進め 2645 words

@@
   The electron transports are powered by photon energy transferred to the respective photosystems, thus enabling electron transfer against the redox potential (called the Z scheme).
-  Because photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) is limited by the slowest step (Fig. 1).
-  When the excess energy is distributed to PSII under the imbalanced energy distribution, the energy distribution to PSI limits the ETR and the photochemical quantum yield of PSII is lowered (Fig.
-1A).
-  When the excess energy is distributed to PSI, the energy distribution to PSII limits the ETR and the yield of PSI is lowered (Fig. 1D).
-  In both cases, a part of absorbed photons is dissipated as heat and fluorescence, and thus the entire photosynthetic quantum yield---the bulk ETR per absorbed photon---becomes smaller.
+  Because photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) through the thylakoid membrane is limited by the slowest step (Fig. 1).
+  When PSII absorbs excess energy **under the imbalanced energy distribution**, the energy distribution to PSI limits the ETR and thus the photochemical quantum yield of PSII is lowered (Fig. 1A).
+  When PSI absorbs excess energy, the energy distribution to PSII limits the ETR and the yield of PSI is lowered (Fig. 1D).
+  In both cases, the excesss energy is dissipated as heat and fluorescence (ROS生成とダメージの話をするか...), and thus the entire photosynthetic quantum yield---the ETR per absorbed photon---becomes smaller.
+  Balancing the excitation energy distribution between PSII and PSI is essential for plants to keep the high photosynthetic quantum yield.
 
-  Note that the balanced distribution should not be 50-50 basis because the rate-limiting photosystem does not always perform the photochemical reaction at a quantum yield of a 100%.
+  **おまけ部分**
+  Note that the balanced distribution might not be a fifty-fifty.
   Even in a dark adapted helthy leaf, the yield of PSII cannot exceed 0.84 (i.e. chl fluorescence parameter *F*~v~/*F*~m~).
   Although there is no clear consensus, the maximum yield of PSI seems to be greater than that of PSII.
-  A little bit greater distribution to PSII should be required to make maximum use of the absorbed photons.
-  Gentyに触れるか？
-  **AEFに言及**
+  Therefore, under the fifty-fifty distribution, the energy supply to PSII is insufficient and that to PSI is excessive.
+  A little bit greater distribution to PSII might be required to make maximum use of the absorbed photons.
+  Gentyに触れるか？AEF
 
-  **The imbalance between the photosystems ** can be caused by the SPD of light.
-
+  The imbalance in the energy distribution between the photosystems is supposed to occur ordinarily (どこで？太陽光？).
   PSII and PSI represent different light absorption spectral distributions due to the difference in the compositions of binding pigments, mainly chlorophyll (chl) *a* and *b*.
@@
   These wavelength dependency of the distribution balance is a determinant of EED under a given SPD of light.
-  この分野の研究では, light with a given SPD is categorized as either PSII or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI, respectively.
-  この判断はおおむね主観で決められている。FRが増えればPSI-light。
+  In several studies of light acclimation of the photosynthetic apparatus, light with a given SPD is categorized as either PSII or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI, respectively.
+  A given SPD of light is classified into either PSII- or PSI-light according to the PFD in the far-red waveband in the relative context.
+  The terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context.
+  For instance, a SPD of light, which is in good balance for PSII-leaves, can overexcite PSII in PSI-leaves (Fig. 1AB).
 
-  Apparently, the distribution is affected by the stoichiometry of the membrane composition, vulnerable to the SPD of light during the leaf growth [@].
+  Apparently, the distribution is affected by the composition of the thylakoid membrane, especially by the stoichiometry between PSII and PSI.
+  The stoichiometry is adjusted to the SPD of light during leaf growth [e.g. @Matsuda_et_al2004PCP;].
   **In the short term, the distribution of excitation energy is adjusted by the dynamic allocation of the light-harvesting antenna complex of PSII (LHCII) to PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].**
@@
   Conversely, under PSI-light, the relative amount increases to achieve a balance [@Chow_et_al1990PCE; @Chow_et_al1990PNAS; @Smith_et_al1993PCE; @Walters_Horton1994Planta; @Walters_Horton1995bPlanta; @Pfannschmidt_et_al1999Nature; @Wagner_et_al2008Planta; @Hogewoning_et_al2012PC].
-  These reactions are believed to be induced so that balance the *excitation balance*.
+  The change in the composition within the respective photosystems might also be involved in the SPD acclimation [@, @Murakami_et_al2016PhysiolPlant].
+  These reactions are believed to be induced so that balance the *excitation balance* and thereafter perform efficient photosynthesis under the growth environments.
+  These adjustments improve photosynthetic light use efficiency under the light during growth.
 
-  The terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context.
-  For instance, a SPD of light, which is in good balance for PSII-leaves, can overexcite PSII in PSI-leaves (Fig. 1AB).
-
-  簡単にいうと、leaves grown under PSII-light tend to distribute the photons to PSI and leaves grown under PSI-light tend to distribute the photons to PSII. 
+  光に対する順化、あとは光自体の偏って吸収されやすさのふたつの要因から、栽培光・測定光のSPDが葉の光合成速度に及ぼす影響には交互作用が生じることが期待される。
   Expected interactions have been reported in several studies [@].
-  In their study on *Pisum sativum*, @Chow_et_al1990PNAS reported that adjustments in PS stoichiometry allowed the plant to maintain a high quantum efficiency of photosynthesis.
-  In that study, pea plants were grown under **cool-white fluorescent lamps with yellow Plexglas and incandescent bulbs with red Plexglas** (PSII- and PSI-light, respectively) and the photosynthetic quantum yield of O~2~ evolution---O~2~ evolution rate per absorbed photons by leaf---was measured under PSII- and PSI-light.
-  When measured under PSII-light, the yield was higher in PSII-light-grown leaves; when measured under PSI-light, the yield was higher in PSI-light-grown leaves.
+  In their pioneering study on *Pisum sativum*, @Chow_et_al1990PNAS grew plants under **cool-white fluorescent lamps with yellow Plexglas** (PSII-light) and **incandescent bulbs with red Plexglas** (PSI-light) and measured the photosynthetic quantum yield of O~2~ evolution---O~2~ evolution rate per absorbed photons by leaf---under PSII- and PSI-light.
+  When measured under PSII-light, the yield was higher in PSII-light-grown leaves:
+  When measured under PSI-light, the yield was higher in PSI-light-grown leaves.
   A similar trend was observed in other studies on *Arabidopsis thaliana* [@Walters_Horton1995aPlanta] and *Cucumis sativus* [@Hogewoning_et_al2012PC; @Murakami_et_al2016PhysiolPlant] (Table. 1).
@@
   These studies indicated that comparisons of leaf photosynthetic rates between plants grown under different SPDs of light can be biased depending on the SPD of measuring light (ML).
-  @Walters2005JXB pointed out.
-
-  One further issue, which is of importance not only for studies on acclimation but also more generally in the analysis of photosynthesis, is that actinic lights used for gas exchange or Chl fluorescence analyses are almost always spectrally distinct from sunlight and from lights used in growth chambers.
-This is very likely to result in an im- balance in the excitation of PSI and PSII: In the case of red or blue LEDs, light is preferentially absorbed by PSII so that PSI excitation is limiting for photosynthesis; con- versely, halogen light sources are rich in longer wave- lengths preferentially absorbed by PSI, so that PSII excitation is limiting (Walters et al., 1999).
-As a result of this mismatch between growth and experimental light sources, experimental determinations of photosynthetic efficiency can be appreciably lower than is the case under growth conditions.
-Indeed, whether PSI or PSII excitation is limiting, measurements of Chl fluorescence in situ routinely show PSII to be markedly more oxidized than is the case under experimental lights of similar irradiance (Walters et al., 2004).
-Therefore, while gas exchange and Chl fluorescence analyses are invaluable in making com- parisons between plants so as to monitor changes which result from acclimation, differences in the spectral quality of growth and experimental lights (as is often unavoidable for technical reasons) mean that such measurements do not necessarily reflect the functioning of the photosynthetic apparatus under growth conditions.
-This places limits on the extent to which such studies are useful in understand- ing the consequences of acclimation for photosynthetic function.
-
-弱光下  
-  Under a higher PFDs, the photosynthetic rate is determined by the ETR and the selective PCO and PCC 
-  Ambient condition
+  The measurements, comparisons, and evaluations of leaves with an identical SPD of ML do not necessarily reflect the differnece in the functioning of the leaf photosynthesis under a given conditions, as as pointed out in @Walters2005JXB.
 
@@
 
-  Since the PFD in the far-red waveband has strong impact on the **energy distribution**, we had better to take special care for the interactions when the leaves grown under FR-poor and FR-rich light were comapred.
-  The impacts of the interaction on the photosynthetic rates should be concerned when the rates of leaves grown under different PFDs of FR.
+  The mechanisms of the SPD acclimation of **energy distribution** are not yet fully elucidated.
+  @Walter_Horton1995aPlanta confirmed the strong adjustment in the photosystem stoichiometry in response to the slight changes in the SPD of growth light.
+  Therefore, we had better pay attention it whenever measure the *P*~n~ and related parameters.
+  Since the PFD in the far-red waveband has strong impact on the **energy distribution**, the diference in the FR PFD during growth is the most likely trigger for the acclimation.
+  Therefore, the impacts of the interaction on the photosynthetic rates should be concerned when the rates of leaves grown under different PFDs of FR.
 
-  For this decade, a number of attempts have been made for plant growth with artificial lighting [e.g. ].
-  The impacts of the SPD of light during growth on the plant traits, **such as the growth rate and resultant biomass**, have been intensively investigated [@].
-(Li Kubota, Shibuya, Jishi?
-Matsuda, Inada？なんかあるっけ)
-  In these papers, the photosynthetic rates were measured with an identical actinic light source, and subsequently the rates were compared and discussed as a key factor of the plant growth.
   Assimilation light provided by the most of the artificial light sources contain little FR (Fig. 3).
-  Blue or red LEDs and most of fluorescent lamps, white LEDs, metal halide lamps, and high-pressure sodium lamps typical PSII-light.
-  On contrary, いくつかのメタハラ and sunlight contain much FR (Fig. 3), thus they serve as PSI-light.
-  FR supplemented light also serve as PSI-light.
-  Therefore, comparing the photosynthetic rates of leaves using the blue and red LED light source might result in relative overestimation in the former group and *vice versa* in the latter group, as demonstrated in our previous report [@Murakami_et_al2016PhysiolPlant].
+  Blue or red LEDs and most of fluorescent lamps, white LEDs, metal halide lamps, and high-pressure sodium lamps emit typical PSII-light.
+  On contrary, sunlight incident on and penetrated through a leaf contain much FR (Fig. 3), thus they serve as PSI-light.
+  Supplemental use of FR LED light with some light sources convert the mixed light into PSI-light.
+
+  For this decade, a number of attempts have been made for plant growth with artificial lighting [e.g.].
+  The impacts of the SPD of light during growth on the plant traits, **such as the growth rate and resultant biomass**, have been intensively investigated [e.g.
+@Matsuda_et_al2004PCP; @Li_Kubota2009EEB; @hogewoning_et_al2010; @Shibuya_et_al20XX].
+  Comparing the photosynthetic rates of leaves using the blue and red LED light source might result in relative overestimation in PSII-light-grown leaves and underestimate in PSI-light-grown leaves, as demonstrated in our previous report [@Murakami_et_al2016PhysiolPlant].
+  The results from the experiments under artificial light sources, where PSII-light is usually used for the growth light, might not reflect the responses under sunlight [@Walter2005JXB].
+  When the response under sunlight is the interest of the experiment, we should conduct an experiment under sunlight.
 
@@
 
-  The results from a chamber experiments, where PSII-light is usually used for the growth light, might not be comparable to the responses under sunlight.
-  We should conduct an experiment under sunlight, not a chamber experiments, when the response under sunlight is the interest of the experiment.
-
   Note that these interaction should be occur in the evaluations of the chlorophyll fluorescence and the photoinhibition.
@@
   Therefore, evaluating PSI-leaves under PSII-biased actinic light should underestimate ΦPSII and overestimate the photoinhibition in connection to those in the PSII-leaves.
+
+  This interaction **has** considerable impact on the *P*~n~ especially under the light limited and/or CO~2~ sturated conditions, where the **大きさ** of the ETR is dominant factor for the photosynthetic CO~2~ fixation [@von].
+  In such conditions, the biases in the ETR directly affect the *P*~n~.
+  The photosynthetic yields and the *P*~n~ at light-limited conditions should be measured with particular attentions on the interaction.
+
+  In contrast, under a higher PFDs and/or CO~2~ limtied conditions, the rate is determined by the **Rubisco activity** rather than the ETR.
+  In such conditions, the effects of the biases in the ETR on *P*~n~ may be demagnified.
+  <!-- In our experiment, however, the interaction was observed under a high PFD (1200 µmol m^--2^ s^--1^) and a low CO~2~ concentration condition (20 Pa in the intercellular space), suggesting the other  -->
 
@@
 
-  Therefore, the *P*~n~ and photosynthetic characteristics of leaves must be discussed in connection with the SPD of ML.
-  The SPD of ML must always be considered when evaluating leaf and whole-plant photosynthesis.
+# Concluding remarks amd future works
 
+  The *P*~n~ and photosynthetic characteristics of leaves must be discussed in connection with the SPD of ML.
+  Evaluation of the photosynthesis should be made under the in situ conditions or multilevels of SPDs of ML so that the evaluation is not biased by the interaction.
   Apparently, measuring the photosynthetic rates under multilevels of SPDs costs much more time, resource, and labor.
-  また太陽光あるいは葉の透過光だったりと複雑な分光分布を再現するのは現実には難しい。
-  To omit the evaluation of the multi-levels of the SPDs in the descriptive evaluation of the leaf photosynthesis, the determinant parameters are required to be defined and to be quantified.
-  これらを避けるためには、交絡因子の数値化が必要であろう。
+  In addition that, imitating the various SPDs of light incident on the leaf for *in situ* evaluation of photosythesis might be difficult or impossible from the technical reasons.
+  To solve these problems, the determinant parameters in the SPD-dependence of the photosynthetic ETR should be defined.
+  To omit the evaluation of the multi-levels of the SPDs in the descriptive evaluation of the leaf photosynthesis,
 
@@
 ```
+
 # References

### 2016-07-19 Main.Rmd
家作業分 2672 words

@@
 
-  The net photosynthetic rate is one of the most important and commonly reported phenotype for the plant sciences.
-  Considering the importance of the photosynthetic rate, the effects on the rates were measured, evaluated, and compared among the leaves cultivated under different conditions, typically control and treatment.
+  The net photosynthetic rate (*P*~n~) is one of the most important and commonly reported phenotype in the plant sciences.
+  Considering the importance of the photosynthetic rate, the effects on the rates were measured, evaluated, and compared among the leaves cultivated under different conditions, typically the control and treatment.
   Based on the measured rates, the impacts of the treatments are discussed.
@@
   A number of studies have reported that the SPD of the ML affected the *P*~n~ of leaves [e.g. @McCree1972AM; @Inada1976PCP; @Hogewoning_et_al2012PC].
-  To eliminate this direct effect, the photosynthetic parameters usually measured under identical SPD conditions in the agricultural and horticultural researches.
-  The most prevailing light source might be blue and red LED light sources.
+  To eliminate this direct effect from the comparison, the photosynthetic rates are measured under identical SPD conditions in the agricultural and horticultural researches.
+  The most prevailing light source might be the commercial blue+red LED light source.
 
@@
   When the difference in the plant growth in the experiments are analyzed, the rates should be measured under the SPD of light the plant recieved.
+  For instance, when the difference in the resultant growth between the treatments are analyzed and the *P*~n~ is used for the explanatory factor, respective growth light must be used for ML.
   These simple solutions may eliminate the problems caused by the interaction.
 
-  Note that the effect of the interaction on the photosytnehtic rate was not prominent compared to those of the other factors such as PPFD and CO~2~ concentration.
+  Note that the effect of the interaction on the photosytnehtic rate is not prominent compared to those of the other factors such as PPFD and CO~2~ concentration.
   Accurate control of the PFD must be set above the regulation of the interaction.
   Fluctuations in the PFD should be removed by using artificial light sources to ensure the reproductivity and reliability of the research.
+  To solve the dilenma between the *in situ* evaluation and PFD stability, the artificial sunlight source might be helpful.
 
   If researchers aim to describe the photosynthetic characteristics or the SPD of light the leaves receive is not predetermined, then *P*~n~ should be measured under both PSII- and PSI-light and the interaction evaluated to detect any biases.
-  Such biases can result in spurious estimates of photosynthetic parameters (e.g.
-initial slopes and compensation points of CO~2~ and PFD photosynthetic rate curves) calculated from the measured *P*~n~ values using model-fitting methods [e.g.
-@Sharkey_et_al2007PCE].
-  When comparing values for such parameters among reports (i.e. in reviews and meta-analyses), particular care should be taken to consider the SPDs of ML.
-  しかし、栽培光環境が葉の光合成特性に及ぼす影響を評価するような研究であれば、議論は慎重に行うべきである。
-  一般性を持たないので、この測定光のもとでは、という但し書きが必要となる。
   The effect of the incteraction should be amplified in the comparison be the leaves with different photosystems stoichiometries.
-  Thus, the interaction should be taken special care when the 
-  When the photosynthetic rates of the leaves grown differently were compared, the responses of the rates to both PSII- and PSI-light had better to be measured, compared, and reported in the paper.
-  At least, the light source of ML must be described in the materials and methods section so that readers can follow its SPD.
+  Thus, the interaction should be taken special care when the cases described in the **former section**.
+  If the significant interaction is not detected in two-way ANOVA, the main effect of the treatment can be assessed.
+  If any the interaction, the results should not be generalized.
+  The responses of the rates to both PSII- and PSI-light had better to be measured, compared, and reported in the paper.
+  A multilevel measurement might be difficult or impossible for technical reasons.
+  In such case, the light source of ML must be declared in the materials and methods section so that readers can follow its SPD.
 
@@
   To omit the evaluation of the multi-levels of the SPDs in the descriptive evaluation of the leaf photosynthesis,
-
-  交互作用の解析をして交互作用が有意な場合、主効果の検討には統計的には意味がない。
 

### 2016-07-19 Main.Rmd
2809 words

@@
 title: "Evaluating the leaf photosynthetic rates?"
-author: "KeachMurakami"
+author: "Keach Murakami, Ryo Matsuda, Kazuhiro Fujiwara"
 date: "June 24, 2016"
@@
 
+IntegratePFD <- 100
+
 # HID_raw <-
@@
   FL_Ocean_raw %>%
-  mutate(value = value * 100 / FL_Ocean_PFD, variable = "FL")
+  mutate(value = value * 100 / FL_Ocean_PFD, variable = "Fluorescent lamp")
 
@@
   HPS_Ocean_raw %>%
-  mutate(value = value * 100 / HPS_Ocean_PFD, variable = "HPS")
+  mutate(value = value * 100 / HPS_Ocean_PFD, variable = "High-pressure sodium lamp")
 
@@
   MH_Ocean_raw %>%
-  mutate(value = value * 100 / MH_Ocean_PFD, variable = "MH")
+  mutate(value = value * 100 / MH_Ocean_PFD, variable = "Metal-halide lamp")
 
+OceanSPDs <-
+  bind_rows(FL_Ocean, HPS_Ocean, MH_Ocean) %>%
+  mutate(panel = "HID, fluorescent lamp")
+
+# FL: FPL55EX-N; IWASAKI ELECTRIC CO., LTD.
 # MH: M220FCELS-W/BUD; IWASAKI ELECTRIC CO., LTD.
@@
   fread("~/Dropbox/materials/Sunlight_JIS.csv") %>%
-  setnames(c("wavelength", "Sun")) %>%
+  setnames(c("wavelength", "Sunlight")) %>%
   left_join(., Absorptances, by = "wavelength") %>%
-  transmute(wavelength, Sun, TransSun = Sun * (100 - ave), Absorptance = ave)
+  transmute(wavelength, Sunlight, `Shaded sunlight` = Sunlight * (100 - ave), Absorptance = ave)
 
@@
 
-# LEDs <-
+LEDs <-
+  fread("~/Dropbox/materials/SPD_FL.csv") %>%
+  transmute(wavelength = `Wavelength[nm]`, W, FR, B = B_HL, R = R_SR) %>%
+  SPDnorm(from = 350, to = 750, integratedPFD = IntegratePFD) %>%
+  gather(variable, value, -wavelength) %>%
+  mutate(panel = "LED") %>%
+  na.omit
 
@@
   Sun %>%
-  SPDnorm(from = 350, to = 750, integratedPFD = 100) %>%
+  SPDnorm(from = 350, to = 750, integratedPFD = IntegratePFD) %>%
   select(-Absorptance) %>%
   gather(variable, value, -wavelength) %>%
-  bind_rows(., FL_Ocean) %>%
-  bind_rows(., HPS_Ocean) %>%
-  bind_rows(., MH_Ocean) %>%
-  filter(between(wavelength, 350, 800)) %>%
+  mutate(panel = "Natural light") %>%
+  bind_rows(., OceanSPDs, LEDs) %>%
+  filter(between(wavelength, 380, 800)) %>%
   ggplot(aes(x = wavelength, y = value, group = variable, col = variable)) +
-  theme_bw2(legend = "right") +
+  theme_bw2(legend = c(.75, .25)) +
+  geom_rect(aes(xmin = 700, xmax = 750, ymin = 0, ymax = +Inf), fill = "grey80", col = NA) +
   geom_line() +
+  facet_wrap( ~ panel, ncol = 2) +
+  gg_xy(c(380, 800, 0, 4)) +
   xlab("Wavelength [nm]") + ylab(u_SPFD("Spectral photon flux density"))
@@
 CapSPD <-
-  "Fig. 2 Spectral photon flux density distribution of light . The distributions at a PFD of 100 µmol m<sup>--2</sup> s<sup>--1</sup> within 400--750 nm are shown."
+  "Fig. 2 Spectral photon flux density distribution of light. The distributions at a PFD of 100 µmol m<sup>--2</sup> s<sup>--1</sup> within 400--750 nm are shown."
 ```
@@
   data_frame(X = rep(X_range, times = 2),
-           ETR = c(dbeta(X_range, 2, 4) * 1.2, dbeta(X_range, 3, 2)),
+           ETR = c(dbeta(X_range, 3, 4.5) * 1.2, dbeta(X_range, 4.5, 3)),
            Trtm = rep(c("W", "WFR"), each = X_div)) %>%
-  ggplot(aes(X, ETR, col = Trtm, group = Trtm)) +
-  theme_bw2() +
-  geom_line()
+  ggplot(aes(X, ETR, linetype = Trtm, group = Trtm)) +
+  theme_bw2(legend = c(.5, .3)) +
+  geom_line() +
+  scale_linetype_manual(values = c(1, 2)) +
+  xlab("The fraction of energy distributed to PSI") +
+  ylab("Relative electron transport rate")
 
@@
 **Abbreviations**
-ETR: 
-ML: measuring light
-Pn: 
+Chl: chlorophyll
+ETR: Electron transport rate
+FR: far-red
+LED: light-emitting diode
+*P*~n~: Net photosynthetic rate
 PPFD: photosynthetic photon flux density
+PSI: photosystem II
+PSII: photosystem I
 SPD: spectral PFD distribution
@@
 
-  A number of studies have reported that the SPD of the ML affected the *P*~n~ of leaves [e.g. @McCree1972AM; @Inada1976PCP; @Hogewoning_et_al2012PC].
-  To eliminate this direct effect from the comparison, the photosynthetic rates are measured under identical SPD conditions in the agricultural and horticultural researches.
-  The most prevailing light source might be the commercial blue+red LED light source.
+  A number of studies have reported that the SPD of light used for the measurement (i.e.
+measuring light or actinic light) affected the *P*~n~ of leaves [e.g.
+@McCree1972AM; @Inada1976PCP; @Hogewoning_et_al2012PC].
+  In the agricultural and horticultural researches, the photosynthetic rates are usually measured under an identical SPD of measuring light irrespective of leaf growth conditions to eliminate the direct effect of the SPD of measuring light from the comparison.
+  The most widely-used measuring light might be mixture of blue and red LED light provided by light sources installed in commercial photosynthesis analyzing systems.
 
   However, our recent paper demonstrated that the light source cannot evaluate the instantaneous leaf photosynthetic properties in some cases [@Murakami_et_al2016PhysiolPlant].
-  @Murakami_et_al2016PhysiolPlant compared the photosynthetic rates of leaves grown under white LED light without and with supplemental far-red LED light (W- and WFR-leaves) using blue-red LED light source sunlight-like SPD of light.
-  The photosynthetic rate of W-leaves was greater than that of WFR-leaves under BR LED light (i.e.
-PSII-light), while the rates were comparable between the leaves, or slightly greater in the WFR-leaves, under sunlight (i.e.
-PSI-light).
-  In other words, the SPDs of light incident on the leaf during growth and the measurement interacts on the photosynthetic rates.
+  @Murakami_et_al2016PhysiolPlant compared *P*~n~ of leaves grown under white LED light without (W) and with (WFR) supplemental far-red (FR) LED light under blue + red LED light and a sunlight-like SPD of light.
+  The *P*~n~ of W-leaves was greater than that of WFR-leaves under blue + red LED light, while the rates were comparable---or slightly greater in the WFR-leaves---under artificial sunlight.
+  In other words, the SPDs of light incident on the leaf during growth and measurement interacted on the *P*~n~ (唐突感ある).
+  Based on the results obtained from the measurement under blue + red LED light, WFR-leaves are evaluated to be less lively and low quality, despite the comparable potential under the sunlight.
   If the plants were evaluated without considering the interactions, the selection and decision might be distorted.
 
-  In this short review, we introduce the papers reporting the interaction and its likely causes, the light energy distribution between the photosystic electron transport.
+  In this short article, we introduce the papers reporting the interaction and its likely causes, the light energy distribution between the photosystic electron transport.
   Subsequently we discuss the practical situations where the interaction should be cared and the recomended measuring methods in the measurements of the photosynthetic rates.
   It is known that the SPD of light affects the instantaneous photosynthetic rate through the other mechanisms, such as the stomatal response [@Shimazaki_et_al2007AnnRev], photo**inhibition** [@Zavafer_et_al2015JPP] and light penetrating depth within the leaf [@Terashima_et_al2009PCP].
-  Thought these subjects are not referred in this article, the cited review articles on these topics are available.
+  Although these subjects are not referred in this article, the cited review articles on these topics are available.
 
@@
   The electron transports are powered by photon energy transferred to the respective photosystems, thus enabling electron transfer against the redox potential (called the Z scheme).
+  energyといいつつも単位はPFD.
   Because photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) through the thylakoid membrane is limited by the slowest step (Fig. 1).
@@
   When PSI absorbs excess energy, the energy distribution to PSII limits the ETR and the yield of PSI is lowered (Fig. 1D).
-  In both cases, the excesss energy is dissipated as heat and fluorescence (ROS生成とダメージの話をするか...), and thus the entire photosynthetic quantum yield---the ETR per absorbed photon---becomes smaller.
+  In both cases, the excesss energy is dissipated as heat and fluorescence (ROS生成とダメージの話をするか...), and thus the entire photosynthetic quantum yield---ETR per absorbed photon---becomes smaller.
   Balancing the excitation energy distribution between PSII and PSI is essential for plants to keep the high photosynthetic quantum yield.
@@
   Monochromatic light at shorter wavelengths (< 680--690 nm) is estimated to be preferentially absorbed by PSII (especially in the wavebands near 470 and 650 nm corresponding to the absorption peaks of chl *b*---abundant in PSII), or evenly absorbed by both PSs [@Evans1986PhotoPhoto; @Evans1987FPB; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
-  These wavelength dependency of the distribution balance is a determinant of EED under a given SPD of light.
-  In several studies of light acclimation of the photosynthetic apparatus, light with a given SPD is categorized as either PSII or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI, respectively.
-  A given SPD of light is classified into either PSII- or PSI-light according to the PFD in the far-red waveband in the relative context.
+  These wavelength dependencies of the distribution balance is a determinant of EED under a given SPD of light.
+  In several studies of the SPD acclimation of the photosynthetic apparatus, light with a given SPD is categorized as either PSII- or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI.
+  A given SPD of light is classified according to the PFD in the FR waveband in the relative context.
   The terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context.
@@
   The stoichiometry is adjusted to the SPD of light during leaf growth [e.g. @Matsuda_et_al2004PCP;].
-  **In the short term, the distribution of excitation energy is adjusted by the dynamic allocation of the light-harvesting antenna complex of PSII (LHCII) to PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].**
-  **When state transitions are insufficient to counterbalance the uneven distribution of excitation energy, a long-term acclimation response occurs [@Dietzel_et_al2008FJ].**
   Under PSII-light, the relative amount of the reaction center complex of PSII to that of PSI in leaves decreases.
@@
   The change in the composition within the respective photosystems might also be involved in the SPD acclimation [@, @Murakami_et_al2016PhysiolPlant].
-  These reactions are believed to be induced so that balance the *excitation balance* and thereafter perform efficient photosynthesis under the growth environments.
+  These reactions are believed to be induced so that balance the *excitation energy distribution* and thereafter perform efficient photosynthesis under the growth environments.
   These adjustments improve photosynthetic light use efficiency under the light during growth.
+  In the short term within an hour, an imbalance in the excitation energy distribution is, at least partly, relieved by the reversible allocation of the light-harvesting antenna complex of PSII (LHCII) between PSII and PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].
+  Slight imbalance in the energy distribution might be covered up by the state transitions.
 
-  光に対する順化、あとは光自体の偏って吸収されやすさのふたつの要因から、栽培光・測定光のSPDが葉の光合成速度に及ぼす影響には交互作用が生じることが期待される。
-  Expected interactions have been reported in several studies [@].
-  In their pioneering study on *Pisum sativum*, @Chow_et_al1990PNAS grew plants under **cool-white fluorescent lamps with yellow Plexglas** (PSII-light) and **incandescent bulbs with red Plexglas** (PSI-light) and measured the photosynthetic quantum yield of O~2~ evolution---O~2~ evolution rate per absorbed photons by leaf---under PSII- and PSI-light.
-  When measured under PSII-light, the yield was higher in PSII-light-grown leaves:
-  When measured under PSI-light, the yield was higher in PSI-light-grown leaves.
+  The energy distribution property of a leaf (e.g. photosystem stoihiometry) is affected by the SPD of growth light and affects the SPD responses of the leaf *P*~n~.
+  That is, the SPDs of growth light and measuring light do not only directly affect the *P*~n~ but also indirectly affect it through their interaction.
+  The expected interactions have been reported in several studies [@Chow_et_al1990PNAS; @Walters_Horton1995aPlanta; @Hogewoning_et_al2012PC; @Murakami_et_al2016PhysiolPlant].
+  In their pioneering study on *Pisum sativum*, @Chow_et_al1990PNAS grew plants under **cool-white fluorescent lamps with yellow Plexglas** (FR-poor PSII-light) and **incandescent bulbs with red Plexglas** (FR-rich PSI-light) and measured the photosynthetic quantum yield of O~2~ evolution---O~2~ evolution rate per absorbed photons by leaf---under PSII- and PSI-light.
+  When measured under PSII-light, the yield was higher in PSII-light-grown leaves: When measured under PSI-light, the yield was higher in PSI-light-grown leaves.
   A similar trend was observed in other studies on *Arabidopsis thaliana* [@Walters_Horton1995aPlanta] and *Cucumis sativus* [@Hogewoning_et_al2012PC; @Murakami_et_al2016PhysiolPlant] (Table. 1).
-  **@Walters_Horton1995aPlanta used halogen lamp and filters **
-  **@Hogewoning_et_al2012PC used an artificial sunlight [@Hogewoning_et_al2010aJXB] and blue LED light as PSII-light and an artificial shadelight as PSI-light.**
-  **@Murakami_et_al2016PhysiolPlant compared the photosynthetic rates of leaves grown under white LED light without and with supplemental far-red LED light (W- and WFR-leaves) using blue-red LED light source sunlight-like SPD of light.**
-  **The photosynthetic rate of W-leaves was greater than that of WFR-leaves under BR LED light (i.e.
-PSII-light), while the rates were comparable between the leaves, or slightly greater in the WFR-leaves, under sunlight (i.e.
-PSI-light).**
-  These studies indicated that comparisons of leaf photosynthetic rates between plants grown under different SPDs of light can be biased depending on the SPD of measuring light (ML).
-  The measurements, comparisons, and evaluations of leaves with an identical SPD of ML do not necessarily reflect the differnece in the functioning of the leaf photosynthesis under a given conditions, as as pointed out in @Walters2005JXB.
+
+  As long as the SPD of measuring light is different from the *in situ* SPD, the measurements do not necessarily reflect the functioning of the *in situ* leaf photosynthesis, as is pointed out in @Walters2005JXB.
+  When the differently grown leaves are compared and evaluated under the blue+red LED light, the results should be inevitably biased by the interaction (Fig. 2).
 
@@
   The mechanisms of the SPD acclimation of **energy distribution** are not yet fully elucidated.
-  @Walter_Horton1995aPlanta confirmed the strong adjustment in the photosystem stoichiometry in response to the slight changes in the SPD of growth light.
-  Therefore, we had better pay attention it whenever measure the *P*~n~ and related parameters.
-  Since the PFD in the far-red waveband has strong impact on the **energy distribution**, the diference in the FR PFD during growth is the most likely trigger for the acclimation.
-  Therefore, the impacts of the interaction on the photosynthetic rates should be concerned when the rates of leaves grown under different PFDs of FR.
+  @Walter_Horton1995aPlanta confirmed typical adjustment in the photosystem stoichiometry in response to the slight changes in the SPD of growth light.
+  Therefore, the interaction should be taken into account whenever the *P*~n~ and related parameters are evaluated.
+  Since the PFD in the FR waveband has strong impact on the **energy distribution**, the diference in the FR PFD during growth is the most likely trigger for the acclimation.
+  The impacts of the interaction on the photosynthetic rates should be payed attention when the rates of leaves grown under different PFDs in the FR waveband.
 
-  Assimilation light provided by the most of the artificial light sources contain little FR (Fig. 3).
-  Blue or red LEDs and most of fluorescent lamps, white LEDs, metal halide lamps, and high-pressure sodium lamps emit typical PSII-light.
+  Assimilation light provided by the most of artificial light sources contain little FR (Fig. 3).
+  Prevailing fluorescent lamps, metal halide lamps, high-pressure sodium lamps, blue, red, and white LEDs emit typical PSII-light.
   On contrary, sunlight incident on and penetrated through a leaf contain much FR (Fig. 3), thus they serve as PSI-light.
@@
   The impacts of the SPD of light during growth on the plant traits, **such as the growth rate and resultant biomass**, have been intensively investigated [e.g.
-@Matsuda_et_al2004PCP; @Li_Kubota2009EEB; @hogewoning_et_al2010; @Shibuya_et_al20XX].
-  Comparing the photosynthetic rates of leaves using the blue and red LED light source might result in relative overestimation in PSII-light-grown leaves and underestimate in PSI-light-grown leaves, as demonstrated in our previous report [@Murakami_et_al2016PhysiolPlant].
+@Matsuda_et_al2004PCP; @Li_Kubota2009EEB; @Hogewoning_et_al2010aJXB; @Hogewoning_et_al2010bJXB].
+  In the most of these experiments, light sources emitting FR-poor PSII-light were used as assimilation light.
+  It should be kept in the mind that the relationhip among the differently grown leaves might be different under PSI-light, typically under sunlight.
+  Comparing the photosynthetic rates of leaves using the blue+red LED light source might result in relative overestimation in PSII-light-grown leaves and underestimate in PSI-light-grown leaves, as demonstrated in our previous report [@Murakami_et_al2016PhysiolPlant].
+  Besides, several recent papers suggest the significance of supplemental FR on the plant growth and development [for a review, see @Demote-Mainard_et_al2016EEB].
   The results from the experiments under artificial light sources, where PSII-light is usually used for the growth light, might not reflect the responses under sunlight [@Walter2005JXB].
@@
 
-  The evaluation of the vertical profile of the photosynthetic properties of the leaves among the plant stand may be biased in the same manner.
+  The evaluation of the vertical profile of the photosynthetic properties of the leaves among the plant stand cultivated in greenhouses may be biased in the same manner.
+  When measured with blue+red LED light, the *P*~n~ of upper leaves acclimated to sunlight might be overestimated while that of lower leaves aclimated to leaf-penetrated light might be underestimated.
   While the leaves in the upper layers were acclimated to sunlight, those in the lower layers were acclimated to the leaf-penetrated light.
@@
   Note that these interaction should be occur in the evaluations of the chlorophyll fluorescence and the photoinhibition.
-  The overexicitation of PSII should result in the lowered PSII photochemical yield, frequently measured as an .
+  The overexicitation of PSII should result in the lowered PSII photochemical yield, frequently measured as a PAM?.
   In addition that, the photoinhibition experiments might also be affected the interaction.
@@
   When the difference in the plant growth in the experiments are analyzed, the rates should be measured under the SPD of light the plant recieved.
-  For instance, when the difference in the resultant growth between the treatments are analyzed and the *P*~n~ is used for the explanatory factor, respective growth light must be used for ML.
+  For instance, when the difference in the resultant growth between the treatments are analyzed and the *P*~n~ is used for the explanatory factor, respective growth light must be used for measuring light.
   These simple solutions may eliminate the problems caused by the interaction.
@@
   A multilevel measurement might be difficult or impossible for technical reasons.
-  In such case, the light source of ML must be declared in the materials and methods section so that readers can follow its SPD.
+  In such case, the light source of measuring light must be declared in the materials and methods section so that readers can follow its SPD.
 
@@
 
-  The *P*~n~ and photosynthetic characteristics of leaves must be discussed in connection with the SPD of ML.
-  Evaluation of the photosynthesis should be made under the in situ conditions or multilevels of SPDs of ML so that the evaluation is not biased by the interaction.
+  The *P*~n~ and photosynthetic characteristics of leaves must be discussed in connection with the SPD of measuring light.
+  Evaluation of the photosynthesis should be made under the in situ conditions or multilevels of SPDs of measuring light so that the evaluation is not biased by the interaction.
   Apparently, measuring the photosynthetic rates under multilevels of SPDs costs much more time, resource, and labor.
@@
 
-# References
+<!-- # References -->

### 2016-07-21 Main.Rmd
–1稿まで完成。2931 words

@@
 ---
-title: "Evaluating the leaf photosynthetic rates?"
+title: "On the spectral photon flux density distribution of light during the measurements of the leaf photosynthetic rate"
 author: "Keach Murakami, Ryo Matsuda, Kazuhiro Fujiwara"
@@
 ```{r load, echo = F, message = F}
+evalFig <- F
+
+if(evalFig){
 devtools::source_url("https://raw.githubusercontent.com/KeachMurakami/Sources/master/Startup.R")
+
+base_size_default <- 12
+R_abs_W <- .79
+FR_abs_W <- .262
+R_abs_WFR <- .783
+FR_abs_WFR <- .20
+# R_abs_W <- .93
+# FR_abs_W <- .311
+# R_abs_WFR <- .922
+# FR_abs_WFR <- .267
+
+options(warn = -1)
+source("~/Dropbox/Publish/2016R_Fr/Functions_CurveFit.R")
+source("~/Dropbox/Publish/2016R_Fr/Pg_Estimate.R")
+source("~/Dropbox/Publish/2016PgEstimate/PgAnalyze.R")
+source("~/Dropbox/Publish/2016PgEstimate/YieldAnalyze.R")
+source("~/Dropbox/Publish/2016PgEstimate/Captions.R")
+options(warn = 1)
+} else {
+library(knitr)
+}
+
 opts_chunk$set(echo = FALSE, fig.width = 7.5, fig.height = 7.5, out.width = "100%",
            message = FALSE, warning = FALSE, cache = F, eval = T)
-
-base_size_default <- 12
-
-options(warn = -1)
-options(warn = 1)
 ```
 
-```{r Spectra}
+```{r Spectra, eval = evalFig}
 
@@
 
-```{r InteractionPict}
+```{r InteractionPict, eval = evalFig}
 
@@
   Considering the importance of the photosynthetic rate, the effects on the rates were measured, evaluated, and compared among the leaves cultivated under different conditions, typically the control and treatment.
-  Based on the measured rates, the impacts of the treatments are discussed.
-  Thus, the reliable measurements must be made prior to the evaluation.
+  The measured *P*~n~ is also used for the estimation of the other photosynthetic parameters, such as initial slope of light response of *P*~n~ and the maximum photosynthetic rate [e.g.
+@Sharkey_et_al2007PCE].
+  Based on the measured rates and estimated parameters, the impacts of the treatments are discussed.
+  Thus, the accurate and reliable *P*~n~ measurements must be essential for **the agricultural and horticultural sciences**.
 
@@
 @McCree1972AM; @Inada1976PCP; @Hogewoning_et_al2012PC].
-  In the agricultural and horticultural researches, the photosynthetic rates are usually measured under an identical SPD of measuring light irrespective of leaf growth conditions to eliminate the direct effect of the SPD of measuring light from the comparison.
-  The most widely-used measuring light might be mixture of blue and red LED light provided by light sources installed in commercial photosynthesis analyzing systems.
+  To eliminate this direct effect from the comparison, the photosynthetic rates are usually measured under an identical SPD of measuring light irrespective of leaf growth conditions in the agricultural and horticultural researches.
+  The most widely-used measuring light might be mixture of blue + red LED light **(BRlight)** provided by light sources installed in commercial photosynthesis analyzing systems.
+  Owing to the their regulatability in the incident photon flux density (PFD), the use of the artificial light sources might enhance the reproducibity、制御しやすさ、解釈しやすさ.
 
-  However, our recent paper demonstrated that the light source cannot evaluate the instantaneous leaf photosynthetic properties in some cases [@Murakami_et_al2016PhysiolPlant].
-  @Murakami_et_al2016PhysiolPlant compared *P*~n~ of leaves grown under white LED light without (W) and with (WFR) supplemental far-red (FR) LED light under blue + red LED light and a sunlight-like SPD of light.
+  @Walters2005JXB warned that the measurement with a different SPD of light from , do not necessarily reflect the functioning of the photosynthesis under growth conditions.
+  Our recent paper, indeed, experimentally demonstrated this problem in the *P*~n~ measurements [@Murakami_et_al2016PP].
+  @Murakami_et_al2016PP grew cucumber seedlings under white LED light without and with supplemental far-red (FR) LED light (W and WFR), and subsequently compared their *P*~n~ under blue + red LED light and the sunlight-like SPD of light.
   The *P*~n~ of W-leaves was greater than that of WFR-leaves under blue + red LED light, while the rates were comparable---or slightly greater in the WFR-leaves---under artificial sunlight.
+  Based on the results obtained from the measurement under blue + red LED light, WFR-leaves are evaluated to be less lively and low quality, despite the comparable potential under the sunlight.
   In other words, the SPDs of light incident on the leaf during growth and measurement interacted on the *P*~n~ (唐突感ある).
-  Based on the results obtained from the measurement under blue + red LED light, WFR-leaves are evaluated to be less lively and low quality, despite the comparable potential under the sunlight.
   If the plants were evaluated without considering the interactions, the selection and decision might be distorted.
 
-  In this short article, we introduce the papers reporting the interaction and its likely causes, the light energy distribution between the photosystic electron transport.
-  Subsequently we discuss the practical situations where the interaction should be cared and the recomended measuring methods in the measurements of the photosynthetic rates.
-  It is known that the SPD of light affects the instantaneous photosynthetic rate through the other mechanisms, such as the stomatal response [@Shimazaki_et_al2007AnnRev], photo**inhibition** [@Zavafer_et_al2015JPP] and light penetrating depth within the leaf [@Terashima_et_al2009PCP].
+  In this short article, we introduce the likely causes of the interaction---the light energy distribution between the photosystic electron transport---and several articles reporting the interaction.
+  Subsequently we suggest the situations where the interaction should be cared.
+  **We also discuss the practical methods for the *P*~n~ measurements 光質に関した的なフレーズ, and related future works.**
+  It is known that the SPD of light affects the instantaneous photosynthesis through the other mechanisms, such as the stomatal response [@Shimazaki_et_al2007AnnRev], photo**inhibition** [@Zavafer_et_al2015JPP] and light penetrating depth within the leaf [@Terashima_et_al2009PCP].
   Although these subjects are not referred in this article, the cited review articles on these topics are available.
@@
   In higher plants, the photosynthetic electron transport chain is anchored by photochemical reactions that occur at two types of photosystems, PSII and PSI.
-  The electron transports are powered by photon energy transferred to the respective photosystems, thus enabling electron transfer against the redox potential (called the Z scheme).
-  energyといいつつも単位はPFD.
-  Because photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) through the thylakoid membrane is limited by the slowest step (Fig. 1).
-  When PSII absorbs excess energy **under the imbalanced energy distribution**, the energy distribution to PSI limits the ETR and thus the photochemical quantum yield of PSII is lowered (Fig. 1A).
-  When PSI absorbs excess energy, the energy distribution to PSII limits the ETR and the yield of PSI is lowered (Fig. 1D).
-  In both cases, the excesss energy is dissipated as heat and fluorescence (ROS生成とダメージの話をするか...), and thus the entire photosynthetic quantum yield---ETR per absorbed photon---becomes smaller.
+  The electron transports are powered by excitation energy, which is derived from absorbed photons and transferred to the respective photosystems, thus enabling electron transfer against the redox potential (called the Z scheme).
+  Note that the term "energy" is used in 
+  Because the photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) through the thylakoid membrane is limited by the slowest step (Fig. 1).
+  When PSII absorbs excess excitation energy **under the imbalanced energy distribution**, the energy distribution to PSI limits the ETR and thus the photochemical quantum yield of PSII is lowered **詰まり由来で的フレーズ** (Fig.
+1A).
+  When PSI absorbs excess excitation energy, the energy distribution to PSII limits the ETR and the yield of PSI is lowered (Fig. 1D).
+  In both cases, the excesss energy is dissipated as heat and fluorescence (ROS生成とダメージの話をするか...), and thus the entire photosynthetic quantum yield---ETR per absorbed PFD---becomes smaller.
   Balancing the excitation energy distribution between PSII and PSI is essential for plants to keep the high photosynthetic quantum yield.
 
-  **おまけ部分**
-  Note that the balanced distribution might not be a fifty-fifty.
-  Even in a dark adapted helthy leaf, the yield of PSII cannot exceed 0.84 (i.e. chl fluorescence parameter *F*~v~/*F*~m~).
-  Although there is no clear consensus, the maximum yield of PSI seems to be greater than that of PSII.
-  Therefore, under the fifty-fifty distribution, the energy supply to PSII is insufficient and that to PSI is excessive.
-  A little bit greater distribution to PSII might be required to make maximum use of the absorbed photons.
-  Gentyに触れるか？AEF
+  <!-- **おまけ部分** -->
+  <!-- Note that the balanced distribution might not be a fifty-fifty. -->
+  <!-- Even in a dark adapted helthy leaf, the yield of PSII cannot exceed 0.84 (i.e. chl fluorescence parameter *F*~v~/*F*~m~). -->
+  <!-- Although there is no clear consensus, the maximum yield of PSI seems to be greater than that of PSII. -->
+  <!-- Therefore, under the fifty-fifty distribution, the energy supply to PSII is insufficient and that to PSI is excessive. -->
+  <!-- A little bit greater distribution to PSII might be required to make maximum use of the absorbed photons. -->
+  <!-- Gentyに触れるか？AEF -->
 
@@
   PSII and PSI represent different light absorption spectral distributions due to the difference in the compositions of binding pigments, mainly chlorophyll (chl) *a* and *b*.
-  Within the chlorophyll (chl) absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [@Evans1986PhotoPhoto; @Evans1987FPB; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
+  Within the chlorophyll (chl) absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [@Evans1986PhotoPhoto; @Evans1987FPB; @Evans_Anderson1987BBA; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
   Such an umbalanced distribution was caused by the facts that only chl *a* can absorb light within the longer waveband and that PSI contains a greater amount of chl *a* than PSII.
-  Monochromatic light at shorter wavelengths (< 680--690 nm) is estimated to be preferentially absorbed by PSII (especially in the wavebands near 470 and 650 nm corresponding to the absorption peaks of chl *b*---abundant in PSII), or evenly absorbed by both PSs [@Evans1986PhotoPhoto; @Evans1987FPB; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
-  These wavelength dependencies of the distribution balance is a determinant of EED under a given SPD of light.
+  Monochromatic light at shorter wavelengths (< 680--690 nm) is estimated to be preferentially absorbed by PSII (especially in the wavebands near 470 and 650 nm corresponding to the absorption peaks of chl *b*---abundant in PSII), or evenly absorbed by both photosystems [@Evans1986PhotoPhoto; @Evans1987FPB; @Evans_Anderson1987BBA; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
+  These wavelength dependencies of the excitation energy distribution is a determinant of the distribution under a given SPD of light.
   In several studies of the SPD acclimation of the photosynthetic apparatus, light with a given SPD is categorized as either PSII- or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI.
   A given SPD of light is classified according to the PFD in the FR waveband in the relative context.
-  The terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context.
-  For instance, a SPD of light, which is in good balance for PSII-leaves, can overexcite PSII in PSI-leaves (Fig. 1AB).
+  Thus, the terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context.
+  For instance, a SPD of light, which is evenly absorbed by PSII and PSI in PSII-leaves, can overexcite PSII in PSI-leaves (Fig. 1AB).
 
-  Apparently, the distribution is affected by the composition of the thylakoid membrane, especially by the stoichiometry between PSII and PSI.
+  Apparently, the excitation energy distribution is affected by the composition of the thylakoid membrane, especially by the stoichiometry between PSII and PSI.
   The stoichiometry is adjusted to the SPD of light during leaf growth [e.g. @Matsuda_et_al2004PCP;].
-  Under PSII-light, the relative amount of the reaction center complex of PSII to that of PSI in leaves decreases.
-  Conversely, under PSI-light, the relative amount increases to achieve a balance [@Chow_et_al1990PCE; @Chow_et_al1990PNAS; @Smith_et_al1993PCE; @Walters_Horton1994Planta; @Walters_Horton1995bPlanta; @Pfannschmidt_et_al1999Nature; @Wagner_et_al2008Planta; @Hogewoning_et_al2012PC].
-  The change in the composition within the respective photosystems might also be involved in the SPD acclimation [@, @Murakami_et_al2016PhysiolPlant].
-  These reactions are believed to be induced so that balance the *excitation energy distribution* and thereafter perform efficient photosynthesis under the growth environments.
-  These adjustments improve photosynthetic light use efficiency under the light during growth.
+  Under PSII-light, the relative amount of the reaction center complex of PSII to that of PSI in leaves decreases; conversely, under PSI-light, the relative amount increases to achieve a balance [@Chow_et_al1990PCE; @Chow_et_al1990PNAS; @Smith_et_al1993PCE; @Walters_Horton1994Planta; @Walters_Horton1995bPlanta; @Pfannschmidt_et_al1999Nature; @Wagner_et_al2008Planta; @Hogewoning_et_al2012PC].
+  The possible involvement of the change in the composition within the respective photosystems in the SPD acclimation was also suggested [@Walters_Horton1995bPlanta, @Murakami_et_al2016PP].
+  These reactions are believed to be induced so that balance the excitation energy distribution.
+  The adjustments in the distribution properties of a leaf help the leaves to keep the higher photosynthetic light use efficiency under the growth condition.
   In the short term within an hour, an imbalance in the excitation energy distribution is, at least partly, relieved by the reversible allocation of the light-harvesting antenna complex of PSII (LHCII) between PSII and PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].
-  Slight imbalance in the energy distribution might be covered up by the state transitions.
+  The A slight imbalance in the energy distribution might be covered up by the state transitions.
+  The adjustments in the distribution properties are supposed to occur when state transitions are insufficient to counterbalance the uneven excitation energy distribution [@Dietzel_et_al2008FJ].
 
-  The energy distribution property of a leaf (e.g. photosystem stoihiometry) is affected by the SPD of growth light and affects the SPD responses of the leaf *P*~n~.
-  That is, the SPDs of growth light and measuring light do not only directly affect the *P*~n~ but also indirectly affect it through their interaction.
-  The expected interactions have been reported in several studies [@Chow_et_al1990PNAS; @Walters_Horton1995aPlanta; @Hogewoning_et_al2012PC; @Murakami_et_al2016PhysiolPlant].
+  The SPD of growth light affects the energy distribution properties of a leaf, which modifies the SPD responses of the leaf ETR (Fig. 2XXX).
+  Therefore, the SPDs of growth light and measuring light do not only directly affect the *P*~n~ but also indirectly affect it through their interaction.
+  The expected interactions have been reported in several studies [@Chow_et_al1990PNAS; @Walters_Horton1995aPlanta; @Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
   In their pioneering study on *Pisum sativum*, @Chow_et_al1990PNAS grew plants under **cool-white fluorescent lamps with yellow Plexglas** (FR-poor PSII-light) and **incandescent bulbs with red Plexglas** (FR-rich PSI-light) and measured the photosynthetic quantum yield of O~2~ evolution---O~2~ evolution rate per absorbed photons by leaf---under PSII- and PSI-light.
-  When measured under PSII-light, the yield was higher in PSII-light-grown leaves: When measured under PSI-light, the yield was higher in PSI-light-grown leaves.
-  A similar trend was observed in other studies on *Arabidopsis thaliana* [@Walters_Horton1995aPlanta] and *Cucumis sativus* [@Hogewoning_et_al2012PC; @Murakami_et_al2016PhysiolPlant] (Table. 1).
+  When measured under PSII-light, the yield was higher in PSII-light-grown leaves; when measured under PSI-light, the yield was higher in PSI-light-grown leaves.
+  A similar trends were observed in other studies on *Arabidopsis thaliana* [@Walters_Horton1995aPlanta] and *Cucumis sativus* [@Hogewoning_et_al2012PC; @Murakami_et_al2016PP] (Table. 1).
 
-  As long as the SPD of measuring light is different from the *in situ* SPD, the measurements do not necessarily reflect the functioning of the *in situ* leaf photosynthesis, as is pointed out in @Walters2005JXB.
-  When the differently grown leaves are compared and evaluated under the blue+red LED light, the results should be inevitably biased by the interaction (Fig. 2).
+  The distribution properties of a leaf grown under a SPD of light may be tuned to the light, and thereby is expected to perform a higher ETR per absorbed PFD under the light than under the more PSII-biased- or PSI-biased-light (Fig.
+3XXX).
+  When leaves grown under different SPDs of light are compared and evaluated under a single-level SPD of light, the results should be inevitably biased by the interaction.
 
@@
 
-  The mechanisms of the SPD acclimation of **energy distribution** are not yet fully elucidated.
-  @Walter_Horton1995aPlanta confirmed typical adjustment in the photosystem stoichiometry in response to the slight changes in the SPD of growth light.
-  Therefore, the interaction should be taken into account whenever the *P*~n~ and related parameters are evaluated.
-  Since the PFD in the FR waveband has strong impact on the **energy distribution**, the diference in the FR PFD during growth is the most likely trigger for the acclimation.
-  The impacts of the interaction on the photosynthetic rates should be payed attention when the rates of leaves grown under different PFDs in the FR waveband.
+  This interaction **has** considerable impact on the *P*~n~ especially under the light limited and/or CO~2~ sturated conditions, where the **大きさ** of the ETR is dominant factor for the photosynthetic CO~2~ fixation [@von].
+  In such conditions, the biases in the ETR directly affect the *P*~n~.
+  In contrast, under a higher PFDs and/or CO~2~ limtied conditions, the rate is determined by the CO~2~ fixation process in the Calvin cycle rather than the ETR.
+  In such conditions, the effects of the biases in the ETR on *P*~n~ may be demagnified.
+  In our experiment, however, the interaction was observed under a high PFD (1200 µmol m^--2^ s^--1^) and a low CO~2~ concentration condition (20 Pa in the intercellular space) [@Murakami_et_al2016PP], suggesting the other factor involved in the interaction.
 
-  Assimilation light provided by the most of artificial light sources contain little FR (Fig. 3).
-  Prevailing fluorescent lamps, metal halide lamps, high-pressure sodium lamps, blue, red, and white LEDs emit typical PSII-light.
-  On contrary, sunlight incident on and penetrated through a leaf contain much FR (Fig. 3), thus they serve as PSI-light.
-  Supplemental use of FR LED light with some light sources convert the mixed light into PSI-light.
+  The mechanisms of the SPD acclimation of **energy distribution** are not yet fully elucidated [see @Murakami_et_al2016PP].
+  <!--' @Walters_Horton1995aPlanta confirmed a typical adjustment in the photosystem stoichiometry in response to the slight difference in the SPD of growth light. -->
+  <!--' They also found no difference in the stoichiometry between the leaves grown with and without supplemental FR [@Walters_Horton1995bPlanta]. -->
+  <!--' Chow and coworkers also reported  -->
+  Considering the sensitively adjusted photosystem stoichiometry to the SPD of light [@Walters_Horton1995aPlanta], the interaction should be taken into account whenever the *P*~n~ and related parameters are evaluated.
+  The impacts of the interaction on the photosynthetic rates should be payed attention when the rates of leaves grown under different PFDs in the FR waveband (FR主張がきつい。怪しいんでしょう？).
+  とくに起こりそうなときには注意しなさい
 
-  For this decade, a number of attempts have been made for plant growth with artificial lighting [e.g.].
-  The impacts of the SPD of light during growth on the plant traits, **such as the growth rate and resultant biomass**, have been intensively investigated [e.g.
-@Matsuda_et_al2004PCP; @Li_Kubota2009EEB; @Hogewoning_et_al2010aJXB; @Hogewoning_et_al2010bJXB].
-  In the most of these experiments, light sources emitting FR-poor PSII-light were used as assimilation light.
-  It should be kept in the mind that the relationhip among the differently grown leaves might be different under PSI-light, typically under sunlight.
-  Comparing the photosynthetic rates of leaves using the blue+red LED light source might result in relative overestimation in PSII-light-grown leaves and underestimate in PSI-light-grown leaves, as demonstrated in our previous report [@Murakami_et_al2016PhysiolPlant].
-  Besides, several recent papers suggest the significance of supplemental FR on the plant growth and development [for a review, see @Demote-Mainard_et_al2016EEB].
-  The results from the experiments under artificial light sources, where PSII-light is usually used for the growth light, might not reflect the responses under sunlight [@Walter2005JXB].
+  For this decade, a number of studies have been investigated the effects of the SPD of growth light on the plant growth and photosynthesis have been intensively investigated [e.g.
+@Matsuda_et_al2004PCP; @Matsuda_et_al2007SSPN; @Matsuda_et_al2008PCP; @Hogewoning_et_al2010aJXB; @Hogewoning_et_al2010bJXB; @Shibuya_et_al2015BP; @Trouwborst_et_al2016EEB].
+  Assimilation light provided by the most of artificial light sources contain little FR.
+  Prevailing fluorescent lamps, metal halide lamps, high-pressure sodium lamps, blue, red, and white LEDs emit typical PSII-light (Fig. 3XXX).
+  This is because FR is not "photosynthetic active" and FR-rich light can induce excessive stem elongation.
+  Although the *P*~n~ measurements were often made using the blue + red LED light sources, it should be kept in the mind that the responses under the blue + red LED light might be different from those under the PSI-light such as sunlight (Fig.
+3XXX).
   When the response under sunlight is the interest of the experiment, we should conduct an experiment under sunlight.
 
+  Several recent papers suggest the significance of supplemental FR on the plant growth and development [for a review, see @Demote-Mainard_et_al2016EEB].
+  Since FR is prefferentially absorbed by PSI and PSI might be relatively overexcited, the excitation energy distribution property of the leaves grown under PSII-light supplemented with FR LED should differ from those of leaves grown without FR.
+  Therefore, comparing the *P*~n~ of leaves grown with and without supplemental FR under the blue + red LED light source might cause a typical interaction, as is demonstrated in the previous report [@Murakami_et_al2016PP].
+
   The evaluation of the vertical profile of the photosynthetic properties of the leaves among the plant stand cultivated in greenhouses may be biased in the same manner.
-  When measured with blue+red LED light, the *P*~n~ of upper leaves acclimated to sunlight might be overestimated while that of lower leaves aclimated to leaf-penetrated light might be underestimated.
   While the leaves in the upper layers were acclimated to sunlight, those in the lower layers were acclimated to the leaf-penetrated light.
-  Due to the higher transmittance in the far-red waveband of a leaf, the leaf-penetrated light contains much FR, namely PSI-light (Fig. 3).
-  Subsequently, the upper and lower leaves can be considered to become PSII- and PSI-leaves.
-  Comparing the photosynthetic rates of these leaves with the blue and red LED light source should cause the interaction and concomittant biases.
+  Due to the higher transmittance in the far-red waveband of a leaf, the leaf-penetrated light contains much FR, namely PSI-light (Fig. 3XXX).
+  When measured with blue+red LED light, the *P*~n~ of upper leaves might be overestimated while that of lower leaves might be underestimated.
 
@@
 
-  This interaction **has** considerable impact on the *P*~n~ especially under the light limited and/or CO~2~ sturated conditions, where the **大きさ** of the ETR is dominant factor for the photosynthetic CO~2~ fixation [@von].
-  In such conditions, the biases in the ETR directly affect the *P*~n~.
-  The photosynthetic yields and the *P*~n~ at light-limited conditions should be measured with particular attentions on the interaction.
-
-  In contrast, under a higher PFDs and/or CO~2~ limtied conditions, the rate is determined by the **Rubisco activity** rather than the ETR.
-  In such conditions, the effects of the biases in the ETR on *P*~n~ may be demagnified.
-  <!-- In our experiment, however, the interaction was observed under a high PFD (1200 µmol m^--2^ s^--1^) and a low CO~2~ concentration condition (20 Pa in the intercellular space), suggesting the other  -->
-
 # How the photosynthetic responses should be measured?
 
+  The photosynthetic yields and the *P*~n~ at light-limited conditions should be measured with particular attentions on the interaction.
   Ideally, the photosynthetic rates should be measured under the *in situ* conditions.
@@
 
-  The *P*~n~ and photosynthetic characteristics of leaves must be discussed in connection with the SPD of measuring light.
-  Evaluation of the photosynthesis should be made under the in situ conditions or multilevels of SPDs of measuring light so that the evaluation is not biased by the interaction.
+  The *P*~n~ measured under a single-level SPD of light is only an aspect of the photosynthetic characteristics of the leaf.
+  Therefore, the values must be discussed in connection with the SPD of measuring light.
+  Evaluation of the photosynthesis should be made under the *in situ* conditions or multilevels of SPDs of measuring light so that the evaluation is not biased by the interaction.
   Apparently, measuring the photosynthetic rates under multilevels of SPDs costs much more time, resource, and labor.
   In addition that, imitating the various SPDs of light incident on the leaf for *in situ* evaluation of photosythesis might be difficult or impossible from the technical reasons.
-  To solve these problems, the determinant parameters in the SPD-dependence of the photosynthetic ETR should be defined.
+  To solve these problems, two processes are remains open;
+  1) 
+  quantitative evaluation of the excitation energy distribution property of a leaf
+  2) 分配特性と分光分布からの電子伝達速度・光合成速度の計算
+  the determinant parameters in the SPD-dependence of the photosynthetic ETR should be defined.
   To omit the evaluation of the multi-levels of the SPDs in the descriptive evaluation of the leaf photosynthesis,
 
-![FigETR](FigETR.png)
+![Fig. XXX The schematic diagrams of the electron transport and the energy flows. under PSII-biased-light (A, C) and PSI-biased-light (B, D)](FigETR.png)
 
-```{r Fig, eval = F, fig.cap = CapSPD}
+![Fig.
+XXX The likely cause of the interaction of the spectral PFD distributions (SPD) of growth light and measuring light on the electron transport rate (ETR) via the excitation energy distribution (EED)](FigPath.png)
+
+```{r Fig, eval = evalFig, fig.cap = CapSPD}
 FigStructure
@@
 
-```{r FigSPD, fig.cap = CapSPD}
+```{r FigSPD, eval = evalFig, fig.cap = CapSPD}
 SPDs
@@
 
-```{r FigInteract, fifig.cap = CapInteract}
+```{r FigInteract, eval = evalFig, fig.cap = CapInteract}
 InteractionView

### 2016-07-22 Main.Rmd
2991 words.

@@
   The most widely-used measuring light might be mixture of blue + red LED light **(BRlight)** provided by light sources installed in commercial photosynthesis analyzing systems.
-  Owing to the their regulatability in the incident photon flux density (PFD), the use of the artificial light sources might enhance the reproducibity、制御しやすさ、解釈しやすさ.
+  Owing to the their regulatability in the incident photon flux density (PFD), the use of the artificial light sources **enables better control of PPFD, and thereby might certificate** the reproducibity of the experimenta.
 
-  @Walters2005JXB warned that the measurement with a different SPD of light from , do not necessarily reflect the functioning of the photosynthesis under growth conditions.
+  @Walters2005JXB warned that the measurement with a different SPD of light from **grothw light**, do not necessarily reflect the functioning of the photosynthesis under growth conditions.
   Our recent paper, indeed, experimentally demonstrated this problem in the *P*~n~ measurements [@Murakami_et_al2016PP].
@@
   In such conditions, the biases in the ETR directly affect the *P*~n~.
+  The photosynthetic yields and the *P*~n~ at light-limited conditions should be measured with particular attentions on the interaction.
   In contrast, under a higher PFDs and/or CO~2~ limtied conditions, the rate is determined by the CO~2~ fixation process in the Calvin cycle rather than the ETR.
@@
   Considering the sensitively adjusted photosystem stoichiometry to the SPD of light [@Walters_Horton1995aPlanta], the interaction should be taken into account whenever the *P*~n~ and related parameters are evaluated.
-  The impacts of the interaction on the photosynthetic rates should be payed attention when the rates of leaves grown under different PFDs in the FR waveband (FR主張がきつい。怪しいんでしょう？).
-  とくに起こりそうなときには注意しなさい
+  The impacts of the interaction on the photosynthetic rates should be payed attention when the rates of leaves, which are expected to **possess** different excitation energy distribution properties, are compared.
 
@@
   Prevailing fluorescent lamps, metal halide lamps, high-pressure sodium lamps, blue, red, and white LEDs emit typical PSII-light (Fig. 3XXX).
-  This is because FR is not "photosynthetic active" and FR-rich light can induce excessive stem elongation.
+  This is because FR is not "photosynthetic active" and FR-rich light sometimes induces excessive stem elongation.
   Although the *P*~n~ measurements were often made using the blue + red LED light sources, it should be kept in the mind that the responses under the blue + red LED light might be different from those under the PSI-light such as sunlight (Fig.
@@
 
-  The evaluation of the vertical profile of the photosynthetic properties of the leaves among the plant stand cultivated in greenhouses may be biased in the same manner.
+  The evaluation of the vertical profile of the photosynthetic properties of the leaves from the plant stand cultivated in greenhouses may be biased in the same manner.
   While the leaves in the upper layers were acclimated to sunlight, those in the lower layers were acclimated to the leaf-penetrated light.
@@
 
-  Note that these interaction should be occur in the evaluations of the chlorophyll fluorescence and the photoinhibition.
-  The overexicitation of PSII should result in the lowered PSII photochemical yield, frequently measured as a PAM?.
-  In addition that, the photoinhibition experiments might also be affected the interaction.
+  Note that these interaction should be cared in the evaluations of the other **photosynthesis-related characteristic**.
+  The overexicitation of PSII (or PSI) results in the lowered photochemical yield at PSII (or PSI) [e.g. Hogewoning_et_al2012PC].
+  Chl fluorescence parameters such as **fai**~PSII~ or NPQ (non-photochemical quenching parameter) should be measured with particular cares.
+  The photoinhibition experiments might also be affected the interaction.
   Imbalance in the excitation balance between the photosystems is supposed to acceralate the photoinhibition [@].
-  Therefore, evaluating PSI-leaves under PSII-biased actinic light should underestimate ΦPSII and overestimate the photoinhibition in connection to those in the PSII-leaves.
+  Therefore, evaluating PSI-leaves under PSII-biased actinic light should underestimate **phi~PSII~** and overestimate the photoinhibition in connection to those in the PSII-leaves.
 
@@
 
-  The photosynthetic yields and the *P*~n~ at light-limited conditions should be measured with particular attentions on the interaction.
   Ideally, the photosynthetic rates should be measured under the *in situ* conditions.
@@
 @Kozai2007POP], and subsequently transferred to a greenhouse and cultivated under sunlight.
-  Therefore, in comparisons of light sources with different SPDs for transplant production, *P*~n~ measurements should be made under sunlight.
-  When the difference in the plant growth in the experiments are analyzed, the rates should be measured under the SPD of light the plant recieved.
-  For instance, when the difference in the resultant growth between the treatments are analyzed and the *P*~n~ is used for the explanatory factor, respective growth light must be used for measuring light.
+  Therefore, in comparisons of light sources with different SPDs for the transplant production, *P*~n~ measurements should be made under sunlight.
+  When the observed differences in the plant growth in the experiments are analyzed, the rates should be measured under the SPDs of light the plants recieved.
+  For instance, when the difference in the resultant dry weight between the plants grown under white LEDs and fluorescent lamps are analyzed and the *P*~n~ is used for the explanatory factor, respective growth light must be used for measuring light.
   These simple solutions may eliminate the problems caused by the interaction.
@@
   Note that the effect of the interaction on the photosytnehtic rate is not prominent compared to those of the other factors such as PPFD and CO~2~ concentration.
-  Accurate control of the PFD must be set above the regulation of the interaction.
-  Fluctuations in the PFD should be removed by using artificial light sources to ensure the reproductivity and reliability of the research.
-  To solve the dilenma between the *in situ* evaluation and PFD stability, the artificial sunlight source might be helpful.
+  The fluctuation in the PFD should be removed by using artificial light sources to ensure the reproductivity and reliability of the research.
+  The use of artificial light sources might be **inconsistent with the *in situ* measurement because the SPD of light from an artificial light source is generally by far different from that of *in situ* light.**
+  To solve the dilenma between *in situ* evaluation and the PFD stability, the artificial sunlight source might be helpful.
 
-  If researchers aim to describe the photosynthetic characteristics or the SPD of light the leaves receive is not predetermined, then *P*~n~ should be measured under both PSII- and PSI-light and the interaction evaluated to detect any biases.
-  The effect of the incteraction should be amplified in the comparison be the leaves with different photosystems stoichiometries.
-  Thus, the interaction should be taken special care when the cases described in the **former section**.
+  If the SPD of light the leaves will receive is not predetermined, then *P*~n~ should be measured under both PSII- and PSI-light.
+  In this type study, researchers should describe the "general" photosynthetic characteristics of the leaves.
+  Therefore, the interaction should be tested so as not to make biased evaluation.
   If the significant interaction is not detected in two-way ANOVA, the main effect of the treatment can be assessed.
   If any the interaction, the results should not be generalized.
-  The responses of the rates to both PSII- and PSI-light had better to be measured, compared, and reported in the paper.
-  A multilevel measurement might be difficult or impossible for technical reasons.
-  In such case, the light source of measuring light must be declared in the materials and methods section so that readers can follow its SPD.
+  The responses of the rates to both PSII- and PSI-light should be measured, compared, and reported in the paper.
+  When **やむおえない事情で位置水準測定をした場合**, the light source of measuring light must be declared in the materials and methods section so that readers can follow the SPD of measuring light.
+  The effect of the incteraction should be amplified in the comparison be the leaves with different excitation energy distribution properties.
+  The interaction should be taken special care when the cases described in the **former section**.
 

### 2016-07-24 Main.Rmd
図1を一新。図2 (機構のパス図) は削除。SPDはSupへ。 もう一息。3295 words

@@
 ```{r load, echo = F, message = F}
-evalFig <- F
+evalFig <- T
 
@@
 
+```{r InteractionPict, eval = evalFig}
+
+X_div <- 100
+X_range <- seq(0, 1, length.out = X_div)
+
+InteractionDat <-
+  data_frame(X = rep(X_range, times = 2),
+           ETR = c(dbeta(X_range, 3, 4.5) * 1.2, dbeta(X_range, 4.5, 3)),
+           Trtm = rep(c("PSII-leaves", "PSI-leaves"), each = X_div))
+
+InteractionLabel <-
+  InteractionDat %>%
+  group_by(Trtm) %>%
+  summarise(ETR = max(ETR)) %>%
+  left_join(., InteractionDat, by = c("Trtm", "ETR"))
+
+InteractionView <-
+  InteractionDat %>%
+  ggplot(aes(X, ETR, linetype = Trtm, group = Trtm)) +
+  theme_bw2() +
+  geom_line() +
+  scale_linetype_manual(values = c(2, 1)) +
+  geom_text(data = InteractionLabel, aes(x = X, y = ETR, label = Trtm), vjust = -1) +
+  xlab("PSI-biased level of measuring light") +
+  ylab("Relative electron transport rate") +
+  gg_xy(c(.1, .9, 0, 3))
+
+CapInteract <-
+  "Fig.
+2  Conceptual diagram of the photosynthetic electron transport rates (ETR) of leaves grown under PSII-light (PSII-leaves; solid line) and PSI-light (PSI-leaves; dashed line) in response to the PSII/PSI-light level of measuring light.
+PSII-leaves performs a higher ETR under PSII-light and a lower ETR under PSI-light compared to PSI-leaves."
+```
+
 ```{r Spectra, eval = evalFig}
@@
 IntegratePFD <- 100
+
+panel_names <- c("HIDs and fluorescent lamp", "LEDs", "Sunlight")
 
@@
   FL_Ocean_raw %>%
-  mutate(value = value * 100 / FL_Ocean_PFD, variable = "Fluorescent lamp")
+  mutate(value = value * 100 / FL_Ocean_PFD, variable = "FL")
 
@@
   HPS_Ocean_raw %>%
-  mutate(value = value * 100 / HPS_Ocean_PFD, variable = "High-pressure sodium lamp")
+  mutate(value = value * 100 / HPS_Ocean_PFD, variable = "HPS")
 
@@
   MH_Ocean_raw %>%
-  mutate(value = value * 100 / MH_Ocean_PFD, variable = "Metal-halide lamp")
+  mutate(value = value * 100 / MH_Ocean_PFD, variable = "MH")
 
@@
   bind_rows(FL_Ocean, HPS_Ocean, MH_Ocean) %>%
-  mutate(panel = "HID, fluorescent lamp")
-
-# FL: FPL55EX-N; IWASAKI ELECTRIC CO., LTD.
-# MH: M220FCELS-W/BUD; IWASAKI ELECTRIC CO., LTD.
-# HPS: NH220FLS; IWASAKI ELECTRIC CO., LTD.
+  mutate(panel = panel_names[1])
 
@@
   left_join(., Absorptances, by = "wavelength") %>%
-  transmute(wavelength, Sunlight, `Shaded sunlight` = Sunlight * (100 - ave), Absorptance = ave)
+  transmute(wavelength, Sun = Sunlight, Shade = Sunlight * (100 - ave), Absorptance = ave)
 
@@
   gather(variable, value, -wavelength) %>%
-  mutate(panel = "LED") %>%
+  mutate(panel = panel_names[2]) %>%
   na.omit
 
+SPD_labels <-
+  data_frame(variable = c("FL", "MH", "HPS", "B", "R", "FR", "W", "Sun", "Shade"),
+             wavelength = c(435, 520, 570, 448, 660, 735, 460, 450, 750),
+             value = c(2.1, .7, 3, 4, 4.4, 3.8, 1.2, 0.3, 2),
+             label = c("FL", "MH", "HPS", "B", "R", "FR", "W", "Sun", "Shade"),
+             panel = rep(panel_names,  c(3, 4, 2)))
+
 SPDs <-
-  # left_join(HIDs, Sun, by = "wavelength") %>%
   Sun %>%
@@
   gather(variable, value, -wavelength) %>%
-  mutate(panel = "Natural light") %>%
+  mutate(panel = panel_names[3]) %>%
   bind_rows(., OceanSPDs, LEDs) %>%
-  filter(between(wavelength, 380, 800)) %>%
+  filter(between(wavelength, 380, 820)) %>%
   ggplot(aes(x = wavelength, y = value, group = variable, col = variable)) +
-  theme_bw2(legend = c(.75, .25)) +
+  theme_bw2() +
   geom_rect(aes(xmin = 700, xmax = 750, ymin = 0, ymax = +Inf), fill = "grey80", col = NA) +
   geom_line() +
-  facet_wrap( ~ panel, ncol = 2) +
-  gg_xy(c(380, 800, 0, 4)) +
+  geom_text(data = SPD_labels, aes(x = wavelength, y = value, label = label)) +
+  facet_wrap( ~ panel, ncol = 1) +
+  gg_xy(c(380, 820, 0, 5)) +
   xlab("Wavelength [nm]") + ylab(u_SPFD("Spectral photon flux density"))
@@
 CapSPD <-
-  "Fig. 2 Spectral photon flux density distribution of light. The distributions at a PFD of 100 µmol m<sup>--2</sup> s<sup>--1</sup> within 400--750 nm are shown."
-```
-
-```{r InteractionPict, eval = evalFig}
-
-X_div <- 100
-X_range <- seq(0, 1, length.out = X_div)
-
-InteractionView <-
-  data_frame(X = rep(X_range, times = 2),
-           ETR = c(dbeta(X_range, 3, 4.5) * 1.2, dbeta(X_range, 4.5, 3)),
-           Trtm = rep(c("W", "WFR"), each = X_div)) %>%
-  ggplot(aes(X, ETR, linetype = Trtm, group = Trtm)) +
-  theme_bw2(legend = c(.5, .3)) +
-  geom_line() +
-  scale_linetype_manual(values = c(1, 2)) +
-  xlab("The fraction of energy distributed to PSI") +
-  ylab("Relative electron transport rate")
-
-CapInteract <-
-  "Fig. 2 Spectral photon flux density distribution of light . The distributions at a PFD of 100 µmol m<sup>--2</sup> s<sup>--1</sup> within 400--750 nm are shown."
+  "Fig. 3  Spectral photon flux density distribution of light. The distributions at a PFD of 100 µmol m<sup>--2</sup> s<sup>--1</sup> within 400--750 nm are shown."
 ```
@@
 
-  The net photosynthetic rate (*P*~n~) is one of the most important and commonly reported phenotype in the plant sciences.
-  Considering the importance of the photosynthetic rate, the effects on the rates were measured, evaluated, and compared among the leaves cultivated under different conditions, typically the control and treatment.
-  The measured *P*~n~ is also used for the estimation of the other photosynthetic parameters, such as initial slope of light response of *P*~n~ and the maximum photosynthetic rate [e.g.
+  The photosynthetic rate is one of the most important and fundamental phenotype in the plant sciences.
+  The rates are measured, evaluated, and compared among the leaves cultivated under different conditions, typically the control and treatment.
+  The measured rates are also used for the estimation of the other photosynthetic parameters, such as initial slope of light response of *P*~n~ and the maximum photosynthetic rate [e.g.
 @Sharkey_et_al2007PCE].
-  Based on the measured rates and estimated parameters, the impacts of the treatments are discussed.
-  Thus, the accurate and reliable *P*~n~ measurements must be essential for **the agricultural and horticultural sciences**.
+  Based on the measured rate and estimated parameters, the effectiveness of the treatment is discussed in agricultural and horticultural studies.
+  Therefore, the accurate and reliable measurements of the photosynthetic rate must be essential.
 
   A number of studies have reported that the SPD of light used for the measurement (i.e.
-measuring light or actinic light) affected the *P*~n~ of leaves [e.g.
+measuring light or actinic light) affected the net photosynthetic rates (*P*~n~) of leaves [e.g.
 @McCree1972AM; @Inada1976PCP; @Hogewoning_et_al2012PC].
-  To eliminate this direct effect from the comparison, the photosynthetic rates are usually measured under an identical SPD of measuring light irrespective of leaf growth conditions in the agricultural and horticultural researches.
+  To eliminate this direct effect from the comparison, *P*~n~ is usually measured under an identical SPD of measuring light irrespective of leaf growth conditions in agricultural and horticultural studies.
   The most widely-used measuring light might be mixture of blue + red LED light **(BRlight)** provided by light sources installed in commercial photosynthesis analyzing systems.
-  Owing to the their regulatability in the incident photon flux density (PFD), the use of the artificial light sources **enables better control of PPFD, and thereby might certificate** the reproducibity of the experimenta.
+  The use of the artificial light sources might enable better control of the incident photosynthetic photon flux density (PPFD) and thereby might certificate the reproducibity of the experiments.
 
@@
   The *P*~n~ of W-leaves was greater than that of WFR-leaves under blue + red LED light, while the rates were comparable---or slightly greater in the WFR-leaves---under artificial sunlight.
-  Based on the results obtained from the measurement under blue + red LED light, WFR-leaves are evaluated to be less lively and low quality, despite the comparable potential under the sunlight.
+  **Based on the results obtained from the measurement under blue + red LED light, WFR-leaves are evaluated to be less lively and low quality, despite the comparable potential under the sunlight.**
   In other words, the SPDs of light incident on the leaf during growth and measurement interacted on the *P*~n~ (唐突感ある).
@@
 
-  In this short article, we introduce the likely causes of the interaction---the light energy distribution between the photosystic electron transport---and several articles reporting the interaction.
+  In this short article, we introduce several articles reporting the interaction and the likely causes---the distribution of the excitation energy between the photosystems.
   Subsequently we suggest the situations where the interaction should be cared.
   **We also discuss the practical methods for the *P*~n~ measurements 光質に関した的なフレーズ, and related future works.**
-  It is known that the SPD of light affects the instantaneous photosynthesis through the other mechanisms, such as the stomatal response [@Shimazaki_et_al2007AnnRev], photo**inhibition** [@Zavafer_et_al2015JPP] and light penetrating depth within the leaf [@Terashima_et_al2009PCP].
+  It is known that the SPD of light affects the photosynthesis through the other mechanisms, such as the stomatal response [@Shimazaki_et_al2007AnnRev], photo**inhibition** [@Zavafer_et_al2015JPP] and light penetrating depth within the leaf [@Terashima_et_al2009PCP].
   Although these subjects are not referred in this article, the cited review articles on these topics are available.
@@
   In higher plants, the photosynthetic electron transport chain is anchored by photochemical reactions that occur at two types of photosystems, PSII and PSI.
-  The electron transports are powered by excitation energy, which is derived from absorbed photons and transferred to the respective photosystems, thus enabling electron transfer against the redox potential (called the Z scheme).
-  Note that the term "energy" is used in 
+  The electron transports are powered by excitation energy, which is derived from absorbed photons.
+  **The excitation energy transferred to the reactino centers of PSII and PSI drives photochemical reactions **
+  **Note that the term "energy" is used in **
+  **The two photochemical reactions at PSII and PSI enables electron transfer against the redox potential (called the Z scheme).**
   Because the photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) through the thylakoid membrane is limited by the slowest step (Fig. 1).
-  When PSII absorbs excess excitation energy **under the imbalanced energy distribution**, the energy distribution to PSI limits the ETR and thus the photochemical quantum yield of PSII is lowered **詰まり由来で的フレーズ** (Fig.
+  When PSII absorbs excess excitation energy **under the imbalanced SPD of light**, the energy distribution to PSI limits the ETR and thus the photochemical quantum yield of PSII is lowered **詰まり由来で的フレーズ** (Fig.
 1A).
@@
   In both cases, the excesss energy is dissipated as heat and fluorescence (ROS生成とダメージの話をするか...), and thus the entire photosynthetic quantum yield---ETR per absorbed PFD---becomes smaller.
-  Balancing the excitation energy distribution between PSII and PSI is essential for plants to keep the high photosynthetic quantum yield.
+  Balancing the excitation energy distribution (EED) between PSII and PSI is essential for plants to keep the high photosynthetic quantum yield.
 
@@
 
-  The imbalance in the energy distribution between the photosystems is supposed to occur ordinarily (どこで？太陽光？).
+  The imbalance in the EED between the photosystems is supposed to occur ordinarily (どこで？太陽光？).
   PSII and PSI represent different light absorption spectral distributions due to the difference in the compositions of binding pigments, mainly chlorophyll (chl) *a* and *b*.
-  Within the chlorophyll (chl) absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [@Evans1986PhotoPhoto; @Evans1987FPB; @Evans_Anderson1987BBA; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
-  Such an umbalanced distribution was caused by the facts that only chl *a* can absorb light within the longer waveband and that PSI contains a greater amount of chl *a* than PSII.
-  Monochromatic light at shorter wavelengths (< 680--690 nm) is estimated to be preferentially absorbed by PSII (especially in the wavebands near 470 and 650 nm corresponding to the absorption peaks of chl *b*---abundant in PSII), or evenly absorbed by both photosystems [@Evans1986PhotoPhoto; @Evans1987FPB; @Evans_Anderson1987BBA; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
-  These wavelength dependencies of the excitation energy distribution is a determinant of the distribution under a given SPD of light.
+  Within the chl absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [@Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
+  Such an umbalanced distribution was caused by the facts that only chl *a* can absorb the longer wavelengths of light and that PSI contains a greater amount of chl *a* than PSII.
+  On contrary, monochromatic light at shorter wavelengths (< 680--690 nm) is estimated to be preferentially absorbed by PSII, or evenly absorbed by both photosystems [@Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
+  These wavelength dependencies of the EED is a determinant of the distribution under a given SPD of light.
   In several studies of the SPD acclimation of the photosynthetic apparatus, light with a given SPD is categorized as either PSII- or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI.
@@
   Thus, the terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context.
-  For instance, a SPD of light, which is evenly absorbed by PSII and PSI in PSII-leaves, can overexcite PSII in PSI-leaves (Fig. 1AB).
+  For instance, a SPD of light, which is evenly absorbed by PSII and PSI in PSII-leaves, can overexcite PSII in PSI-leaves (Fig. 1AC).
 
-  Apparently, the excitation energy distribution is affected by the composition of the thylakoid membrane, especially by the stoichiometry between PSII and PSI.
-  The stoichiometry is adjusted to the SPD of light during leaf growth [e.g. @Matsuda_et_al2004PCP;].
+  Apparently, the EED is affected by the composition of the thylakoid membrane, especially by the stoichiometry between PSII and PSI.
+  The stoichiometry is reported to be adjusted to the SPD of growth light.
   Under PSII-light, the relative amount of the reaction center complex of PSII to that of PSI in leaves decreases; conversely, under PSI-light, the relative amount increases to achieve a balance [@Chow_et_al1990PCE; @Chow_et_al1990PNAS; @Smith_et_al1993PCE; @Walters_Horton1994Planta; @Walters_Horton1995bPlanta; @Pfannschmidt_et_al1999Nature; @Wagner_et_al2008Planta; @Hogewoning_et_al2012PC].
-  The possible involvement of the change in the composition within the respective photosystems in the SPD acclimation was also suggested [@Walters_Horton1995bPlanta, @Murakami_et_al2016PP].
-  These reactions are believed to be induced so that balance the excitation energy distribution.
-  The adjustments in the distribution properties of a leaf help the leaves to keep the higher photosynthetic light use efficiency under the growth condition.
-  In the short term within an hour, an imbalance in the excitation energy distribution is, at least partly, relieved by the reversible allocation of the light-harvesting antenna complex of PSII (LHCII) between PSII and PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].
-  The A slight imbalance in the energy distribution might be covered up by the state transitions.
-  The adjustments in the distribution properties are supposed to occur when state transitions are insufficient to counterbalance the uneven excitation energy distribution [@Dietzel_et_al2008FJ].
+  The possible involvement of the change in the composition within the respective photosystems in the SPD acclimation was also suggested [@Walters_Horton1995bPlanta; @Murakami_et_al2016PP].
+  The adjustments in the EED properties might help the leaves to keep the higher photosynthetic light use efficiency under growth light.
+  In the short term within an hour, an imbalance in the EED is, at least partly, relieved by the reversible allocation of the light-harvesting antenna complex of PSII (LHCII) between PSII and PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].
+  A slight imbalance in the EED might be covered up by the state transitions.
+  The adjustments in the distribution properties are supposed to occur when state transitions are insufficient to counterbalance the uneven EED [@Dietzel_et_al2008FJ].
 
-  The SPD of growth light affects the energy distribution properties of a leaf, which modifies the SPD responses of the leaf ETR (Fig. 2XXX).
-  Therefore, the SPDs of growth light and measuring light do not only directly affect the *P*~n~ but also indirectly affect it through their interaction.
+  The SPD of growth light affects the EED properties of a leaf, which modifies the responses of the ETR and thereafter *P*~n~ to the SPD of measuring light.
+  Thus, the SPDs of growth light and measuring light do not only directly affect the *P*~n~ but also indirectly affect it through their interaction.
   The expected interactions have been reported in several studies [@Chow_et_al1990PNAS; @Walters_Horton1995aPlanta; @Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
-  In their pioneering study on *Pisum sativum*, @Chow_et_al1990PNAS grew plants under **cool-white fluorescent lamps with yellow Plexglas** (FR-poor PSII-light) and **incandescent bulbs with red Plexglas** (FR-rich PSI-light) and measured the photosynthetic quantum yield of O~2~ evolution---O~2~ evolution rate per absorbed photons by leaf---under PSII- and PSI-light.
+  In their pioneering study on *Pisum sativum*, @Chow_et_al1990PNAS grew plants under cool-white fluorescent lamps with yellow Plexglas (FR-poor PSII-light) and incandescent bulbs with red Plexglas (FR-rich PSI-light) and measured the photosynthetic quantum yield of O~2~ evolution---O~2~ evolution rate per absorbed photons by leaf---under PSII- and PSI-light.
   When measured under PSII-light, the yield was higher in PSII-light-grown leaves; when measured under PSI-light, the yield was higher in PSI-light-grown leaves.
-  A similar trends were observed in other studies on *Arabidopsis thaliana* [@Walters_Horton1995aPlanta] and *Cucumis sativus* [@Hogewoning_et_al2012PC; @Murakami_et_al2016PP] (Table. 1).
+  A similar trends were observed in *Arabidopsis thaliana* [@Walters_Horton1995aPlanta] and *Cucumis sativus* [@Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
+  @Walters_Horton1995aPlanta showed the interaction in the O~2~ evolution yield using halogen lamp and color-conversion filter.
+  @Hogewoning_et_al2012PC found the interaction in the *P*~n~ using artificial sunlight (PSII-light) and shadelight (PSI-light) as growth light and 19 monochromatic LED light as measuring light.
+  **They demonstrated that the interaction can occur 違う組合せでも**.
+  @Murakami_et_al2016PP showed the interaction in the *P*~n~ using white LED light without or with FR LED light (PSII-light and PSI-light) as growth light and BR-light (PSII-light) and artificial sunlight (PSI-light) as measuring light.
+  The potential problem in the use of BR-light for the *P*~n~ measurements was clearly demonstrated.
 
-  The distribution properties of a leaf grown under a SPD of light may be tuned to the light, and thereby is expected to perform a higher ETR per absorbed PFD under the light than under the more PSII-biased- or PSI-biased-light (Fig.
-3XXX).
+  <!-- A similar trends were observed in other studies on *Arabidopsis thaliana* [@Walters_Horton1995aPlanta] and *Cucumis sativus* [@Hogewoning_et_al2012PC; @Murakami_et_al2016PP] (Table. 1). -->
+
+  The distribution properties of a leaf seems to be tuned to the SPD of growth light, and thereby is expected to perform a higher photosynthetic quantum yield under **light the same PSII-biased level to growth light** (Fig.
+2).
   When leaves grown under different SPDs of light are compared and evaluated under a single-level SPD of light, the results should be inevitably biased by the interaction.
 
-# Where and When the interactions should be cared.
+# Where the interaction should be cared.
 
-  This interaction **has** considerable impact on the *P*~n~ especially under the light limited and/or CO~2~ sturated conditions, where the **大きさ** of the ETR is dominant factor for the photosynthetic CO~2~ fixation [@von].
-  In such conditions, the biases in the ETR directly affect the *P*~n~.
-  The photosynthetic yields and the *P*~n~ at light-limited conditions should be measured with particular attentions on the interaction.
-  In contrast, under a higher PFDs and/or CO~2~ limtied conditions, the rate is determined by the CO~2~ fixation process in the Calvin cycle rather than the ETR.
-  In such conditions, the effects of the biases in the ETR on *P*~n~ may be demagnified.
-  In our experiment, however, the interaction was observed under a high PFD (1200 µmol m^--2^ s^--1^) and a low CO~2~ concentration condition (20 Pa in the intercellular space) [@Murakami_et_al2016PP], suggesting the other factor involved in the interaction.
+  This interaction **has** considerable impact on the *P*~n~ especially under the light limited and/or CO~2~ sturated conditions, where the extent of the ETR is dominant factor for the photosynthetic CO~2~ uptake rate [@vonCaemmerer_Farquhar1981Planta].
+  In such conditions, the biases in the ETR should be directly reflected in the *P*~n~.
+  Therefore, the *P*~n~ at light-limited conditions may be measured with particular attentions on the interaction.
+  <!-- In contrast, under a higher PFDs and/or CO~2~ limtied conditions, the *P*~n~ is determined by the CO~2~ fixation process in the Calvin cycle rather than the ETR. -->
+  <!-- In such conditions, the effects of the biases in the ETR on *P*~n~ may be demagnified. -->
+  <!-- In our experiment, however, the interaction was observed under a high PFD (1200 µmol m^--2^ s^--1^) and a low CO~2~ concentration condition (20 Pa in the intercellular space) [@Murakami_et_al2016PP], suggesting the other factor involved in the interaction.
+-->
 
@@
   <!--' Chow and coworkers also reported  -->
-  Considering the sensitively adjusted photosystem stoichiometry to the SPD of light [@Walters_Horton1995aPlanta], the interaction should be taken into account whenever the *P*~n~ and related parameters are evaluated.
-  The impacts of the interaction on the photosynthetic rates should be payed attention when the rates of leaves, which are expected to **possess** different excitation energy distribution properties, are compared.
+  Considering the sensitively adjusted photosystem stoichiometry to the SPD of light [@Walters_Horton1995aPlanta], the interaction may be always taken into account whenever the *P*~n~ and related parameters are evaluated.
+  The impacts of the interaction on the photosynthetic rates should be payed particular attention when the measured leaves are expected to **possess** different excitation energy distribution properties.
 
@@
   Assimilation light provided by the most of artificial light sources contain little FR.
-  Prevailing fluorescent lamps, metal halide lamps, high-pressure sodium lamps, blue, red, and white LEDs emit typical PSII-light (Fig. 3XXX).
+  Prevailing fluorescent lamps, metal halide lamps, high-pressure sodium lamps, blue, red, and white LEDs emit typical PSII-light (Supplemental Information S1).
   This is because FR is not "photosynthetic active" and FR-rich light sometimes induces excessive stem elongation.
@@
   The overexicitation of PSII (or PSI) results in the lowered photochemical yield at PSII (or PSI) [e.g. Hogewoning_et_al2012PC].
-  Chl fluorescence parameters such as **fai**~PSII~ or NPQ (non-photochemical quenching parameter) should be measured with particular cares.
+  Chl fluorescence parameters such as *F*~q~′/*F*~m~′ (PSII operating efficiency, also known as Φ~PSII~ and *Y*~II~) or NPQ (non-photochemical quenching parameter) should be measured with particular cares.
   The photoinhibition experiments might also be affected the interaction.
   Imbalance in the excitation balance between the photosystems is supposed to acceralate the photoinhibition [@].
-  Therefore, evaluating PSI-leaves under PSII-biased actinic light should underestimate **phi~PSII~** and overestimate the photoinhibition in connection to those in the PSII-leaves.
+  Therefore, evaluating PSI-leaves under PSII-biased actinic light should underestimate Φ~PSII~ and overestimate the photoinhibition in connection to those in the PSII-leaves.
 
@@
 
-![Fig. XXX The schematic diagrams of the electron transport and the energy flows. under PSII-biased-light (A, C) and PSI-biased-light (B, D)](FigETR.png)
+![Fig.
+1  The schematic the excitation energy distribution between the photosystems (PSII and PSI) on the photosynthetic electron transport rate (ETR).
+Expected electron flow (grey lines) and energy flow (black lines) of leaves grown under PSII-light (A, B) and PSI-light (C, D) measured under PSII-light (A, C) and PSI-light (B, D) were shown.](FigETR.png)
 
-![Fig.
-XXX The likely cause of the interaction of the spectral PFD distributions (SPD) of growth light and measuring light on the electron transport rate (ETR) via the excitation energy distribution (EED)](FigPath.png)
-
-```{r Fig, eval = evalFig, fig.cap = CapSPD}
-FigStructure
-```
-
-```{r FigSPD, eval = evalFig, fig.cap = CapSPD}
-SPDs
-```
+<!-- ![Fig.
+2  The likely cause of the interaction of the spectral PFD distributions (SPD) of growth light and measuring light on the electron transport rate (ETR) via the excitation energy distribution (EED)](FigPath.png) -->
 
@@
 
-<!-- # References -->
+```{r child = "~/Dropbox/Publish/ECB2016Review/Sup1.Rmd"}
+
+```
+
+# References

### 2016-07-24 Sup1.Rmd
図1を一新。図2 (機構のパス図) は削除。SPDはSupへ。 もう一息。3295 words

# Supplemental Information S1

Information of the light sources and measuring instruments.

| Light                           | Model code        | Supplier                        | Measuring instrument              |
|:---------                       |:-----------       |:---------                       |:---------------------             |
| Fluorescent lamp (FL)           | FPL55EX-N         | IWASAKI ELECTRIC CO., LTD.      | HR2000 (Ocean Optics Inc.)        |
| Metalhalide lmap (MH)           | M220FCELS-W/BUD   | IWASAKI ELECTRIC CO., LTD.      | HR2000 (Ocean Optics Inc.)        |
| High-pressure sodium lamp (HPS) | NH220FLS          | IWASAKI ELECTRIC CO., LTD.      | HR2000 (Ocean Optics Inc.)        |
| Blue LED (B)                    | HBL3-3S55-LE      | Tricon Co.                      | MS-720 (EKO Instruments Co. Ltd.) |
| Red LED (R)                     | SRK3-3A80-LE      | Tricon Co.                      | MS-720 (EKO Instruments Co. Ltd.) |
| Far-red LED (FR)                | L735-36AU         | Epitex Inc.                     | MS-720 (EKO Instruments Co. Ltd.) |
| White LED (W)                   | NSPW310DS         | Nichia Chemical Industries Ltd. | MS-720 (EKO Instruments Co. Ltd.) |

The SPD of sunlight was adapted from JIS C8904-3.
The SPD of the shaded sunlight was calculated from the SPD of sunlight and the transmittance spectrum of a cucumber leaf (Murakami et al. 2016).

```{r FigSPD, eval = evalFig, fig.cap = CapSPD}
SPDs
```

### 2016-07-25 Main.Rmd
引用スタイルなども追加。3209 words

@@
 bibliography: ~/Dropbox/R/List.bib
-# csl: new-phytologist.csl
+csl: ECB.csl
 output:
@@
     theme: sandstone
-    self_contained: TRUE
+    self_contained: F
     fig_caption: true
@@
 devtools::source_url("https://raw.githubusercontent.com/KeachMurakami/Sources/master/Startup.R")
-
-base_size_default <- 12
-R_abs_W <- .79
-FR_abs_W <- .262
-R_abs_WFR <- .783
-FR_abs_WFR <- .20
-# R_abs_W <- .93
-# FR_abs_W <- .311
-# R_abs_WFR <- .922
-# FR_abs_WFR <- .267
-
-options(warn = -1)
-source("~/Dropbox/Publish/2016R_Fr/Functions_CurveFit.R")
-source("~/Dropbox/Publish/2016R_Fr/Pg_Estimate.R")
-source("~/Dropbox/Publish/2016PgEstimate/PgAnalyze.R")
-source("~/Dropbox/Publish/2016PgEstimate/YieldAnalyze.R")
-source("~/Dropbox/Publish/2016PgEstimate/Captions.R")
-options(warn = 1)
 } else {
@@
 
-opts_chunk$set(echo = FALSE, fig.width = 7.5, fig.height = 7.5, out.width = "100%",
-           message = FALSE, warning = FALSE, cache = F, eval = T)
+opts_chunk$set(echo = FALSE, fig.width = 5, fig.height = 5, out.width = '500pixel', out.heit = '500pixel', dpi = 200, fig.align = "center", message = FALSE, warning = FALSE, cache = F, eval = T)
+```
+
+```{r Captions}
+CapETRs <-
+  "Fig.
+1  The conceptual diagrams of the effects of the excitation energy distribution between the photosystems (PSII and PSI) on the photosynthetic electron transport rate (ETR).
+Electron flow (grey lines) and energy flow (black lines) of leaves grown under PSII-light (A, B) and PSI-light (C, D) measured using PSII-light (A, C) and PSI-light (B, D) were shown."
+
+CapInteract <-
+  "Fig.
+2  The conceptual diagram of the photosynthetic electron transport rates (ETR) of leaves grown under PSII-light (PSII-leaves) and PSI-light (PSI-leaves) in response to the PSII/PSI-light level of measuring light."
 ```
@@
 
-X_div <- 100
+X_div <- 101
 X_range <- seq(0, 1, length.out = X_div)
+x_breaks <- c(0.2, 0.4, 0.65)
 
@@
   data_frame(X = rep(X_range, times = 2),
-           ETR = c(dbeta(X_range, 3, 4.5) * 1.2, dbeta(X_range, 4.5, 3)),
+           ETR = c(sqrt(dbeta(X_range, 4.5, 3)) * 1.1, sqrt(dbeta(X_range, 3, 4.5))),
            Trtm = rep(c("PSII-leaves", "PSI-leaves"), each = X_div))
@@
 
+InteractionPoint <-
+  InteractionDat %>%
+  filter(X %in% x_breaks)
+
+InteractionText <-
+  InteractionDat %>%
+  filter(X %in% x_breaks) %>%
+  mutate(labels = c("far-red LED light", "Sunlight", "blue + red LED light", rep("", length(x_breaks)))) %>%
+  mutate(ETR = c(0.1, 0.1, 0.1, numeric(length(x_breaks))))
+
 InteractionView <-
   InteractionDat %>%
-  ggplot(aes(X, ETR, linetype = Trtm, group = Trtm)) +
+  ggplot(aes(X, ETR, linetype = Trtm, fill = Trtm, group = Trtm)) +
   theme_bw2() +
+  theme(axis.text.y = element_blank(),
+        axis.ticks = element_blank(),
+        panel.grid.major = element_blank()) +
+  geom_vline(aes(xintercept = x_breaks[1]), linetype = 3, size = .75, col = "grey") +
+  geom_vline(aes(xintercept = x_breaks[2]), linetype = 3, size = .75, col = "grey") +
+  geom_vline(aes(xintercept = x_breaks[3]), linetype = 3, size = .75, col = "grey") +
   geom_line() +
+  geom_point(data = InteractionPoint, col = "black", size = 3, shape = 21) +
+  geom_text(data = InteractionLabel, aes(x = X, y = ETR, label = Trtm), vjust = -1) +
+  geom_text(data = InteractionText, aes(label = labels), vjust = 1) +
+  scale_fill_manual(values = c("white", "black")) +
   scale_linetype_manual(values = c(2, 1)) +
-  geom_text(data = InteractionLabel, aes(x = X, y = ETR, label = Trtm), vjust = -1) +
-  xlab("PSI-biased level of measuring light") +
+  scale_x_continuous(breaks = c(0.1, 0.9), limits = c(0.05, 0.95), labels = c("PSI-biased", "PSII-biased")) +
+  xlab("PSII-biased level of measuring light") +
   ylab("Relative electron transport rate") +
-  gg_xy(c(.1, .9, 0, 3))
-
-CapInteract <-
-  "Fig.
-2  Conceptual diagram of the photosynthetic electron transport rates (ETR) of leaves grown under PSII-light (PSII-leaves; solid line) and PSI-light (PSI-leaves; dashed line) in response to the PSII/PSI-light level of measuring light.
-PSII-leaves performs a higher ETR under PSII-light and a lower ETR under PSI-light compared to PSI-leaves."
-```
-
-```{r Spectra, eval = evalFig}
-
-# set integrate ranges
-PFD_integrate_min <- 350
-PFD_integrate_max <- 750
-
-IntegratePFD <- 100
-
-panel_names <- c("HIDs and fluorescent lamp", "LEDs", "Sunlight")
-
-# HID_raw <-
-#   fread("~/Dropbox/R/spectrum/HID.csv", skip = 13)
-# 
-# HIDs <-
-#   HID_raw %>%
-#   setnames(., c("wavelength", paste0("ID", 1:(dim(HID_raw)[2] - 1)))) %>%
-#   select(1, HPS_ = 12, MH_ = 21)
-FL_Ocean_raw <-
-  fread("~/Dropbox/materials/SPD_FL.csv") %>%
-  transmute(wavelength = `Wavelength[nm]`, value = FL) %>%
-  na.omit
-
-FL_Ocean_PFD <-
-  smooth.spline(FL_Ocean_raw$wavelength, FL_Ocean_raw$value) %>%
-    predict(., seq(PFD_integrate_min, PFD_integrate_max)) %>%
-    .$y %>%
-  sum
-
-FL_Ocean <-
-  FL_Ocean_raw %>%
-  mutate(value = value * 100 / FL_Ocean_PFD, variable = "FL")
-
-HPS_Ocean_raw <-
-  fread("~/Dropbox/materials/SPD_HPS.txt", skip = 50, nrow = 2000) %>%
-  rename(wavelength = V1, value = V2)
-
-HPS_Ocean_PFD <-
-  smooth.spline(HPS_Ocean_raw$wavelength, HPS_Ocean_raw$value) %>%
-    predict(., seq(PFD_integrate_min, PFD_integrate_max)) %>%
-    .$y %>%
-  sum
-
-HPS_Ocean <-
-  HPS_Ocean_raw %>%
-  mutate(value = value * 100 / HPS_Ocean_PFD, variable = "HPS")
-
-MH_Ocean_raw <-
-  fread("~/Dropbox/materials/SPD_MH.txt", skip = 50, nrow = 2000) %>%
-  rename(wavelength = V1, value = V2)
-
-MH_Ocean_PFD <-
-  smooth.spline(MH_Ocean_raw$wavelength, MH_Ocean_raw$value) %>%
-    predict(., seq(PFD_integrate_min, PFD_integrate_max)) %>%
-    .$y %>%
-  sum
-
-MH_Ocean <-
-  MH_Ocean_raw %>%
-  mutate(value = value * 100 / MH_Ocean_PFD, variable = "MH")
-
-OceanSPDs <-
-  bind_rows(FL_Ocean, HPS_Ocean, MH_Ocean) %>%
-  mutate(panel = panel_names[1])
-
-Absorptances <-
-  fread("~/Dropbox/materials/SpectrumCucumber.csv") %>%
-  filter(Trtm %in% c("W", "WFR", "FL")) %>%
-  mutate(wavelength = as.numeric(wavelength)) %>%
-  filter(variable == "absorption", Trtm == "W")
-
-Sun <-
-  fread("~/Dropbox/materials/Sunlight_JIS.csv") %>%
-  setnames(c("wavelength", "Sunlight")) %>%
-  left_join(., Absorptances, by = "wavelength") %>%
-  transmute(wavelength, Sun = Sunlight, Shade = Sunlight * (100 - ave), Absorptance = ave)
-
-# Sun: JIS C8904-3
-
-LEDs <-
-  fread("~/Dropbox/materials/SPD_FL.csv") %>%
-  transmute(wavelength = `Wavelength[nm]`, W, FR, B = B_HL, R = R_SR) %>%
-  SPDnorm(from = 350, to = 750, integratedPFD = IntegratePFD) %>%
-  gather(variable, value, -wavelength) %>%
-  mutate(panel = panel_names[2]) %>%
-  na.omit
-
-SPD_labels <-
-  data_frame(variable = c("FL", "MH", "HPS", "B", "R", "FR", "W", "Sun", "Shade"),
-             wavelength = c(435, 520, 570, 448, 660, 735, 460, 450, 750),
-             value = c(2.1, .7, 3, 4, 4.4, 3.8, 1.2, 0.3, 2),
-             label = c("FL", "MH", "HPS", "B", "R", "FR", "W", "Sun", "Shade"),
-             panel = rep(panel_names,  c(3, 4, 2)))
-
-SPDs <-
-  Sun %>%
-  SPDnorm(from = 350, to = 750, integratedPFD = IntegratePFD) %>%
-  select(-Absorptance) %>%
-  gather(variable, value, -wavelength) %>%
-  mutate(panel = panel_names[3]) %>%
-  bind_rows(., OceanSPDs, LEDs) %>%
-  filter(between(wavelength, 380, 820)) %>%
-  ggplot(aes(x = wavelength, y = value, group = variable, col = variable)) +
-  theme_bw2() +
-  geom_rect(aes(xmin = 700, xmax = 750, ymin = 0, ymax = +Inf), fill = "grey80", col = NA) +
-  geom_line() +
-  geom_text(data = SPD_labels, aes(x = wavelength, y = value, label = label)) +
-  facet_wrap( ~ panel, ncol = 1) +
-  gg_xy(c(380, 820, 0, 5)) +
-  xlab("Wavelength [nm]") + ylab(u_SPFD("Spectral photon flux density"))
-
-CapSPD <-
-  "Fig. 3  Spectral photon flux density distribution of light. The distributions at a PFD of 100 µmol m<sup>--2</sup> s<sup>--1</sup> within 400--750 nm are shown."
+  gg_y(c(0, 2))
 ```
@@
 **Abbreviations**
-Chl: chlorophyll
-ETR: Electron transport rate
-FR: far-red
-LED: light-emitting diode
-*P*~n~: Net photosynthetic rate
-PPFD: photosynthetic photon flux density
-PSI: photosystem II
-PSII: photosystem I
-SPD: spectral PFD distribution
+BR-light: blue + red LED light 
+Chl: chlorophyll,
+ETR: electron transport rate,
+FR: far-red,
+LED: light-emitting diode,
+*P*~n~: net photosynthetic rate,
+PFD: photon flux density,
+PPFD: photosynthetic photon flux density,
+PSI: photosystem I,
+PSII: photosystem II,
+SPD: relative spectral PFD distribution
 
@@
   The rates are measured, evaluated, and compared among the leaves cultivated under different conditions, typically the control and treatment.
-  The measured rates are also used for the estimation of the other photosynthetic parameters, such as initial slope of light response of *P*~n~ and the maximum photosynthetic rate [e.g.
-@Sharkey_et_al2007PCE].
-  Based on the measured rate and estimated parameters, the effectiveness of the treatment is discussed in agricultural and horticultural studies.
-  Therefore, the accurate and reliable measurements of the photosynthetic rate must be essential.
+  The measured rates are also used for the calculation of the other photosynthetic parameters, such as light, water, and nitrogen use efficiencies.
+  The effectiveness of treatments is sometimes discussed based on the measured photosynthetic rate and calculated parameters in agricultural and horticultural studies.
+  Therefore, the accurate measurements of the photosynthetic rate must be essential.
+  A number of studies have reported that the relative spectral photon-flux-density (PFD) distribution (SPD) of light used for the measurement (i.e.
+measuring light or actinic light) affected the net photosynthetic rates (*P*~n~) of leaves [e.g.
+@McCree1972AM; @Inada1976PCP].
+  To eliminate this direct effect from the comparison, *P*~n~ is usually measured under a single-level SPD of measuring light irrespective of the leaf growth conditions in these fields.
+  The most widely-used measuring light might be mixture of blue + red LED light (BR-light) provided by light sources installed in commercial photosynthesis analyzing systems.
+  The use of the artificial light sources might enable precise control of the photosynthetic PFD (PPFD) and SPD incident on the leaf thereby ensure the reproducibility and reliability of the experiments.
 
-  A number of studies have reported that the SPD of light used for the measurement (i.e.
-measuring light or actinic light) affected the net photosynthetic rates (*P*~n~) of leaves [e.g.
-@McCree1972AM; @Inada1976PCP; @Hogewoning_et_al2012PC].
-  To eliminate this direct effect from the comparison, *P*~n~ is usually measured under an identical SPD of measuring light irrespective of leaf growth conditions in agricultural and horticultural studies.
-  The most widely-used measuring light might be mixture of blue + red LED light **(BRlight)** provided by light sources installed in commercial photosynthesis analyzing systems.
-  The use of the artificial light sources might enable better control of the incident photosynthetic photon flux density (PPFD) and thereby might certificate the reproducibity of the experiments.
-
-  @Walters2005JXB warned that the measurement with a different SPD of light from **grothw light**, do not necessarily reflect the functioning of the photosynthesis under growth conditions.
-  Our recent paper, indeed, experimentally demonstrated this problem in the *P*~n~ measurements [@Murakami_et_al2016PP].
-  @Murakami_et_al2016PP grew cucumber seedlings under white LED light without and with supplemental far-red (FR) LED light (W and WFR), and subsequently compared their *P*~n~ under blue + red LED light and the sunlight-like SPD of light.
-  The *P*~n~ of W-leaves was greater than that of WFR-leaves under blue + red LED light, while the rates were comparable---or slightly greater in the WFR-leaves---under artificial sunlight.
-  **Based on the results obtained from the measurement under blue + red LED light, WFR-leaves are evaluated to be less lively and low quality, despite the comparable potential under the sunlight.**
-  In other words, the SPDs of light incident on the leaf during growth and measurement interacted on the *P*~n~ (唐突感ある).
+  @Walters2005JXB pointed out that the measurements with a SPD of light different from growth light do not necessarily reflect the functioning of the photosynthesis under growth conditions.
+  Our recent study, indeed, experimentally demonstrated this problem in the *P*~n~ measurements [@Murakami_et_al2016PP].
+  In that experiment, cucumber seedlings were grown under white light-emitting diode (LED) light without and with supplemental far-red (FR) LED light (W and WFR), and subsequently the *P*~n~ of the leaves were compared under BR-light and a sunlight-like SPD of light.
+  The *P*~n~ of W-leaves was greater than that of WFR-leaves under BR-light, while the rates were comparable---or slightly greater in the WFR-leaves---under artificial sunlight [@Murakami_et_al2016PP].
+  Based on the results obtained from the measurement under BR-light, the prospective growth rate of WFR-plants is evaluated to be smaller than that of W-plants despite the comparable *P*~n~ under the sunlight.
+  **In other words, the SPDs of light incident on the leaf during growth and measurement interacted on the *P*~n~**.
   If the plants were evaluated without considering the interactions, the selection and decision might be distorted.
@@
   Subsequently we suggest the situations where the interaction should be cared.
-  **We also discuss the practical methods for the *P*~n~ measurements 光質に関した的なフレーズ, and related future works.**
-  It is known that the SPD of light affects the photosynthesis through the other mechanisms, such as the stomatal response [@Shimazaki_et_al2007AnnRev], photo**inhibition** [@Zavafer_et_al2015JPP] and light penetrating depth within the leaf [@Terashima_et_al2009PCP].
+  We also discuss the good practice for the selection of the SPD of measuring light used for *P*~n~ measurements.
+  The SPD of light affects the photosynthesis through the other mechanisms, such as the stomatal response [@Shimazaki_et_al2007AnnRev], photoinhibition [@Zavafer_et_al2015JPP], and the light-penetrating depth within a leaf [@Terashima_et_al2009PCP].
   Although these subjects are not referred in this article, the cited review articles on these topics are available.
 
-# How the interactions are generated
+# How the interaction is generated
 
@@
   In higher plants, the photosynthetic electron transport chain is anchored by photochemical reactions that occur at two types of photosystems, PSII and PSI.
-  The electron transports are powered by excitation energy, which is derived from absorbed photons.
-  **The excitation energy transferred to the reactino centers of PSII and PSI drives photochemical reactions **
+  The reactions are powered by excitation energy derived from absorbed photons.
+  **The excitation energy  the photosystems and their anntena complexes is transferred to the reaction centers, and then consumed photochemical reactions in the unit of mol**
   **Note that the term "energy" is used in **
@@
   Because the photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) through the thylakoid membrane is limited by the slowest step (Fig. 1).
-  When PSII absorbs excess excitation energy **under the imbalanced SPD of light**, the energy distribution to PSI limits the ETR and thus the photochemical quantum yield of PSII is lowered **詰まり由来で的フレーズ** (Fig.
-1A).
-  When PSI absorbs excess excitation energy, the energy distribution to PSII limits the ETR and the yield of PSI is lowered (Fig. 1D).
-  In both cases, the excesss energy is dissipated as heat and fluorescence (ROS生成とダメージの話をするか...), and thus the entire photosynthetic quantum yield---ETR per absorbed PFD---becomes smaller.
+  When PSII absorbs excess excitation energy under PSII-biased light, the energy distribution to PSI limits the ETR and thus the photochemical quantum yield of PSII should be lowered (Fig. 1A).
+  When PSI absorbs excess excitation energy, the energy distribution to PSII limits the ETR and the yield of PSI should be lowered (Fig. 1D).
+  In both cases, the excesss energy is dissipated as heat and fluorescence, and thus the entire photosynthetic quantum yield---ETR per absorbed PFD---becomes smaller.
+  An imbalance excitation between the photosystems can harm leaves by generating reactive oxygen species, which cause oxidative damage to chloroplast components [for reviews, see @Asada1999AnnRev; @Asada2006PP].
   Balancing the excitation energy distribution (EED) between PSII and PSI is essential for plants to keep the high photosynthetic quantum yield.
@@
   <!-- Note that the balanced distribution might not be a fifty-fifty. -->
-  <!-- Even in a dark adapted helthy leaf, the yield of PSII cannot exceed 0.84 (i.e. chl fluorescence parameter *F*~v~/*F*~m~). -->
+  <!-- Even in a dark adapted helthy leaf, the yield of PSII cannot exceed 0.84 (i.e. Chl fluorescence parameter *F*~v~/*F*~m~). -->
   <!-- Although there is no clear consensus, the maximum yield of PSI seems to be greater than that of PSII. -->
@@
 
-  The imbalance in the EED between the photosystems is supposed to occur ordinarily (どこで？太陽光？).
-  PSII and PSI represent different light absorption spectral distributions due to the difference in the compositions of binding pigments, mainly chlorophyll (chl) *a* and *b*.
+  <!-- The imbalance in the EED between the photosystems is supposed to occur ordinarily (どこで？太陽光？). -->
+  PSII and PSI represent different light absorption spectral distributions due to the difference in the compositions of binding pigments, mainly chl *a* and chl *b*.
   Within the chl absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [@Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
@@
   A given SPD of light is classified according to the PFD in the FR waveband in the relative context.
+  For instance, a SPD of light, which is evenly absorbed by PSII and PSI in PSII-leaves, can overexcite PSII in PSI-leaves (Fig. 1AC).
   Thus, the terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context.
-  For instance, a SPD of light, which is evenly absorbed by PSII and PSI in PSII-leaves, can overexcite PSII in PSI-leaves (Fig. 1AC).
 
   Apparently, the EED is affected by the composition of the thylakoid membrane, especially by the stoichiometry between PSII and PSI.
-  The stoichiometry is reported to be adjusted to the SPD of growth light.
-  Under PSII-light, the relative amount of the reaction center complex of PSII to that of PSI in leaves decreases; conversely, under PSI-light, the relative amount increases to achieve a balance [@Chow_et_al1990PCE; @Chow_et_al1990PNAS; @Smith_et_al1993PCE; @Walters_Horton1994Planta; @Walters_Horton1995bPlanta; @Pfannschmidt_et_al1999Nature; @Wagner_et_al2008Planta; @Hogewoning_et_al2012PC].
+  The stoichiometry seems to be adjusted to the SPD of growth light.
+  Under PSII-light, the relative amount of the reaction center complex of PSII to that of PSI in leaves decreases; conversely, under PSI-light, the relative amount increases to achieve a balance [e.g.
+@Melis1991BBA; @Pfannschmidt_et_al1999Nature].
   The possible involvement of the change in the composition within the respective photosystems in the SPD acclimation was also suggested [@Walters_Horton1995bPlanta; @Murakami_et_al2016PP].
+  <!-- Galka_et_al2012PC -->
   The adjustments in the EED properties might help the leaves to keep the higher photosynthetic light use efficiency under growth light.
   In the short term within an hour, an imbalance in the EED is, at least partly, relieved by the reversible allocation of the light-harvesting antenna complex of PSII (LHCII) between PSII and PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].
-  A slight imbalance in the EED might be covered up by the state transitions.
-  The adjustments in the distribution properties are supposed to occur when state transitions are insufficient to counterbalance the uneven EED [@Dietzel_et_al2008FJ].
+  Although a slight imbalance in the EED might be covered up by the state transitions, the long-term adjustments in the EED properties are supposed to occur when state transitions are insufficient to counterbalance the uneven EED [@Dietzel_et_al2008FJ].
 
@@
   @Hogewoning_et_al2012PC found the interaction in the *P*~n~ using artificial sunlight (PSII-light) and shadelight (PSI-light) as growth light and 19 monochromatic LED light as measuring light.
-  **They demonstrated that the interaction can occur 違う組合せでも**.
+  They demonstrated that the interaction can occur 違う組合せでも**.
   @Murakami_et_al2016PP showed the interaction in the *P*~n~ using white LED light without or with FR LED light (PSII-light and PSI-light) as growth light and BR-light (PSII-light) and artificial sunlight (PSI-light) as measuring light.
@@
 
-# Where the interaction should be cared.
+# Where the interaction should be cared
 
-  This interaction **has** considerable impact on the *P*~n~ especially under the light limited and/or CO~2~ sturated conditions, where the extent of the ETR is dominant factor for the photosynthetic CO~2~ uptake rate [@vonCaemmerer_Farquhar1981Planta].
-  In such conditions, the biases in the ETR should be directly reflected in the *P*~n~.
-  Therefore, the *P*~n~ at light-limited conditions may be measured with particular attentions on the interaction.
+  This interaction may have considerable impact on the *P*~n~ especially under the light limited and/or CO~2~ saturated conditions, where the extent of the ETR is dominant factor for the photosynthetic CO~2~ uptake rate [@vonCaemmerer_Farquhar1981Planta].
+  In such conditions, any bias in the ETR is directly reflected in the *P*~n~.
+  Therefore, the *P*~n~ at light-limited conditions should be measured with particular attentions on the interaction.
   <!-- In contrast, under a higher PFDs and/or CO~2~ limtied conditions, the *P*~n~ is determined by the CO~2~ fixation process in the Calvin cycle rather than the ETR. -->
@@
 
-  The mechanisms of the SPD acclimation of **energy distribution** are not yet fully elucidated [see @Murakami_et_al2016PP].
+  The mechanisms of the SPD acclimation of the EED property are not yet fully elucidated [see @Murakami_et_al2016PP].
   <!--' @Walters_Horton1995aPlanta confirmed a typical adjustment in the photosystem stoichiometry in response to the slight difference in the SPD of growth light. -->
@@
   <!--' Chow and coworkers also reported  -->
-  Considering the sensitively adjusted photosystem stoichiometry to the SPD of light [@Walters_Horton1995aPlanta], the interaction may be always taken into account whenever the *P*~n~ and related parameters are evaluated.
-  The impacts of the interaction on the photosynthetic rates should be payed particular attention when the measured leaves are expected to **possess** different excitation energy distribution properties.
+  Considering the sensitively adjusted photosystem stoichiometry in response to the SPD of light [@Walters_Horton1995aPlanta], the interaction may be always taken into account whenever the *P*~n~ and related parameters are evaluated.
+  The impacts of the interaction on the photosynthetic rates should be payed particular attention when the measured leaves are expected to represent different EED properties.
 
-  For this decade, a number of studies have been investigated the effects of the SPD of growth light on the plant growth and photosynthesis have been intensively investigated [e.g.
+  For this decade, a number of studies have investigated the effects of the SPD of growth light on the plant growth and photosynthesis [e.g.
 @Matsuda_et_al2004PCP; @Matsuda_et_al2007SSPN; @Matsuda_et_al2008PCP; @Hogewoning_et_al2010aJXB; @Hogewoning_et_al2010bJXB; @Shibuya_et_al2015BP; @Trouwborst_et_al2016EEB].
-  Assimilation light provided by the most of artificial light sources contain little FR.
-  Prevailing fluorescent lamps, metal halide lamps, high-pressure sodium lamps, blue, red, and white LEDs emit typical PSII-light (Supplemental Information S1).
-  This is because FR is not "photosynthetic active" and FR-rich light sometimes induces excessive stem elongation.
-  Although the *P*~n~ measurements were often made using the blue + red LED light sources, it should be kept in the mind that the responses under the blue + red LED light might be different from those under the PSI-light such as sunlight (Fig.
+  Assimilation light provided by most of artificial light sources contain little FR.
+  In general, fluorescent lamps, metal halide lamps, high-pressure sodium lamps, and blue, red, and white LEDs emit typical PSII-light (Supplemental Information S1).
+  This is because FR is not "photosynthetically active" and FR-rich light promotes excessive stem elongation.
+  <!-- It should be kept in the mind that the *P*~n~ of leaves grown under these light sources can be overestimated if measured with BR-light, and the measured *P*~n~ might be different from those under the PSI-light such as sunlight (Fig.
 3XXX).
-  When the response under sunlight is the interest of the experiment, we should conduct an experiment under sunlight.
+-->
+  <!-- When the response under sunlight is the interest of the experiment, we should carry out measurements under sunlight. -->
+  On the other hand, several recent papers suggest the significance of supplemental FR on the plant growth and development [for a review, see @Demote-Mainard_et_al2016EEB].
+  Since FR overexcites PSI, leaves grown under PSII-light supplemented with FR LED can become relatively PSI-leaves like EED property compared to those grown without supplemental FR.
+  Therefore, comparing the *P*~n~ of leaves grown with and without supplemental FR using BR-light might result in typical biased evaluation caused by the interaction, as is demonstrated in the previous report [@Murakami_et_al2016PP].
 
-  Several recent papers suggest the significance of supplemental FR on the plant growth and development [for a review, see @Demote-Mainard_et_al2016EEB].
-  Since FR is prefferentially absorbed by PSI and PSI might be relatively overexcited, the excitation energy distribution property of the leaves grown under PSII-light supplemented with FR LED should differ from those of leaves grown without FR.
-  Therefore, comparing the *P*~n~ of leaves grown with and without supplemental FR under the blue + red LED light source might cause a typical interaction, as is demonstrated in the previous report [@Murakami_et_al2016PP].
+  Evaluating the vertical profiles of the photosynthetic characteristics of the plant stand cultivated in greenhouses may be vulnerable to the biases in the same manner.
+  While the leaves in the upper layers were acclimated to sunlight, those in the lower layers were acclimated to the leaf-penetrated light.
+  Due to the higher transmittance in the FR waveband of a leaf, leaf-penetrated light contains much FR, namely PSI-light (Supplemental Information S1).
+  Therefore, when measured using BR-light, the *P*~n~ of upper leaves might be overestimated while that of lower leaves might be underestimated.
 
-  The evaluation of the vertical profile of the photosynthetic properties of the leaves from the plant stand cultivated in greenhouses may be biased in the same manner.
-  While the leaves in the upper layers were acclimated to sunlight, those in the lower layers were acclimated to the leaf-penetrated light.
-  Due to the higher transmittance in the far-red waveband of a leaf, the leaf-penetrated light contains much FR, namely PSI-light (Fig. 3XXX).
-  When measured with blue+red LED light, the *P*~n~ of upper leaves might be overestimated while that of lower leaves might be underestimated.
+  Further investigation is required to elucidate the extent of the interaction in the *P*~n~ under the above mentioned conditions.
+  Note that such an interaction should be taken into account in the evaluations of the other photosynthesis-related characteristic, such as chl fluorescence parameters.
+  The overexicitation of PSII (or PSI) results in the lowered photochemical yield at PSII (or PSI) [e.g. Hogewoning_et_al2012PC].
+  Imbalance in the excitation balance between the photosystems is supposed to acceralate the photoinhibition [@].
+  Chl fluorescence parameters such as *F*~q~′/*F*~m~′ (PSII operating efficiency, also known as Φ~PSII~ and *Y*~II~) and photoinhibition indicator such as **Fv/Fm** should be measured with particular care.
 
-  Note that these interaction should be cared in the evaluations of the other **photosynthesis-related characteristic**.
-  The overexicitation of PSII (or PSI) results in the lowered photochemical yield at PSII (or PSI) [e.g. Hogewoning_et_al2012PC].
-  Chl fluorescence parameters such as *F*~q~′/*F*~m~′ (PSII operating efficiency, also known as Φ~PSII~ and *Y*~II~) or NPQ (non-photochemical quenching parameter) should be measured with particular cares.
-  The photoinhibition experiments might also be affected the interaction.
-  Imbalance in the excitation balance between the photosystems is supposed to acceralate the photoinhibition [@].
-  Therefore, evaluating PSI-leaves under PSII-biased actinic light should underestimate Φ~PSII~ and overestimate the photoinhibition in connection to those in the PSII-leaves.
-
-# How the photosynthetic responses should be measured?
+# How the photosynthetic responses should be measured
 
   Ideally, the photosynthetic rates should be measured under the *in situ* conditions.
-  When the plant growth in the subsequent condition are focused, the rates should be measured under the SPD of light the plant will recieve.
-  For instance, commercial transplants are sometimes raised in a closed system with artificial lighting [e.g.
+  In the prospective study focusing on the plant growth after the *P*~n~ measurements, the rates should be measured under the SPD of light the plant will subject to.
+  For instance, evaluation of the photosynthesis of the transplants grown under artificial lighting [e.g.
+@Kozai2007POP] should be made under sunlight because they are subsequently transferred to a greenhouse and cultivated under sunlight.
+  <!-- For instance, commercial transplants are sometimes raised in a closed system with artificial lighting [e.g.
 @Kozai2007POP], and subsequently transferred to a greenhouse and cultivated under sunlight.
-  Therefore, in comparisons of light sources with different SPDs for the transplant production, *P*~n~ measurements should be made under sunlight.
-  When the observed differences in the plant growth in the experiments are analyzed, the rates should be measured under the SPDs of light the plants recieved.
-  For instance, when the difference in the resultant dry weight between the plants grown under white LEDs and fluorescent lamps are analyzed and the *P*~n~ is used for the explanatory factor, respective growth light must be used for measuring light.
-  These simple solutions may eliminate the problems caused by the interaction.
+-->
+  <!-- Therefore, in comparisons of light sources with different SPDs for the transplant production, *P*~n~ measurements should be made under sunlight. -->
+  Note that the effect of the interaction seems to be less prominent than those of the other factors, such as the incident PPFD.
+  The *P*~n~ measurements under sunlight, which usually generates fluctuations in the incident PFD, should be avoided and thus the measurements should be made under the artificial light sources to ensure the reproducibility and reliability of the research.
+  The use of artificial light sources will lower the uncertainty caused by the fluctuations in the incident PPFD at the expense of the biases possibly caused by the interaction.
+  This is because the SPD of light from an artificial light source is generally by far different from that of *in situ* light.
+  To solve this dilenma between the *in situ* evaluation and the PPFD stability, the SPD-controllable light source might be helpful [e.g. @Yano_Fujiwara2012PM; @Fujiwara_et_al2013Proc].
 
-  Note that the effect of the interaction on the photosytnehtic rate is not prominent compared to those of the other factors such as PPFD and CO~2~ concentration.
-  The fluctuation in the PFD should be removed by using artificial light sources to ensure the reproductivity and reliability of the research.
-  The use of artificial light sources might be **inconsistent with the *in situ* measurement because the SPD of light from an artificial light source is generally by far different from that of *in situ* light.**
-  To solve the dilenma between *in situ* evaluation and the PFD stability, the artificial sunlight source might be helpful.
+  In the retrospective study elucidating the causes of the differences in the experimental groups, the rates should be measured under the SPDs of light the plants recieved during the treatments.
+  <!-- When the aim of the research is to analyze the origins of the differences in the growth of the plants subject to several light treatments, the rates should be measured under the SPDs of light the plants recieved.
+-->
+  For instance, when the difference in the resultant dry weight between the plants grown under white LEDs and fluorescent lamps are analyzed and the *P*~n~ is used for the explanatory variable, the measurements should be made using white LED for the plants grown under white LEDs light and using fluorescent lamps for those grown under fluorescent lamps.
 
-  If the SPD of light the leaves will receive is not predetermined, then *P*~n~ should be measured under both PSII- and PSI-light.
-  In this type study, researchers should describe the "general" photosynthetic characteristics of the leaves.
+  In both the prospective and retrospective studies, these simple solutions will eliminate the problems caused by the interaction.
+  On the other hand, if the SPD of light the leaves will receive is not predetermined, then *P*~n~ should be measured under both PSII- and PSI-light.
+  Researchers had better describe the "general" photosynthetic characteristics of the leaves in these kind of studies.
   Therefore, the interaction should be tested so as not to make biased evaluation.
@@
   The responses of the rates to both PSII- and PSI-light should be measured, compared, and reported in the paper.
-  When **やむおえない事情で位置水準測定をした場合**, the light source of measuring light must be declared in the materials and methods section so that readers can follow the SPD of measuring light.
-  The effect of the incteraction should be amplified in the comparison be the leaves with different excitation energy distribution properties.
-  The interaction should be taken special care when the cases described in the **former section**.
+  When the measuments were made only under a single-level of SPD of measuring light because of unavoidable circumstances, the light source must be declared in the materials and methods section so that readers can follow the SPD.
+  <!-- The effect of the incteraction should be amplified in the comparison be the leaves with different EED properties. -->
+  <!-- The interaction should be taken special care when the cases described in the **former section**. -->
 
-# Concluding remarks amd future works
+# Concluding remarks and future works
 
   The *P*~n~ measured under a single-level SPD of light is only an aspect of the photosynthetic characteristics of the leaf.
-  Therefore, the values must be discussed in connection with the SPD of measuring light.
+  The obtained results must be discussed in connection with the SPD of measuring light.
   Evaluation of the photosynthesis should be made under the *in situ* conditions or multilevels of SPDs of measuring light so that the evaluation is not biased by the interaction.
-  Apparently, measuring the photosynthetic rates under multilevels of SPDs costs much more time, resource, and labor.
-  In addition that, imitating the various SPDs of light incident on the leaf for *in situ* evaluation of photosythesis might be difficult or impossible from the technical reasons.
-  To solve these problems, two processes are remains open;
-  1) 
-  quantitative evaluation of the excitation energy distribution property of a leaf
-  2) 分配特性と分光分布からの電子伝達速度・光合成速度の計算
-  the determinant parameters in the SPD-dependence of the photosynthetic ETR should be defined.
-  To omit the evaluation of the multi-levels of the SPDs in the descriptive evaluation of the leaf photosynthesis,
+  Imitating the various SPDs of light incident on the leaf for *in situ* evaluation might be difficult or impossible from the technical reasons.
+  In addition that, measuring the *P*~n~ under multilevels of SPDs costs much more time, resource, and labor.
+  Thus, these two approaches might not always be applied for evaluation of the leaf *P*~n~.
+  **Futher research is required to make the quantitative analysis of the leaf *P*~n~ in response to the SPD of measuring light.**
 
-![Fig.
-1  The schematic the excitation energy distribution between the photosystems (PSII and PSI) on the photosynthetic electron transport rate (ETR).
-Expected electron flow (grey lines) and energy flow (black lines) of leaves grown under PSII-light (A, B) and PSI-light (C, D) measured under PSII-light (A, C) and PSI-light (B, D) were shown.](FigETR.png)
+```{r, eval = evalFig, fig.cap = CapETRs}
+knitr::include_graphics("FigETR.png")
+```
 
@@
 
-```{r child = "~/Dropbox/Publish/ECB2016Review/Sup1.Rmd"}
+```{r child = "~/Dropbox/Publish/ECB2016Review/Sup1.Rmd", fig.width = 7.5, fig.height = 7.5, out.width = '500pixel', out.heit = '500pixel', dpi = 200}
 

### 2016-07-25 Sup1.Rmd
引用スタイルなども追加。3209 words

@@
 
-| Light                           | Model code        | Supplier                        | Measuring instrument              |
-|:---------                       |:-----------       |:---------                       |:---------------------             |
+```{r Spectra, eval = evalFig}
+
+# set integrate ranges
+PFD_integrate_min <- 350
+PFD_integrate_max <- 750
+
+IntegratePFD <- 100
+
+panel_names <- c("(A) HIDs and fluorescent lamp", "(B) LEDs", "(C) Sunlight")
+
+# HID_raw <-
+#   fread("~/Dropbox/R/spectrum/HID.csv", skip = 13)
+# 
+# HIDs <-
+#   HID_raw %>%
+#   setnames(., c("wavelength", paste0("ID", 1:(dim(HID_raw)[2] - 1)))) %>%
+#   select(1, HPS_ = 12, MH_ = 21)
+FL_Ocean_raw <-
+  fread("~/Dropbox/materials/SPD_FL.csv") %>%
+  transmute(wavelength = `Wavelength[nm]`, value = FL) %>%
+  na.omit
+
+FL_Ocean_PFD <-
+  smooth.spline(FL_Ocean_raw$wavelength, FL_Ocean_raw$value) %>%
+    predict(., seq(PFD_integrate_min, PFD_integrate_max)) %>%
+    .$y %>%
+  sum
+
+FL_Ocean <-
+  FL_Ocean_raw %>%
+  mutate(value = value * 100 / FL_Ocean_PFD, variable = "FL")
+
+HPS_Ocean_raw <-
+  fread("~/Dropbox/materials/SPD_HPS.txt", skip = 50, nrow = 2000) %>%
+  rename(wavelength = V1, value = V2)
+
+HPS_Ocean_PFD <-
+  smooth.spline(HPS_Ocean_raw$wavelength, HPS_Ocean_raw$value) %>%
+    predict(., seq(PFD_integrate_min, PFD_integrate_max)) %>%
+    .$y %>%
+  sum
+
+HPS_Ocean <-
+  HPS_Ocean_raw %>%
+  mutate(value = value * 100 / HPS_Ocean_PFD, variable = "HPS")
+
+MH_Ocean_raw <-
+  fread("~/Dropbox/materials/SPD_MH.txt", skip = 50, nrow = 2000) %>%
+  rename(wavelength = V1, value = V2)
+
+MH_Ocean_PFD <-
+  smooth.spline(MH_Ocean_raw$wavelength, MH_Ocean_raw$value) %>%
+    predict(., seq(PFD_integrate_min, PFD_integrate_max)) %>%
+    .$y %>%
+  sum
+
+MH_Ocean <-
+  MH_Ocean_raw %>%
+  mutate(value = value * 100 / MH_Ocean_PFD, variable = "MH")
+
+OceanSPDs <-
+  bind_rows(FL_Ocean, HPS_Ocean, MH_Ocean) %>%
+  mutate(panel = panel_names[1])
+
+Absorptances <-
+  fread("~/Dropbox/materials/SpectrumCucumber.csv") %>%
+  filter(Trtm %in% c("W", "WFR", "FL")) %>%
+  mutate(wavelength = as.numeric(wavelength)) %>%
+  filter(variable == "absorption", Trtm == "W")
+
+Sun <-
+  fread("~/Dropbox/materials/Sunlight_JIS.csv") %>%
+  setnames(c("wavelength", "Sunlight")) %>%
+  left_join(., Absorptances, by = "wavelength") %>%
+  transmute(wavelength, Sun = Sunlight, Shade = Sunlight * (100 - ave), Absorptance = ave)
+
+# Sun: JIS C8904-3
+
+LEDs <-
+  fread("~/Dropbox/materials/SPD_FL.csv") %>%
+  transmute(wavelength = `Wavelength[nm]`, W, FR, B = B_HL, R = R_SR) %>%
+  SPDnorm(from = 350, to = 750, integratedPFD = IntegratePFD) %>%
+  gather(variable, value, -wavelength) %>%
+  mutate(panel = panel_names[2]) %>%
+  na.omit
+
+SPD_labels <-
+  data_frame(variable = c("FL", "MH", "HPS", "B", "R", "FR", "W", "Sun", "Shade"),
+             wavelength = c(435, 520, 570, 448, 660, 735, 460, 450, 750),
+             value = c(2.2, .6, 3, 4, 4.2, 3.8, 1.3, 0.6, 2),
+             label = c("FL", "MH", "HPS", "B", "R", "FR", "W", "Sun", "Leaf transmitted sunlight"),
+             panel = rep(panel_names,  c(3, 4, 2)))
+
+SPDs <-
+  Sun %>%
+  SPDnorm(from = 350, to = 750, integratedPFD = IntegratePFD) %>%
+  select(-Absorptance) %>%
+  gather(variable, value, -wavelength) %>%
+  mutate(panel = panel_names[3]) %>%
+  bind_rows(., OceanSPDs, LEDs) %>%
+  filter(between(wavelength, 380, 820)) %>%
+  ggplot(aes(x = wavelength, y = value, group = variable, col = variable, linetype = variable)) +
+  theme_bw2() +
+  geom_rect(aes(xmin = 700, xmax = 750, ymin = 0, ymax = +Inf), fill = "grey90", col = NA) +
+  geom_line() +
+  geom_text(data = SPD_labels, aes(x = wavelength, y = value, label = label)) +
+  scale_linetype_manual(values = c(1, 1, 3, 2, 4, 2, 2, 1, 4)) +
+  scale_color_manual(values = c("blue", "black", "darkred", "orange", "purple", "red", "grey50", "black", "black")) +
+  facet_grid(panel ~ .) +
+  gg_xy(c(380, 820, 0, 4.5)) +
+  xlab("Wavelength [nm]") + ylab(u_SPFD("Spectral photon flux density"))
+
+CapSPD <-
+  "Fig.
+S1  Spectral photon flux density distribution of light.
+The distributions at a PFD of 100 µmol m<sup>--2</sup> s<sup>--1</sup> within 400--750 nm are shown.
+The far-red waveband (700--750 nm) is filled in grey."
+```
+
+```{r FigSPD, eval = evalFig, fig.cap = CapSPD}
+SPDs
+```
+
+| Light (abbreviation)            | Model code        | Supplier                        | Measuring instrument              |
+|:--------------------------------|:------------------|:--------------------------------|:----------------------------------|
 | Fluorescent lamp (FL)           | FPL55EX-N         | IWASAKI ELECTRIC CO., LTD.      | HR2000 (Ocean Optics Inc.)        |
@@
 
-The SPD of sunlight was adapted from JIS C8904-3.
+The SPD of sunlight was adapted from JIS C 8904-3.
 The SPD of the shaded sunlight was calculated from the SPD of sunlight and the transmittance spectrum of a cucumber leaf (Murakami et al. 2016).
 
-```{r FigSPD, eval = evalFig, fig.cap = CapSPD}
-SPDs
-```
+#### Supplementary Reference
+JIS C 8904-3. 2011. [Photovoltaic devices-Part 3: Measurement principles for photovoltaic(PV) solar devices with reference spectral irradiance data](http://www.jisc.go.jp/app/pager?id=2769864).

### 2016-07-26 Main.Rmd
明日には0稿完成。3347 words.

@@
     theme: sandstone
-    self_contained: F
+    self_contained: T
     fig_caption: true
@@
 
-opts_chunk$set(echo = FALSE, fig.width = 5, fig.height = 5, out.width = '500pixel', out.heit = '500pixel', dpi = 200, fig.align = "center", message = FALSE, warning = FALSE, cache = F, eval = T)
+opts_chunk$set(echo = FALSE, fig.width = 5, fig.height = 5,
+               out.width = '500pixel', out.heit = '500pixel', dpi = 200,
+               message = FALSE, warning = FALSE, cache = F, eval = T)
 ```
@@
   data_frame(X = rep(X_range, times = 2),
-           ETR = c(sqrt(dbeta(X_range, 4.5, 3)) * 1.1, sqrt(dbeta(X_range, 3, 4.5))),
+           ETR = c(sqrt(dbeta(X_range, 4.5, 3.5)) * 1.1, sqrt(dbeta(X_range, 3, 5))),
            Trtm = rep(c("PSII-leaves", "PSI-leaves"), each = X_div))
@@
   scale_linetype_manual(values = c(2, 1)) +
-  scale_x_continuous(breaks = c(0.1, 0.9), limits = c(0.05, 0.95), labels = c("PSI-biased", "PSII-biased")) +
-  xlab("PSII-biased level of measuring light") +
+  scale_x_continuous(breaks = c(0.07, 0.92), limits = c(0.05, 0.95), labels = c("PSI-biased", "PSII-biased")) +
+  xlab("PSII/PSI-biased level of measuring light") +
   ylab("Relative electron transport rate") +
@@
 
-  The photosynthetic rate is one of the most important and fundamental phenotype in the plant sciences.
+  The photosynthetic rate is one of the most important and fundamental trait of the plant.
   The rates are measured, evaluated, and compared among the leaves cultivated under different conditions, typically the control and treatment.
@@
   In that experiment, cucumber seedlings were grown under white light-emitting diode (LED) light without and with supplemental far-red (FR) LED light (W and WFR), and subsequently the *P*~n~ of the leaves were compared under BR-light and a sunlight-like SPD of light.
-  The *P*~n~ of W-leaves was greater than that of WFR-leaves under BR-light, while the rates were comparable---or slightly greater in the WFR-leaves---under artificial sunlight [@Murakami_et_al2016PP].
-  Based on the results obtained from the measurement under BR-light, the prospective growth rate of WFR-plants is evaluated to be smaller than that of W-plants despite the comparable *P*~n~ under the sunlight.
+  The *P*~n~ of W-leaves was greater than that of WFR-leaves under BR-light, while the rates were comparable under artificial sunlight [@Murakami_et_al2016PP].
+  Based on the results obtained from the measurement under BR-light, the prospective growth rate of WFR-plants is evaluated to be smaller than that of W-plants despite the comparable rates under the sunlight.
   **In other words, the SPDs of light incident on the leaf during growth and measurement interacted on the *P*~n~**.
@@
 
-  In this short article, we introduce several articles reporting the interaction and the likely causes---the distribution of the excitation energy between the photosystems.
-  Subsequently we suggest the situations where the interaction should be cared.
+  In this short article, we introduce a likely cause of the interaction and several articles reporting the interaction.
+  We then suggest the situations where the interaction should be cared.
   We also discuss the good practice for the selection of the SPD of measuring light used for *P*~n~ measurements.
-  The SPD of light affects the photosynthesis through the other mechanisms, such as the stomatal response [@Shimazaki_et_al2007AnnRev], photoinhibition [@Zavafer_et_al2015JPP], and the light-penetrating depth within a leaf [@Terashima_et_al2009PCP].
+  The SPD of light affects the photosynthesis through the other mechanisms, such as the stomatal response [@Shimazaki_et_al2007AnnRev], the photoinhibition [@Zavafer_et_al2015JPP], and the light-penetrating depth within a leaf [@Terashima_et_al2009PCP].
   Although these subjects are not referred in this article, the cited review articles on these topics are available.
@@
 
-  The knowledge about the photosynthetic electron transport is required to understand the mechanism of the interaction.
-  Light energy absorbed by a leaf drives the electron transport, and thereby the photosynthetic O~2~ evolution and CO~2~ uptake.
+  Fundamental knowledge about the photosynthetic electron transport is required to understand the mechanism of the interaction.
+  Light energy absorbed by a leaf drives the electron transport and thereby the photosynthetic O~2~ evolution and CO~2~ uptake.
   In higher plants, the photosynthetic electron transport chain is anchored by photochemical reactions that occur at two types of photosystems, PSII and PSI.
   The reactions are powered by excitation energy derived from absorbed photons.
-  **The excitation energy  the photosystems and their anntena complexes is transferred to the reaction centers, and then consumed photochemical reactions in the unit of mol**
-  **Note that the term "energy" is used in **
-  **The two photochemical reactions at PSII and PSI enables electron transfer against the redox potential (called the Z scheme).**
+  The excitation energy transferred to the reaction centers of the photosystems is consumed by the photochemical reactions in units of moles.
+  The serial photochemical reactions at PSII and PSI enables electron transfer against the redox potential (called the Z scheme).
   Because the photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) through the thylakoid membrane is limited by the slowest step (Fig. 1).
-  When PSII absorbs excess excitation energy under PSII-biased light, the energy distribution to PSI limits the ETR and thus the photochemical quantum yield of PSII should be lowered (Fig. 1A).
-  When PSI absorbs excess excitation energy, the energy distribution to PSII limits the ETR and the yield of PSI should be lowered (Fig. 1D).
-  In both cases, the excesss energy is dissipated as heat and fluorescence, and thus the entire photosynthetic quantum yield---ETR per absorbed PFD---becomes smaller.
+  When PSII absorbs excess excitation energy under PSII-biased light, the energy distribution to PSI limits the ETR and thus the photochemical quantum yield of PSII should be lowered (Fig. 1C).
+  When PSI absorbs excess excitation energy, the energy distribution to PSII limits the ETR and the yield of PSI should be lowered (Fig. 1B).
+  In both cases, the excesss energy is dissipated as heat and fluorescence, and thus the entire photosynthetic quantum yield---ETR per absorbed photons---becomes smaller.
   An imbalance excitation between the photosystems can harm leaves by generating reactive oxygen species, which cause oxidative damage to chloroplast components [for reviews, see @Asada1999AnnRev; @Asada2006PP].
@@
   PSII and PSI represent different light absorption spectral distributions due to the difference in the compositions of binding pigments, mainly chl *a* and chl *b*.
-  Within the chl absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [@Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
-  Such an umbalanced distribution was caused by the facts that only chl *a* can absorb the longer wavelengths of light and that PSI contains a greater amount of chl *a* than PSII.
-  On contrary, monochromatic light at shorter wavelengths (< 680--690 nm) is estimated to be preferentially absorbed by PSII, or evenly absorbed by both photosystems [@Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
-  These wavelength dependencies of the EED is a determinant of the distribution under a given SPD of light.
-  In several studies of the SPD acclimation of the photosynthetic apparatus, light with a given SPD is categorized as either PSII- or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI.
-  A given SPD of light is classified according to the PFD in the FR waveband in the relative context.
-  For instance, a SPD of light, which is evenly absorbed by PSII and PSI in PSII-leaves, can overexcite PSII in PSI-leaves (Fig. 1AC).
+  Within the chlorophyll (chl) absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [@Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
+  Such an imbalanced excitation was caused by the facts that only chl *a* can absorb the longer wavelengths of light and that PSI contains a greater amount of chl *a* than PSII.
+  In contrast, monochromatic light at shorter wavelengths (< 680--690 nm) is estimated to be preferentially absorbed by PSII, or evenly absorbed by both photosystems [@Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
+  These wavelength dependencies of the EED is a determinant of the EED under a given SPD of light.
+  In several studies of the SPD acclimation of the photosynthetic apparatus, light with a given SPD is categorized as either PSII- or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI based on the relative scale, not on the absolute scale.
+  For instance, a SPD of light, which is evenly absorbed by PSII and PSI in PSII-light-grown leaves (Fig. 1A), can overexcite PSII in PSI-light-grown leaves (Fig. 1C).
   Thus, the terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context.
@@
 
-  The SPD of growth light affects the EED properties of a leaf, which modifies the responses of the ETR and thereafter *P*~n~ to the SPD of measuring light.
+  The SPD of growth light affects the EED properties of a leaf, which modifies the responses of the ETR and thereafter *P*~n~ to the SPD of measuring light (Fig. 2).
   Thus, the SPDs of growth light and measuring light do not only directly affect the *P*~n~ but also indirectly affect it through their interaction.
   The expected interactions have been reported in several studies [@Chow_et_al1990PNAS; @Walters_Horton1995aPlanta; @Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
-  In their pioneering study on *Pisum sativum*, @Chow_et_al1990PNAS grew plants under cool-white fluorescent lamps with yellow Plexglas (FR-poor PSII-light) and incandescent bulbs with red Plexglas (FR-rich PSI-light) and measured the photosynthetic quantum yield of O~2~ evolution---O~2~ evolution rate per absorbed photons by leaf---under PSII- and PSI-light.
-  When measured under PSII-light, the yield was higher in PSII-light-grown leaves; when measured under PSI-light, the yield was higher in PSI-light-grown leaves.
+  In their pioneering study on *Pisum sativum*, @Chow_et_al1990PNAS grew plants under light provided by cool-white fluorescent lamps with yellow Plexglas (FR-poor PSII-light) and incandescent bulbs with red Plexglas (FR-rich PSI-light), and subsequently measured the photosynthetic quantum yield of O~2~ evolution---O~2~ evolution rate per absorbed photons by leaf---under the PSII- and PSI-light.
+  When measured under the PSII-light, the yield was higher in the PSII-light-grown leaves; when measured under the PSI-light, the yield was higher in the PSI-light-grown leaves.
   A similar trends were observed in *Arabidopsis thaliana* [@Walters_Horton1995aPlanta] and *Cucumis sativus* [@Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
-  @Walters_Horton1995aPlanta showed the interaction in the O~2~ evolution yield using halogen lamp and color-conversion filter.
-  @Hogewoning_et_al2012PC found the interaction in the *P*~n~ using artificial sunlight (PSII-light) and shadelight (PSI-light) as growth light and 19 monochromatic LED light as measuring light.
-  They demonstrated that the interaction can occur 違う組合せでも**.
+  @Hogewoning_et_al2012PC observed the interaction in the photosynthetic quantum yield of CO~2~ uptake using artificial sunlight (PSII-light) and shadelight (PSI-light) as growth light and 19 monochromatic LED light as measuring light.
+  They demonstrated that the interaction cannot occur only in the case growth light was used as measuring light but also in the case the other SPDs of light was used.
   @Murakami_et_al2016PP showed the interaction in the *P*~n~ using white LED light without or with FR LED light (PSII-light and PSI-light) as growth light and BR-light (PSII-light) and artificial sunlight (PSI-light) as measuring light.
@@
 
-  <!-- A similar trends were observed in other studies on *Arabidopsis thaliana* [@Walters_Horton1995aPlanta] and *Cucumis sativus* [@Hogewoning_et_al2012PC; @Murakami_et_al2016PP] (Table. 1). -->
-
-  The distribution properties of a leaf seems to be tuned to the SPD of growth light, and thereby is expected to perform a higher photosynthetic quantum yield under **light the same PSII-biased level to growth light** (Fig.
-2).
-  When leaves grown under different SPDs of light are compared and evaluated under a single-level SPD of light, the results should be inevitably biased by the interaction.
+  These reports might suggest that the EED propertiy of a leaf is tuned to the **PSII/PSI-biased level of** growth light.
+  It is expected that a leaf performs a higher ETR per absorbed photons by the photosystems under **measuring light with the same PSII/PSI-biased level to that of growth light** (Fig. 2).
+  When leaves grown under different SPDs of light are compared and evaluated under a single-level SPD of light, the results should be inevitably biased depending on the SPD of measuring light.
 
@@
 
-  This interaction may have considerable impact on the *P*~n~ especially under the light limited and/or CO~2~ saturated conditions, where the extent of the ETR is dominant factor for the photosynthetic CO~2~ uptake rate [@vonCaemmerer_Farquhar1981Planta].
+  This interaction may have considerable impact on the *P*~n~ especially in the measurements under the low PPFD and/or high CO~2~ concentration, where the extent of the ETR is dominant factor for the photosynthetic CO~2~ uptake rate [@vonCaemmerer_Farquhar1981Planta].
   In such conditions, any bias in the ETR is directly reflected in the *P*~n~.
-  Therefore, the *P*~n~ at light-limited conditions should be measured with particular attentions on the interaction.
+  Therefore, the *P*~n~ at light-limited conditions should be measured with particular attention on the interaction.
   <!-- In contrast, under a higher PFDs and/or CO~2~ limtied conditions, the *P*~n~ is determined by the CO~2~ fixation process in the Calvin cycle rather than the ETR. -->
@@
 
-  The mechanisms of the SPD acclimation of the EED property are not yet fully elucidated [see @Murakami_et_al2016PP].
+  The mechanisms of the SPD acclimation of the EED property have not yet been fully elucidated [see @Murakami_et_al2016PP].
   <!--' @Walters_Horton1995aPlanta confirmed a typical adjustment in the photosystem stoichiometry in response to the slight difference in the SPD of growth light. -->
@@
   <!--' Chow and coworkers also reported  -->
-  Considering the sensitively adjusted photosystem stoichiometry in response to the SPD of light [@Walters_Horton1995aPlanta], the interaction may be always taken into account whenever the *P*~n~ and related parameters are evaluated.
-  The impacts of the interaction on the photosynthetic rates should be payed particular attention when the measured leaves are expected to represent different EED properties.
+  Considering the sensitively adjusted the photosystem stoichiometry in response to the SPD of growth light reported in  @Walters_Horton1995aPlanta, the interaction should be always taken into account whenever the *P*~n~ and related parameters are evaluated.
+  The impacts of the interaction on the *P*~n~ should be paid particular attention, at least when the measured leaves are expected to represent different EED properties.
 
@@
   On the other hand, several recent papers suggest the significance of supplemental FR on the plant growth and development [for a review, see @Demote-Mainard_et_al2016EEB].
-  Since FR overexcites PSI, leaves grown under PSII-light supplemented with FR LED can become relatively PSI-leaves like EED property compared to those grown without supplemental FR.
-  Therefore, comparing the *P*~n~ of leaves grown with and without supplemental FR using BR-light might result in typical biased evaluation caused by the interaction, as is demonstrated in the previous report [@Murakami_et_al2016PP].
+  Since FR overexcites PSI, leaves grown under PSII-light supplemented with FR LED can represent relatively PSI-leaves like EED property compared to those grown without supplemental FR.
+  Therefore, comparing the *P*~n~ of leaves grown with and without supplemental FR using BR-light might result in typical biased evaluation caused by the interaction, as demonstrated in the previous report [@Murakami_et_al2016PP].
 
@@
 
-  Further investigation is required to elucidate the extent of the interaction in the *P*~n~ under the above mentioned conditions.
-  Note that such an interaction should be taken into account in the evaluations of the other photosynthesis-related characteristic, such as chl fluorescence parameters.
-  The overexicitation of PSII (or PSI) results in the lowered photochemical yield at PSII (or PSI) [e.g. Hogewoning_et_al2012PC].
-  Imbalance in the excitation balance between the photosystems is supposed to acceralate the photoinhibition [@].
-  Chl fluorescence parameters such as *F*~q~′/*F*~m~′ (PSII operating efficiency, also known as Φ~PSII~ and *Y*~II~) and photoinhibition indicator such as **Fv/Fm** should be measured with particular care.
+  Note that such an interaction might have impacts on the other characteristics related to the photosynthetic electron transport, such as chl fluorescence parameters and the photoinhibition indicators.
+  The overexicitation of PSII (or PSI) results in the lowered photochemical yield at PSII (or PSI) [e.g.
+@Hogewoning_et_al2012PC; @Laisk_et_al2014BBA], and the imbalance in the excitation should hastes the photoinhibition caused by the reactive oxygen species.
+  Evaluation of these characteristics should also be measured with particular care on the interaction.
 
-# How the photosynthetic responses should be measured
+# How the photosynthesis should be measured
 
-  Ideally, the photosynthetic rates should be measured under the *in situ* conditions.
-  In the prospective study focusing on the plant growth after the *P*~n~ measurements, the rates should be measured under the SPD of light the plant will subject to.
+  Ideally, the photosynthetic rates and related parameters should be measured under the *in situ* conditions.
+  In the prospective study focusing on the plant growth after the measurements, the measurements should be made under the SPD of light the plant will subject to.
   For instance, evaluation of the photosynthesis of the transplants grown under artificial lighting [e.g.
 @Kozai2007POP] should be made under sunlight because they are subsequently transferred to a greenhouse and cultivated under sunlight.
-  <!-- For instance, commercial transplants are sometimes raised in a closed system with artificial lighting [e.g.
-@Kozai2007POP], and subsequently transferred to a greenhouse and cultivated under sunlight.
--->
-  <!-- Therefore, in comparisons of light sources with different SPDs for the transplant production, *P*~n~ measurements should be made under sunlight. -->
   Note that the effect of the interaction seems to be less prominent than those of the other factors, such as the incident PPFD.
-  The *P*~n~ measurements under sunlight, which usually generates fluctuations in the incident PFD, should be avoided and thus the measurements should be made under the artificial light sources to ensure the reproducibility and reliability of the research.
-  The use of artificial light sources will lower the uncertainty caused by the fluctuations in the incident PPFD at the expense of the biases possibly caused by the interaction.
+  The measurements under sunlight, which usually causes fluctuations in the incident PPFD, should be avoided and thus the measurements should be made under the artificial light sources to ensure the reproducibility and reliability of the research.
+  The use of artificial light sources will mitigate the uncertainty caused by the fluctuations in the incident PPFD at the expense of the biases possibly caused by the interaction.
   This is because the SPD of light from an artificial light source is generally by far different from that of *in situ* light.
@@
 
-  In the retrospective study elucidating the causes of the differences in the experimental groups, the rates should be measured under the SPDs of light the plants recieved during the treatments.
+  In the retrospective study aiming to elucidate the causes of the differences between the experimental groups, the measurements should be made under the SPDs of light the plants recieved during the treatments.
   <!-- When the aim of the research is to analyze the origins of the differences in the growth of the plants subject to several light treatments, the rates should be measured under the SPDs of light the plants recieved.
 -->
-  For instance, when the difference in the resultant dry weight between the plants grown under white LEDs and fluorescent lamps are analyzed and the *P*~n~ is used for the explanatory variable, the measurements should be made using white LED for the plants grown under white LEDs light and using fluorescent lamps for those grown under fluorescent lamps.
+  For instance, when the difference in the resultant dry weight between the plants grown under white LEDs and fluorescent lamps are analyzed and the *P*~n~ is used for the explanatory variable, the measurements should be made using the white LEDs for the plants grown under white LEDs light and using the fluorescent lamps for those grown under fluorescent lamps.
+  In both the prospective and retrospective studies, these simple solutions will eliminate the problems caused by the interaction.
 
-  In both the prospective and retrospective studies, these simple solutions will eliminate the problems caused by the interaction.
-  On the other hand, if the SPD of light the leaves will receive is not predetermined, then *P*~n~ should be measured under both PSII- and PSI-light.
-  Researchers had better describe the "general" photosynthetic characteristics of the leaves in these kind of studies.
-  Therefore, the interaction should be tested so as not to make biased evaluation.
-  If the significant interaction is not detected in two-way ANOVA, the main effect of the treatment can be assessed.
-  If any the interaction, the results should not be generalized.
-  The responses of the rates to both PSII- and PSI-light should be measured, compared, and reported in the paper.
+  If the SPD of light the leaves will receive is not predetermined, then the measurements should be made under several levels of SPDs of light including PSII- and PSI-light.
+  Researchers had better describe the "general" characteristics of the leaves in these kind of studies.
+  **Therefore, the interaction should be tested so as not to make biased evaluation.**
+  **If the significant interaction is not detected in two-way ANOVA, the main effect of the treatment can be assessed.**
+  **If any the interaction, the results should not be generalized.**
+  **The responses of the rates to both PSII- and PSI-light should be measured, compared, and reported in the paper.**
   When the measuments were made only under a single-level of SPD of measuring light because of unavoidable circumstances, the light source must be declared in the materials and methods section so that readers can follow the SPD.
@@
   The *P*~n~ measured under a single-level SPD of light is only an aspect of the photosynthetic characteristics of the leaf.
-  The obtained results must be discussed in connection with the SPD of measuring light.
+  Therefore, the obtained results must be discussed in connection with the SPD of measuring light.
+  Further carefull investigations are required to elucidate the extent of the interaction in the *P*~n~ under the above mentioned conditions.
   Evaluation of the photosynthesis should be made under the *in situ* conditions or multilevels of SPDs of measuring light so that the evaluation is not biased by the interaction.
@@
 
-```{r child = "~/Dropbox/Publish/ECB2016Review/Sup1.Rmd", fig.width = 7.5, fig.height = 7.5, out.width = '500pixel', out.heit = '500pixel', dpi = 200}
+```{r child = "~/Dropbox/Publish/ECB2016Review/Sup1.Rmd"}
 

### 2016-07-26 Sup1.Rmd
明日には0稿完成。3347 words.

@@
 
-panel_names <- c("(A) HIDs and fluorescent lamp", "(B) LEDs", "(C) Sunlight")
+panel_names <- c("(A) HIDs and fluorescent lamps", "(B) LEDs", "(C) Incident and leaf transmitted sunlight")
 
@@
              value = c(2.2, .6, 3, 4, 4.2, 3.8, 1.3, 0.6, 2),
-             label = c("FL", "MH", "HPS", "B", "R", "FR", "W", "Sun", "Leaf transmitted sunlight"),
+             label = c("FL", "MH", "HPS", "B", "R", "FR", "W", "Sunlight", "Leaf transmitted sunlight"),
              panel = rep(panel_names,  c(3, 4, 2)))
@@
   scale_color_manual(values = c("blue", "black", "darkred", "orange", "purple", "red", "grey50", "black", "black")) +
-  facet_grid(panel ~ .) +
+  # facet_grid(panel ~ .) +
+  facet_wrap(~ panel, ncol = 1) +
   gg_xy(c(380, 820, 0, 4.5)) +
@@
   "Fig.
-S1  Spectral photon flux density distribution of light.
-The distributions at a PFD of 100 µmol m<sup>--2</sup> s<sup>--1</sup> within 400--750 nm are shown.
+S1  The spectral photon flux density distributions of light provided by (A) high-intensity dischage lamps (HIDs) and fluorescent lamps, (B) light-emitting diodes (LEDs), and (C) incident and leaf transmitted sunlight (see also Table S1).
+The distributions at a photon flux density of 100 µmol m<sup>--2</sup> s<sup>--1</sup> within 400--750 nm are shown.
+The distribution of sunlight was adopted from JIS C 8904-3.
+The distribution of the leaf transmitted sunlight was calculated from that of sunlight and the transmittance spectrum of a cucumber leaf (Murakami et al.
+2016).
 The far-red waveband (700--750 nm) is filled in grey."
@@
 
-| Light (abbreviation)            | Model code        | Supplier                        | Measuring instrument              |
-|:--------------------------------|:------------------|:--------------------------------|:----------------------------------|
-| Fluorescent lamp (FL)           | FPL55EX-N         | IWASAKI ELECTRIC CO., LTD.      | HR2000 (Ocean Optics Inc.)        |
-| Metalhalide lmap (MH)           | M220FCELS-W/BUD   | IWASAKI ELECTRIC CO., LTD.      | HR2000 (Ocean Optics Inc.)        |
-| High-pressure sodium lamp (HPS) | NH220FLS          | IWASAKI ELECTRIC CO., LTD.      | HR2000 (Ocean Optics Inc.)        |
-| Blue LED (B)                    | HBL3-3S55-LE      | Tricon Co.                      | MS-720 (EKO Instruments Co. Ltd.) |
-| Red LED (R)                     | SRK3-3A80-LE      | Tricon Co.                      | MS-720 (EKO Instruments Co. Ltd.) |
-| Far-red LED (FR)                | L735-36AU         | Epitex Inc.                     | MS-720 (EKO Instruments Co. Ltd.) |
-| White LED (W)                   | NSPW310DS         | Nichia Chemical Industries Ltd. | MS-720 (EKO Instruments Co. Ltd.) |
+Table S1.  Description of the light sources and the instruments used for the measurements of the spectral photon flux density distributions.
 
-The SPD of sunlight was adapted from JIS C 8904-3.
-The SPD of the shaded sunlight was calculated from the SPD of sunlight and the transmittance spectrum of a cucumber leaf (Murakami et al. 2016).
+| Light source (abbreviation)     | Model code                    | Measuring instrument              |
+|:--------------------------------|:------------------------------|:----------------------------------|
+| Fluorescent lamp (FL)           | FPL55EX-N<sup>\*1</sup>       | HR2000 (Ocean Optics Inc.)        |
+| Metal halide lmap (MH)          | M220FCELS-W/BUD<sup>\*1</sup> | HR2000 (Ocean Optics Inc.)        |
+| High-pressure sodium lamp (HPS) | NH220FLS<sup>\*1</sup>        | HR2000 (Ocean Optics Inc.)        |
+| Blue LED (B)                    | HBL3-3S55-LE<sup>\*2</sup>    | MS-720 (EKO Instruments Co. Ltd.) |
+| Red LED (R)                     | SRK3-3A80-LE<sup>\*2</sup>    | MS-720 (EKO Instruments Co. Ltd.) |
+| Far-red LED (FR)                | L735-36AU<sup>\*3</sup>       | MS-720 (EKO Instruments Co. Ltd.) |
+| White LED (W)                   | NSPW310DS<sup>\*4</sup>       | MS-720 (EKO Instruments Co. Ltd.) |
+
+^\*1^IWASAKI ELECTRIC CO., LTD., Tokyo, Japan; ^\*2^Tricon Co., Shimane, Japan; ^\*3^Epitex Inc., Kyoto, Japan; ^\*4^Nichia Chemical Industries Ltd., Tokushima, Japan.
+
+<!-- | Light (abbreviation)            | Model code        | Supplier                        | Measuring instrument              | -->
+<!-- |:--------------------------------|:------------------|:--------------------------------|:----------------------------------| -->
+<!-- | Fluorescent lamp (FL)           | FPL55EX-N         | IWASAKI ELECTRIC CO., LTD.      | HR2000 (Ocean Optics Inc.)        | -->
+<!-- | Metal halide lmap (MH)          | M220FCELS-W/BUD   | IWASAKI ELECTRIC CO., LTD.      | HR2000 (Ocean Optics Inc.)        | -->
+<!-- | High-pressure sodium lamp (HPS) | NH220FLS          | IWASAKI ELECTRIC CO., LTD.      | HR2000 (Ocean Optics Inc.)        | -->
+<!-- | Blue LED (B)                    | HBL3-3S55-LE      | Tricon Co.                      | MS-720 (EKO Instruments Co. Ltd.) | -->
+<!-- | Red LED (R)                     | SRK3-3A80-LE      | Tricon Co.                      | MS-720 (EKO Instruments Co. Ltd.) | -->
+<!-- | Far-red LED (FR)                | L735-36AU         | Epitex Inc.                     | MS-720 (EKO Instruments Co. Ltd.) | -->
+<!-- | White LED (W)                   | NSPW310DS         | Nichia Chemical Industries Ltd. | MS-720 (EKO Instruments Co. Ltd.) | -->
 

### 2016-07-27 Main.Rmd
第０稿完成。3327 words

@@
 ---
-title: "On the spectral photon flux density distribution of light during the measurements of the leaf photosynthetic rate"
-author: "Keach Murakami, Ryo Matsuda, Kazuhiro Fujiwara"
-date: "June 24, 2016"
+title: "A practical guide for selecting the spectral photon flux density distribution of light during the measurements of the leaf photosynthetic rate"
+author: "Keach Murakami^1\\*^, Ryo Matsuda^1^, Kazuhiro Fujiwara^1^"
 bibliography: ~/Dropbox/R/List.bib
@@
     theme: sandstone
-    self_contained: T
+    self_contained: TRUE
     fig_caption: true
@@
   # word_document:
-#   toc: true
-#   fig_caption: true
   #   pandoc_args: [
@@
 if(evalFig){
-devtools::source_url("https://raw.githubusercontent.com/KeachMurakami/Sources/master/Startup.R")
+devtools::source_url("https://raw.githubusercontent.com/KeachMurakami/Sources/master/Startup_silent.R")
 } else {
@@
 opts_chunk$set(echo = FALSE, fig.width = 5, fig.height = 5,
-               out.width = '500pixel', out.heit = '500pixel', dpi = 200,
+               out.width = '500pixel', out.height = '500pixel', dpi = 100,
                message = FALSE, warning = FALSE, cache = F, eval = T)
@@
   "Fig.
-2  The conceptual diagram of the photosynthetic electron transport rates (ETR) of leaves grown under PSII-light (PSII-leaves) and PSI-light (PSI-leaves) in response to the PSII/PSI-light level of measuring light."
+2  The conceptual diagram of the photosynthetic electron transport rates per absorbed photons by the photosystems grown under PSII-light (PSII-leaves) and PSI-light (PSI-leaves) in response to the PSII/PSI-bised level of measuring light."
 ```
@@
 
-Authors: Keach Murakami^1+^, Ryo Matsuda^1^, and Kazuhiro Fujiwara^1^
-
 Affiliations: ^1^Graduate School of Agricultural and Life Sciences, The University of Tokyo
@@
 
+------
+
+**Abstract**
+
+------
+
 **Abbreviations**
-BR-light: blue + red LED light 
+BR-light: blue + red LED light,
 Chl: chlorophyll,
@@
 
-  The photosynthetic rate is one of the most important and fundamental trait of the plant.
-  The rates are measured, evaluated, and compared among the leaves cultivated under different conditions, typically the control and treatment.
+  The photosynthetic rate is one of the most important and fundamental traits of the plant.
+  The rates are measured, evaluated, and compared among the leaves cultivated under different conditions.
   The measured rates are also used for the calculation of the other photosynthetic parameters, such as light, water, and nitrogen use efficiencies.
-  The effectiveness of treatments is sometimes discussed based on the measured photosynthetic rate and calculated parameters in agricultural and horticultural studies.
+  In agricultural and horticultural studies, the effectiveness of treatments is sometimes discussed based on the measured photosynthetic rate and calculated parameters. 
   Therefore, the accurate measurements of the photosynthetic rate must be essential.
+
   A number of studies have reported that the relative spectral photon-flux-density (PFD) distribution (SPD) of light used for the measurement (i.e.
@@
   Our recent study, indeed, experimentally demonstrated this problem in the *P*~n~ measurements [@Murakami_et_al2016PP].
-  In that experiment, cucumber seedlings were grown under white light-emitting diode (LED) light without and with supplemental far-red (FR) LED light (W and WFR), and subsequently the *P*~n~ of the leaves were compared under BR-light and a sunlight-like SPD of light.
+  In that experiment, cucumber seedlings were grown under white light-emitting diode (LED) light without and with supplemental far-red (FR) LED light (W and WFR), and subsequently the *P*~n~ of the leaves were compared under BR-light and light with the SPD resembling that of sunlight.
   The *P*~n~ of W-leaves was greater than that of WFR-leaves under BR-light, while the rates were comparable under artificial sunlight [@Murakami_et_al2016PP].
-  Based on the results obtained from the measurement under BR-light, the prospective growth rate of WFR-plants is evaluated to be smaller than that of W-plants despite the comparable rates under the sunlight.
-  **In other words, the SPDs of light incident on the leaf during growth and measurement interacted on the *P*~n~**.
-  If the plants were evaluated without considering the interactions, the selection and decision might be distorted.
+  Based on the results obtained from the measurement under BR-light, the prospective growth rate of WFR-plants may be evaluated to be smaller than that of W-plants despite the comparable rates under the sunlight.
 
-  In this short article, we introduce a likely cause of the interaction and several articles reporting the interaction.
+  The effect of the SPD of growth light on the *P*~n~ depended on the level of the SPD of measuring light.
+  In other words, the SPDs of growth light and measuring light interacted on the *P*~n~ of a leaf.
+  In this short article, we introduce a plausible cause of the interaction and several articles reporting the interaction.
   We then suggest the situations where the interaction should be cared.
@@
 
-# How the interaction is generated
+# How the interaction is generated?
 
@@
   The serial photochemical reactions at PSII and PSI enables electron transfer against the redox potential (called the Z scheme).
-  Because the photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) through the thylakoid membrane is limited by the slowest step (Fig. 1).
+  Because the photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) through the thylakoid membranes should be limited by the slowest step (Fig. 1).
   When PSII absorbs excess excitation energy under PSII-biased light, the energy distribution to PSI limits the ETR and thus the photochemical quantum yield of PSII should be lowered (Fig. 1C).
   When PSI absorbs excess excitation energy, the energy distribution to PSII limits the ETR and the yield of PSI should be lowered (Fig. 1B).
-  In both cases, the excesss energy is dissipated as heat and fluorescence, and thus the entire photosynthetic quantum yield---ETR per absorbed photons---becomes smaller.
+  In both cases, the excess energy is dissipated as heat and fluorescence, and thus the entire photosynthetic quantum yield---ETR per absorbed photons by the leaf---becomes smaller.
   An imbalance excitation between the photosystems can harm leaves by generating reactive oxygen species, which cause oxidative damage to chloroplast components [for reviews, see @Asada1999AnnRev; @Asada2006PP].
@@
   Within the chlorophyll (chl) absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [@Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
-  Such an imbalanced excitation was caused by the facts that only chl *a* can absorb the longer wavelengths of light and that PSI contains a greater amount of chl *a* than PSII.
+  Such an imbalanced excitation is caused by the facts that only chl *a* can absorb the longer wavelengths of light and that PSI contains a greater amount of chl *a* than PSII.
   In contrast, monochromatic light at shorter wavelengths (< 680--690 nm) is estimated to be preferentially absorbed by PSII, or evenly absorbed by both photosystems [@Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
   These wavelength dependencies of the EED is a determinant of the EED under a given SPD of light.
-  In several studies of the SPD acclimation of the photosynthetic apparatus, light with a given SPD is categorized as either PSII- or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI based on the relative scale, not on the absolute scale.
+  In several studies of the SPD acclimation of the photosynthetic apparatus, light with a given SPD is categorized as either PSII- or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI
+  This categorization is defined in the relative scale, not in the absolute scale.
   For instance, a SPD of light, which is evenly absorbed by PSII and PSI in PSII-light-grown leaves (Fig. 1A), can overexcite PSII in PSI-light-grown leaves (Fig. 1C).
@@
 
-  Apparently, the EED is affected by the composition of the thylakoid membrane, especially by the stoichiometry between PSII and PSI.
+  Apparently, the EED at a given SPD of light is also affected by the composition of the thylakoid membrane, especially by the stoichiometry between PSII and PSI.
   The stoichiometry seems to be adjusted to the SPD of growth light.
@@
   <!-- Galka_et_al2012PC -->
-  The adjustments in the EED properties might help the leaves to keep the higher photosynthetic light use efficiency under growth light.
+  The adjustments in the EED properties might help the leaves to keep the high photosynthetic quantum yield under growth light.
   In the short term within an hour, an imbalance in the EED is, at least partly, relieved by the reversible allocation of the light-harvesting antenna complex of PSII (LHCII) between PSII and PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].
@@
 
-  The SPD of growth light affects the EED properties of a leaf, which modifies the responses of the ETR and thereafter *P*~n~ to the SPD of measuring light (Fig. 2).
+  The SPD of growth light affects the EED properties of a leaf, which modifies the responses of the ETR and thereafter the *P*~n~ to the SPD of measuring light.
   Thus, the SPDs of growth light and measuring light do not only directly affect the *P*~n~ but also indirectly affect it through their interaction.
   The expected interactions have been reported in several studies [@Chow_et_al1990PNAS; @Walters_Horton1995aPlanta; @Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
-  In their pioneering study on *Pisum sativum*, @Chow_et_al1990PNAS grew plants under light provided by cool-white fluorescent lamps with yellow Plexglas (FR-poor PSII-light) and incandescent bulbs with red Plexglas (FR-rich PSI-light), and subsequently measured the photosynthetic quantum yield of O~2~ evolution---O~2~ evolution rate per absorbed photons by leaf---under the PSII- and PSI-light.
+  In their pioneering study on *Pisum sativum*, @Chow_et_al1990PNAS grew plants under light provided by cool-white fluorescent lamps with yellow Plexglas (FR-poor PSII-light) and incandescent bulbs with red Plexglas (FR-rich PSI-light), and subsequently measured the photosynthetic quantum yield of O~2~ evolution---O~2~ evolution rate per absorbed photons by the leaf---under the PSII- and PSI-light.
   When measured under the PSII-light, the yield was higher in the PSII-light-grown leaves; when measured under the PSI-light, the yield was higher in the PSI-light-grown leaves.
-  A similar trends were observed in *Arabidopsis thaliana* [@Walters_Horton1995aPlanta] and *Cucumis sativus* [@Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
+  Similar trends were observed in *Arabidopsis thaliana* [@Walters_Horton1995aPlanta] and *Cucumis sativus* [@Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
   @Hogewoning_et_al2012PC observed the interaction in the photosynthetic quantum yield of CO~2~ uptake using artificial sunlight (PSII-light) and shadelight (PSI-light) as growth light and 19 monochromatic LED light as measuring light.
@@
 
-  These reports might suggest that the EED propertiy of a leaf is tuned to the **PSII/PSI-biased level of** growth light.
-  It is expected that a leaf performs a higher ETR per absorbed photons by the photosystems under **measuring light with the same PSII/PSI-biased level to that of growth light** (Fig. 2).
+  These reports might suggest that the EED property of a leaf is tuned to the PSII/PSI-biased level of growth light.
+  It is expected that a leaf performs a higher ETR per absorbed photons by the photosystems under measuring light with the same PSII/PSI-biased level to that of growth light (Fig. 2).
   When leaves grown under different SPDs of light are compared and evaluated under a single-level SPD of light, the results should be inevitably biased depending on the SPD of measuring light.
 
-# Where the interaction should be cared
+# Where the interaction should be concerned?
 
-  This interaction may have considerable impact on the *P*~n~ especially in the measurements under the low PPFD and/or high CO~2~ concentration, where the extent of the ETR is dominant factor for the photosynthetic CO~2~ uptake rate [@vonCaemmerer_Farquhar1981Planta].
+  This interaction may have considerable impact on the *P*~n~ especially in the measurements under the low PPFD and/or high CO~2~ concentration, where the extent of the ETR is a dominant factor for the photosynthetic rate [@vonCaemmerer_Farquhar1981Planta].
   In such conditions, any bias in the ETR is directly reflected in the *P*~n~.
-  Therefore, the *P*~n~ at light-limited conditions should be measured with particular attention on the interaction.
+  Therefore, the *P*~n~ under these conditions should be measured with particular attention on the interaction.
   <!-- In contrast, under a higher PFDs and/or CO~2~ limtied conditions, the *P*~n~ is determined by the CO~2~ fixation process in the Calvin cycle rather than the ETR. -->
@@
 
+  Note that such an interaction might have impacts on the other characteristics related to the photosynthetic electron transport, such as chl fluorescence parameters and the photoinhibition indicators.
+  The overexicitation of PSII (or PSI) results in the lowered photochemical yield at PSII (or PSI) [e.g.
+@Hogewoning_et_al2012PC; @Laisk_et_al2014BBA], and the imbalance in the excitation should haste the photoinhibition caused by the reactive oxygen species.
+  Evaluation of these characteristics should also be measured with particular care on the interaction.
+
   The mechanisms of the SPD acclimation of the EED property have not yet been fully elucidated [see @Murakami_et_al2016PP].
@@
   <!--' Chow and coworkers also reported  -->
-  Considering the sensitively adjusted the photosystem stoichiometry in response to the SPD of growth light reported in  @Walters_Horton1995aPlanta, the interaction should be always taken into account whenever the *P*~n~ and related parameters are evaluated.
+  Considering the sensitively adjusted photosystem stoichiometry in response to the SPD of growth light [@Walters_Horton1995aPlanta], the interaction should always be taken into account whenever the *P*~n~ and related parameters are evaluated.
   The impacts of the interaction on the *P*~n~ should be paid particular attention, at least when the measured leaves are expected to represent different EED properties.
@@
   Assimilation light provided by most of artificial light sources contain little FR.
-  In general, fluorescent lamps, metal halide lamps, high-pressure sodium lamps, and blue, red, and white LEDs emit typical PSII-light (Supplemental Information S1).
-  This is because FR is not "photosynthetically active" and FR-rich light promotes excessive stem elongation.
+  In general, fluorescent lamps, metal halide lamps, high-pressure sodium lamps, and blue, red, and white LEDs used for assimilation lighting emit typical PSII-light (Supplemental Information S1).
+  This is because FR is not ‘photosynthetically active’ and FR-rich light promotes excessive stem elongation.
   <!-- It should be kept in the mind that the *P*~n~ of leaves grown under these light sources can be overestimated if measured with BR-light, and the measured *P*~n~ might be different from those under the PSI-light such as sunlight (Fig.
@@
   Evaluating the vertical profiles of the photosynthetic characteristics of the plant stand cultivated in greenhouses may be vulnerable to the biases in the same manner.
-  While the leaves in the upper layers were acclimated to sunlight, those in the lower layers were acclimated to the leaf-penetrated light.
-  Due to the higher transmittance in the FR waveband of a leaf, leaf-penetrated light contains much FR, namely PSI-light (Supplemental Information S1).
+  While the leaves in the upper layers were acclimated to sunlight, those in the lower layers were acclimated to the leaf transmitted light.
+  Due to the higher transmittance in the FR waveband of a leaf, leaf transmitted light contains much FR, namely PSI-light (Supplemental Information S1).
   Therefore, when measured using BR-light, the *P*~n~ of upper leaves might be overestimated while that of lower leaves might be underestimated.
 
-  Note that such an interaction might have impacts on the other characteristics related to the photosynthetic electron transport, such as chl fluorescence parameters and the photoinhibition indicators.
-  The overexicitation of PSII (or PSI) results in the lowered photochemical yield at PSII (or PSI) [e.g.
-@Hogewoning_et_al2012PC; @Laisk_et_al2014BBA], and the imbalance in the excitation should hastes the photoinhibition caused by the reactive oxygen species.
-  Evaluation of these characteristics should also be measured with particular care on the interaction.
-
-# How the photosynthesis should be measured
+# How the photosynthesis should be measured?
 
@@
   Note that the effect of the interaction seems to be less prominent than those of the other factors, such as the incident PPFD.
-  The measurements under sunlight, which usually causes fluctuations in the incident PPFD, should be avoided and thus the measurements should be made under the artificial light sources to ensure the reproducibility and reliability of the research.
-  The use of artificial light sources will mitigate the uncertainty caused by the fluctuations in the incident PPFD at the expense of the biases possibly caused by the interaction.
-  This is because the SPD of light from an artificial light source is generally by far different from that of *in situ* light.
-  To solve this dilenma between the *in situ* evaluation and the PPFD stability, the SPD-controllable light source might be helpful [e.g. @Yano_Fujiwara2012PM; @Fujiwara_et_al2013Proc].
-
-  In the retrospective study aiming to elucidate the causes of the differences between the experimental groups, the measurements should be made under the SPDs of light the plants recieved during the treatments.
+  The measurements under sunlight, which usually causes a fluctuation in the incident PPFD, should be avoided and thus the measurements should be made under the artificial light sources to ensure the reproducibility and reliability of the research.
+  The use of artificial light sources will mitigate the uncertainty caused by the fluctuation in the incident PPFD at the expense of the possible biases caused by the interaction.
+  This is because the SPDs of light from the artificial light sources are generally by far different from that of *in situ* light.
+  To solve this dilemma between the *in situ* evaluation and the PPFD stability, SPD-controllable light sources might be helpful [e.g. @Yano_Fujiwara2012PM; @Fujiwara_et_al2013Proc].
+  In the retrospective study aiming to elucidate the causes of the differences between the experimental groups, the measurements should be made under the SPDs of light the plants received during the treatments.
   <!-- When the aim of the research is to analyze the origins of the differences in the growth of the plants subject to several light treatments, the rates should be measured under the SPDs of light the plants recieved.
 -->
-  For instance, when the difference in the resultant dry weight between the plants grown under white LEDs and fluorescent lamps are analyzed and the *P*~n~ is used for the explanatory variable, the measurements should be made using the white LEDs for the plants grown under white LEDs light and using the fluorescent lamps for those grown under fluorescent lamps.
-  In both the prospective and retrospective studies, these simple solutions will eliminate the problems caused by the interaction.
+  For instance, when the difference in the resultant dry weight between the plants grown under white LEDs and fluorescent lamps are analyzed and the *P*~n~ is used for the explanatory variable, the measurements should be made using the white LEDs for the plants grown under the white LEDs and using the fluorescent lamps for those grown under the fluorescent lamps.
+  In both the prospective and retrospective studies, these simple *in situ* measurements will eliminate the problems caused by the interaction.
 
-  If the SPD of light the leaves will receive is not predetermined, then the measurements should be made under several levels of SPDs of light including PSII- and PSI-light.
-  Researchers had better describe the "general" characteristics of the leaves in these kind of studies.
-  **Therefore, the interaction should be tested so as not to make biased evaluation.**
-  **If the significant interaction is not detected in two-way ANOVA, the main effect of the treatment can be assessed.**
-  **If any the interaction, the results should not be generalized.**
-  **The responses of the rates to both PSII- and PSI-light should be measured, compared, and reported in the paper.**
-  When the measuments were made only under a single-level of SPD of measuring light because of unavoidable circumstances, the light source must be declared in the materials and methods section so that readers can follow the SPD.
+  If the SPD of light the leaves will subject to is not predetermined, then the measurements should be made under several levels of SPDs of light including PSII- and PSI-light.
+  Researchers had better report the ‘general’ characteristics of the leaves in these descriptive studies.
+  Therefore, the interaction should be tested so as not to make biased evaluation.
+  If any the interaction, the results should be descriptively reported and should not be generalized.
+  <!-- **The responses of the rates to both PSII- and PSI-light should be measured, compared, and reported in the paper.** -->
+  <!-- **If the significant interaction is not detected in two-way ANOVA, the main effect of the treatment can be assessed.** -->
+  When the measurements were made only under a single-level of SPD of measuring light because of unavoidable circumstances, the light source must be declared in the materials and methods section so that readers can follow the SPD.
   <!-- The effect of the incteraction should be amplified in the comparison be the leaves with different EED properties. -->
@@
 
-# Concluding remarks and future works
+# Concluding remarks
 
-  The *P*~n~ measured under a single-level SPD of light is only an aspect of the photosynthetic characteristics of the leaf.
-  Therefore, the obtained results must be discussed in connection with the SPD of measuring light.
-  Further carefull investigations are required to elucidate the extent of the interaction in the *P*~n~ under the above mentioned conditions.
-  Evaluation of the photosynthesis should be made under the *in situ* conditions or multilevels of SPDs of measuring light so that the evaluation is not biased by the interaction.
+  The *P*~n~ under a single-level SPD of measuring light is only an aspect of the photosynthetic characteristics of the leaf.
+  Therefore, the obtained result must be discussed in connection with the SPD of measuring light.
+  Evaluation of the photosynthesis should be made under the *in situ* conditions or multi-levels of SPDs of measuring light so that the evaluation is not biased by the interaction.
   Imitating the various SPDs of light incident on the leaf for *in situ* evaluation might be difficult or impossible from the technical reasons.
-  In addition that, measuring the *P*~n~ under multilevels of SPDs costs much more time, resource, and labor.
+  In addition, measuring the *P*~n~ under multi-levels of SPDs costs much more time, resource, and labor.
   Thus, these two approaches might not always be applied for evaluation of the leaf *P*~n~.
-  **Futher research is required to make the quantitative analysis of the leaf *P*~n~ in response to the SPD of measuring light.**
+  Further research is required to make the quantitative analysis of the leaf *P*~n~ in response to the SPD of measuring light.
 

### 2016-07-27 Sup1.Rmd
第０稿完成。3327 words

@@
 # Supplemental Information S1
-
-Information of the light sources and measuring instruments.
 
@@
   data_frame(variable = c("FL", "MH", "HPS", "B", "R", "FR", "W", "Sun", "Shade"),
-             wavelength = c(435, 520, 570, 448, 660, 735, 460, 450, 750),
+             wavelength = c(435, 520, 570, 448, 660, 735, 460, 450, 700),
              value = c(2.2, .6, 3, 4, 4.2, 3.8, 1.3, 0.6, 2),
@@
   filter(between(wavelength, 380, 820)) %>%
-  ggplot(aes(x = wavelength, y = value, group = variable, col = variable, linetype = variable)) +
+  # ggplot(aes(x = wavelength, y = value, group = variable, col = variable, linetype = variable)) +
+  ggplot(aes(x = wavelength, y = value, group = variable, col = variable)) +
   theme_bw2() +
@@
   geom_text(data = SPD_labels, aes(x = wavelength, y = value, label = label)) +
-  scale_linetype_manual(values = c(1, 1, 3, 2, 4, 2, 2, 1, 4)) +
+  # scale_linetype_manual(values = c(1, 1, 3, 2, 4, 2, 2, 1, 4)) +
   scale_color_manual(values = c("blue", "black", "darkred", "orange", "purple", "red", "grey50", "black", "black")) +
@@
   "Fig.
-S1  The spectral photon flux density distributions of light provided by (A) high-intensity dischage lamps (HIDs) and fluorescent lamps, (B) light-emitting diodes (LEDs), and (C) incident and leaf transmitted sunlight (see also Table S1).
+S1  The spectral photon flux density distributions of light provided by (A) high-intensity discharge lamps (HIDs) and fluorescent lamps, (B) light-emitting diodes (LEDs), and (C) incident and leaf transmitted sunlight (see also Table S1).
 The distributions at a photon flux density of 100 µmol m<sup>--2</sup> s<sup>--1</sup> within 400--750 nm are shown.
@@
 ```
+
+Information of the spectral distributions of artificial assimilation light and sunlight.
 
@@
 | Fluorescent lamp (FL)           | FPL55EX-N<sup>\*1</sup>       | HR2000 (Ocean Optics Inc.)        |
-| Metal halide lmap (MH)          | M220FCELS-W/BUD<sup>\*1</sup> | HR2000 (Ocean Optics Inc.)        |
+| Metal halide lamp (MH)          | M220FCELS-W/BUD<sup>\*1</sup> | HR2000 (Ocean Optics Inc.)        |
 | High-pressure sodium lamp (HPS) | NH220FLS<sup>\*1</sup>        | HR2000 (Ocean Optics Inc.)        |

### 2016-07-27 Main.Rmd
引用スタイルとbibtexの修正

@@
 author: "Keach Murakami^1\\*^, Ryo Matsuda^1^, Kazuhiro Fujiwara^1^"
-bibliography: ~/Dropbox/R/List.bib
+bibliography: ~/GitHub/BeeLabR/BibTex/with.bib
 csl: ECB.csl
@@
   html_document:
-    toc: true
-    # toc_float: true
+    toc: TRUE
     depth: 3
@@
     self_contained: TRUE
-    fig_caption: true
+    fig_caption: TRUE
     pandoc_args: [

### 2016-07-30 Main.Rmd
ECBにはsupplementalがないらしいので、構成を結構変更。 RM指摘に対応した削りが進み、2867 words

@@
 ---
-title: "A practical guide for selecting the spectral photon flux density distribution of light during the measurements of the leaf photosynthetic rate"
+title: "A practical guide for selecting the spectral photon flux density distribution of light for comparing photosynthetic rates of leaves grown under different spectral light conditions"
 author: "Keach Murakami^1\\*^, Ryo Matsuda^1^, Kazuhiro Fujiwara^1^"
@@
 csl: ECB.csl
+header-includes:
+  - \setmainfont{Helvetica Neue} 
+  - \usepackage{zxjatype} # 日本語を使う
+  - \setjamainfont{Hiragino Kaku Gothic Pro} # 日本語フォント
+  - \usepackage{lscape} # 図を回転する
+  - \newcommand{\blandscape}{\begin{landscape}} # 図回転用のbegin command
+  - \newcommand{\elandscape}{\end{landscape}} # 図回転用のend command
+  - \usepackage{setspace} # 行間の調節
+  - \newcommand{\bdoublespace}{\begin{spacing}{1.5}} # 行間を広げるbegin command
+  - \newcommand{\edoublespace}{\end{spacing}{1.5}} # 行間を広げるbegin command
+
 output:
@@
 
+@JIS_sunlight
+
 ```{r load, echo = F, message = F}
+rm(list = ls())
+
 evalFig <- T
-
 if(evalFig){
@@
 
-opts_chunk$set(echo = FALSE, fig.width = 5, fig.height = 5,
+opts_chunk$set(cache = F, echo = FALSE, fig.width = 5, fig.height = 5,
                out.width = '500pixel', out.height = '500pixel', dpi = 100,
-               message = FALSE, warning = FALSE, cache = F, eval = T)
+               message = FALSE, warning = FALSE, eval = T)
 ```
 
-```{r Captions}
+```{r Captions, eval = evalFig}
 CapETRs <-
@@
 
+CapEED <-
+  "Fig. 2  The excitation balance between photosystems in response to wavelength of light."
+
 CapInteract <-
   "Fig.
-2  The conceptual diagram of the photosynthetic electron transport rates per absorbed photons by the photosystems grown under PSII-light (PSII-leaves) and PSI-light (PSI-leaves) in response to the PSII/PSI-bised level of measuring light."
+3  The conceptual diagram of the photosynthetic electron transport rates per absorbed photons by the photosystems grown under PSII-light (PSII-leaves) and PSI-light (PSI-leaves) in response to the PSII/PSI-bised level of measuring light."
+
+CapSPD <-
+  "Fig.
+4  The spectral photon flux density distributions of light provided by (a) fluorescent lamp (FL; FPL55EX-N<sup>1</sup>), metal halide lamp (MH; M220FCELS-W/BUD<sup>1</sup>), and, high-pressure sodium lamp (HPS; NH220FLS<sup>1</sup>), (b) blue (B; HBL3-3S55-LE<sup>2</sup>), red (R; SRK3-3A80-LE<sup>2</sup>), far-red (FR; L735-36AU<sup>3</sup>), and white (W; NSPW310DS<sup>4</sup>) light-emitting diodes, and (c) incident and leaf transmitted sunlight.
+The distributions at a photon flux density of 100 µmol m<sup>--2</sup> s<sup>--1</sup> within 400--750 nm are shown.
+The distribution of sunlight was adopted from JIS C 8904-3.
+The distribution of the leaf transmitted sunlight was calculated from that of sunlight and the transmittance spectrum of a cucumber leaf (Murakami et al.
+2016).
+The far-red waveband (700--750 nm) is filled in grey.
+<br><sup>1</sup>IWASAKI ELECTRIC CO., LTD, Tokyo, Japan; <sup>2</sup>Tricon Co., Shimane, Japan; <sup>3</sup>Epitex Inc., Kyoto, Japan; <sup>4</sup>Nichia Chemical Industries Ltd., Tokushima, Japan."
 ```
@@
 
+```{r EED, eval = evalFig}
+library(EBImage)
+which_mean <- function(x) x %>% which %>% mean
+Join_by <- function(x, y) join(x, y, by = "wavelength")
+
+  Hoge_PSII <- readImage("~/Dropbox/Publish/2016PgEstimate/Data/Hoge_PSII.png")
+  Hoge_PSI <- readImage("~/Dropbox/Publish/2016PgEstimate/Data/Hoge_PSI.png")
+
+  Abs_PSII <-
+    (Hoge_PSII[, , 1] < .8 & Hoge_PSII[, , 3] > .8) %>%
+    .@.Data %>%
+    data.frame %>%
+    t %>%
+    aaply(.margins = 2, .fun = which_mean) %>%
+    data.frame(wavelength = seq(400, 800, by = 1), abs = (dim(Hoge_PSII)[2] - .)) %>%
+    select(wavelength, PSII = abs)
+
+  Abs_PSI <-
+    (Hoge_PSI[, , 1] > .8 & Hoge_PSI[, , 3] < .8) %>%
+    .@.Data %>%
+    data.frame %>%
+    t %>%
+    aaply(.margins = 2, .fun = which_mean) %>%
+    data.frame(wavelength = seq(400, 800, by = 1), abs = (dim(Hoge_PSI)[2] - .)) %>%
+    select(wavelength, PSI = abs)
+
+Mole_abs <-
+  Reduce(Join_by, list(Abs_PSII, Abs_PSI)) %>%
+  filter(wavelength %% 1 == 0)
+
+Abs_ratio <-
+  function(cut_row, simulate){
+    simulate_dat <-
+      simulate %>% slice(cut_row)
+
+    Infos <-
+      data.frame(`L_RCII` = simulate_dat$L_trimer_per_RCII,
+                 `L2_L1L2` = simulate_dat$L_trimer_to_PSII,
+                 `RCI_RCII` = simulate_dat$RCI_per_RCII)
+
+    Mole_abs %>%
+      transmute(
+        wavelength,
+        # AlltoPSII = ((PSII + Infos[1, 1] * Infos[1, 2] * LHCII) / (Infos[1, 3] * PSI + PSII + Infos[1, 1] * LHCII))
+        AlltoPSII = PSII / (PSII + Infos[1,3] * PSI)
+      ) %>%
+      list(data = ., Info = Infos) %>%
+      return
+  }
+
+EEDs <-
+  Mole_abs %>%
+  transmute(
+    wavelength,
+    AlltoPSII = PSII / (1.5 * PSI + PSII)
+  ) %>%
+  filter(AlltoPSII >= 0)  %>%
+  replace_na(list(AlltoPSII = 0)) %>%
+  ggplot(aes(x = wavelength, y = AlltoPSII)) +
+  theme_bw2() +
+  gg_xy(c(380, 770, -0.05, 1.05)) +
+  # geom_ribbon(aes(ymin = AlltoPSII_max, ymax = AlltoPSII_min), col = "grey50") +
+  geom_line() +
+  xlab("Wavelength [nm]") + ylab("")
+```
+
+```{r Spectra, eval = evalFig}
+
+# set integrate ranges
+PFD_integrate_min <- 350
+PFD_integrate_max <- 750
+
+IntegratePFD <- 100
+
+panel_names <- c("(a)", "(b)", "(c)")
+
+# HID_raw <-
+#   fread("~/Dropbox/R/spectrum/HID.csv", skip = 13)
+# 
+# HIDs <-
+#   HID_raw %>%
+#   setnames(., c("wavelength", paste0("ID", 1:(dim(HID_raw)[2] - 1)))) %>%
+#   select(1, HPS_ = 12, MH_ = 21)
+FL_Ocean_raw <-
+  fread("~/Dropbox/materials/SPD_FL.csv") %>%
+  transmute(wavelength = `Wavelength[nm]`, value = FL) %>%
+  na.omit
+
+FL_Ocean_PFD <-
+  smooth.spline(FL_Ocean_raw$wavelength, FL_Ocean_raw$value) %>%
+    predict(., seq(PFD_integrate_min, PFD_integrate_max)) %>%
+    .$y %>%
+  sum
+
+FL_Ocean <-
+  FL_Ocean_raw %>%
+  mutate(value = value * 100 / FL_Ocean_PFD, variable = "FL")
+
+HPS_Ocean_raw <-
+  fread("~/Dropbox/materials/SPD_HPS.txt", skip = 50, nrow = 2000) %>%
+  rename(wavelength = V1, value = V2)
+
+HPS_Ocean_PFD <-
+  smooth.spline(HPS_Ocean_raw$wavelength, HPS_Ocean_raw$value) %>%
+    predict(., seq(PFD_integrate_min, PFD_integrate_max)) %>%
+    .$y %>%
+  sum
+
+HPS_Ocean <-
+  HPS_Ocean_raw %>%
+  mutate(value = value * 100 / HPS_Ocean_PFD, variable = "HPS")
+
+MH_Ocean_raw <-
+  fread("~/Dropbox/materials/SPD_MH.txt", skip = 50, nrow = 2000) %>%
+  rename(wavelength = V1, value = V2)
+
+MH_Ocean_PFD <-
+  smooth.spline(MH_Ocean_raw$wavelength, MH_Ocean_raw$value) %>%
+    predict(., seq(PFD_integrate_min, PFD_integrate_max)) %>%
+    .$y %>%
+  sum
+
+MH_Ocean <-
+  MH_Ocean_raw %>%
+  mutate(value = value * 100 / MH_Ocean_PFD, variable = "MH")
+
+OceanSPDs <-
+  bind_rows(FL_Ocean, HPS_Ocean, MH_Ocean) %>%
+  mutate(panel = panel_names[1])
+
+Absorptances <-
+  fread("~/Dropbox/materials/SpectrumCucumber.csv") %>%
+  filter(Trtm %in% c("W", "WFR", "FL")) %>%
+  mutate(wavelength = as.numeric(wavelength)) %>%
+  filter(variable == "absorption", Trtm == "W")
+
+Sun <-
+  fread("~/Dropbox/materials/Sunlight_JIS.csv") %>%
+  setnames(c("wavelength", "Sunlight")) %>%
+  left_join(., Absorptances, by = "wavelength") %>%
+  transmute(wavelength, Sun = Sunlight, Shade = Sunlight * (100 - ave), Absorptance = ave)
+
+# Sun: JIS C8904-3
+
+LEDs <-
+  fread("~/Dropbox/materials/SPD_FL.csv") %>%
+  transmute(wavelength = `Wavelength[nm]`, W, FR, B = B_HL, R = R_SR) %>%
+  SPDnorm(from = 350, to = 750, integratedPFD = IntegratePFD) %>%
+  gather(variable, value, -wavelength) %>%
+  mutate(panel = panel_names[2]) %>%
+  na.omit
+
+SPD_labels <-
+  data_frame(variable = c("FL", "MH", "HPS", "B", "R", "FR", "W", "Sun", "Shade"),
+             wavelength = c(435, 520, 570, 448, 660, 735, 460, 450, 700),
+             value = c(2.2, .6, 3, 4, 4.2, 3.8, 1.3, 0.6, 2),
+             label = c("FL", "MH", "HPS", "B", "R", "FR", "W", "Sunlight", "Leaf transmitted sunlight"),
+             panel = rep(panel_names,  c(3, 4, 2)))
+
+SPD_panel <-
+  data_frame(variable = "FL",
+           wavelength = 400, value = 4,
+           label = letters[1:3],
+           panel = rep(panel_names))
+
+SPDs <-
+  Sun %>%
+  SPDnorm(from = 350, to = 750, integratedPFD = IntegratePFD) %>%
+  select(-Absorptance) %>%
+  gather(variable, value, -wavelength) %>%
+  mutate(panel = panel_names[3]) %>%
+  bind_rows(., OceanSPDs, LEDs) %>%
+  filter(between(wavelength, 380, 820)) %>%
+  ggplot(aes(x = wavelength, y = value, group = variable, col = variable, linetype = variable)) +
+  theme_bw2() +
+  theme(strip.background = element_blank(),
+        strip.text = element_blank(),
+        panel.grid.major = element_blank()) +
+  geom_rect(aes(xmin = 700, xmax = 750, ymin = 0, ymax = +Inf), fill = "grey90", col = NA) +
+  geom_line() +
+  geom_text(data = SPD_labels, aes(x = wavelength, y = value, label = label)) +
+  geom_text(data = SPD_panel, col = "black", aes(label = panel)) +
+  scale_linetype_manual(values = c(1, 1, 3, 2, 4, 2, 2, 1, 4)) +
+  scale_color_manual(values = c("blue", "black", "darkred", "orange", "purple", "red", "grey25", "black", "black")) +
+  facet_grid(panel ~ .) +
+  gg_xy(c(380, 820, 0, 4.5)) +
+  xlab("Wavelength [nm]") + ylab(u_SPFD("Spectral photon flux density"))
+
+```
+
 Affiliations: ^1^Graduate School of Agricultural and Life Sciences, The University of Tokyo
@@
 **Abstract**
+
+Check terms:
+level
 
@@
 
-  The photosynthetic rate is one of the most important and fundamental traits of the plant.
+  The photosynthetic rate is one of the most important and fundamental *traits of the plant (aspects? for growth? of plants*.
   The rates are measured, evaluated, and compared among the leaves cultivated under different conditions.
-  The measured rates are also used for the calculation of the other photosynthetic parameters, such as light, water, and nitrogen use efficiencies.
-  In agricultural and horticultural studies, the effectiveness of treatments is sometimes discussed based on the measured photosynthetic rate and calculated parameters. 
-  Therefore, the accurate measurements of the photosynthetic rate must be essential.
+  The measured rates are also used for the calculation of the other photosynthesis-related indices, such as light-, water-, and nitrogen-use efficiencies for photosynthesis.
+  In agricultural and horticultural studies, the effectiveness of treatments is sometimes discussed based on the measured photosynthetic rates and calculated parameters. 
+  Therefore, accurate measurements of the photosynthetic rates must be essential.
 
   A number of studies have reported that the relative spectral photon-flux-density (PFD) distribution (SPD) of light used for the measurement (i.e.
-measuring light or actinic light) affected the net photosynthetic rates (*P*~n~) of leaves [e.g.
+measuring light or actinic light) affected leaf net photosynthetic rates (*P*~n~) [e.g.
 @McCree1972AM; @Inada1976PCP].
-  To eliminate this direct effect from the comparison, *P*~n~ is usually measured under a single-level SPD of measuring light irrespective of the leaf growth conditions in these fields.
-  The most widely-used measuring light might be mixture of blue + red LED light (BR-light) provided by light sources installed in commercial photosynthesis analyzing systems.
-  The use of the artificial light sources might enable precise control of the photosynthetic PFD (PPFD) and SPD incident on the leaf thereby ensure the reproducibility and reliability of the experiments.
+  To eliminate this direct effect from the comparison, *P*~n~ is usually measured under a common SPD of measuring light irrespective of leaf growth conditions in agricultural and horticultural studies.
+  One of the most widely-used measuring light is mixture of blue and red light provided by LED light sources (BR-light) installed in commercial photosynthesis analyzing systems (e.g.
+LI6400 and LI6400XT, LI-COR Inc.; GFS-3000, Heinz Walz GmbH).
+  The use of artificial light sources enables precise control of the photosynthetic PFD (PPFD) and SPD incident on the leaf and therefore ensure the reproducibility and reliability of the experiments.
 
-  @Walters2005JXB pointed out that the measurements with a SPD of light different from growth light do not necessarily reflect the functioning of the photosynthesis under growth conditions.
+  @Walters2005JXB pointed out that measuring photosynthetic rates with a SPD of light different from that of growth light do not necessarily reflect the functioning of photosynthesis under growth conditions.
   Our recent study, indeed, experimentally demonstrated this problem in the *P*~n~ measurements [@Murakami_et_al2016PP].
-  In that experiment, cucumber seedlings were grown under white light-emitting diode (LED) light without and with supplemental far-red (FR) LED light (W and WFR), and subsequently the *P*~n~ of the leaves were compared under BR-light and light with the SPD resembling that of sunlight.
-  The *P*~n~ of W-leaves was greater than that of WFR-leaves under BR-light, while the rates were comparable under artificial sunlight [@Murakami_et_al2016PP].
-  Based on the results obtained from the measurement under BR-light, the prospective growth rate of WFR-plants may be evaluated to be smaller than that of W-plants despite the comparable rates under the sunlight.
+  In that experiment, cucumber seedlings were grown under white light-emitting diode (LED) light without and with supplemental far-red (FR) LED light (W and WFR), and subsequently *P*~n~ of the leaves were compared under BR-light and light with the SPD resembling that of sunlight (‘artificial’ sunlight).
+  The *P*~n~ of W-leaves was greater than that of WFR-leaves under BR-light, while the rates were comparable under the artificial sunlight [@Murakami_et_al2016PP].
+  Based on the results obtained from the measurement under BR-light, the prospective **growth (leaf photosynthetic)** rate of WFR-plants may be evaluated to be smaller than that of W-plants despite the comparable rates under sunlight.
 
-  The effect of the SPD of growth light on the *P*~n~ depended on the level of the SPD of measuring light.
-  In other words, the SPDs of growth light and measuring light interacted on the *P*~n~ of a leaf.
+  The effect of the SPD of growth light on *P*~n~ depends on the SPD of measuring light.
+  In other words, the SPDs of growth light and measuring light interact on *P*~n~ of a leaf.
   In this short article, we introduce a plausible cause of the interaction and several articles reporting the interaction.
-  We then suggest the situations where the interaction should be cared.
-  We also discuss the good practice for the selection of the SPD of measuring light used for *P*~n~ measurements.
-  The SPD of light affects the photosynthesis through the other mechanisms, such as the stomatal response [@Shimazaki_et_al2007AnnRev], the photoinhibition [@Zavafer_et_al2015JPP], and the light-penetrating depth within a leaf [@Terashima_et_al2009PCP].
-  Although these subjects are not referred in this article, the cited review articles on these topics are available.
+  We then suggest situations in which the interaction should be **particularly?** cared.
+  We also discuss the good practice for selecting of the SPD of measuring light for *P*~n~ measurements.
+  The SPD of light affects photosynthesis through **the other mechanisms (何のほかか、が不明瞭。EEDを上で簡単に書いておきたい)**, such as stomatal responses [@Shimazaki_et_al2007AnnRev], photoinhibition [@Zavafer_et_al2015JPP], and vertical PFD profile within a leaf [@Terashima_et_al2009PCP].
+  Although these subjects are not referred in this article, the cited articles are available for these topics.
 
-# How the interaction is generated?
+# How the interaction is generated? **(見出し軽すぎ)**
 
   Fundamental knowledge about the photosynthetic electron transport is required to understand the mechanism of the interaction.
-  Light energy absorbed by a leaf drives the electron transport and thereby the photosynthetic O~2~ evolution and CO~2~ uptake.
+  Light energy absorbed by a leaf drives the phtoosynthetic electron transport, O~2~ evolution, and CO~2~ uptake.
   In higher plants, the photosynthetic electron transport chain is anchored by photochemical reactions that occur at two types of photosystems, PSII and PSI.
   The reactions are powered by excitation energy derived from absorbed photons.
-  The excitation energy transferred to the reaction centers of the photosystems is consumed by the photochemical reactions in units of moles.
-  The serial photochemical reactions at PSII and PSI enables electron transfer against the redox potential (called the Z scheme).
+  The excitation energy transferred to the reaction centers of the photosystems is consumed by the photochemical reactions **in units of moles**.
+  The serial photochemical reactions at PSII and PSI enables electron transfer from water to NADP^+^ (called the Z scheme).
   Because the photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) through the thylakoid membranes should be limited by the slowest step (Fig. 1).
-  When PSII absorbs excess excitation energy under PSII-biased light, the energy distribution to PSI limits the ETR and thus the photochemical quantum yield of PSII should be lowered (Fig. 1C).
-  When PSI absorbs excess excitation energy, the energy distribution to PSII limits the ETR and the yield of PSI should be lowered (Fig. 1B).
+  When the excitation energy is in excess at PSII, the **energy distribution (この書き方は，いきなりだと知らない人にはわかりにくいものと思われる。)** to PSI limits the ETR and thus the photochemical quantum yield of PSII should be lowered (Fig.
+1C).
+  When PSI absorbs the excess excitation energy, the energy distribution to PSII limits the ETR and the yield of PSI should be lowered (Fig. 1B).
   In both cases, the excess energy is dissipated as heat and fluorescence, and thus the entire photosynthetic quantum yield---ETR per absorbed photons by the leaf---becomes smaller.
-  An imbalance excitation between the photosystems can harm leaves by generating reactive oxygen species, which cause oxidative damage to chloroplast components [for reviews, see @Asada1999AnnRev; @Asada2006PP].
+  **Imbalanced excitation between the photosystems can harm leaves (これは強く言える？微妙)** by generating reactive oxygen species, which cause oxidative damage to chloroplast components [for reviews, see @Asada1999AnnRev; @Asada2006PP].
   Balancing the excitation energy distribution (EED) between PSII and PSI is essential for plants to keep the high photosynthetic quantum yield.
-
   <!-- **おまけ部分** -->
@@
   <!-- The imbalance in the EED between the photosystems is supposed to occur ordinarily (どこで？太陽光？). -->
-  PSII and PSI represent different light absorption spectral distributions due to the difference in the compositions of binding pigments, mainly chl *a* and chl *b*.
+  PSII and PSI represent different light absorption spectral distributions due to the difference in the compositions of binding pigments, mainly chl *a* and chl *b*. **(図があるとわかりやすい)**
   Within the chlorophyll (chl) absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [@Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
-  Such an imbalanced excitation is caused by the facts that only chl *a* can absorb the longer wavelengths of light and that PSI contains a greater amount of chl *a* than PSII.
+  This is because only chl *a* can absorb the longer wavelengths of light and PSI contains a greater amount of chl *a* than PSII.
   In contrast, monochromatic light at shorter wavelengths (< 680--690 nm) is estimated to be preferentially absorbed by PSII, or evenly absorbed by both photosystems [@Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
-  These wavelength dependencies of the EED is a determinant of the EED under a given SPD of light.
-  In several studies of the SPD acclimation of the photosynthetic apparatus, light with a given SPD is categorized as either PSII- or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI
-  This categorization is defined in the relative scale, not in the absolute scale.
+  These wavelength dependencies of the excitation is a determinant of the EED under a given SPD of light.
+  In studies on the acclimation of the photosynthetic apparatus to the SPD of growth light, light with a given SPD is categorized as either PSII- or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI [e.g.
+@Chow_et_al1990PNAS; @Melis1991BBA; @Pfannschmidt_et_al2001JBC; @Fan_et_al2007BBA; @Pfannschmidt_et_al2009AB; @Hogewoning_et_al2012PC].
+  **This categorization is defined in the relative scale, not in the absolute scale.「absolute」と「relative」が何を指しているのかなど，，もう少し具体的に書きたい。ある特定の葉に対してのみ定義できる**
   For instance, a SPD of light, which is evenly absorbed by PSII and PSI in PSII-light-grown leaves (Fig. 1A), can overexcite PSII in PSI-light-grown leaves (Fig. 1C).
@@
 
-  Apparently, the EED at a given SPD of light is also affected by the composition of the thylakoid membrane, especially by the stoichiometry between PSII and PSI.
+  Apparently, the EED at a given SPD of light is also affected by the composition of the thylakoid components, especially by the stoichiometry between PSII and PSI.
   The stoichiometry seems to be adjusted to the SPD of growth light.
@@
 @Melis1991BBA; @Pfannschmidt_et_al1999Nature].
-  The possible involvement of the change in the composition within the respective photosystems in the SPD acclimation was also suggested [@Walters_Horton1995bPlanta; @Murakami_et_al2016PP].
+  **Possible involvement of the change in the composition within the respective photosystems in the acclimation to SPD was also suggested [@Walters_Horton1995bPlanta; @Murakami_et_al2016PP].
+具体的に何か、言っとくべき**
   <!-- Galka_et_al2012PC -->
@@
   In the short term within an hour, an imbalance in the EED is, at least partly, relieved by the reversible allocation of the light-harvesting antenna complex of PSII (LHCII) between PSII and PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].
-  Although a slight imbalance in the EED might be covered up by the state transitions, the long-term adjustments in the EED properties are supposed to occur when state transitions are insufficient to counterbalance the uneven EED [@Dietzel_et_al2008FJ].
+  Although a slight imbalance in the EED might be compensated for by the state transitions, the long-term adjustments in the EED properties are supposed to occur when state transitions are insufficient to counterbalance the uneven EED [@Dietzel_et_al2008FJ].
 
-  The SPD of growth light affects the EED properties of a leaf, which modifies the responses of the ETR and thereafter the *P*~n~ to the SPD of measuring light.
+  The SPD of growth light affects the EED properties of a leaf, which modifies the responses of ETR and thereby *P*~n~ to the SPD of measuring light.
   Thus, the SPDs of growth light and measuring light do not only directly affect the *P*~n~ but also indirectly affect it through their interaction.
   The expected interactions have been reported in several studies [@Chow_et_al1990PNAS; @Walters_Horton1995aPlanta; @Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
-  In their pioneering study on *Pisum sativum*, @Chow_et_al1990PNAS grew plants under light provided by cool-white fluorescent lamps with yellow Plexglas (FR-poor PSII-light) and incandescent bulbs with red Plexglas (FR-rich PSI-light), and subsequently measured the photosynthetic quantum yield of O~2~ evolution---O~2~ evolution rate per absorbed photons by the leaf---under the PSII- and PSI-light.
+  In their pioneering study, @Chow_et_al1990PNAS grew *Pisum sativum* plants under light provided by cool-white fluorescent lamps with yellow Plexiglas (PSII-light) and incandescent bulbs with red Plexiglas (PSI-light) and measured the photosynthetic quantum yield of O~2~ evolution---O~2~ evolution rate per absorbed photons by the leaf---under the PSII- and PSI-light reciprocally.
   When measured under the PSII-light, the yield was higher in the PSII-light-grown leaves; when measured under the PSI-light, the yield was higher in the PSI-light-grown leaves.
   Similar trends were observed in *Arabidopsis thaliana* [@Walters_Horton1995aPlanta] and *Cucumis sativus* [@Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
-  @Hogewoning_et_al2012PC observed the interaction in the photosynthetic quantum yield of CO~2~ uptake using artificial sunlight (PSII-light) and shadelight (PSI-light) as growth light and 19 monochromatic LED light as measuring light.
-  They demonstrated that the interaction cannot occur only in the case growth light was used as measuring light but also in the case the other SPDs of light was used.
-  @Murakami_et_al2016PP showed the interaction in the *P*~n~ using white LED light without or with FR LED light (PSII-light and PSI-light) as growth light and BR-light (PSII-light) and artificial sunlight (PSI-light) as measuring light.
-  The potential problem in the use of BR-light for the *P*~n~ measurements was clearly demonstrated.
+  @Hogewoning_et_al2012PC observed the interaction in the photosynthetic quantum yield of CO~2~ uptake using artificial sunlight (PSII-light) and shadelight (PSI-light) as growth light and 19 kinds of monochromatic LED light as measuring light.
+  **They demonstrated that the interaction cannot occur only in the case growth light was used as measuring light but also in the case the other SPDs of light was used.**
+  @Murakami_et_al2016PP showed the interaction in the *P*~n~ using white LED light without or with FR LED light (PSII-light and PSI-light) as growth light and BR-light (PSII-light) and the artificial sunlight (PSI-light) as measuring light.
+  It was clearly demonstrated that the use of BR-light for *P*~n~ measurements could result in the biased evaluation.
 
-  These reports might suggest that the EED property of a leaf is tuned to the PSII/PSI-biased level of growth light.
-  It is expected that a leaf performs a higher ETR per absorbed photons by the photosystems under measuring light with the same PSII/PSI-biased level to that of growth light (Fig. 2).
-  When leaves grown under different SPDs of light are compared and evaluated under a single-level SPD of light, the results should be inevitably biased depending on the SPD of measuring light.
+  These reports suggest that the EED properties of a leaf might be tuned to the PSII/PSI-biased level of growth light.
+  It is expected that a leaf performs a higher ETR per absorbed photons by the photosystems under measuring light with a PSII/PSI-biased level similar to that of growth light (Fig. 2).
+  When leaves grown under different SPDs of light are compared and evaluated under a specific SPD of light, the results should be inevitably biased depending on the SPD of measuring light.
 
@@
 
-  This interaction may have considerable impact on the *P*~n~ especially in the measurements under the low PPFD and/or high CO~2~ concentration, where the extent of the ETR is a dominant factor for the photosynthetic rate [@vonCaemmerer_Farquhar1981Planta].
-  In such conditions, any bias in the ETR is directly reflected in the *P*~n~.
+  This interaction may have considerable impact on *P*~n~ especially measured under low PPFDs and/or high CO~2~ concentrations, where the ETR is a limiting factor for the photosynthetic CO~2~ fixation [@vonCaemmerer_Farquhar1981Planta].
+  Under such conditions, any bias in the ETR is directly reflected in *P*~n~.
   Therefore, the *P*~n~ under these conditions should be measured with particular attention on the interaction.
@@
 
-  Note that such an interaction might have impacts on the other characteristics related to the photosynthetic electron transport, such as chl fluorescence parameters and the photoinhibition indicators.
-  The overexicitation of PSII (or PSI) results in the lowered photochemical yield at PSII (or PSI) [e.g.
+<!--   Note that such an interaction might have impacts on the other characteristics related to the photosynthetic electron transport, such as chl fluorescence parameters and the photoinhibition indicators.
+-->
+<!--   The overexicitation of PSII (or PSI) results in the lowered photochemical yield at PSII (or PSI) [e.g.
 @Hogewoning_et_al2012PC; @Laisk_et_al2014BBA], and the imbalance in the excitation should haste the photoinhibition caused by the reactive oxygen species.
-  Evaluation of these characteristics should also be measured with particular care on the interaction.
+-->
+<!--   Evaluation of these characteristics should also be measured with particular care on the interaction. -->
 
-  The mechanisms of the SPD acclimation of the EED property have not yet been fully elucidated [see @Murakami_et_al2016PP].
-  <!--' @Walters_Horton1995aPlanta confirmed a typical adjustment in the photosystem stoichiometry in response to the slight difference in the SPD of growth light. -->
-  <!--' They also found no difference in the stoichiometry between the leaves grown with and without supplemental FR [@Walters_Horton1995bPlanta]. -->
-  <!--' Chow and coworkers also reported  -->
-  Considering the sensitively adjusted photosystem stoichiometry in response to the SPD of growth light [@Walters_Horton1995aPlanta], the interaction should always be taken into account whenever the *P*~n~ and related parameters are evaluated.
-  The impacts of the interaction on the *P*~n~ should be paid particular attention, at least when the measured leaves are expected to represent different EED properties.
+  The mechanisms of the acclimation of the EED properties to SPD have not yet been fully elucidated [see @Murakami_et_al2016PP].
+  Considering the sensitively adjusted photosystem stoichiometry in response to the SPD of growth light [@Walters_Horton1995aPlanta], the interaction should always be taken into account whenever the *P*~n~ and related indices are compared among the leaves grown under differet SPDs of light.
+  Particular attention should be paid to the impacts of the interaction on the *P*~n~, at least when the measured leaves are expected to represent different EED properties.
 
-  For this decade, a number of studies have investigated the effects of the SPD of growth light on the plant growth and photosynthesis [e.g.
+  For this decade, a number of studies have investigated the effects of SPD of growth light on plant growth and photosynthesis [e.g.
 @Matsuda_et_al2004PCP; @Matsuda_et_al2007SSPN; @Matsuda_et_al2008PCP; @Hogewoning_et_al2010aJXB; @Hogewoning_et_al2010bJXB; @Shibuya_et_al2015BP; @Trouwborst_et_al2016EEB].
-  Assimilation light provided by most of artificial light sources contain little FR.
-  In general, fluorescent lamps, metal halide lamps, high-pressure sodium lamps, and blue, red, and white LEDs used for assimilation lighting emit typical PSII-light (Supplemental Information S1).
-  This is because FR is not ‘photosynthetically active’ and FR-rich light promotes excessive stem elongation.
-  <!-- It should be kept in the mind that the *P*~n~ of leaves grown under these light sources can be overestimated if measured with BR-light, and the measured *P*~n~ might be different from those under the PSI-light such as sunlight (Fig.
-3XXX).
--->
-  <!-- When the response under sunlight is the interest of the experiment, we should carry out measurements under sunlight. -->
-  On the other hand, several recent papers suggest the significance of supplemental FR on the plant growth and development [for a review, see @Demote-Mainard_et_al2016EEB].
-  Since FR overexcites PSI, leaves grown under PSII-light supplemented with FR LED can represent relatively PSI-leaves like EED property compared to those grown without supplemental FR.
-  Therefore, comparing the *P*~n~ of leaves grown with and without supplemental FR using BR-light might result in typical biased evaluation caused by the interaction, as demonstrated in the previous report [@Murakami_et_al2016PP].
+  Growth light provided by most of artificial light sources contains little FR light.
+  In general, fluorescent lamps, metal halide lamps, high-pressure sodium lamps, and blue, red, and white LEDs used for assimilation lighting all emit typical PSII-light (Fig. XX).
+  This is because FR light is hardly ‘photosynthetically active’ and FR light promotes excessive stem elongation.
+  On the other hand, several recent papers suggest the significance of supplemental FR light on plant growth and development [for a review, see @Demotes-Mainard_et_al2016EEB].
+  Since FR light overexcites PSI, leaves grown under PSII-light with supplemental FR light can represent relatively PSI-leaves like EED properties compared to those grown without supplemental FR light.
+  Therefore, comparing the *P*~n~ of leaves grown with and without supplemental FR light using BR-light as measuring light might result in typical biased evaluation due to the interaction, as demonstrated in the previous report [@Murakami_et_al2016PP].
 
-  Evaluating the vertical profiles of the photosynthetic characteristics of the plant stand cultivated in greenhouses may be vulnerable to the biases in the same manner.
-  While the leaves in the upper layers were acclimated to sunlight, those in the lower layers were acclimated to the leaf transmitted light.
-  Due to the higher transmittance in the FR waveband of a leaf, leaf transmitted light contains much FR, namely PSI-light (Supplemental Information S1).
+  Evaluating vertical profiles of leaf photosynthetic characteristics of a plant stand cultivated in greenhouses may be vulnerable to the biases in the same manner.
+  While leaves in the upper layers were acclimated to sunlight, those in the lower layers were acclimated to light that has penetrated the upper leaves.
+  Due to the higher transmittance in the FR waveband of a leaf, the transmitted light incident on lower leaves contains a relatively greater proportion of FR light (Fig. XX) and is namely PSI-light.
   Therefore, when measured using BR-light, the *P*~n~ of upper leaves might be overestimated while that of lower leaves might be underestimated.
 
-# How the photosynthesis should be measured?
+# How should net photosynthetic rate be measured?
 
-  Ideally, the photosynthetic rates and related parameters should be measured under the *in situ* conditions.
-  In the prospective study focusing on the plant growth after the measurements, the measurements should be made under the SPD of light the plant will subject to.
+  Ideally, photosynthetic rates and related indices should be measured under *in situ* conditions.
+  In prospective studies focusing on plant growth after the measurements, the measurements should be made under the SPD of light that the plant will be subject to.
   For instance, evaluation of the photosynthesis of the transplants grown under artificial lighting [e.g.
-@Kozai2007POP] should be made under sunlight because they are subsequently transferred to a greenhouse and cultivated under sunlight.
-  Note that the effect of the interaction seems to be less prominent than those of the other factors, such as the incident PPFD.
-  The measurements under sunlight, which usually causes a fluctuation in the incident PPFD, should be avoided and thus the measurements should be made under the artificial light sources to ensure the reproducibility and reliability of the research.
+@Kozai2007POP] should be made under sunlight because they are subsequently transferred to a greenhouse and cultivated under sunlight **(状況の限定)**.
+  Note that the effect of the interaction seems to be less prominent than that of incident PPFD.
+  **The measurements under *actual* sunlight, which usually causes a fluctuation in the incident PPFD, should be avoided and thus the measurements should be made under the artificial light sources to ensure the reproducibility and reliability of the research.**
   The use of artificial light sources will mitigate the uncertainty caused by the fluctuation in the incident PPFD at the expense of the possible biases caused by the interaction.
-  This is because the SPDs of light from the artificial light sources are generally by far different from that of *in situ* light.
+  **This (明確に)** is because the SPDs of light from the artificial light sources are generally by far different from that of *in situ* light.
   To solve this dilemma between the *in situ* evaluation and the PPFD stability, SPD-controllable light sources might be helpful [e.g. @Yano_Fujiwara2012PM; @Fujiwara_et_al2013Proc].
-  In the retrospective study aiming to elucidate the causes of the differences between the experimental groups, the measurements should be made under the SPDs of light the plants received during the treatments.
+  In retrospective studies aiming to elucidate causes of differences between the experimental groups, the measurements should be made under the SPDs of light that the plants have received during the treatments.
   <!-- When the aim of the research is to analyze the origins of the differences in the growth of the plants subject to several light treatments, the rates should be measured under the SPDs of light the plants recieved.
 -->
-  For instance, when the difference in the resultant dry weight between the plants grown under white LEDs and fluorescent lamps are analyzed and the *P*~n~ is used for the explanatory variable, the measurements should be made using the white LEDs for the plants grown under the white LEDs and using the fluorescent lamps for those grown under the fluorescent lamps.
+  For instance, when the difference in the resultant dry weight between the plants grown under white LEDs and fluorescent lamps are analyzed and the *P*~n~ is used for an explanatory variable, the measurements should be made using the white LEDs for the plants grown under the white LEDs and using the fluorescent lamps for those grown under the fluorescent lamps.
   In both the prospective and retrospective studies, these simple *in situ* measurements will eliminate the problems caused by the interaction.
 
-  If the SPD of light the leaves will subject to is not predetermined, then the measurements should be made under several levels of SPDs of light including PSII- and PSI-light.
+  If the SPD of light that the leaves will be subject to is not predetermined, then the measurements should be made under several SPDs of light including PSII- and PSI-light.
   Researchers had better report the ‘general’ characteristics of the leaves in these descriptive studies.
@@
   Imitating the various SPDs of light incident on the leaf for *in situ* evaluation might be difficult or impossible from the technical reasons.
-  In addition, measuring the *P*~n~ under multi-levels of SPDs costs much more time, resource, and labor.
+  In addition, measuring the *P*~n~ under multi-levels of SPDs is time-, resource-, and labor-consuming.
   Thus, these two approaches might not always be applied for evaluation of the leaf *P*~n~.
-  Further research is required to make the quantitative analysis of the leaf *P*~n~ in response to the SPD of measuring light.
+  At least in cases, measuements should be 少なくともできる場合には、努力すべきだ
 
@@
 
-<!-- ![Fig.
-2  The likely cause of the interaction of the spectral PFD distributions (SPD) of growth light and measuring light on the electron transport rate (ETR) via the excitation energy distribution (EED)](FigPath.png) -->
+```{r, eval = evalFig, fig.cap = CapEED}
+EEDs
+```
 
@@
 
-```{r child = "~/Dropbox/Publish/ECB2016Review/Sup1.Rmd"}
-
+```{r FigSPD, eval = evalFig, fig.width = 5, fig.height = 5, out.width = '500pixel', out.height = '500pixel'}
+SPDs
 ```

### 2016-07-31 Main.Rmd
直し進め。 2895 words.

@@
 ---
-title: "A practical guide for selecting the spectral photon flux density distribution of light for comparing photosynthetic rates of leaves grown under different spectral light conditions"
+title: "A practical guide for selecting the spectral photon flux density distribution of light for comparing photosynthetic rates of leaves grown under different spectral light environments"
 author: "Keach Murakami^1\\*^, Ryo Matsuda^1^, Kazuhiro Fujiwara^1^"
@@
   - \newcommand{\edoublespace}{\end{spacing}{1.5}} # 行間を広げるbegin command
-
 output:
@@
 ---
-
-@JIS_sunlight
 
@@
 1  The conceptual diagrams of the effects of the excitation energy distribution between the photosystems (PSII and PSI) on the photosynthetic electron transport rate (ETR).
-Electron flow (grey lines) and energy flow (black lines) of leaves grown under PSII-light (A, B) and PSI-light (C, D) measured using PSII-light (A, C) and PSI-light (B, D) were shown."
+Electron flow (grey lines) and energy flow (black lines) of leaves grown under PSII-light (A, B) and PSI-light (C, D) measured using PSII-light (A, C) and PSI-light (B, D) were shown.
+The leaves grown under PSII-light "
 
 CapEED <-
-  "Fig. 2  The excitation balance between photosystems in response to wavelength of light."
+  "Fig. 2  The excitation balance between photosystems in response to wavelength of measuring light. "
 
@@
 2016).
-The far-red waveband (700--750 nm) is filled in grey.
-<br><sup>1</sup>IWASAKI ELECTRIC CO., LTD, Tokyo, Japan; <sup>2</sup>Tricon Co., Shimane, Japan; <sup>3</sup>Epitex Inc., Kyoto, Japan; <sup>4</sup>Nichia Chemical Industries Ltd., Tokushima, Japan."
+The far-red waveband (700--750 nm) is filled in grey.<br><sup>1</sup>IWASAKI ELECTRIC CO., LTD, Tokyo, Japan; <sup>2</sup>Tricon Co., Shimane, Japan; <sup>3</sup>Epitex Inc., Kyoto, Japan; <sup>4</sup>Nichia Chemical Industries Ltd., Tokushima, Japan."
 ```
@@
   Reduce(Join_by, list(Abs_PSII, Abs_PSI)) %>%
-  filter(wavelength %% 1 == 0)
+  filter(wavelength %% 1 == 0) %>%
+  na.omit
 
-Abs_ratio <-
-  function(cut_row, simulate){
-    simulate_dat <-
-      simulate %>% slice(cut_row)
-
-    Infos <-
-      data.frame(`L_RCII` = simulate_dat$L_trimer_per_RCII,
-                 `L2_L1L2` = simulate_dat$L_trimer_to_PSII,
-                 `RCI_RCII` = simulate_dat$RCI_per_RCII)
-
-    Mole_abs %>%
-      transmute(
-        wavelength,
-        # AlltoPSII = ((PSII + Infos[1, 1] * Infos[1, 2] * LHCII) / (Infos[1, 3] * PSI + PSII + Infos[1, 1] * LHCII))
-        AlltoPSII = PSII / (PSII + Infos[1,3] * PSI)
-      ) %>%
-      list(data = ., Info = Infos) %>%
-      return
-  }
-
-EEDs <-
+EED_dat <-
   Mole_abs %>%
@@
     AlltoPSII = PSII / (1.5 * PSI + PSII)
-  ) %>%
-  filter(AlltoPSII >= 0)  %>%
+  )
+
+EEDs <-
+  EED_dat %>%
+    mutate(All2_for = c(tail(EED_dat$AlltoPSII, -1), 0),
+           All2_back = c(0, head(EED_dat$AlltoPSII, -1)),
+           AlltoPSII = (AlltoPSII + All2_for + All2_back) / 3) %>% # get moving average
+    filter(wavelength > 400)  %>%
     replace_na(list(AlltoPSII = 0)) %>%
@@
     theme_bw2() +
-  gg_xy(c(380, 770, -0.05, 1.05)) +
+    theme(panel.grid.major = element_blank()) +
+    geom_hline(yintercept = 0.5, col = "grey50", linetype = 3) +
+    gg_xy(c(380, 770, 0, 1.0)) +
     # geom_ribbon(aes(ymin = AlltoPSII_max, ymax = AlltoPSII_min), col = "grey50") +
     geom_line() +
-  xlab("Wavelength [nm]") + ylab("")
+    xlab("Wavelength [nm]") + ylab("Fraction of the excitation energy distributed to PSII")
 ```
@@
 
-# HID_raw <-
-#   fread("~/Dropbox/R/spectrum/HID.csv", skip = 13)
-# 
-# HIDs <-
-#   HID_raw %>%
-#   setnames(., c("wavelength", paste0("ID", 1:(dim(HID_raw)[2] - 1)))) %>%
-#   select(1, HPS_ = 12, MH_ = 21)
 FL_Ocean_raw <-
@@
 
+# Sun: JIS C8904-3
 Sun <-
@@
   transmute(wavelength, Sun = Sunlight, Shade = Sunlight * (100 - ave), Absorptance = ave)
-
-# Sun: JIS C8904-3
 
@@
 
+@JIS_sunlight
 ------
@@
 
-  The photosynthetic rate is one of the most important and fundamental *traits of the plant (aspects? for growth? of plants*.
+  The photosynthetic rate is one of the most important and fundamental aspects for growth of plants.
   The rates are measured, evaluated, and compared among the leaves cultivated under different conditions.
@@
   The *P*~n~ of W-leaves was greater than that of WFR-leaves under BR-light, while the rates were comparable under the artificial sunlight [@Murakami_et_al2016PP].
-  Based on the results obtained from the measurement under BR-light, the prospective **growth (leaf photosynthetic)** rate of WFR-plants may be evaluated to be smaller than that of W-plants despite the comparable rates under sunlight.
+  Based on the results obtained from the measurement under BR-light, the prospective leaf photosynthetic rate of WFR-plants may be evaluated to be smaller than that of W-plants despite the comparable rates under sunlight.
 
@@
   In other words, the SPDs of growth light and measuring light interact on *P*~n~ of a leaf.
-  In this short article, we introduce a plausible cause of the interaction and several articles reporting the interaction.
-  We then suggest situations in which the interaction should be **particularly?** cared.
+  In this short article, we introduce a plausible cause of the interaction---**the excitation balance between the photosystems**.
+  We then suggest situations in which the interaction should be particularly cared.
   We also discuss the good practice for selecting of the SPD of measuring light for *P*~n~ measurements.
-  The SPD of light affects photosynthesis through **the other mechanisms (何のほかか、が不明瞭。EEDを上で簡単に書いておきたい)**, such as stomatal responses [@Shimazaki_et_al2007AnnRev], photoinhibition [@Zavafer_et_al2015JPP], and vertical PFD profile within a leaf [@Terashima_et_al2009PCP].
+  The SPD of light affects photosynthesis through **several mechanisms other than the excitation balance**, such as stomatal responses [@Shimazaki_et_al2007AnnRev], photoinhibition [@Zavafer_et_al2015JPP], and vertical PFD profile within a leaf [@Terashima_et_al2009PCP].
   Although these subjects are not referred in this article, the cited articles are available for these topics.
@@
   Fundamental knowledge about the photosynthetic electron transport is required to understand the mechanism of the interaction.
-  Light energy absorbed by a leaf drives the phtoosynthetic electron transport, O~2~ evolution, and CO~2~ uptake.
+  Light energy absorbed by a leaf drives the photosynthetic electron transport, O~2~ evolution, and CO~2~ uptake.
   In higher plants, the photosynthetic electron transport chain is anchored by photochemical reactions that occur at two types of photosystems, PSII and PSI.
   The reactions are powered by excitation energy derived from absorbed photons.
-  The excitation energy transferred to the reaction centers of the photosystems is consumed by the photochemical reactions **in units of moles**.
+  The excitation energy transferred to the reaction centers of the photosystems is consumed by the photochemical reactions.
   The serial photochemical reactions at PSII and PSI enables electron transfer from water to NADP^+^ (called the Z scheme).
@@
   In both cases, the excess energy is dissipated as heat and fluorescence, and thus the entire photosynthetic quantum yield---ETR per absorbed photons by the leaf---becomes smaller.
-  **Imbalanced excitation between the photosystems can harm leaves (これは強く言える？微妙)** by generating reactive oxygen species, which cause oxidative damage to chloroplast components [for reviews, see @Asada1999AnnRev; @Asada2006PP].
+  Imbalanced excitation between the photosystems is supposed to harm leaves by generating reactive oxygen species, which cause oxidative damage to chloroplast components [for reviews, see @Asada1999AnnRev; @Asada2006PP].
   Balancing the excitation energy distribution (EED) between PSII and PSI is essential for plants to keep the high photosynthetic quantum yield.
-  <!-- **おまけ部分** -->
-  <!-- Note that the balanced distribution might not be a fifty-fifty. -->
-  <!-- Even in a dark adapted helthy leaf, the yield of PSII cannot exceed 0.84 (i.e. Chl fluorescence parameter *F*~v~/*F*~m~). -->
-  <!-- Although there is no clear consensus, the maximum yield of PSI seems to be greater than that of PSII. -->
-  <!-- Therefore, under the fifty-fifty distribution, the energy supply to PSII is insufficient and that to PSI is excessive. -->
-  <!-- A little bit greater distribution to PSII might be required to make maximum use of the absorbed photons. -->
-  <!-- Gentyに触れるか？AEF -->
 
-  <!-- The imbalance in the EED between the photosystems is supposed to occur ordinarily (どこで？太陽光？). -->
-  PSII and PSI represent different light absorption spectral distributions due to the difference in the compositions of binding pigments, mainly chl *a* and chl *b*. **(図があるとわかりやすい)**
-  Within the chlorophyll (chl) absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [@Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
+  PSII and PSI represent different light absorption spectral distributions due to the difference in the compositions of binding pigments, mainly chl *a* and chl *b*.
+  Within the chlorophyll (chl) absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [Fig.
+XXX; @Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
   This is because only chl *a* can absorb the longer wavelengths of light and PSI contains a greater amount of chl *a* than PSII.
-  In contrast, monochromatic light at shorter wavelengths (< 680--690 nm) is estimated to be preferentially absorbed by PSII, or evenly absorbed by both photosystems [@Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
+  In contrast, monochromatic light at shorter wavelengths (< 680--690 nm) is estimated to be preferentially absorbed by PSII, or evenly absorbed by both photosystems [Fig.
+XXX; @Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
   These wavelength dependencies of the excitation is a determinant of the EED under a given SPD of light.
@@
 @Chow_et_al1990PNAS; @Melis1991BBA; @Pfannschmidt_et_al2001JBC; @Fan_et_al2007BBA; @Pfannschmidt_et_al2009AB; @Hogewoning_et_al2012PC].
-  **This categorization is defined in the relative scale, not in the absolute scale.「absolute」と「relative」が何を指しているのかなど，，もう少し具体的に書きたい。ある特定の葉に対してのみ定義できる**
+  **This categorization is defined for a given leaf in the relative scale, not in the absolute scale.「absolute」と「relative」が何を指しているのかなど，，もう少し具体的に書きたい。ある特定の葉に対してのみ定義できる**
   For instance, a SPD of light, which is evenly absorbed by PSII and PSI in PSII-light-grown leaves (Fig. 1A), can overexcite PSII in PSI-light-grown leaves (Fig. 1C).
@@
 @Melis1991BBA; @Pfannschmidt_et_al1999Nature].
-  **Possible involvement of the change in the composition within the respective photosystems in the acclimation to SPD was also suggested [@Walters_Horton1995bPlanta; @Murakami_et_al2016PP].
-具体的に何か、言っとくべき**
-  <!-- Galka_et_al2012PC -->
   The adjustments in the EED properties might help the leaves to keep the high photosynthetic quantum yield under growth light.
@@
   @Murakami_et_al2016PP showed the interaction in the *P*~n~ using white LED light without or with FR LED light (PSII-light and PSI-light) as growth light and BR-light (PSII-light) and the artificial sunlight (PSI-light) as measuring light.
+  The risk of the biased evaluation by the use of BR-light for *P*~n~ measurements was clearly demonstrated.
   It was clearly demonstrated that the use of BR-light for *P*~n~ measurements could result in the biased evaluation.
@@
   Therefore, the *P*~n~ under these conditions should be measured with particular attention on the interaction.
-  <!-- In contrast, under a higher PFDs and/or CO~2~ limtied conditions, the *P*~n~ is determined by the CO~2~ fixation process in the Calvin cycle rather than the ETR. -->
-  <!-- In such conditions, the effects of the biases in the ETR on *P*~n~ may be demagnified. -->
-  <!-- In our experiment, however, the interaction was observed under a high PFD (1200 µmol m^--2^ s^--1^) and a low CO~2~ concentration condition (20 Pa in the intercellular space) [@Murakami_et_al2016PP], suggesting the other factor involved in the interaction.
--->
-
-<!--   Note that such an interaction might have impacts on the other characteristics related to the photosynthetic electron transport, such as chl fluorescence parameters and the photoinhibition indicators.
--->
-<!--   The overexicitation of PSII (or PSI) results in the lowered photochemical yield at PSII (or PSI) [e.g.
-@Hogewoning_et_al2012PC; @Laisk_et_al2014BBA], and the imbalance in the excitation should haste the photoinhibition caused by the reactive oxygen species.
--->
-<!--   Evaluation of these characteristics should also be measured with particular care on the interaction. -->
 
   The mechanisms of the acclimation of the EED properties to SPD have not yet been fully elucidated [see @Murakami_et_al2016PP].
-  Considering the sensitively adjusted photosystem stoichiometry in response to the SPD of growth light [@Walters_Horton1995aPlanta], the interaction should always be taken into account whenever the *P*~n~ and related indices are compared among the leaves grown under differet SPDs of light.
+  Considering the sensitively adjusted photosystem stoichiometry in response to the SPD of growth light [@Walters_Horton1995aPlanta], the interaction should always be taken into account whenever the *P*~n~ and related indices are compared among the leaves grown under different SPDs of light.
   Particular attention should be paid to the impacts of the interaction on the *P*~n~, at least when the measured leaves are expected to represent different EED properties.
@@
   In retrospective studies aiming to elucidate causes of differences between the experimental groups, the measurements should be made under the SPDs of light that the plants have received during the treatments.
-  <!-- When the aim of the research is to analyze the origins of the differences in the growth of the plants subject to several light treatments, the rates should be measured under the SPDs of light the plants recieved.
--->
   For instance, when the difference in the resultant dry weight between the plants grown under white LEDs and fluorescent lamps are analyzed and the *P*~n~ is used for an explanatory variable, the measurements should be made using the white LEDs for the plants grown under the white LEDs and using the fluorescent lamps for those grown under the fluorescent lamps.
@@
   If any the interaction, the results should be descriptively reported and should not be generalized.
-  <!-- **The responses of the rates to both PSII- and PSI-light should be measured, compared, and reported in the paper.** -->
-  <!-- **If the significant interaction is not detected in two-way ANOVA, the main effect of the treatment can be assessed.** -->
   When the measurements were made only under a single-level of SPD of measuring light because of unavoidable circumstances, the light source must be declared in the materials and methods section so that readers can follow the SPD.
-  <!-- The effect of the incteraction should be amplified in the comparison be the leaves with different EED properties. -->
-  <!-- The interaction should be taken special care when the cases described in the **former section**. -->
 
@@
   At least in cases, measuements should be 少なくともできる場合には、努力すべきだ
+
+**Acknowledgements**
+
+  The authors are grateful to Dr Sander W. Hogewoning (Plant Lighting B.V., the Netherlands) for his kindness for 
+  This work was supported by JSPS KAKENHI Grant Number 26·9372.
 

### 2016-08-01 Header.Rmd
推敲 3070

---
title: "A guide for selecting the spectral photon flux density distribution of light for comparing photosynthetic rates of leaves grown under different spectral light environments"
author: "Keach Murakami^1\\*^, Ryo Matsuda^1^, Kazuhiro Fujiwara^1^"
bibliography: ~/GitHub/BeeLabR/BibTex/with.bib
csl: ECB.csl
header-includes:
  - \setmainfont{Helvetica}
  - \usepackage{zxjatype} # 日本語を使う
  - \setjamainfont{Hiragino Kaku Gothic Pro} # 日本語フォント
  - \usepackage{lscape} # 図を回転する
  - \newcommand{\blandscape}{\begin{landscape}} # 図回転用のbegin command
  - \newcommand{\elandscape}{\end{landscape}} # 図回転用のend command
  - \usepackage{setspace} # 行間の調節
  - \newcommand{\bdoublespace}{\begin{spacing}{1.5}} # 行間を広げるbegin command
  - \newcommand{\edoublespace}{\end{spacing}{1.5}} # 行間を広げるbegin command

output:
# pdf_document:
#   latex_engine: xelatex
#     toc: TRUE # table of contents
#     toc_depth: 3
#     number_sections: TRUE
#     fig_caption: TRUE
# fontsize: 12pt
# geometry: margin=1.2in
  html_document:
    toc: TRUE
    depth: 3
    theme: sandstone
    self_contained: TRUE
    fig_caption: TRUE
---

```{r, echo = F, message = F}
rm(list = ls())

evalFig <- T
if(evalFig){
devtools::source_url("https://raw.githubusercontent.com/KeachMurakami/Sources/master/Startup_silent.R")
} else {
library(knitr)
}

opts_chunk$set(cache = F, echo = FALSE, fig.width = 5, fig.height = 5,
               out.width = '500pixel', out.height = '500pixel', dpi = 100,
               message = FALSE, warning = FALSE, eval = T)
```

```{r, child = "./Main.Rmd"}
```

# References

### 2016-08-01 Main.Rmd
推敲 3070

@@
----
-title: "A practical guide for selecting the spectral photon flux density distribution of light for comparing photosynthetic rates of leaves grown under different spectral light environments"
-author: "Keach Murakami^1\\*^, Ryo Matsuda^1^, Kazuhiro Fujiwara^1^"
-bibliography: ~/GitHub/BeeLabR/BibTex/with.bib
-csl: ECB.csl
-header-includes:
-  - \setmainfont{Helvetica Neue} 
-  - \usepackage{zxjatype} # 日本語を使う
-  - \setjamainfont{Hiragino Kaku Gothic Pro} # 日本語フォント
-  - \usepackage{lscape} # 図を回転する
-  - \newcommand{\blandscape}{\begin{landscape}} # 図回転用のbegin command
-  - \newcommand{\elandscape}{\end{landscape}} # 図回転用のend command
-  - \usepackage{setspace} # 行間の調節
-  - \newcommand{\bdoublespace}{\begin{spacing}{1.5}} # 行間を広げるbegin command
-  - \newcommand{\edoublespace}{\end{spacing}{1.5}} # 行間を広げるbegin command
-output:
-  html_document:
-    toc: TRUE
-    depth: 3
-    theme: sandstone
-    self_contained: TRUE
-    fig_caption: TRUE
-    pandoc_args: [
-    "--latexmathml"
-    ]
-  # word_document:
-  #   pandoc_args: [
-  #   "--latexmathml"
-  #   ]
----
+```{r Captions, eval = evalFig}
+CapEED <-
+  "Fig.
+1  The excitation balance between photosystems in response to wavelength of measuring light.
+The spectrum was calculated from the absorbance spectra of PSII and PSI complexes in solvent (Hogewoning et al.
+2012)."
 
-```{r load, echo = F, message = F}
-rm(list = ls())
-
-evalFig <- T
-if(evalFig){
-devtools::source_url("https://raw.githubusercontent.com/KeachMurakami/Sources/master/Startup_silent.R")
-} else {
-library(knitr)
-}
-
-opts_chunk$set(cache = F, echo = FALSE, fig.width = 5, fig.height = 5,
-               out.width = '500pixel', out.height = '500pixel', dpi = 100,
-               message = FALSE, warning = FALSE, eval = T)
-```
-
-```{r Captions, eval = evalFig}
 CapETRs <-
   "Fig.
-1  The conceptual diagrams of the effects of the excitation energy distribution between the photosystems (PSII and PSI) on the photosynthetic electron transport rate (ETR).
+2  The conceptual diagrams of the effects of the excitation energy distribution between the photosystems (PSII and PSI) on the photosynthetic electron transport rate (ETR).
 Electron flow (grey lines) and energy flow (black lines) of leaves grown under PSII-light (A, B) and PSI-light (C, D) measured using PSII-light (A, C) and PSI-light (B, D) were shown.
-The leaves grown under PSII-light "
-
-CapEED <-
-  "Fig. 2  The excitation balance between photosystems in response to wavelength of measuring light. "
+"
 
@@
 CapSPD <-
-  "Fig.
+  'Fig.
 4  The spectral photon flux density distributions of light provided by (a) fluorescent lamp (FL; FPL55EX-N<sup>1</sup>), metal halide lamp (MH; M220FCELS-W/BUD<sup>1</sup>), and, high-pressure sodium lamp (HPS; NH220FLS<sup>1</sup>), (b) blue (B; HBL3-3S55-LE<sup>2</sup>), red (R; SRK3-3A80-LE<sup>2</sup>), far-red (FR; L735-36AU<sup>3</sup>), and white (W; NSPW310DS<sup>4</sup>) light-emitting diodes, and (c) incident and leaf transmitted sunlight.
@@
 2016).
-The far-red waveband (700--750 nm) is filled in grey.<br><sup>1</sup>IWASAKI ELECTRIC CO., LTD, Tokyo, Japan; <sup>2</sup>Tricon Co., Shimane, Japan; <sup>3</sup>Epitex Inc., Kyoto, Japan; <sup>4</sup>Nichia Chemical Industries Ltd., Tokushima, Japan."
+The far-red waveband (700--750 nm) is filled in grey.
+<sup>1</sup>IWASAKI ELECTRIC CO., LTD, Tokyo, Japan; <sup>2</sup>Tricon Co., Shimane, Japan; <sup>3</sup>Epitex Inc., Kyoto, Japan; <sup>4</sup>Nichia Chemical Industries Ltd., Tokushima, Japan.'
 ```
@@
     geom_hline(yintercept = 0.5, col = "grey50", linetype = 3) +
-    gg_xy(c(380, 770, 0, 1.0)) +
+    gg_x(c(380, 770)) +
     # geom_ribbon(aes(ymin = AlltoPSII_max, ymax = AlltoPSII_min), col = "grey50") +
     geom_line() +
+    scale_y_continuous(labels = c("0    ", "0.25", "0.50", "0.75", "1.00"),
+                       breaks = c(0, 0.25, 0.5, 0.75, 1),
+                       limits = c(0, 1.0),
+                       expand = c(0, 0)) +
     xlab("Wavelength [nm]") + ylab("Fraction of the excitation energy distributed to PSII")
@@
 
-Check terms:
-level
+  The spectral photon flux density distributions (SPDs) of durign growth and for measurements do not only directly affect the net photosynthetic rate (*P*~n~) but also interacts on it.
+  The plausible origin of the interaction, some situations in which the interaction should be concerned, and the selection of appropriate measuring light are summarized.
+  *P*~n~ should be measured under *in situ* conditions depending on the purpose of the study.
+  In prospective studies focusing on plant growth after the measurements, the measurements should be made under the SPD of light that the plant will be subject to.
+  In retrospective studies aiming to elucidate causes of differences between the experimental groups, the measurements should be made under the SPDs of light that the plants have received during the treatments.
+  In descriptive studies, *P*~n~ should be evaluated under several SPDs of measuring light to comprehend generalized characteristics.
+  *P*~n~ under a single-pattern SPD of measuring light is only an aspect of the photosynthetic characteristics of the leaf.
+  The obtained result must be discussed in connection with the SPD of measuring light so as not to make biased evaluation caused by the interaction.
 
-@JIS_sunlight
 ------
@@
 **Abbreviations**
-BR-light: blue + red LED light,
+BR-light: blue and red LED light,
 Chl: chlorophyll,
@@
 
-# How the interaction is generated? **(見出し軽すぎ)**
+# A plausible origin of the interaction
 
@@
   The serial photochemical reactions at PSII and PSI enables electron transfer from water to NADP^+^ (called the Z scheme).
-  Because the photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) through the thylakoid membranes should be limited by the slowest step (Fig. 1).
-  When the excitation energy is in excess at PSII, the **energy distribution (この書き方は，いきなりだと知らない人にはわかりにくいものと思われる。)** to PSI limits the ETR and thus the photochemical quantum yield of PSII should be lowered (Fig.
-1C).
-  When PSI absorbs the excess excitation energy, the energy distribution to PSII limits the ETR and the yield of PSI should be lowered (Fig. 1B).
-  In both cases, the excess energy is dissipated as heat and fluorescence, and thus the entire photosynthetic quantum yield---ETR per absorbed photons by the leaf---becomes smaller.
-  Imbalanced excitation between the photosystems is supposed to harm leaves by generating reactive oxygen species, which cause oxidative damage to chloroplast components [for reviews, see @Asada1999AnnRev; @Asada2006PP].
-  Balancing the excitation energy distribution (EED) between PSII and PSI is essential for plants to keep the high photosynthetic quantum yield.
 
@@
   Within the chlorophyll (chl) absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [Fig.
-XXX; @Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
+1; @Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
   This is because only chl *a* can absorb the longer wavelengths of light and PSI contains a greater amount of chl *a* than PSII.
   In contrast, monochromatic light at shorter wavelengths (< 680--690 nm) is estimated to be preferentially absorbed by PSII, or evenly absorbed by both photosystems [Fig.
-XXX; @Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
+1; @Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
   These wavelength dependencies of the excitation is a determinant of the EED under a given SPD of light.
   In studies on the acclimation of the photosynthetic apparatus to the SPD of growth light, light with a given SPD is categorized as either PSII- or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI [e.g.
-@Chow_et_al1990PNAS; @Melis1991BBA; @Pfannschmidt_et_al2001JBC; @Fan_et_al2007BBA; @Pfannschmidt_et_al2009AB; @Hogewoning_et_al2012PC].
-  **This categorization is defined for a given leaf in the relative scale, not in the absolute scale.「absolute」と「relative」が何を指しているのかなど，，もう少し具体的に書きたい。ある特定の葉に対してのみ定義できる**
-  For instance, a SPD of light, which is evenly absorbed by PSII and PSI in PSII-light-grown leaves (Fig. 1A), can overexcite PSII in PSI-light-grown leaves (Fig. 1C).
+@Chow_et_al1990PNAS; @Melis1991BBA; @Pfannschmidt_et_al2001JBC; @Fan_et_al2007BBA; @Dietzel_et_al2008FJ; @Pfannschmidt_et_al2009AB; @Dietzel_et_al2011PC; @Hogewoning_et_al2012PC].
+  This categorization is defined for a given leaf in the relative scale, not in the absolute scale.
+  For instance, a SPD of light, which is evenly absorbed by PSII and PSI in PSII-light-grown leaves (Fig. 2A), can overexcite PSII in PSI-light-grown leaves (Fig. 2C).
   Thus, the terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context.
+
+  Because the photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) through the thylakoid membranes should be limited by the slowest step (Fig. 2).
+  **When the excitation energy is in excess at PSII, the fewer energy distributed to PSI results in the smaller photochemical reaction rate in PSI.**
+  **This shortage in PSI limits the ETR and therefore the photochemical quantum yield of PSII should be lowered (Fig. 2C).**
+  When PSI absorbs the excess excitation energy, the energy distribution to PSII limits the ETR and the yield of PSI should be lowered (Fig. 2B).
+  In both cases, the excess energy is dissipated mainly as heat and fluorescence, and thus the entire photosynthetic quantum yield---ETR per absorbed photons by the leaf---becomes smaller.
+  Imbalanced excitation between the photosystems is supposed to harm leaves by generating reactive oxygen species, which cause oxidative damage to chloroplast components [for reviews, see @Asada1999AnnRev; @Asada2006PP].
+  Balancing the excitation energy distribution (EED) between PSII and PSI is essential for plants to keep the high photosynthetic quantum yield.
 
@@
 @Melis1991BBA; @Pfannschmidt_et_al1999Nature].
-  The adjustments in the EED properties might help the leaves to keep the high photosynthetic quantum yield under growth light.
+  As a result of these resposes adjusting the EED, the excitation spectrum (Fig. XXX) differs depending on the SPD of grown light.
+  The adjustments in the EED properties might help the leaves to keep the high photosynthetic quantum yield under growth light [@Chow_et_al1990PNAS].
   In the short term within an hour, an imbalance in the EED is, at least partly, relieved by the reversible allocation of the light-harvesting antenna complex of PSII (LHCII) between PSII and PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].
@@
   When measured under the PSII-light, the yield was higher in the PSII-light-grown leaves; when measured under the PSI-light, the yield was higher in the PSI-light-grown leaves.
-  Similar trends were observed in *Arabidopsis thaliana* [@Walters_Horton1995aPlanta] and *Cucumis sativus* [@Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
-  @Hogewoning_et_al2012PC observed the interaction in the photosynthetic quantum yield of CO~2~ uptake using artificial sunlight (PSII-light) and shadelight (PSI-light) as growth light and 19 kinds of monochromatic LED light as measuring light.
-  **They demonstrated that the interaction cannot occur only in the case growth light was used as measuring light but also in the case the other SPDs of light was used.**
-  @Murakami_et_al2016PP showed the interaction in the *P*~n~ using white LED light without or with FR LED light (PSII-light and PSI-light) as growth light and BR-light (PSII-light) and the artificial sunlight (PSI-light) as measuring light.
-  The risk of the biased evaluation by the use of BR-light for *P*~n~ measurements was clearly demonstrated.
-  It was clearly demonstrated that the use of BR-light for *P*~n~ measurements could result in the biased evaluation.
+  Similar trends were observed in *Arabidopsis thaliana* [@Walters_Horton1995aPlanta] and *Cucumis sativus* in the photosynthetic quantum yield of CO~2~ uptake [@Hogewoning_et_al2012PC] and in the *P*~n~ [see also Introduction; @Murakami_et_al2016PP].
 
   These reports suggest that the EED properties of a leaf might be tuned to the PSII/PSI-biased level of growth light.
-  It is expected that a leaf performs a higher ETR per absorbed photons by the photosystems under measuring light with a PSII/PSI-biased level similar to that of growth light (Fig. 2).
+  It is expected that a leaf performs a higher ETR per absorbed photons by the photosystems under measuring light with a PSII/PSI-biased level similar to that of growth light (Fig. 3).
   When leaves grown under different SPDs of light are compared and evaluated under a specific SPD of light, the results should be inevitably biased depending on the SPD of measuring light.
 
-# Where the interaction should be concerned?
+# Some situations in which the interaction should be concerned
 
@@
   Growth light provided by most of artificial light sources contains little FR light.
-  In general, fluorescent lamps, metal halide lamps, high-pressure sodium lamps, and blue, red, and white LEDs used for assimilation lighting all emit typical PSII-light (Fig. XX).
+  In general, fluorescent lamps, metal halide lamps, high-pressure sodium lamps, and blue, red, and white LEDs used for assimilation lighting all emit typical PSII-light (Fig. 4).
   This is because FR light is hardly ‘photosynthetically active’ and FR light promotes excessive stem elongation.
@@
   While leaves in the upper layers were acclimated to sunlight, those in the lower layers were acclimated to light that has penetrated the upper leaves.
-  Due to the higher transmittance in the FR waveband of a leaf, the transmitted light incident on lower leaves contains a relatively greater proportion of FR light (Fig. XX) and is namely PSI-light.
+  Due to the higher transmittance in the FR waveband of a leaf, the transmitted light incident on lower leaves contains a relatively greater proportion of FR light (Fig. 4) and is namely PSI-light.
   Therefore, when measured using BR-light, the *P*~n~ of upper leaves might be overestimated while that of lower leaves might be underestimated.
 
-# How should net photosynthetic rate be measured?
+# Appropriate SPDs of measuring light for evaluating photosythetic rates
 
@@
   In prospective studies focusing on plant growth after the measurements, the measurements should be made under the SPD of light that the plant will be subject to.
-  For instance, evaluation of the photosynthesis of the transplants grown under artificial lighting [e.g.
-@Kozai2007POP] should be made under sunlight because they are subsequently transferred to a greenhouse and cultivated under sunlight **(状況の限定)**.
-  Note that the effect of the interaction seems to be less prominent than that of incident PPFD.
-  **The measurements under *actual* sunlight, which usually causes a fluctuation in the incident PPFD, should be avoided and thus the measurements should be made under the artificial light sources to ensure the reproducibility and reliability of the research.**
-  The use of artificial light sources will mitigate the uncertainty caused by the fluctuation in the incident PPFD at the expense of the possible biases caused by the interaction.
-  **This (明確に)** is because the SPDs of light from the artificial light sources are generally by far different from that of *in situ* light.
-  To solve this dilemma between the *in situ* evaluation and the PPFD stability, SPD-controllable light sources might be helpful [e.g. @Yano_Fujiwara2012PM; @Fujiwara_et_al2013Proc].
+  For instance, in case of evaluation of the transplants grown under artificial lighting [e.g.
+@Kozai2007POP] from the the prospective viewpoint, the measurements should be made under sunlight because they are subsequently transferred to a greenhouse and cultivated under sunlight.
+  However, the measurements under sunlight might become uncertain due to fluctations in the incident PPFD.
+  SPD-controllable light sources might be helpful [e.g.
+@Yano_Fujiwara2012PM; @Fujiwara_et_al2013Proc] to make *in situ* evaluation under a PPFD stable condition and to ensure the reproducibility and reliability of studies.
   In retrospective studies aiming to elucidate causes of differences between the experimental groups, the measurements should be made under the SPDs of light that the plants have received during the treatments.
   For instance, when the difference in the resultant dry weight between the plants grown under white LEDs and fluorescent lamps are analyzed and the *P*~n~ is used for an explanatory variable, the measurements should be made using the white LEDs for the plants grown under the white LEDs and using the fluorescent lamps for those grown under the fluorescent lamps.
-  In both the prospective and retrospective studies, these simple *in situ* measurements will eliminate the problems caused by the interaction.
+  In both prospective and retrospective studies, these simple *in situ* measurements will eliminate the problems caused by the interaction.
 
@@
   If any the interaction, the results should be descriptively reported and should not be generalized.
-  When the measurements were made only under a single-level of SPD of measuring light because of unavoidable circumstances, the light source must be declared in the materials and methods section so that readers can follow the SPD.
+  When the measurements were made only under a single-pattern of SPD of measuring light because of unavoidable circumstances, the light source must be declared in the materials and methods section so that readers can follow the SPD.
 
@@
 
-  The *P*~n~ under a single-level SPD of measuring light is only an aspect of the photosynthetic characteristics of the leaf.
+  The *P*~n~ under a single-pattern SPD of measuring light is only an aspect of the photosynthetic characteristics of the leaf.
   Therefore, the obtained result must be discussed in connection with the SPD of measuring light.
-  Evaluation of the photosynthesis should be made under the *in situ* conditions or multi-levels of SPDs of measuring light so that the evaluation is not biased by the interaction.
+  Evaluation of the photosynthesis should be made under the *in situ* conditions or multi-pattern of SPDs of measuring light so that the evaluation is not biased by the interaction.
   Imitating the various SPDs of light incident on the leaf for *in situ* evaluation might be difficult or impossible from the technical reasons.
-  In addition, measuring the *P*~n~ under multi-levels of SPDs is time-, resource-, and labor-consuming.
-  Thus, these two approaches might not always be applied for evaluation of the leaf *P*~n~.
-  At least in cases, measuements should be 少なくともできる場合には、努力すべきだ
+  In addition, measuring the *P*~n~ under multi-pattern of SPDs is time-, resource-, and labor-consuming.
+  Although these two approaches might not always be applied for evaluation of the leaf *P*~n~, the interaction should be kept in mind to make circumspect conclusions.
 
@@
 
-  The authors are grateful to Dr Sander W. Hogewoning (Plant Lighting B.V., the Netherlands) for his kindness for 
+  We thank Dr Sander W. Hogewoning (Plant Lighting B.V., the Netherlands) for providing data of absorpbance spectra of photosystems.
   This work was supported by JSPS KAKENHI Grant Number 26·9372.
+
+```{r, eval = evalFig, fig.cap = CapEED}
+EEDs
+```
 
@@
 
-```{r, eval = evalFig, fig.cap = CapEED}
-EEDs
-```
-
-```{r FigInteract, eval = evalFig, fig.cap = CapInteract}
+```{r, eval = evalFig, fig.cap = CapInteract}
 InteractionView
@@
 
-```{r FigSPD, eval = evalFig, fig.width = 5, fig.height = 5, out.width = '500pixel', out.height = '500pixel'}
+```{r, eval = evalFig, htmlcap = CapSPD}
 SPDs
@@
 
-# References
+```{r, eval = evalFig, fig.cap = ""}
+```

### 2016-08-04 Header.Rmd
英文構成を依頼 (Edanz)。3089 words

@@
 ---
-title: "A guide for selecting the spectral photon flux density distribution of light for comparing photosynthetic rates of leaves grown under different spectral light environments"
+title: "Evaluating effects of light quality: A basis for selecting the spectral photon flux density distribution of light for measuring photosynthetic rates of leaves"
 author: "Keach Murakami^1\\*^, Ryo Matsuda^1^, Kazuhiro Fujiwara^1^"
@@
 
+Affiliations: ^1^Graduate School of Agricultural and Life Sciences, The University of Tokyo
+
+Address: ^1^Yayoi, Bunkyo, Tokyo, 113--8657, Japan
+
+e-mail: keach.murakami@gmail.com
+
+------
+
+**Abstract**
+
+  The spectral photon flux density distribution (SPD) of light during growth and for measurements do not only directly affect the net photosynthetic rate (*P*~n~) but also interacts on it.
+  A plausible mechanisms of the interaction, some situations in which the interaction should be concerned, and the selection of appropriate measuring light for evaluation of photosynthesis are summarized.
+  *P*~n~ should be measured under *in situ* conditions depending on the purpose of the study.
+  In prospective studies focusing on plant growth after the measurements, the measurements should be made under the SPD of light that the plant will be subject to.
+  In retrospective studies aiming to elucidate causes of differences between the experimental groups, the measurements should be made under the SPDs of light that the plants have received during the treatments.
+  In descriptive studies, *P*~n~ should be evaluated under several SPDs of measuring light to comprehend general photosynthetic characteristics of the leaves.
+  *P*~n~ under a single-pattern SPD of measuring light is only an aspect of the photosynthetic characteristics of the leaf.
+  The obtained result must be discussed in connection with the SPD of measuring light so as not to make biased evaluation caused by the interaction.
+
+------
+
+**Abbreviations**
+BR-light: blue and red LED light,
+Chl: chlorophyll,
+ETR: electron transport rate,
+FR: far-red,
+LED: light-emitting diode,
+*P*~n~: net photosynthetic rate,
+PFD: photon flux density,
+PPFD: photosynthetic photon flux density,
+PSI: photosystem I,
+PSII: photosystem II,
+SPD: relative spectral PFD distribution
+
+------
+
 ```{r, child = "./Main.Rmd"}

### 2016-08-04 Main.Rmd
英文構成を依頼 (Edanz)。3089 words

@@
-```{r Captions, eval = evalFig}
+# Introduction
+
+  The photosynthetic rate is one of the most important and fundamental aspects for growth of plants.
+  The rates are measured, evaluated, and compared among the leaves cultivated under different conditions.
+  The measured rates are also used for the calculation of the other photosynthesis-related indices, such as photosynthetic light-, water-, and nitrogen-use efficiencies.
+  In agricultural and horticultural studies, the effectiveness of treatments is sometimes discussed based on the measured photosynthetic rates and calculated indices. 
+  Therefore, accurate measurements of the photosynthetic rates must be essential.
+
+  A number of studies have reported that the relative spectral photon-flux-density (PFD) distribution (SPD) of light used for the measurement (i.e.
+measuring light or actinic light) affected leaf net photosynthetic rates (*P*~n~) [e.g.
+@McCree1972AM; @Inada1976PCP].
+  To eliminate this direct effect from the comparison, *P*~n~ is usually measured under a common SPD of measuring light irrespective of leaf growth conditions in agricultural and horticultural studies.
+  One of the most widely-used measuring light is mixture of blue and red light provided by LED light sources (BR-light) installed in commercial photosynthesis analyzing systems (e.g.
+LI6400 and LI6400XT, LI-COR Inc., Lincoln, NE; GFS-3000, Heinz Walz GmbH, Effeltrich, Germany).
+  The use of artificial light sources enables precise control of the photosynthetic PFD (PPFD) and SPD incident on the leaf and therefore ensures the reproducibility and reliability of the experiments.
+
+  @Walters2005JXB pointed out that measuring photosynthetic rates with a SPD of light different from that of growth light do not necessarily reflect the functioning of photosynthesis under growth conditions.
+  Our recent study, indeed, experimentally demonstrated this problem in *P*~n~ measurements [@Murakami_et_al2016PP].
+  In that experiment, cucumber seedlings were grown under white light-emitting diode (LED) light without and with supplemental far-red (FR) LED light (W and WFR), and subsequently *P*~n~ of the leaves were compared under BR-light and light with the SPD resembling that of sunlight (‘artificial’ sunlight).
+  The *P*~n~ of W-grown-leaves was greater than that of WFR-grown-leaves under BR-light, while the rates were comparable under the artificial sunlight [@Murakami_et_al2016PP].
+  Based on the results obtained from the measurement under BR-light, the prospective leaf photosynthetic rate of WFR-grown-plants may be evaluated to be smaller than that of W-grown-plants despite the comparable rates under sunlight.
+
+  The effect of the SPD of growth light on *P*~n~ depends on the SPD of measuring light.
+  In other words, the SPDs of growth light and measuring light interact on *P*~n~ of a leaf.
+  In this short article, we describe a plausible mechanism of the interaction through the excitation balance between the photosystems.
+  We then suggest situations in which the interaction should be particularly cared.
+  We also discuss the good practice for selecting of the SPD of measuring light for *P*~n~ measurements.
+  Several mechanisms other than the excitation balance, such as stomatal responses [@Shimazaki_et_al2007AnnRev], photoinhibition [@Zavafer_et_al2015JPP], and vertical PFD profile within a leaf [@Terashima_et_al2009PCP], affect photosynthesis through the SPD of measuring light.
+  Although these subjects are not referred in this article, the cited articles are available for these topics.
+
+# A plausible origin of the interaction
+
+  Fundamental knowledge about the photosynthetic electron transport is required to understand the mechanism of the interaction.
+  Light energy absorbed by a leaf drives the photosynthetic electron transport, O~2~ evolution, and CO~2~ uptake.
+  In higher plants, the photosynthetic electron transport chain is anchored by photochemical reactions that occur at two types of photosystems, PSII and PSI.
+  The excitation energy derived from absorbed photons and transferred to the reaction centers of the photosystems is consumed by the photochemical reactions.
+  The serial photochemical reactions at PSII and PSI enable electron transfer from water to NADP^+^, called the Z scheme.
+
+  PSII and PSI represent different spectral light absorption distributions due to the difference in the compositions of binding pigments, mainly chl *a* and chl *b*.
+  Within the chlorophyll (chl) absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [Fig.
+1; @Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
+  This is because only chl *a* can absorb longer wavelengths of light and PSI contains a greater amount of chl *a* than PSII.
+  In contrast, monochromatic light at shorter wavelengths (< 680--690 nm) is estimated to be preferentially absorbed by PSII, or evenly absorbed by both photosystems [Fig.
+1; @Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
+  These wavelength dependencies of the excitation balance between PSII and PSI determine the excitation energy distribution (EED) under a given SPD of light.
+  Light with a given SPD is sometimes categorized as either PSII- or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI [e.g.
+@Chow_et_al1990PNAS; @Melis1991BBA; @Pfannschmidt_et_al2001JBC; @Fan_et_al2007BBA; @Dietzel_et_al2008FJ; @Pfannschmidt_et_al2009AB; @Dietzel_et_al2011PC; @Hogewoning_et_al2012PC].
+
+  Because the photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) through the thylakoid membrane should be limited by the slowest step (Fig. 2).
+  When the excitation energy is in excess at PSII (i.e. under PSII-light), the fewer excitation energy distributed to PSI results in the smaller photochemical reaction rate in PSI than that in PSII.
+  This shortage in the EED to PSI limits the ETR and therefore the photochemical quantum yield of PSII should be lowered (Fig. 2C).
+  When PSI absorbs the excess excitation energy (i.e. under PSI-light), the excitation energy distributed to PSII limits the ETR and the yield of PSI should be lowered (Fig. 2B).
+  In both cases, the excess energy is dissipated mainly as heat and fluorescence, and thus the entire photosynthetic quantum yield---ETR per absorbed photons by the leaf---becomes smaller.
+  Therefore, balancing the EED between PSII and PSI is essential for plants to keep the high photosynthetic quantum yield.
+  Imbalanced excitation between the photosystems is supposed to harm leaves by generating reactive oxygen species, which cause oxidative damage to chloroplast components [for reviews, see @Asada1999AnnRev; @Asada2006PP].
+
+  Apparently, the EED at a given SPD of light is also affected by the composition of the thylakoid components, especially by the stoichiometry between PSII and PSI.
+  The stoichiometry seems to be adjusted to the SPD of growth light.
+  Under PSII-light, the relative amount of the reaction center complex of PSII to that of PSI in leaves decreases; conversely, under PSI-light, the relative amount increases to achieve a balance [e.g.
+@Melis1991BBA; @Pfannschmidt_et_al1999Nature].
+  These adjustments in the EED properties might help the leaves to keep the high photosynthetic quantum yield under growth light [@Chow_et_al1990PNAS].
+  As a result of these resposes adjusting the EED properties of a leaf, the spectrum of excitation balance (Fig. 1) differs depending on the SPD of grown light.
+  The categories of light---‘PSII-light’ and ‘PSI-light’---are defined for a given leaf in the relative scale, not in the absolute scale.
+  For instance, a SPD of light, which is evenly absorbed by PSII and PSI in PSII-light-grown leaves (Fig. 2A), can overexcite PSII in PSI-light-grown leaves (Fig. 2C).
+  Therefore, the terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context.
+  In the short term within an hour, an imbalance in the EED is, at least partly, relieved by the reversible allocation of the light-harvesting antenna complex of PSII (LHCII) between PSII and PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].
+  Although a slight imbalance in the EED might be compensated for by the state transitions, the long-term adjustments in the EED properties are supposed to occur when state transitions are insufficient to counterbalance the uneven EED [@Dietzel_et_al2008FJ].
+
+  The SPD of growth light affects the EED properties of a leaf, which modifies the responses of ETR and thereby *P*~n~ to the SPD of measuring light.
+  Thus, the SPDs of growth light and measuring light do not only directly affect the *P*~n~ but also indirectly affect it through their interaction.
+  The expected interaction has been reported in several studies [@Chow_et_al1990PNAS; @Walters_Horton1995aPlanta; @Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
+  In their pioneering study, @Chow_et_al1990PNAS grew *Pisum sativum* plants under light provided by cool-white fluorescent lamps with yellow Plexiglas (PSII-light) and incandescent bulbs with red Plexiglas (PSI-light) and measured the photosynthetic quantum yield of O~2~ evolution---O~2~ evolution rate per absorbed photons by the leaf---under the PSII- and PSI-light reciprocally.
+  When measured under the PSII-light, the yield was higher in the PSII-light-grown leaves; when measured under the PSI-light, the yield was higher in the PSI-light-grown leaves.
+  Similar trends were observed in *Arabidopsis thaliana* [@Walters_Horton1995aPlanta] and *Cucumis sativus* in the photosynthetic quantum yield of CO~2~ uptake [@Hogewoning_et_al2012PC] and in the *P*~n~ [see also Introduction; @Murakami_et_al2016PP].
+
+  These reports suggest that the EED properties of a leaf might be tuned to the PSII/PSI-biased level of growth light.
+  It is expected that a leaf performs a higher ETR per absorbed photons by the leaf under measuring light with a PSII/PSI-biased level similar to that of growth light (Fig. 3).
+  When leaves grown under different SPDs of light are compared and evaluated under a specific SPD of light, the results should be inevitably biased depending on the SPD of measuring light.
+
+# Some situations in which the interaction should be concerned
+
+  The interaction may have considerable impact on *P*~n~ especially measured under low PPFDs and/or high CO~2~ concentrations, where the ETR is a limiting factor for the photosynthetic CO~2~ fixation [@vonCaemmerer_Farquhar1981Planta].
+  Under such conditions, any bias in the ETR is directly reflected in *P*~n~.
+  Therefore, the *P*~n~ under these conditions should be measured with particular attention on the interaction.
+
+  The mechanisms of the acclimation of the EED properties to SPD have not yet been fully elucidated [see @Murakami_et_al2016PP].
+  Considering the sensitively adjusted photosystem stoichiometry in response to the SPD of growth light [@Walters_Horton1995aPlanta], the interaction should always be taken into account whenever the *P*~n~ and related indices are compared among the leaves grown under different SPDs of light.
+  Particular attention should be paid to the impacts of the interaction on the *P*~n~, at least when the measured leaves are expected to represent different EED properties.
+
+  For this decade, a number of studies have investigated the effects of SPD of growth light on plant growth and photosynthesis [e.g.
+@Matsuda_et_al2004PCP; @Matsuda_et_al2007SSPN; @Matsuda_et_al2008PCP; @Hogewoning_et_al2010aJXB; @Hogewoning_et_al2010bJXB; @Shibuya_et_al2015BP; @Trouwborst_et_al2016EEB].
+  Growth light provided by most of artificial light sources contains little FR light.
+  In general, fluorescent lamps, metal halide lamps, high-pressure sodium lamps, and blue, red, and white LEDs used for assimilation lighting all emit typical PSII-light (Fig. 4).
+  This is because FR light is hardly ‘photosynthetically active’ and FR light promotes excessive stem elongation.
+  On the other hand, several recent papers suggest the significance of supplemental FR light on plant growth and development [for a review, see @Demotes-Mainard_et_al2016EEB].
+  Since FR light overexcites PSI, leaves grown under PSII-light with supplemental FR light can represent relatively PSI-leaves like EED properties compared to those grown without supplemental FR light.
+  Therefore, comparing the *P*~n~ of leaves grown with and without supplemental FR light using BR-light as measuring light might result in typical biased evaluation due to the interaction, as demonstrated in the previous report [@Murakami_et_al2016PP].
+
+  Evaluating vertical profiles of leaf photosynthetic characteristics of a plant stand cultivated in greenhouses may be vulnerable to the biases in the same manner.
+  While leaves in the upper layers were acclimated to sunlight, those in the lower layers were acclimated to light that has penetrated the upper leaves.
+  Due to the higher transmittance in the FR waveband of a leaf, the transmitted light incident on lower leaves contains a relatively greater proportion of FR light (Fig. 4) and is namely PSI-light.
+  Therefore, when measured using BR-light, the *P*~n~ of upper leaves might be overestimated while that of lower leaves might be underestimated.
+
+# Appropriate SPDs of measuring light for evaluating photosythetic rates
+
+  Ideally, photosynthetic rates and related indices should be measured under *in situ* conditions.
+  In prospective studies focusing on plant growth after the measurements, the measurements should be made under the SPD of light that the plant will be subject to.
+  For instance, in case of evaluation of the transplants grown under artificial lighting [e.g.
+@Kozai2007POP] from the the prospective viewpoint, the measurements should be made under sunlight because they are subsequently transferred to a greenhouse and cultivated under sunlight.
+  However, the measurements under sunlight might become uncertain due to fluctations in the incident PPFD.
+  SPD-controllable light sources might be helpful [e.g.
+@Yano_Fujiwara2012PM; @Fujiwara_et_al2013Proc] to make *in situ* evaluation under a PPFD stable condition and to ensure the reproducibility and reliability of studies.
+  In retrospective studies aiming to elucidate causes of differences between the experimental groups, the measurements should be made under the SPDs of light that the plants have received during the treatments.
+  For instance, when the difference in the resultant dry weight between the plants grown under white LEDs and fluorescent lamps are analyzed and the *P*~n~ is used for an explanatory variable, the measurements should be made using the white LEDs for the plants grown under the white LEDs and using the fluorescent lamps for those grown under the fluorescent lamps.
+  In both prospective and retrospective studies, these simple *in situ* measurements will eliminate the problems caused by the interaction.
+
+  On the other hand, in descriptive studies making no assumption as to *in situ* condition, the measurements should be made under several SPDs of light including PSII- and PSI-light.
+  Researchers had better report the ‘general’ characteristics of the leaves in these studies.
+  Therefore, the interaction should be tested so as not to make biased evaluation.
+  If any the interaction, the results should be descriptively reported and should not be generalized.
+  When the measurements were made only under a single-pattern of SPD of measuring light because of unavoidable circumstances, the light source must be declared in the materials and methods section so that readers can follow the SPD.
+
+# Concluding remarks
+
+  The *P*~n~ under a single-pattern SPD of measuring light is only an aspect of the photosynthetic characteristics of the leaf.
+  Therefore, the obtained result must be discussed in connection with the SPD of measuring light.
+  Evaluation of the photosynthesis should be made under the *in situ* conditions or multi-pattern of SPDs of measuring light so that the evaluation is not biased by the interaction.
+  Imitating the various SPDs of light incident on the leaf for *in situ* evaluation might be difficult or impossible from the technical reasons.
+  In addition, measuring the *P*~n~ under multi-pattern of SPDs is time-, resource-, and labor-consuming.
+  Although these two approaches might not always be applied for evaluation of leaf *P*~n~, the interaction should always be kept in mind to make circumspect conclusions.
+
+**Acknowledgements**
+
+  We thank Dr Sander W. Hogewoning (Plant Lighting B.V., the Netherlands) for providing data of absorpbance spectra of photosystems.
+  This work was supported by JSPS KAKENHI Grant Number 26·9372.
+
+```{r Captions}
 CapEED <-
   "Fig.
-1  The excitation balance between photosystems in response to wavelength of measuring light.
-The spectrum was calculated from the absorbance spectra of PSII and PSI complexes in solvent (Hogewoning et al.
+1  Excitation balance between photosystems in response to wavelength of measuring light.
+The spectrum was calculated from absorbance spectra of PSII and PSI complexes in solvent (Hogewoning et al.
 2012)."
@@
   "Fig.
-2  The conceptual diagrams of the effects of the excitation energy distribution between the photosystems (PSII and PSI) on the photosynthetic electron transport rate (ETR).
+2  Conceptual diagrams of the effects of the excitation energy distribution between the photosystems (PSII and PSI) on the photosynthetic electron transport rate (ETR).
 Electron flow (grey lines) and energy flow (black lines) of leaves grown under PSII-light (A, B) and PSI-light (C, D) measured using PSII-light (A, C) and PSI-light (B, D) were shown.
@@
   "Fig.
-3  The conceptual diagram of the photosynthetic electron transport rates per absorbed photons by the photosystems grown under PSII-light (PSII-leaves) and PSI-light (PSI-leaves) in response to the PSII/PSI-bised level of measuring light."
+3  Conceptual diagram of the photosynthetic electron transport rates per absorbed photons by the leaf grown under PSII-light (PSII-leaves) and PSI-light (PSI-leaves) in response to the PSII/PSI-bised level of measuring light."
 
@@
   'Fig.
-4  The spectral photon flux density distributions of light provided by (a) fluorescent lamp (FL; FPL55EX-N<sup>1</sup>), metal halide lamp (MH; M220FCELS-W/BUD<sup>1</sup>), and, high-pressure sodium lamp (HPS; NH220FLS<sup>1</sup>), (b) blue (B; HBL3-3S55-LE<sup>2</sup>), red (R; SRK3-3A80-LE<sup>2</sup>), far-red (FR; L735-36AU<sup>3</sup>), and white (W; NSPW310DS<sup>4</sup>) light-emitting diodes, and (c) incident and leaf transmitted sunlight.
+4  Spectral photon flux density distributions of light provided by (a) fluorescent lamp (FL; FPL55EX-N<sup>1</sup>), metal halide lamp (MH; M220FCELS-W/BUD<sup>1</sup>), and, high-pressure sodium lamp (HPS; NH220FLS<sup>1</sup>), (b) blue (B; HBL3-3S55-LE<sup>2</sup>), red (R; SRK3-3A80-LE<sup>2</sup>), far-red (FR; L735-36AU<sup>3</sup>), and white (W; NSPW310DS<sup>4</sup>) light-emitting diodes, and (c) incident and leaf transmitted sunlight.
 The distributions at a photon flux density of 100 µmol m<sup>--2</sup> s<sup>--1</sup> within 400--750 nm are shown.
-The distribution of sunlight was adopted from JIS C 8904-3.
-The distribution of the leaf transmitted sunlight was calculated from that of sunlight and the transmittance spectrum of a cucumber leaf (Murakami et al.
-2016).
 The far-red waveband (700--750 nm) is filled in grey.
-<sup>1</sup>IWASAKI ELECTRIC CO., LTD, Tokyo, Japan; <sup>2</sup>Tricon Co., Shimane, Japan; <sup>3</sup>Epitex Inc., Kyoto, Japan; <sup>4</sup>Nichia Chemical Industries Ltd., Tokushima, Japan.'
+The distribution of sunlight was adopted from the International Electrotechnical Commission Standard 60904–3 [@IEC2007].
+The distribution of the leaf transmitted sunlight was calculated from that of incident sunlight and the transmittance spectrum of a cucumber leaf (Murakami et al.
+2016).<br><sup>1</sup>IWASAKI ELECTRIC CO., LTD, Tokyo, Japan; <sup>2</sup>Tricon Co., Shimane, Japan; <sup>3</sup>Epitex Inc., Kyoto, Japan; <sup>4</sup>Nichia Chemical Industries Ltd., Tokushima, Japan.'
 ```
@@
 
-Affiliations: ^1^Graduate School of Agricultural and Life Sciences, The University of Tokyo
-
-Address: ^1^Yayoi, Bunkyo, Tokyo, 113--8657, Japan
-
-e-mail: keach.murakami@gmail.com
-
-------
-
-**Abstract**
-
-  The spectral photon flux density distributions (SPDs) of durign growth and for measurements do not only directly affect the net photosynthetic rate (*P*~n~) but also interacts on it.
-  The plausible origin of the interaction, some situations in which the interaction should be concerned, and the selection of appropriate measuring light are summarized.
-  *P*~n~ should be measured under *in situ* conditions depending on the purpose of the study.
-  In prospective studies focusing on plant growth after the measurements, the measurements should be made under the SPD of light that the plant will be subject to.
-  In retrospective studies aiming to elucidate causes of differences between the experimental groups, the measurements should be made under the SPDs of light that the plants have received during the treatments.
-  In descriptive studies, *P*~n~ should be evaluated under several SPDs of measuring light to comprehend generalized characteristics.
-  *P*~n~ under a single-pattern SPD of measuring light is only an aspect of the photosynthetic characteristics of the leaf.
-  The obtained result must be discussed in connection with the SPD of measuring light so as not to make biased evaluation caused by the interaction.
-
-------
-
-**Abbreviations**
-BR-light: blue and red LED light,
-Chl: chlorophyll,
-ETR: electron transport rate,
-FR: far-red,
-LED: light-emitting diode,
-*P*~n~: net photosynthetic rate,
-PFD: photon flux density,
-PPFD: photosynthetic photon flux density,
-PSI: photosystem I,
-PSII: photosystem II,
-SPD: relative spectral PFD distribution
-
-------
-
-# Introduction
-
-  The photosynthetic rate is one of the most important and fundamental aspects for growth of plants.
-  The rates are measured, evaluated, and compared among the leaves cultivated under different conditions.
-  The measured rates are also used for the calculation of the other photosynthesis-related indices, such as light-, water-, and nitrogen-use efficiencies for photosynthesis.
-  In agricultural and horticultural studies, the effectiveness of treatments is sometimes discussed based on the measured photosynthetic rates and calculated parameters. 
-  Therefore, accurate measurements of the photosynthetic rates must be essential.
-
-  A number of studies have reported that the relative spectral photon-flux-density (PFD) distribution (SPD) of light used for the measurement (i.e.
-measuring light or actinic light) affected leaf net photosynthetic rates (*P*~n~) [e.g.
-@McCree1972AM; @Inada1976PCP].
-  To eliminate this direct effect from the comparison, *P*~n~ is usually measured under a common SPD of measuring light irrespective of leaf growth conditions in agricultural and horticultural studies.
-  One of the most widely-used measuring light is mixture of blue and red light provided by LED light sources (BR-light) installed in commercial photosynthesis analyzing systems (e.g.
-LI6400 and LI6400XT, LI-COR Inc.; GFS-3000, Heinz Walz GmbH).
-  The use of artificial light sources enables precise control of the photosynthetic PFD (PPFD) and SPD incident on the leaf and therefore ensure the reproducibility and reliability of the experiments.
-
-  @Walters2005JXB pointed out that measuring photosynthetic rates with a SPD of light different from that of growth light do not necessarily reflect the functioning of photosynthesis under growth conditions.
-  Our recent study, indeed, experimentally demonstrated this problem in the *P*~n~ measurements [@Murakami_et_al2016PP].
-  In that experiment, cucumber seedlings were grown under white light-emitting diode (LED) light without and with supplemental far-red (FR) LED light (W and WFR), and subsequently *P*~n~ of the leaves were compared under BR-light and light with the SPD resembling that of sunlight (‘artificial’ sunlight).
-  The *P*~n~ of W-leaves was greater than that of WFR-leaves under BR-light, while the rates were comparable under the artificial sunlight [@Murakami_et_al2016PP].
-  Based on the results obtained from the measurement under BR-light, the prospective leaf photosynthetic rate of WFR-plants may be evaluated to be smaller than that of W-plants despite the comparable rates under sunlight.
-
-  The effect of the SPD of growth light on *P*~n~ depends on the SPD of measuring light.
-  In other words, the SPDs of growth light and measuring light interact on *P*~n~ of a leaf.
-  In this short article, we introduce a plausible cause of the interaction---**the excitation balance between the photosystems**.
-  We then suggest situations in which the interaction should be particularly cared.
-  We also discuss the good practice for selecting of the SPD of measuring light for *P*~n~ measurements.
-  The SPD of light affects photosynthesis through **several mechanisms other than the excitation balance**, such as stomatal responses [@Shimazaki_et_al2007AnnRev], photoinhibition [@Zavafer_et_al2015JPP], and vertical PFD profile within a leaf [@Terashima_et_al2009PCP].
-  Although these subjects are not referred in this article, the cited articles are available for these topics.
-
-# A plausible origin of the interaction
-
-  Fundamental knowledge about the photosynthetic electron transport is required to understand the mechanism of the interaction.
-  Light energy absorbed by a leaf drives the photosynthetic electron transport, O~2~ evolution, and CO~2~ uptake.
-  In higher plants, the photosynthetic electron transport chain is anchored by photochemical reactions that occur at two types of photosystems, PSII and PSI.
-  The reactions are powered by excitation energy derived from absorbed photons.
-  The excitation energy transferred to the reaction centers of the photosystems is consumed by the photochemical reactions.
-  The serial photochemical reactions at PSII and PSI enables electron transfer from water to NADP^+^ (called the Z scheme).
-
-  PSII and PSI represent different light absorption spectral distributions due to the difference in the compositions of binding pigments, mainly chl *a* and chl *b*.
-  Within the chlorophyll (chl) absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [Fig.
-1; @Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
-  This is because only chl *a* can absorb the longer wavelengths of light and PSI contains a greater amount of chl *a* than PSII.
-  In contrast, monochromatic light at shorter wavelengths (< 680--690 nm) is estimated to be preferentially absorbed by PSII, or evenly absorbed by both photosystems [Fig.
-1; @Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
-  These wavelength dependencies of the excitation is a determinant of the EED under a given SPD of light.
-  In studies on the acclimation of the photosynthetic apparatus to the SPD of growth light, light with a given SPD is categorized as either PSII- or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI [e.g.
-@Chow_et_al1990PNAS; @Melis1991BBA; @Pfannschmidt_et_al2001JBC; @Fan_et_al2007BBA; @Dietzel_et_al2008FJ; @Pfannschmidt_et_al2009AB; @Dietzel_et_al2011PC; @Hogewoning_et_al2012PC].
-  This categorization is defined for a given leaf in the relative scale, not in the absolute scale.
-  For instance, a SPD of light, which is evenly absorbed by PSII and PSI in PSII-light-grown leaves (Fig. 2A), can overexcite PSII in PSI-light-grown leaves (Fig. 2C).
-  Thus, the terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context.
-
-  Because the photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) through the thylakoid membranes should be limited by the slowest step (Fig. 2).
-  **When the excitation energy is in excess at PSII, the fewer energy distributed to PSI results in the smaller photochemical reaction rate in PSI.**
-  **This shortage in PSI limits the ETR and therefore the photochemical quantum yield of PSII should be lowered (Fig. 2C).**
-  When PSI absorbs the excess excitation energy, the energy distribution to PSII limits the ETR and the yield of PSI should be lowered (Fig. 2B).
-  In both cases, the excess energy is dissipated mainly as heat and fluorescence, and thus the entire photosynthetic quantum yield---ETR per absorbed photons by the leaf---becomes smaller.
-  Imbalanced excitation between the photosystems is supposed to harm leaves by generating reactive oxygen species, which cause oxidative damage to chloroplast components [for reviews, see @Asada1999AnnRev; @Asada2006PP].
-  Balancing the excitation energy distribution (EED) between PSII and PSI is essential for plants to keep the high photosynthetic quantum yield.
-
-  Apparently, the EED at a given SPD of light is also affected by the composition of the thylakoid components, especially by the stoichiometry between PSII and PSI.
-  The stoichiometry seems to be adjusted to the SPD of growth light.
-  Under PSII-light, the relative amount of the reaction center complex of PSII to that of PSI in leaves decreases; conversely, under PSI-light, the relative amount increases to achieve a balance [e.g.
-@Melis1991BBA; @Pfannschmidt_et_al1999Nature].
-  As a result of these resposes adjusting the EED, the excitation spectrum (Fig. XXX) differs depending on the SPD of grown light.
-  The adjustments in the EED properties might help the leaves to keep the high photosynthetic quantum yield under growth light [@Chow_et_al1990PNAS].
-  In the short term within an hour, an imbalance in the EED is, at least partly, relieved by the reversible allocation of the light-harvesting antenna complex of PSII (LHCII) between PSII and PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].
-  Although a slight imbalance in the EED might be compensated for by the state transitions, the long-term adjustments in the EED properties are supposed to occur when state transitions are insufficient to counterbalance the uneven EED [@Dietzel_et_al2008FJ].
-
-  The SPD of growth light affects the EED properties of a leaf, which modifies the responses of ETR and thereby *P*~n~ to the SPD of measuring light.
-  Thus, the SPDs of growth light and measuring light do not only directly affect the *P*~n~ but also indirectly affect it through their interaction.
-  The expected interactions have been reported in several studies [@Chow_et_al1990PNAS; @Walters_Horton1995aPlanta; @Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
-  In their pioneering study, @Chow_et_al1990PNAS grew *Pisum sativum* plants under light provided by cool-white fluorescent lamps with yellow Plexiglas (PSII-light) and incandescent bulbs with red Plexiglas (PSI-light) and measured the photosynthetic quantum yield of O~2~ evolution---O~2~ evolution rate per absorbed photons by the leaf---under the PSII- and PSI-light reciprocally.
-  When measured under the PSII-light, the yield was higher in the PSII-light-grown leaves; when measured under the PSI-light, the yield was higher in the PSI-light-grown leaves.
-  Similar trends were observed in *Arabidopsis thaliana* [@Walters_Horton1995aPlanta] and *Cucumis sativus* in the photosynthetic quantum yield of CO~2~ uptake [@Hogewoning_et_al2012PC] and in the *P*~n~ [see also Introduction; @Murakami_et_al2016PP].
-
-  These reports suggest that the EED properties of a leaf might be tuned to the PSII/PSI-biased level of growth light.
-  It is expected that a leaf performs a higher ETR per absorbed photons by the photosystems under measuring light with a PSII/PSI-biased level similar to that of growth light (Fig. 3).
-  When leaves grown under different SPDs of light are compared and evaluated under a specific SPD of light, the results should be inevitably biased depending on the SPD of measuring light.
-
-# Some situations in which the interaction should be concerned
-
-  This interaction may have considerable impact on *P*~n~ especially measured under low PPFDs and/or high CO~2~ concentrations, where the ETR is a limiting factor for the photosynthetic CO~2~ fixation [@vonCaemmerer_Farquhar1981Planta].
-  Under such conditions, any bias in the ETR is directly reflected in *P*~n~.
-  Therefore, the *P*~n~ under these conditions should be measured with particular attention on the interaction.
-
-  The mechanisms of the acclimation of the EED properties to SPD have not yet been fully elucidated [see @Murakami_et_al2016PP].
-  Considering the sensitively adjusted photosystem stoichiometry in response to the SPD of growth light [@Walters_Horton1995aPlanta], the interaction should always be taken into account whenever the *P*~n~ and related indices are compared among the leaves grown under different SPDs of light.
-  Particular attention should be paid to the impacts of the interaction on the *P*~n~, at least when the measured leaves are expected to represent different EED properties.
-
-  For this decade, a number of studies have investigated the effects of SPD of growth light on plant growth and photosynthesis [e.g.
-@Matsuda_et_al2004PCP; @Matsuda_et_al2007SSPN; @Matsuda_et_al2008PCP; @Hogewoning_et_al2010aJXB; @Hogewoning_et_al2010bJXB; @Shibuya_et_al2015BP; @Trouwborst_et_al2016EEB].
-  Growth light provided by most of artificial light sources contains little FR light.
-  In general, fluorescent lamps, metal halide lamps, high-pressure sodium lamps, and blue, red, and white LEDs used for assimilation lighting all emit typical PSII-light (Fig. 4).
-  This is because FR light is hardly ‘photosynthetically active’ and FR light promotes excessive stem elongation.
-  On the other hand, several recent papers suggest the significance of supplemental FR light on plant growth and development [for a review, see @Demotes-Mainard_et_al2016EEB].
-  Since FR light overexcites PSI, leaves grown under PSII-light with supplemental FR light can represent relatively PSI-leaves like EED properties compared to those grown without supplemental FR light.
-  Therefore, comparing the *P*~n~ of leaves grown with and without supplemental FR light using BR-light as measuring light might result in typical biased evaluation due to the interaction, as demonstrated in the previous report [@Murakami_et_al2016PP].
-
-  Evaluating vertical profiles of leaf photosynthetic characteristics of a plant stand cultivated in greenhouses may be vulnerable to the biases in the same manner.
-  While leaves in the upper layers were acclimated to sunlight, those in the lower layers were acclimated to light that has penetrated the upper leaves.
-  Due to the higher transmittance in the FR waveband of a leaf, the transmitted light incident on lower leaves contains a relatively greater proportion of FR light (Fig. 4) and is namely PSI-light.
-  Therefore, when measured using BR-light, the *P*~n~ of upper leaves might be overestimated while that of lower leaves might be underestimated.
-
-# Appropriate SPDs of measuring light for evaluating photosythetic rates
-
-  Ideally, photosynthetic rates and related indices should be measured under *in situ* conditions.
-  In prospective studies focusing on plant growth after the measurements, the measurements should be made under the SPD of light that the plant will be subject to.
-  For instance, in case of evaluation of the transplants grown under artificial lighting [e.g.
-@Kozai2007POP] from the the prospective viewpoint, the measurements should be made under sunlight because they are subsequently transferred to a greenhouse and cultivated under sunlight.
-  However, the measurements under sunlight might become uncertain due to fluctations in the incident PPFD.
-  SPD-controllable light sources might be helpful [e.g.
-@Yano_Fujiwara2012PM; @Fujiwara_et_al2013Proc] to make *in situ* evaluation under a PPFD stable condition and to ensure the reproducibility and reliability of studies.
-  In retrospective studies aiming to elucidate causes of differences between the experimental groups, the measurements should be made under the SPDs of light that the plants have received during the treatments.
-  For instance, when the difference in the resultant dry weight between the plants grown under white LEDs and fluorescent lamps are analyzed and the *P*~n~ is used for an explanatory variable, the measurements should be made using the white LEDs for the plants grown under the white LEDs and using the fluorescent lamps for those grown under the fluorescent lamps.
-  In both prospective and retrospective studies, these simple *in situ* measurements will eliminate the problems caused by the interaction.
-
-  If the SPD of light that the leaves will be subject to is not predetermined, then the measurements should be made under several SPDs of light including PSII- and PSI-light.
-  Researchers had better report the ‘general’ characteristics of the leaves in these descriptive studies.
-  Therefore, the interaction should be tested so as not to make biased evaluation.
-  If any the interaction, the results should be descriptively reported and should not be generalized.
-  When the measurements were made only under a single-pattern of SPD of measuring light because of unavoidable circumstances, the light source must be declared in the materials and methods section so that readers can follow the SPD.
-
-# Concluding remarks
-
-  The *P*~n~ under a single-pattern SPD of measuring light is only an aspect of the photosynthetic characteristics of the leaf.
-  Therefore, the obtained result must be discussed in connection with the SPD of measuring light.
-  Evaluation of the photosynthesis should be made under the *in situ* conditions or multi-pattern of SPDs of measuring light so that the evaluation is not biased by the interaction.
-  Imitating the various SPDs of light incident on the leaf for *in situ* evaluation might be difficult or impossible from the technical reasons.
-  In addition, measuring the *P*~n~ under multi-pattern of SPDs is time-, resource-, and labor-consuming.
-  Although these two approaches might not always be applied for evaluation of the leaf *P*~n~, the interaction should be kept in mind to make circumspect conclusions.
-
-**Acknowledgements**
-
-  We thank Dr Sander W. Hogewoning (Plant Lighting B.V., the Netherlands) for providing data of absorpbance spectra of photosystems.
-  This work was supported by JSPS KAKENHI Grant Number 26·9372.
-
-```{r, eval = evalFig, fig.cap = CapEED}
+```{r, eval = evalFig, html.cap = CapEED}
 EEDs
@@
 
-```{r, eval = evalFig, fig.cap = CapETRs}
-knitr::include_graphics("FigETR.png")
+```{r, eval = evalFig, html.cap = CapETRs}
+knitr::include_graphics("./Figs/FigETR.png")
 ```
 
-```{r, eval = evalFig, fig.cap = CapInteract}
+```{r, eval = evalFig, html.cap = CapInteract}
 InteractionView
@@
 
-```{r, eval = evalFig, htmlcap = CapSPD}
+```{r, eval = evalFig, html.cap = CapSPD}
 SPDs
 ```
-
-```{r, eval = evalFig, fig.cap = ""}
-```

### 2016-08-04 NotUsed/Sup1.Rmd
英文構成を依頼 (Edanz)。3089 words

--- 2016-07-27 Sup1.Rmd
@@
 # Supplemental Information S1
-
-```{r Spectra, eval = evalFig}
-
-# set integrate ranges
-PFD_integrate_min <- 350
-PFD_integrate_max <- 750
-
-IntegratePFD <- 100
-
-panel_names <- c("(A) HIDs and fluorescent lamps", "(B) LEDs", "(C) Incident and leaf transmitted sunlight")
-
-# HID_raw <-
-#   fread("~/Dropbox/R/spectrum/HID.csv", skip = 13)
-# 
-# HIDs <-
-#   HID_raw %>%
-#   setnames(., c("wavelength", paste0("ID", 1:(dim(HID_raw)[2] - 1)))) %>%
-#   select(1, HPS_ = 12, MH_ = 21)
-FL_Ocean_raw <-
-  fread("~/Dropbox/materials/SPD_FL.csv") %>%
-  transmute(wavelength = `Wavelength[nm]`, value = FL) %>%
-  na.omit
-
-FL_Ocean_PFD <-
-  smooth.spline(FL_Ocean_raw$wavelength, FL_Ocean_raw$value) %>%
-    predict(., seq(PFD_integrate_min, PFD_integrate_max)) %>%
-    .$y %>%
-  sum
-
-FL_Ocean <-
-  FL_Ocean_raw %>%
-  mutate(value = value * 100 / FL_Ocean_PFD, variable = "FL")
-
-HPS_Ocean_raw <-
-  fread("~/Dropbox/materials/SPD_HPS.txt", skip = 50, nrow = 2000) %>%
-  rename(wavelength = V1, value = V2)
-
-HPS_Ocean_PFD <-
-  smooth.spline(HPS_Ocean_raw$wavelength, HPS_Ocean_raw$value) %>%
-    predict(., seq(PFD_integrate_min, PFD_integrate_max)) %>%
-    .$y %>%
-  sum
-
-HPS_Ocean <-
-  HPS_Ocean_raw %>%
-  mutate(value = value * 100 / HPS_Ocean_PFD, variable = "HPS")
-
-MH_Ocean_raw <-
-  fread("~/Dropbox/materials/SPD_MH.txt", skip = 50, nrow = 2000) %>%
-  rename(wavelength = V1, value = V2)
-
-MH_Ocean_PFD <-
-  smooth.spline(MH_Ocean_raw$wavelength, MH_Ocean_raw$value) %>%
-    predict(., seq(PFD_integrate_min, PFD_integrate_max)) %>%
-    .$y %>%
-  sum
-
-MH_Ocean <-
-  MH_Ocean_raw %>%
-  mutate(value = value * 100 / MH_Ocean_PFD, variable = "MH")
-
-OceanSPDs <-
-  bind_rows(FL_Ocean, HPS_Ocean, MH_Ocean) %>%
-  mutate(panel = panel_names[1])
-
-Absorptances <-
-  fread("~/Dropbox/materials/SpectrumCucumber.csv") %>%
-  filter(Trtm %in% c("W", "WFR", "FL")) %>%
-  mutate(wavelength = as.numeric(wavelength)) %>%
-  filter(variable == "absorption", Trtm == "W")
-
-Sun <-
-  fread("~/Dropbox/materials/Sunlight_JIS.csv") %>%
-  setnames(c("wavelength", "Sunlight")) %>%
-  left_join(., Absorptances, by = "wavelength") %>%
-  transmute(wavelength, Sun = Sunlight, Shade = Sunlight * (100 - ave), Absorptance = ave)
-
-# Sun: JIS C8904-3
-
-LEDs <-
-  fread("~/Dropbox/materials/SPD_FL.csv") %>%
-  transmute(wavelength = `Wavelength[nm]`, W, FR, B = B_HL, R = R_SR) %>%
-  SPDnorm(from = 350, to = 750, integratedPFD = IntegratePFD) %>%
-  gather(variable, value, -wavelength) %>%
-  mutate(panel = panel_names[2]) %>%
-  na.omit
-
-SPD_labels <-
-  data_frame(variable = c("FL", "MH", "HPS", "B", "R", "FR", "W", "Sun", "Shade"),
-             wavelength = c(435, 520, 570, 448, 660, 735, 460, 450, 700),
-             value = c(2.2, .6, 3, 4, 4.2, 3.8, 1.3, 0.6, 2),
-             label = c("FL", "MH", "HPS", "B", "R", "FR", "W", "Sunlight", "Leaf transmitted sunlight"),
-             panel = rep(panel_names,  c(3, 4, 2)))
-
-SPDs <-
-  Sun %>%
-  SPDnorm(from = 350, to = 750, integratedPFD = IntegratePFD) %>%
-  select(-Absorptance) %>%
-  gather(variable, value, -wavelength) %>%
-  mutate(panel = panel_names[3]) %>%
-  bind_rows(., OceanSPDs, LEDs) %>%
-  filter(between(wavelength, 380, 820)) %>%
-  # ggplot(aes(x = wavelength, y = value, group = variable, col = variable, linetype = variable)) +
-  ggplot(aes(x = wavelength, y = value, group = variable, col = variable)) +
-  theme_bw2() +
-  geom_rect(aes(xmin = 700, xmax = 750, ymin = 0, ymax = +Inf), fill = "grey90", col = NA) +
-  geom_line() +
-  geom_text(data = SPD_labels, aes(x = wavelength, y = value, label = label)) +
-  # scale_linetype_manual(values = c(1, 1, 3, 2, 4, 2, 2, 1, 4)) +
-  scale_color_manual(values = c("blue", "black", "darkred", "orange", "purple", "red", "grey50", "black", "black")) +
-  # facet_grid(panel ~ .) +
-  facet_wrap(~ panel, ncol = 1) +
-  gg_xy(c(380, 820, 0, 4.5)) +
-  xlab("Wavelength [nm]") + ylab(u_SPFD("Spectral photon flux density"))
-
-CapSPD <-
-  "Fig.
-S1  The spectral photon flux density distributions of light provided by (A) high-intensity discharge lamps (HIDs) and fluorescent lamps, (B) light-emitting diodes (LEDs), and (C) incident and leaf transmitted sunlight (see also Table S1).
-The distributions at a photon flux density of 100 µmol m<sup>--2</sup> s<sup>--1</sup> within 400--750 nm are shown.
-The distribution of sunlight was adopted from JIS C 8904-3.
-The distribution of the leaf transmitted sunlight was calculated from that of sunlight and the transmittance spectrum of a cucumber leaf (Murakami et al.
-2016).
-The far-red waveband (700--750 nm) is filled in grey."
-```
 
@@
 
-```{r FigSPD, eval = evalFig, fig.cap = CapSPD}
-SPDs
-```
+<!-- Table S1.  Description of the light sources and the instruments used for the measurements of the spectral photon flux density distributions.  -->
 
-Table S1.  Description of the light sources and the instruments used for the measurements of the spectral photon flux density distributions.
+<!-- | Light source (abbreviation)     | Model code                    | Measuring instrument              | -->
+<!-- |:--------------------------------|:------------------------------|:----------------------------------| -->
+<!-- | Fluorescent lamp (FL)           | FPL55EX-N<sup>\*1</sup>       | HR2000 (Ocean Optics Inc.)        | -->
+<!-- | Metal halide lamp (MH)          | M220FCELS-W/BUD<sup>\*1</sup> | HR2000 (Ocean Optics Inc.)        | -->
+<!-- | High-pressure sodium lamp (HPS) | NH220FLS<sup>\*1</sup>        | HR2000 (Ocean Optics Inc.)        | -->
+<!-- | Blue LED (B)                    | HBL3-3S55-LE<sup>\*2</sup>    | MS-720 (EKO Instruments Co. Ltd.) | -->
+<!-- | Red LED (R)                     | SRK3-3A80-LE<sup>\*2</sup>    | MS-720 (EKO Instruments Co. Ltd.) | -->
+<!-- | Far-red LED (FR)                | L735-36AU<sup>\*3</sup>       | MS-720 (EKO Instruments Co. Ltd.) | -->
+<!-- | White LED (W)                   | NSPW310DS<sup>\*4</sup>       | MS-720 (EKO Instruments Co. Ltd.) | -->
 
-| Light source (abbreviation)     | Model code                    | Measuring instrument              |
-|:--------------------------------|:------------------------------|:----------------------------------|
-| Fluorescent lamp (FL)           | FPL55EX-N<sup>\*1</sup>       | HR2000 (Ocean Optics Inc.)        |
-| Metal halide lamp (MH)          | M220FCELS-W/BUD<sup>\*1</sup> | HR2000 (Ocean Optics Inc.)        |
-| High-pressure sodium lamp (HPS) | NH220FLS<sup>\*1</sup>        | HR2000 (Ocean Optics Inc.)        |
-| Blue LED (B)                    | HBL3-3S55-LE<sup>\*2</sup>    | MS-720 (EKO Instruments Co. Ltd.) |
-| Red LED (R)                     | SRK3-3A80-LE<sup>\*2</sup>    | MS-720 (EKO Instruments Co. Ltd.) |
-| Far-red LED (FR)                | L735-36AU<sup>\*3</sup>       | MS-720 (EKO Instruments Co. Ltd.) |
-| White LED (W)                   | NSPW310DS<sup>\*4</sup>       | MS-720 (EKO Instruments Co. Ltd.) |
-
-^\*1^IWASAKI ELECTRIC CO., LTD., Tokyo, Japan; ^\*2^Tricon Co., Shimane, Japan; ^\*3^Epitex Inc., Kyoto, Japan; ^\*4^Nichia Chemical Industries Ltd., Tokushima, Japan.
+<!-- ^\*1^IWASAKI ELECTRIC CO., LTD., Tokyo, Japan; ^\*2^Tricon Co., Shimane, Japan; ^\*3^Epitex Inc., Kyoto, Japan; ^\*4^Nichia Chemical Industries Ltd., Tokushima, Japan. -->
 

### 2016-08-08 Main.Rmd
英文校正 (Edanz) を反映。3090words

@@
 
-  The photosynthetic rate is one of the most important and fundamental aspects for growth of plants.
-  The rates are measured, evaluated, and compared among the leaves cultivated under different conditions.
-  The measured rates are also used for the calculation of the other photosynthesis-related indices, such as photosynthetic light-, water-, and nitrogen-use efficiencies.
+  The photosynthetic rate is one of the most important and fundamental aspects for plant growth.
+  In many studies this rate is measured, evaluated, and compared among the leaves of plants cultivated under different conditions.
+  The measured rates are also used to calculate other photosynthesis-related indices, such as photosynthetic light-, water-, and nitrogen-use efficiencies.
   In agricultural and horticultural studies, the effectiveness of treatments is sometimes discussed based on the measured photosynthetic rates and calculated indices. 
-  Therefore, accurate measurements of the photosynthetic rates must be essential.
+  Therefore, accurate measurements of photosynthetic rates are essential.
 
-  A number of studies have reported that the relative spectral photon-flux-density (PFD) distribution (SPD) of light used for the measurement (i.e.
-measuring light or actinic light) affected leaf net photosynthetic rates (*P*~n~) [e.g.
+  A number of studies have reported that the relative spectral photon-flux-density (PFD) distribution (SPD) of light used for   measurement (i.e.
+measuring light or actinic light) affects leaf net photosynthetic rates (*P*~n~) [e.g.
 @McCree1972AM; @Inada1976PCP].
   To eliminate this direct effect from the comparison, *P*~n~ is usually measured under a common SPD of measuring light irrespective of leaf growth conditions in agricultural and horticultural studies.
-  One of the most widely-used measuring light is mixture of blue and red light provided by LED light sources (BR-light) installed in commercial photosynthesis analyzing systems (e.g.
+  One of the most widely-used measuring lights is a mixture of blue and red light (BR-light) provided by light-emitting diodes (LEDs) installed in commercial photosynthesis analysis systems (e.g.
 LI6400 and LI6400XT, LI-COR Inc., Lincoln, NE; GFS-3000, Heinz Walz GmbH, Effeltrich, Germany).
-  The use of artificial light sources enables precise control of the photosynthetic PFD (PPFD) and SPD incident on the leaf and therefore ensures the reproducibility and reliability of the experiments.
+  The use of artificial light sources enables precise control of the photosynthetic PFD (PPFD) and SPD incident on the leaf, and therefore, ensures reproducibility and reliability among experiments.
 
-  @Walters2005JXB pointed out that measuring photosynthetic rates with a SPD of light different from that of growth light do not necessarily reflect the functioning of photosynthesis under growth conditions.
-  Our recent study, indeed, experimentally demonstrated this problem in *P*~n~ measurements [@Murakami_et_al2016PP].
-  In that experiment, cucumber seedlings were grown under white light-emitting diode (LED) light without and with supplemental far-red (FR) LED light (W and WFR), and subsequently *P*~n~ of the leaves were compared under BR-light and light with the SPD resembling that of sunlight (‘artificial’ sunlight).
+  @Walters2005JXB noted that photosynthetic rates measured with a SPD of light different from that of the growth light do not necessarily reflect the functioning of photosynthesis under the actual growth conditions.
+  Indeed, we have experimentally demonstrated this problem in *P*~n~ measurements in our recent study [@Murakami_et_al2016PP].
+  In that experiment, cucumber seedlings were grown under white LED without and with supplemental far-red (FR) LED light (W and WFR, respectively), and the *P*~n~ of the leaves was subsequently compared under BR-light and under light with a SPD resembling that of sunlight (‘artificial’ sunlight).
   The *P*~n~ of W-grown-leaves was greater than that of WFR-grown-leaves under BR-light, while the rates were comparable under the artificial sunlight [@Murakami_et_al2016PP].
-  Based on the results obtained from the measurement under BR-light, the prospective leaf photosynthetic rate of WFR-grown-plants may be evaluated to be smaller than that of W-grown-plants despite the comparable rates under sunlight.
+  Based on the results obtained from measurement under BR-light, the prospective leaf photosynthetic rate of WFR-grown-plants may be evaluated to be smaller than that of W-grown-plants, despite the comparable rates under sunlight.
 
-  The effect of the SPD of growth light on *P*~n~ depends on the SPD of measuring light.
-  In other words, the SPDs of growth light and measuring light interact on *P*~n~ of a leaf.
-  In this short article, we describe a plausible mechanism of the interaction through the excitation balance between the photosystems.
-  We then suggest situations in which the interaction should be particularly cared.
-  We also discuss the good practice for selecting of the SPD of measuring light for *P*~n~ measurements.
-  Several mechanisms other than the excitation balance, such as stomatal responses [@Shimazaki_et_al2007AnnRev], photoinhibition [@Zavafer_et_al2015JPP], and vertical PFD profile within a leaf [@Terashima_et_al2009PCP], affect photosynthesis through the SPD of measuring light.
-  Although these subjects are not referred in this article, the cited articles are available for these topics.
+  The effect of the SPD of growth light on *P*~n~ depends on the SPD of the measuring light.
+  In other words, the interaction between the SPDs of the growth light and the measuring light affect the *P*~n~ of a leaf.
+  In this short article, we describe a plausible mechanism for this interaction, based on the excitation energy distribution balance between the photosystems.
+  We then suggest situations in which the interaction should be particularly considered.
+  We also discuss good practice for selecting measuring light with an appropriate SPD for *P*~n~ measurements.
+  Several mechanisms other than the excitation balance, such as stomatal responses [@Shimazaki_et_al2007AnnRev], photoinhibition [@Zavafer_et_al2015JPP], and vertical PFD profile within a leaf [@Terashima_et_al2009PCP] affect photosynthesis via the SPD of measuring light.
+  Although these subjects are not discussed in this article, several cited articles are available for these topics.
 
-# A plausible origin of the interaction
+# Plausible origin of the interaction
 
-  Fundamental knowledge about the photosynthetic electron transport is required to understand the mechanism of the interaction.
-  Light energy absorbed by a leaf drives the photosynthetic electron transport, O~2~ evolution, and CO~2~ uptake.
-  In higher plants, the photosynthetic electron transport chain is anchored by photochemical reactions that occur at two types of photosystems, PSII and PSI.
-  The excitation energy derived from absorbed photons and transferred to the reaction centers of the photosystems is consumed by the photochemical reactions.
-  The serial photochemical reactions at PSII and PSI enable electron transfer from water to NADP^+^, called the Z scheme.
+  Fundamental knowledge about photosynthetic electron transport is required to understand the mechanism of the interaction.
+  Light energy absorbed by a leaf drives photosynthetic electron transport, O~2~ evolution, and CO~2~ uptake.
+  In higher plants, the photosynthetic electron transport chain is anchored by photochemical reactions that occur at the two photosystems; PSII and PSI.
+  The excitation energy derived from absorbed photons and transferred to the reaction centers of the photosystems is consumed by photochemical reactions.
+  The serial photochemical reactions at PSII and PSI enable electron transfer from water to NADP^+^, via the so-called Z scheme.
 
-  PSII and PSI represent different spectral light absorption distributions due to the difference in the compositions of binding pigments, mainly chl *a* and chl *b*.
+  The two photosystems---PSII and PSI---represent different spectral light absorption distributions due to their different compositions of binding pigments, mainly chl *a* and chl *b*.
   Within the chlorophyll (chl) absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [Fig.
 1; @Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
-  This is because only chl *a* can absorb longer wavelengths of light and PSI contains a greater amount of chl *a* than PSII.
+  This is because only chl *a* can absorb longer wavelengths of light, and PSI contains more chl *a* than does PSII.
   In contrast, monochromatic light at shorter wavelengths (< 680--690 nm) is estimated to be preferentially absorbed by PSII, or evenly absorbed by both photosystems [Fig.
@@
 
-  Because the photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) through the thylakoid membrane should be limited by the slowest step (Fig. 2).
-  When the excitation energy is in excess at PSII (i.e. under PSII-light), the fewer excitation energy distributed to PSI results in the smaller photochemical reaction rate in PSI than that in PSII.
-  This shortage in the EED to PSI limits the ETR and therefore the photochemical quantum yield of PSII should be lowered (Fig. 2C).
-  When PSI absorbs the excess excitation energy (i.e. under PSI-light), the excitation energy distributed to PSII limits the ETR and the yield of PSI should be lowered (Fig. 2B).
-  In both cases, the excess energy is dissipated mainly as heat and fluorescence, and thus the entire photosynthetic quantum yield---ETR per absorbed photons by the leaf---becomes smaller.
-  Therefore, balancing the EED between PSII and PSI is essential for plants to keep the high photosynthetic quantum yield.
-  Imbalanced excitation between the photosystems is supposed to harm leaves by generating reactive oxygen species, which cause oxidative damage to chloroplast components [for reviews, see @Asada1999AnnRev; @Asada2006PP].
+  Because the photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) through the thylakoid membrane is limited by the slowest step (Fig. 2).
+  When there is excess excitation energy at PSII (i.e. under PSII-light), the smaller amoutn of excitation energy distributed to PSI results in lower photochemical reaction rates at PSI than at PSII.
+  This shortage in the EED to PSI limits the ETR, thereby leading to lwoer photochemical quantum yield of PSII (Fig. 2C).
+  When PSI absorbs excess excitation energy (i.e. under PSI-light), the excitation energy distributed to PSII limits the ETR and lowers the yield of PSI (Fig. 2B).
+  In both cases, the excess energy is dissipated mainly as heat and fluorescence.
+  Consequently, the entire photosynthetic quantum yield---ETR per absorbed photons by the leaf---becomes smaller.
+  Therefore, balancing the EED between PSII and PSI is essential for plants to retain a high photosynthetic quantum yield.
+  Imbalanced excitation between the photosystems is supposed to damage leaves by generating reactive oxygen species, which cause oxidative damage to chloroplast components [for reviews, see @Asada1999AnnRev; @Asada2006PP].
 
-  Apparently, the EED at a given SPD of light is also affected by the composition of the thylakoid components, especially by the stoichiometry between PSII and PSI.
-  The stoichiometry seems to be adjusted to the SPD of growth light.
+  Apparently, the EED at a given SPD of light is also affected by the composition of the thylakoid components, especially the stoichiometry between PSII and PSI.
+  The stoichiometry appears to adjust to the SPD of the growth light.
   Under PSII-light, the relative amount of the reaction center complex of PSII to that of PSI in leaves decreases; conversely, under PSI-light, the relative amount increases to achieve a balance [e.g.
 @Melis1991BBA; @Pfannschmidt_et_al1999Nature].
-  These adjustments in the EED properties might help the leaves to keep the high photosynthetic quantum yield under growth light [@Chow_et_al1990PNAS].
-  As a result of these resposes adjusting the EED properties of a leaf, the spectrum of excitation balance (Fig. 1) differs depending on the SPD of grown light.
-  The categories of light---‘PSII-light’ and ‘PSI-light’---are defined for a given leaf in the relative scale, not in the absolute scale.
-  For instance, a SPD of light, which is evenly absorbed by PSII and PSI in PSII-light-grown leaves (Fig. 2A), can overexcite PSII in PSI-light-grown leaves (Fig. 2C).
+  These adjustments in the EED properties might help the leaves to maintain a high photosynthetic quantum yield under different growth lights [@Chow_et_al1990PNAS].
+  As a result of these adjustments in the EED properties of a leaf, the spectrum of excitation balance (Fig. 1) differs depending on the SPD of the growth light.
+  **PSII-light PSI-light が使われることがある**.
+  The categories of light, that is, ‘PSII-light’ and ‘PSI-light’, are defined for a given leaf on a relative scale, not an absolute scale.
+  For instance, the SPD of light that is evenly absorbed by PSII and PSI in PSII-light-grown leaves (Fig. 2A), can overexcite PSII in PSI-light-grown leaves (Fig. 2C).
   Therefore, the terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context.
-  In the short term within an hour, an imbalance in the EED is, at least partly, relieved by the reversible allocation of the light-harvesting antenna complex of PSII (LHCII) between PSII and PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].
-  Although a slight imbalance in the EED might be compensated for by the state transitions, the long-term adjustments in the EED properties are supposed to occur when state transitions are insufficient to counterbalance the uneven EED [@Dietzel_et_al2008FJ].
+  In the short term within an hour, an imbalance in the EED is, at least partly, relieved by the reversible allocation of the light-harvesting antenna complexes of PSII (LHCII) between PSII and PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].
+  Although a slight imbalance in the EED might be compensated for by state transitions, the long-term adjustments in the EED properties are thought to occur when state transitions are insufficient to counterbalance the uneven EED [@Dietzel_et_al2008FJ].
 
-  The SPD of growth light affects the EED properties of a leaf, which modifies the responses of ETR and thereby *P*~n~ to the SPD of measuring light.
-  Thus, the SPDs of growth light and measuring light do not only directly affect the *P*~n~ but also indirectly affect it through their interaction.
-  The expected interaction has been reported in several studies [@Chow_et_al1990PNAS; @Walters_Horton1995aPlanta; @Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
-  In their pioneering study, @Chow_et_al1990PNAS grew *Pisum sativum* plants under light provided by cool-white fluorescent lamps with yellow Plexiglas (PSII-light) and incandescent bulbs with red Plexiglas (PSI-light) and measured the photosynthetic quantum yield of O~2~ evolution---O~2~ evolution rate per absorbed photons by the leaf---under the PSII- and PSI-light reciprocally.
-  When measured under the PSII-light, the yield was higher in the PSII-light-grown leaves; when measured under the PSI-light, the yield was higher in the PSI-light-grown leaves.
-  Similar trends were observed in *Arabidopsis thaliana* [@Walters_Horton1995aPlanta] and *Cucumis sativus* in the photosynthetic quantum yield of CO~2~ uptake [@Hogewoning_et_al2012PC] and in the *P*~n~ [see also Introduction; @Murakami_et_al2016PP].
+  The SPD of growth light affects the EED properties of a leaf.
+  This modifies the ETR responses, and therefore the *P*~n~, to the SPD of measuring light.
+  Thus, the SPDs of growth light and measuring light not only directly affect the *P*~n~, but also indirectly affect it through their interaction.
+  This expected interaction has been reported in several studies [@Chow_et_al1990PNAS; @Walters_Horton1995aPlanta; @Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
+  In their pioneering study, @Chow_et_al1990PNAS grew *Pisum sativum* plants under light provided by cool-white fluorescent lamps with yellow Plexiglas (PSII-light) and incandescent bulbs with red Plexiglas (PSI-light) and measured the photosynthetic quantum yield of O~2~ evolution---O~2~ evolution rate per absorbed photons by the leaf---under the PSII- and PSI-lights reciprocally.
+  When measured under PSII-light, the yield was higher in the PSII-light-grown leaves; when measured under PSI-light, the yield was higher in the PSI-light-grown leaves.
+  Similar trends in the photosynthetic quantum yield of O~2~ evolution [in *Arabidopsis thaliana*; @Walters_Horton1995aPlanta], in the photosynthetic quantum yield of CO~2~ uptake [in *Cucumis sativus*; @Hogewoning_et_al2012PC], and in *P*~n~ [in *C.
+sativus*, see also Introduction; @Murakami_et_al2016PP] were observed.
 
-  These reports suggest that the EED properties of a leaf might be tuned to the PSII/PSI-biased level of growth light.
-  It is expected that a leaf performs a higher ETR per absorbed photons by the leaf under measuring light with a PSII/PSI-biased level similar to that of growth light (Fig. 3).
-  When leaves grown under different SPDs of light are compared and evaluated under a specific SPD of light, the results should be inevitably biased depending on the SPD of measuring light.
+  These reports suggested that the EED properties of a leaf might be tuned to the PSII/PSI-biased level of the growth light.
+  It is expected that a leaf will perform a higher ETR per absorbed photons by the leaf under a measuring light with a PSII/PSI-biased level similar to that of the growth light (Fig. 3).
+  When leaves grown under different SPDs of light are compared and evaluated under a specific SPD of light, the results will inevitably be biased depending on the SPD of the measuring light.
 
@@
 
-  The interaction may have considerable impact on *P*~n~ especially measured under low PPFDs and/or high CO~2~ concentrations, where the ETR is a limiting factor for the photosynthetic CO~2~ fixation [@vonCaemmerer_Farquhar1981Planta].
+  The interaction may have a considerable impact on *P*~n~, especially when it is measured under low PPFDs and/or high CO~2~ concentrations, where the ETR is a limiting factor for photosynthetic CO~2~ fixation [@vonCaemmerer_Farquhar1981Planta].
   Under such conditions, any bias in the ETR is directly reflected in *P*~n~.
-  Therefore, the *P*~n~ under these conditions should be measured with particular attention on the interaction.
+  Therefore, the interaction should be considered carefully when measuring *P*~n~ under such conditions.
 
-  The mechanisms of the acclimation of the EED properties to SPD have not yet been fully elucidated [see @Murakami_et_al2016PP].
-  Considering the sensitively adjusted photosystem stoichiometry in response to the SPD of growth light [@Walters_Horton1995aPlanta], the interaction should always be taken into account whenever the *P*~n~ and related indices are compared among the leaves grown under different SPDs of light.
-  Particular attention should be paid to the impacts of the interaction on the *P*~n~, at least when the measured leaves are expected to represent different EED properties.
+  The mechanisms of how EED properties adapt to SPD have not yet been fully elucidated [see @Murakami_et_al2016PP].
+  Considering the sensitive adjustments of photosystem stoichiometry in response to the SPD of growth light [e.g.
+@Walters_Horton1995aPlanta], the interaction should always be taken into account whenever the *P*~n~ and related indices are compared among leaves grown under different SPDs of light.
+  Particular attention should be paid to the effects of the interaction on *P*~n~, at least when the measured leaves are expected to represent different EED properties.
 
-  For this decade, a number of studies have investigated the effects of SPD of growth light on plant growth and photosynthesis [e.g.
+  Several studies published over the last decade have investigated the effects of the SPD of the growth light on plant growth and photosynthesis [e.g.
 @Matsuda_et_al2004PCP; @Matsuda_et_al2007SSPN; @Matsuda_et_al2008PCP; @Hogewoning_et_al2010aJXB; @Hogewoning_et_al2010bJXB; @Shibuya_et_al2015BP; @Trouwborst_et_al2016EEB].
-  Growth light provided by most of artificial light sources contains little FR light.
+  Growth light provided by most artificial light sources contains little FR light.
   In general, fluorescent lamps, metal halide lamps, high-pressure sodium lamps, and blue, red, and white LEDs used for assimilation lighting all emit typical PSII-light (Fig. 4).
-  This is because FR light is hardly ‘photosynthetically active’ and FR light promotes excessive stem elongation.
-  On the other hand, several recent papers suggest the significance of supplemental FR light on plant growth and development [for a review, see @Demotes-Mainard_et_al2016EEB].
-  Since FR light overexcites PSI, leaves grown under PSII-light with supplemental FR light can represent relatively PSI-leaves like EED properties compared to those grown without supplemental FR light.
-  Therefore, comparing the *P*~n~ of leaves grown with and without supplemental FR light using BR-light as measuring light might result in typical biased evaluation due to the interaction, as demonstrated in the previous report [@Murakami_et_al2016PP].
+  This is because FR light is hardly ‘photosynthetically active’ and promotes excessive stem elongation.
+  However, several recent papers have suggested the significance of supplemental FR light on plant growth and development [for a review, see @Demotes-Mainard_et_al2016EEB].
+  Since FR light overexcites PSI, leaves grown under PSII-light with supplemental FR light are more similar to PSI-leaves in terms of their EED properties, compared with leaves of plants grown without supplemental FR light.
+  Therefore, comparing the *P*~n~ of leaves of plants grown with and without supplemental FR light using BR-light as the measuring light might lead to a biased evaluation because of the interaction, as demonstrated in our recent report [@Murakami_et_al2016PP].
 
-  Evaluating vertical profiles of leaf photosynthetic characteristics of a plant stand cultivated in greenhouses may be vulnerable to the biases in the same manner.
-  While leaves in the upper layers were acclimated to sunlight, those in the lower layers were acclimated to light that has penetrated the upper leaves.
-  Due to the higher transmittance in the FR waveband of a leaf, the transmitted light incident on lower leaves contains a relatively greater proportion of FR light (Fig. 4) and is namely PSI-light.
-  Therefore, when measured using BR-light, the *P*~n~ of upper leaves might be overestimated while that of lower leaves might be underestimated.
+  Such biases can also occur when evaluating the vertical profiles of leaf photosynthetic characteristics of plants cultivated in greenhouses.
+  While leaves in the upper layers are acclimated to sunlight, those in the lower layers are acclimated to light that has penetrated through the upper leaves.
+  Due to the higher transmittance in the FR waveband of a leaf, the transmitted light incident on lower leaves contains a relatively greater proportion of FR light (Fig. 4) and is therefore PSI-light.
+  Consequently, when measured using BR-light, the *P*~n~ of upper leaves might be overestimated while that of lower leaves might be underestimated.
 
-# Appropriate SPDs of measuring light for evaluating photosythetic rates
+# Selecting appropriate SPDs of measuring light for evaluating photosynthetic rates
 
   Ideally, photosynthetic rates and related indices should be measured under *in situ* conditions.
-  In prospective studies focusing on plant growth after the measurements, the measurements should be made under the SPD of light that the plant will be subject to.
-  For instance, in case of evaluation of the transplants grown under artificial lighting [e.g.
-@Kozai2007POP] from the the prospective viewpoint, the measurements should be made under sunlight because they are subsequently transferred to a greenhouse and cultivated under sunlight.
-  However, the measurements under sunlight might become uncertain due to fluctations in the incident PPFD.
-  SPD-controllable light sources might be helpful [e.g.
-@Yano_Fujiwara2012PM; @Fujiwara_et_al2013Proc] to make *in situ* evaluation under a PPFD stable condition and to ensure the reproducibility and reliability of studies.
-  In retrospective studies aiming to elucidate causes of differences between the experimental groups, the measurements should be made under the SPDs of light that the plants have received during the treatments.
-  For instance, when the difference in the resultant dry weight between the plants grown under white LEDs and fluorescent lamps are analyzed and the *P*~n~ is used for an explanatory variable, the measurements should be made using the white LEDs for the plants grown under the white LEDs and using the fluorescent lamps for those grown under the fluorescent lamps.
-  In both prospective and retrospective studies, these simple *in situ* measurements will eliminate the problems caused by the interaction.
+  In prospective studies focusing on plant growth after measurements, the measurements should be made under the SPD of light that the plant will be subjected to.
+  For instance, when evaluating plants grown under artificial lighting that will be transplanted [e.g.
+@Kozai2007POP], the measurements should be made under sunlight because the plants will be transferred to a greenhouse and cultivated under sunlight.
+  However, the measurements under sunlight may be less reliable because of fluctations in the incident PPFD.
+  In such cases, SPD-controllable light sources might be helpful [e.g.
+@Yano_Fujiwara2012PM; @Fujiwara_et_al2013Proc] to make *in situ* evaluations under PPFD-stable conditions and to ensure the reproducibility and reliability of the results.
+  In retrospective studies that aim to explain differences among experimental groups, the measurements should be made under the SPDs of light that the plants received during the treatments.
+  For instance, when differences in dry weight between plants grown under white LEDs and those grown under fluorescent lamps are analyzed and *P*~n~ is used as an explanatory variable, the measurements should be made using the white LEDs for the plants grown under white LEDs and using the fluorescent lamps for those grown under fluorescent lamps.
+  In both prospective and retrospective studies, these simple *in situ* measurements will eliminate the problems caused by the interaction between the growth and the measuring light.
 
-  On the other hand, in descriptive studies making no assumption as to *in situ* condition, the measurements should be made under several SPDs of light including PSII- and PSI-light.
-  Researchers had better report the ‘general’ characteristics of the leaves in these studies.
-  Therefore, the interaction should be tested so as not to make biased evaluation.
-  If any the interaction, the results should be descriptively reported and should not be generalized.
-  When the measurements were made only under a single-pattern of SPD of measuring light because of unavoidable circumstances, the light source must be declared in the materials and methods section so that readers can follow the SPD.
+  On the other hand, in descriptive studies that make no assumption about the *in situ* conditions, *P*~n~ measurements should be made under several SPDs of light including PSII- and PSI-light.
+  It is better for researchers to report on the ‘general’ characteristics of the leaves in these studies.
+  Therefore, the interaction should be tested so as not to make biased evaluations.
+  If there is any interaction, the results should be descriptively reported and should not be generalized.
+  When the measurements are made only under a single-pattern of SPD of measuring light because there is no other option, the light source must be described in the materials and methods section so that the reader knows the SPD.
 
@@
 
-  The *P*~n~ under a single-pattern SPD of measuring light is only an aspect of the photosynthetic characteristics of the leaf.
-  Therefore, the obtained result must be discussed in connection with the SPD of measuring light.
-  Evaluation of the photosynthesis should be made under the *in situ* conditions or multi-pattern of SPDs of measuring light so that the evaluation is not biased by the interaction.
-  Imitating the various SPDs of light incident on the leaf for *in situ* evaluation might be difficult or impossible from the technical reasons.
-  In addition, measuring the *P*~n~ under multi-pattern of SPDs is time-, resource-, and labor-consuming.
-  Although these two approaches might not always be applied for evaluation of leaf *P*~n~, the interaction should always be kept in mind to make circumspect conclusions.
+  The *P*~n~ under a single-pattern SPD of measuring light is only one aspect of the photosynthetic characteristics of a leaf.
+  Therefore, the obtained results must be discussed in relation to the SPD of the measuring light.
+  Photosynthesis should be evaluated under *in situ* conditions or multi-pattern SPDs of measuring light so that the evaluation is not biased by the interaction between the SPDs of the growth and measureing lights.
+  Imitating the various SPDs of light incident on the leaf for *in situ* evaluation might be difficult or impossible for technical reasons.
+  In addition, measuring the *P*~n~ under multi-pattern SPDs is time-, resource-, and labor-consuming.
+  Although these two approaches might not always be used to evaluate leaf *P*~n~, the interaction should always be considered  to make circumspect conclusions.
 
@@
 1  Excitation balance between photosystems in response to wavelength of measuring light.
-The spectrum was calculated from absorbance spectra of PSII and PSI complexes in solvent (Hogewoning et al.
+Spectrum was calculated from absorbance spectra of PSII and PSI complexes in solvent (Hogewoning et al.
 2012)."
@@
   "Fig.
-2  Conceptual diagrams of the effects of the excitation energy distribution between the photosystems (PSII and PSI) on the photosynthetic electron transport rate (ETR).
-Electron flow (grey lines) and energy flow (black lines) of leaves grown under PSII-light (A, B) and PSI-light (C, D) measured using PSII-light (A, C) and PSI-light (B, D) were shown.
-"
+2  Conceptual diagrams of effects of excitation energy distribution between photosystems (PSII and PSI) on photosynthetic electron transport rate (ETR).
+Figure shows electron flow (grey lines) and energy flow (black lines) in leaves grown under PSII-light (A, B) and PSI-light (C, D) and measured using PSII-light (A, C) and PSI-light (B, D)."
 
@@
   "Fig.
-3  Conceptual diagram of the photosynthetic electron transport rates per absorbed photons by the leaf grown under PSII-light (PSII-leaves) and PSI-light (PSI-leaves) in response to the PSII/PSI-bised level of measuring light."
+3  Conceptual diagram of photosynthetic electron transport rates per absorbed photons by leaves grown under PSII-light (PSII-leaves) and PSI-light (PSI-leaves) in response to the PSII/PSI-bised level of measuring light."
 
@@
   'Fig.
-4  Spectral photon flux density distributions of light provided by (a) fluorescent lamp (FL; FPL55EX-N<sup>1</sup>), metal halide lamp (MH; M220FCELS-W/BUD<sup>1</sup>), and, high-pressure sodium lamp (HPS; NH220FLS<sup>1</sup>), (b) blue (B; HBL3-3S55-LE<sup>2</sup>), red (R; SRK3-3A80-LE<sup>2</sup>), far-red (FR; L735-36AU<sup>3</sup>), and white (W; NSPW310DS<sup>4</sup>) light-emitting diodes, and (c) incident and leaf transmitted sunlight.
-The distributions at a photon flux density of 100 µmol m<sup>--2</sup> s<sup>--1</sup> within 400--750 nm are shown.
-The far-red waveband (700--750 nm) is filled in grey.
-The distribution of sunlight was adopted from the International Electrotechnical Commission Standard 60904–3 [@IEC2007].
-The distribution of the leaf transmitted sunlight was calculated from that of incident sunlight and the transmittance spectrum of a cucumber leaf (Murakami et al.
+4  Spectral photon flux density distributions of light provided by (a) fluorescent lamp (FL; FPL55EX-N<sup>1</sup>); metal halide lamp (MH; M220FCELS-W/BUD<sup>1</sup>); high-pressure sodium lamp (HPS; NH220FLS<sup>1</sup>), (b) blue (B; HBL3-3S55-LE<sup>2</sup>), red (R; SRK3-3A80-LE<sup>2</sup>), far-red (FR; L735-36AU<sup>3</sup>), and white (W; NSPW310DS<sup>4</sup>) light-emitting diodes, and (c) incident and leaf-transmitted sunlight.
+Distributions at a photon flux density of 100 µmol m<sup>--2</sup> s<sup>--1</sup> within 400--750 nm are shown.
+Grey shading indicates far-red waveband (700--750 nm).
+Distribution of sunlight is from International Electrotechnical Commission Standard 60904–3 [@IEC2007].
+Distribution of leaf-transmitted sunlight was calculated from that of incident sunlight and transmittance spectrum of cucumber leaf (Murakami et al.
 2016).<br><sup>1</sup>IWASAKI ELECTRIC CO., LTD, Tokyo, Japan; <sup>2</sup>Tricon Co., Shimane, Japan; <sup>3</sup>Epitex Inc., Kyoto, Japan; <sup>4</sup>Nichia Chemical Industries Ltd., Tokushima, Japan.'

### 2016-08-10 Main.Rmd
微修正。

@@
 
-  On the other hand, in descriptive studies that make no assumption about the *in situ* conditions, *P*~n~ measurements should be made under several SPDs of light including PSII- and PSI-light.
+  On the other hand, in descriptive studies that hardly make assumption about the *in situ* conditions, *P*~n~ measurements should be made under several SPDs of light including PSII- and PSI-light.
   It is better for researchers to report on the ‘general’ characteristics of the leaves in these studies.

### 2016-08-11 Header.Rmd
パス図をDrフォルダへ。使うかは微妙。 あとは論文中の図を微修正、本文をわずかに修正など。 3091 words

@@
 author: "Keach Murakami^1\\*^, Ryo Matsuda^1^, Kazuhiro Fujiwara^1^"
-bibliography: ~/GitHub/BeeLabR/BibTex/with.bib
 csl: ECB.csl
+bibliography: ~/GitHub/BeeLabR/BibTex/With.bib
 header-includes:
-  - \setmainfont{Helvetica}
-  - \usepackage{zxjatype} # 日本語を使う
-  - \setjamainfont{Hiragino Kaku Gothic Pro} # 日本語フォント
-  - \usepackage{lscape} # 図を回転する
+  - \setmainfont{Times New Roman}
+  # - \setmainfont{Helvetica Neue}
+  - \usepackage{zxjatype} # 日本語を使うためのパッケージ
+  - \setjamainfont{Hiragino Kaku Gothic Pro} # 日本語フォントの指定
+  - \usepackage{lscape} # 図を回転するためのパッケージ
   - \newcommand{\blandscape}{\begin{landscape}} # 図回転用のbegin command
   - \newcommand{\elandscape}{\end{landscape}} # 図回転用のend command
-  - \usepackage{setspace} # 行間の調節
+  - \usepackage{setspace} # 行間の調節ためのパッケージ
   - \newcommand{\bdoublespace}{\begin{spacing}{1.5}} # 行間を広げるbegin command
   - \newcommand{\edoublespace}{\end{spacing}{1.5}} # 行間を広げるbegin command
+  - \usepackage{lineno} # 行番号を追加するためのパッケージ
+  - \linenumbers # 行番号を追加する
 
 output:
-# pdf_document:
-#   latex_engine: xelatex
-#     toc: TRUE # table of contents
-#     toc_depth: 3
-#     number_sections: TRUE
+  pdf_document:
+    latex_engine: xelatex
+    fig_caption: TRUE
+fontsize: 20pt
+geometry: margin=1.2in
+  # html_document:
+  #   toc: TRUE
+  #   depth: 3
+  #   theme: sandstone
+  #   self_contained: TRUE
   #   fig_caption: TRUE
-# fontsize: 12pt
-# geometry: margin=1.2in
-  html_document:
-    toc: TRUE
-    depth: 3
-    theme: sandstone
-    self_contained: TRUE
-    fig_caption: TRUE
+  # word_document:
+  #   toc: FALSE
+  #   fig_caption: TRUE
 ---
@@
 evalFig <- T
+base_size <- 20
+Annotate_size <- 6
+
+source("./caption.R")
 if(evalFig){
   devtools::source_url("https://raw.githubusercontent.com/KeachMurakami/Sources/master/Startup_silent.R")
-} else {
-  library(knitr)
 }
 
-opts_chunk$set(cache = F, echo = FALSE, fig.width = 5, fig.height = 5,
-               out.width = '500pixel', out.height = '500pixel', dpi = 100,
+knitr::opts_chunk$set(cache = F, echo = FALSE, fig.width = 7, fig.height = 7, dpi = 300,
                       message = FALSE, warning = FALSE, eval = T)
+               # out.width = '500pixel', out.height = '500pixel', dpi = 100,
 ```
@@
 e-mail: keach.murakami@gmail.com
-
-------
 

### 2016-08-11 Main.Rmd
パス図をDrフォルダへ。使うかは微妙。 あとは論文中の図を微修正、本文をわずかに修正など。 3091 words

@@
 
-```{r Captions}
-CapEED <-
-  "Fig.
-1  Excitation balance between photosystems in response to wavelength of measuring light.
-Spectrum was calculated from absorbance spectra of PSII and PSI complexes in solvent (Hogewoning et al.
-2012)."
-
-CapETRs <-
-  "Fig.
-2  Conceptual diagrams of effects of excitation energy distribution between photosystems (PSII and PSI) on photosynthetic electron transport rate (ETR).
-Figure shows electron flow (grey lines) and energy flow (black lines) in leaves grown under PSII-light (A, B) and PSI-light (C, D) and measured using PSII-light (A, C) and PSI-light (B, D)."
-
-CapInteract <-
-  "Fig.
-3  Conceptual diagram of photosynthetic electron transport rates per absorbed photons by leaves grown under PSII-light (PSII-leaves) and PSI-light (PSI-leaves) in response to the PSII/PSI-bised level of measuring light."
-
-CapSPD <-
-  'Fig.
-4  Spectral photon flux density distributions of light provided by (a) fluorescent lamp (FL; FPL55EX-N<sup>1</sup>); metal halide lamp (MH; M220FCELS-W/BUD<sup>1</sup>); high-pressure sodium lamp (HPS; NH220FLS<sup>1</sup>), (b) blue (B; HBL3-3S55-LE<sup>2</sup>), red (R; SRK3-3A80-LE<sup>2</sup>), far-red (FR; L735-36AU<sup>3</sup>), and white (W; NSPW310DS<sup>4</sup>) light-emitting diodes, and (c) incident and leaf-transmitted sunlight.
-Distributions at a photon flux density of 100 µmol m<sup>--2</sup> s<sup>--1</sup> within 400--750 nm are shown.
-Grey shading indicates far-red waveband (700--750 nm).
-Distribution of sunlight is from International Electrotechnical Commission Standard 60904–3 [@IEC2007].
-Distribution of leaf-transmitted sunlight was calculated from that of incident sunlight and transmittance spectrum of cucumber leaf (Murakami et al.
-2016).<br><sup>1</sup>IWASAKI ELECTRIC CO., LTD, Tokyo, Japan; <sup>2</sup>Tricon Co., Shimane, Japan; <sup>3</sup>Epitex Inc., Kyoto, Japan; <sup>4</sup>Nichia Chemical Industries Ltd., Tokushima, Japan.'
-```
-
-```{r InteractionPict, eval = evalFig}
-
-X_div <- 101
-X_range <- seq(0, 1, length.out = X_div)
-x_breaks <- c(0.2, 0.4, 0.65)
-
-InteractionDat <-
-  data_frame(X = rep(X_range, times = 2),
-           ETR = c(sqrt(dbeta(X_range, 4.5, 3.5)) * 1.1, sqrt(dbeta(X_range, 3, 5))),
-           Trtm = rep(c("PSII-leaves", "PSI-leaves"), each = X_div))
-
-InteractionLabel <-
-  InteractionDat %>%
-  group_by(Trtm) %>%
-  summarise(ETR = max(ETR)) %>%
-  left_join(., InteractionDat, by = c("Trtm", "ETR"))
-
-InteractionPoint <-
-  InteractionDat %>%
-  filter(X %in% x_breaks)
-
-InteractionText <-
-  InteractionDat %>%
-  filter(X %in% x_breaks) %>%
-  mutate(labels = c("far-red LED light", "Sunlight", "blue + red LED light", rep("", length(x_breaks)))) %>%
-  mutate(ETR = c(0.1, 0.1, 0.1, numeric(length(x_breaks))))
-
-InteractionView <-
-  InteractionDat %>%
-  ggplot(aes(X, ETR, linetype = Trtm, fill = Trtm, group = Trtm)) +
-  theme_bw2() +
-  theme(axis.text.y = element_blank(),
-        axis.ticks = element_blank(),
-        panel.grid.major = element_blank()) +
-  geom_vline(aes(xintercept = x_breaks[1]), linetype = 3, size = .75, col = "grey") +
-  geom_vline(aes(xintercept = x_breaks[2]), linetype = 3, size = .75, col = "grey") +
-  geom_vline(aes(xintercept = x_breaks[3]), linetype = 3, size = .75, col = "grey") +
-  geom_line() +
-  geom_point(data = InteractionPoint, col = "black", size = 3, shape = 21) +
-  geom_text(data = InteractionLabel, aes(x = X, y = ETR, label = Trtm), vjust = -1) +
-  geom_text(data = InteractionText, aes(label = labels), vjust = 1) +
-  scale_fill_manual(values = c("white", "black")) +
-  scale_linetype_manual(values = c(2, 1)) +
-  scale_x_continuous(breaks = c(0.07, 0.92), limits = c(0.05, 0.95), labels = c("PSI-biased", "PSII-biased")) +
-  xlab("PSII/PSI-biased level of measuring light") +
-  ylab("Relative electron transport rate") +
-  gg_y(c(0, 2))
-```
-
 ```{r EED, eval = evalFig}
@@
     ggplot(aes(x = wavelength, y = AlltoPSII)) +
-    theme_bw2() +
-    theme(panel.grid.major = element_blank()) +
+    theme_thesis(base_family = "serif", base_size = base_size) +
     geom_hline(yintercept = 0.5, col = "grey50", linetype = 3) +
@@
                        breaks = c(0, 0.25, 0.5, 0.75, 1),
-                       limits = c(0, 1.0),
+                       limits = c(-.005, 1.005),
                        expand = c(0, 0)) +
     xlab("Wavelength [nm]") + ylab("Fraction of the excitation energy distributed to PSII")
+```
+
+```{r InteractionPict, eval = evalFig}
+
+X_div <- 101
+X_range <- seq(0, 1, length.out = X_div)
+x_breaks <- c(0.2, 0.4, 0.65)
+
+InteractionDat <-
+  data_frame(X = rep(X_range, times = 2),
+           ETR = c(sqrt(dbeta(X_range, 4.5, 3.5)) * 1.1, sqrt(dbeta(X_range, 3, 5))),
+           Trtm = rep(c("PSII-leaves", "PSI-leaves"), each = X_div))
+
+InteractionLabel <-
+  InteractionDat %>%
+  group_by(Trtm) %>%
+  summarise(ETR = max(ETR)) %>%
+  left_join(., InteractionDat, by = c("Trtm", "ETR"))
+
+InteractionPoint <-
+  InteractionDat %>%
+  filter(X %in% x_breaks)
+
+InteractionText <-
+  InteractionDat %>%
+  filter(X %in% x_breaks) %>%
+  mutate(labels = c("far-red LED light", "Sunlight", "blue + red LED light", rep("", length(x_breaks)))) %>%
+  mutate(ETR = c(0.1, 0.1, 0.1, numeric(length(x_breaks))))
+
+InteractionView <-
+  InteractionDat %>%
+  ggplot(aes(X, ETR, linetype = Trtm, fill = Trtm, group = Trtm)) +
+  theme_thesis(base_family = "serif", base_size = base_size) +
+  geom_vline(aes(xintercept = x_breaks[1]), linetype = 3, size = .75, col = "grey") +
+  geom_vline(aes(xintercept = x_breaks[2]), linetype = 3, size = .75, col = "grey") +
+  geom_vline(aes(xintercept = x_breaks[3]), linetype = 3, size = .75, col = "grey") +
+  geom_line() +
+  geom_point(data = InteractionPoint, col = "black", size = 3, shape = 21) +
+  geom_text(data = InteractionLabel, aes(x = X, y = ETR, label = Trtm), vjust = -1, family = "serif", size = Annotate_size) +
+  geom_text(data = InteractionText, aes(label = labels), vjust = 1, family = "serif", size = Annotate_size) +
+  scale_fill_manual(values = c("white", "black")) +
+  scale_linetype_manual(values = c(2, 1)) +
+  scale_x_continuous(breaks = c(0.07, 0.92),
+                     limits = c(0.05, 0.95),
+                     labels = c("PSI-biased", "PSII-biased")) +
+  scale_y_continuous(breaks = NULL,
+                     limits = c(-0.05, 2.05)) +
+  xlab("PSII/PSI-biased level of measuring light") +
+  ylab("Relative electron transport rate")
+
 ```
@@
              value = c(2.2, .6, 3, 4, 4.2, 3.8, 1.3, 0.6, 2),
-             label = c("FL", "MH", "HPS", "B", "R", "FR", "W", "Sunlight", "Leaf transmitted sunlight"),
+             label = c("FL", "MH", "HPS", "B", "R", "FR", "W", "Sunlight", "Leaf-transmitted sunlight"),
              panel = rep(panel_names,  c(3, 4, 2)))
@@
   ggplot(aes(x = wavelength, y = value, group = variable, col = variable, linetype = variable)) +
-  theme_bw2() +
-  theme(strip.background = element_blank(),
-        strip.text = element_blank(),
-        panel.grid.major = element_blank()) +
+  theme_thesis(base_family = "serif", base_size = base_size) +
   geom_rect(aes(xmin = 700, xmax = 750, ymin = 0, ymax = +Inf), fill = "grey90", col = NA) +
   geom_line() +
-  geom_text(data = SPD_labels, aes(x = wavelength, y = value, label = label)) +
-  geom_text(data = SPD_panel, col = "black", aes(label = panel)) +
+  geom_text(data = SPD_labels, aes(x = wavelength, y = value, label = label), family = "serif", size = Annotate_size) +
+  geom_text(data = SPD_panel, col = "black", aes(label = panel), family = "serif", size = Annotate_size * .8) +
   scale_linetype_manual(values = c(1, 1, 3, 2, 4, 2, 2, 1, 4)) +
@@
   facet_grid(panel ~ .) +
-  gg_xy(c(380, 820, 0, 4.5)) +
+  gg_xy(c(380, 820, -.01, 4.5)) +
   xlab("Wavelength [nm]") + ylab(u_SPFD("Spectral photon flux density"))
-
 ```
@@
 EEDs
+# pdf("./Figs/EEDs.pdf", family = "Times", width = 3.15, height = 2.5)
+#   EEDs + theme_thesis(base_size = 5)
+# dev.off()
 ```
@@
 InteractionView
+# pdf("./Figs/Interactions.pdf", family = "Times", width = 3.15, height = 2.5)
+#   InteractionView + theme_thesis(base_size = 5)
+# dev.off()
 ```
@@
 SPDs
+# pdf("./Figs/SPDs.pdf", family = "Times", width = 3.15, height = 4)
+#   InteractionView + theme_thesis(base_size = 5)
+# dev.off()
 ```

### 2016-08-11 caption.R

@@ -1,0 +1,11 @@
+CapEED <-
+  "Fig. 1  Typical excitation balance between photosystems in response to wavelength of measuring light. Spectrum was calculated from absorbance spectra of PSII and PSI complexes in solvent (Hogewoning et al. 2012)."
+
+CapETRs <-
+  "Fig. 2  Conceptual diagrams of effects of excitation energy distribution between photosystems (PSII and PSI) on photosynthetic electron transport rate (ETR). Figure shows electron flow (grey lines) and energy flow (black lines) in leaves grown under PSII-light (A, B) and PSI-light (C, D) and measured using PSII-light (A, C) and PSI-light (B, D)."
+
+CapInteract <-
+  "Fig. 3  Conceptual diagram of photosynthetic electron transport rates per absorbed photons by leaves grown under PSII-light (PSII-leaves) and PSI-light (PSI-leaves) in response to the PSII/PSI-bised level of measuring light."
+
+CapSPD <-
+  'Fig. 4  Spectral photon flux density distributions of light provided by (a) fluorescent lamp (FL; FPL55EX-N^1^); metal halide lamp (MH; M220FCELS-W/BUD^1^); high-pressure sodium lamp (HPS; NH220FLS^1^), (b) blue (B; HBL3-3S55-LE^2^), red (R; SRK3-3A80-LE^2^), far-red (FR; L735-36AU^3^), and white (W; NSPW310DS^4^) light-emitting diodes, and (c) incident and leaf-transmitted sunlight. Distributions at a photon flux density of 100 µmol m^--2^ s^--1^ within 400--750 nm are shown. Grey shading indicates far-red waveband (700--750 nm). Distribution of sunlight is from International Electrotechnical Commission Standard 60904–3 [@IEC2007]. Distribution of leaf-transmitted sunlight was calculated from that of incident sunlight and transmittance spectrum of cucumber leaf (Murakami et al. 2016).<br>^1^IWASAKI ELECTRIC CO., LTD, Tokyo, Japan; ^2^Tricon Co., Shimane, Japan; ^3^Epitex Inc., Kyoto, Japan; ^4^Nichia Chemical Industries Ltd., Tokushima, Japan.'

### 2016-08-12 Header.Rmd
図・アブストを修正など 3102 words。 ラストの確認をしてRM・KFにパスかな。

@@
 output:
-  pdf_document:
-    latex_engine: xelatex
-    fig_caption: TRUE
-fontsize: 20pt
-geometry: margin=1.2in
+#   pdf_document:
+#     latex_engine: xelatex
+#     fig_caption: TRUE
+# fontsize: 20pt
+# geometry: margin=1.2in
   # html_document:
@@
   #   fig_caption: TRUE
-  # word_document:
-  #   toc: FALSE
-  #   fig_caption: TRUE
+  word_document:
+    toc: FALSE
+    fig_caption: TRUE
 ---
@@
 base_size <- 20
-Annotate_size <- 6
+Annotate_size <- 5
 
@@
 
-  The spectral photon flux density distribution (SPD) of light during growth and for measurements do not only directly affect the net photosynthetic rate (*P*~n~) but also interacts on it.
-  A plausible mechanisms of the interaction, some situations in which the interaction should be concerned, and the selection of appropriate measuring light for evaluation of photosynthesis are summarized.
-  *P*~n~ should be measured under *in situ* conditions depending on the purpose of the study.
-  In prospective studies focusing on plant growth after the measurements, the measurements should be made under the SPD of light that the plant will be subject to.
-  In retrospective studies aiming to elucidate causes of differences between the experimental groups, the measurements should be made under the SPDs of light that the plants have received during the treatments.
-  In descriptive studies, *P*~n~ should be evaluated under several SPDs of measuring light to comprehend general photosynthetic characteristics of the leaves.
-  *P*~n~ under a single-pattern SPD of measuring light is only an aspect of the photosynthetic characteristics of the leaf.
-  The obtained result must be discussed in connection with the SPD of measuring light so as not to make biased evaluation caused by the interaction.
+  The spectral photon flux density distributions (SPDs) of light during growth and for measurements do not only directly affect the net photosynthetic rate (*P*~n~), but also interacts on it.
+  This paper summarizes a plausible mechanism of the interaction, some situations in which the interaction should be considered, and recommendations for selecting appropriate measuring light to evaluate photosynthesis.
+  The *P*~n~ should be measured under *in situ* conditions, depending on the purpose of the study.
+  For studies focusing on plant growth after measurements, *P*~n~ should be measured under the SPD of light that the plant will be subjected to.
+  In retrospective studies aiming to elucidate the causes of differences among experimental groups, measurements should be made under the SPDs of the lights the plants were grown under.
+  In descriptive studies, *P*~n~ should be evaluated under several SPDs of measuring light to understand the general photosynthetic characteristics of the leaves.
+  The *P*~n~ under a single-pattern SPD of measuring light is only one aspect of the photosynthetic characteristics of a leaf.
+  The obtained results must be discussed in relation to the SPD of measuring light so as not to make biased evaluations.
 

### 2016-08-12 Main.Rmd
図・アブストを修正など 3102 words。 ラストの確認をしてRM・KFにパスかな。

@@
 
-  The effect of the SPD of growth light on *P*~n~ depends on the SPD of the measuring light.
-  In other words, the interaction between the SPDs of the growth light and the measuring light affect the *P*~n~ of a leaf.
+  The effect of the SPD of growth light on *P*~n~ depends on the SPD of measuring light.
+  In other words, the interaction between the SPDs of growth light and measuring light affect the *P*~n~ of a leaf.
   In this short article, we describe a plausible mechanism for this interaction, based on the excitation energy distribution balance between the photosystems.
@@
   Because the photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) through the thylakoid membrane is limited by the slowest step (Fig. 2).
-  When there is excess excitation energy at PSII (i.e. under PSII-light), the smaller amoutn of excitation energy distributed to PSI results in lower photochemical reaction rates at PSI than at PSII.
-  This shortage in the EED to PSI limits the ETR, thereby leading to lwoer photochemical quantum yield of PSII (Fig. 2C).
+  When there is excess excitation energy at PSII (i.e. under PSII-light), the smaller amount of excitation energy distributed to PSI results in lower photochemical reaction rates at PSI than at PSII.
+  This shortage in the EED to PSI limits the ETR, thereby leading to lower photochemical quantum yield of PSII and balaced ETR between PSII and PSI (Fig. 2C).
   When PSI absorbs excess excitation energy (i.e. under PSI-light), the excitation energy distributed to PSII limits the ETR and lowers the yield of PSI (Fig. 2B).
@@
   As a result of these adjustments in the EED properties of a leaf, the spectrum of excitation balance (Fig. 1) differs depending on the SPD of the growth light.
-  **PSII-light PSI-light が使われることがある**.
   The categories of light, that is, ‘PSII-light’ and ‘PSI-light’, are defined for a given leaf on a relative scale, not an absolute scale.
@@
 
-  These reports suggested that the EED properties of a leaf might be tuned to the PSII/PSI-biased level of the growth light.
-  It is expected that a leaf will perform a higher ETR per absorbed photons by the leaf under a measuring light with a PSII/PSI-biased level similar to that of the growth light (Fig. 3).
-  When leaves grown under different SPDs of light are compared and evaluated under a specific SPD of light, the results will inevitably be biased depending on the SPD of the measuring light.
+  These reports suggested that the EED properties of a leaf might be tuned to the PSII/PSI-biased level of growth light.
+  It is expected that a leaf will perform a higher ETR per absorbed photons by the leaf under measuring light with a PSII/PSI-biased level similar to that of the growth light (Fig. 3).
+  When leaves grown under different SPDs of light are compared and evaluated under a specific SPD of measuring light, the results will inevitably be biased depending on the SPD of the measuring light.
 
@@
   Several studies published over the last decade have investigated the effects of the SPD of the growth light on plant growth and photosynthesis [e.g.
-@Matsuda_et_al2004PCP; @Matsuda_et_al2007SSPN; @Matsuda_et_al2008PCP; @Hogewoning_et_al2010aJXB; @Hogewoning_et_al2010bJXB; @Shibuya_et_al2015BP; @Trouwborst_et_al2016EEB].
+@Matsuda_et_al2004PCP; @Matsuda_et_al2007SSPN; @Matsuda_et_al2008PCP; @Hogewoning_et_al2010aJXB; @Hogewoning_et_al2010bJXB; @Hogewoning_et_al2012PC; @Shibuya_et_al2015BP; @Trouwborst_et_al2016EEB].
   Growth light provided by most artificial light sources contains little FR light.
@@
   In such cases, SPD-controllable light sources might be helpful [e.g.
-@Yano_Fujiwara2012PM; @Fujiwara_et_al2013Proc] to make *in situ* evaluations under PPFD-stable conditions and to ensure the reproducibility and reliability of the results.
+@Yano_Fujiwara2012PM; @Fujiwara_et_al2013Proc] to make *in situ* evaluations under PPFD-stable conditions and to ensure reproducibility and reliability of the results.
   In retrospective studies that aim to explain differences among experimental groups, the measurements should be made under the SPDs of light that the plants received during the treatments.

### 2016-08-12 caption.R

@@ -2,7 +2,7 @@ CapEED <-
   "Fig. 1  Typical excitation balance between photosystems in response to wavelength of measuring light. Spectrum was calculated from absorbance spectra of PSII and PSI complexes in solvent (Hogewoning et al. 2012)."
 
 CapETRs <-
-  "Fig. 2  Conceptual diagrams of effects of excitation energy distribution between photosystems (PSII and PSI) on photosynthetic electron transport rate (ETR). Figure shows electron flow (grey lines) and energy flow (black lines) in leaves grown under PSII-light (A, B) and PSI-light (C, D) and measured using PSII-light (A, C) and PSI-light (B, D)."
+  "Fig. 2  Conceptual diagrams of effects of excitation energy distribution between photosystems (PSII and PSI) on photosynthetic electron transport rate (ETR). Figure shows electron flow (grey lines) and energy flow (black lines) in leaves grown under PSII-light (a, b) and PSI-light (c, d) and measured using PSII-light (a, c) and PSI-light (b, d). Excitation energy distribution properties of leaves are adjusted depending on growth light. GL: growth light, ML: measuring light."
 
 CapInteract <-
   "Fig. 3  Conceptual diagram of photosynthetic electron transport rates per absorbed photons by leaves grown under PSII-light (PSII-leaves) and PSI-light (PSI-leaves) in response to the PSII/PSI-bised level of measuring light."

### 2016-08-13 Header.Rmd
微修正など。

@@
 ---
-title: "Evaluating effects of light quality: A basis for selecting the spectral photon flux density distribution of light for measuring photosynthetic rates of leaves"
+title: "A basis for selecting the spectral photon flux density distribution of light for measuring leaf photosynthetic rates in light quality response studies"
 author: "Keach Murakami^1\\*^, Ryo Matsuda^1^, Kazuhiro Fujiwara^1^"
@@
 output:
-#   pdf_document:
-#     latex_engine: xelatex
-#     fig_caption: TRUE
-# fontsize: 20pt
-# geometry: margin=1.2in
+  pdf_document:
+    latex_engine: xelatex
+    fig_caption: TRUE
+fontsize: 20pt
+geometry: margin=1.2in
   # html_document:
@@
   #   fig_caption: TRUE
-  word_document:
-    toc: FALSE
-    fig_caption: TRUE
+  # word_document:
+  #   toc: FALSE
+  #   fig_caption: TRUE
 ---

### 2016-08-13 caption.R

@@ -2,7 +2,7 @@ CapEED <-
   "Fig. 1  Typical excitation balance between photosystems in response to wavelength of measuring light. Spectrum was calculated from absorbance spectra of PSII and PSI complexes in solvent (Hogewoning et al. 2012)."
 
 CapETRs <-
-  "Fig. 2  Conceptual diagrams of effects of excitation energy distribution between photosystems (PSII and PSI) on photosynthetic electron transport rate (ETR). Figure shows electron flow (grey lines) and energy flow (black lines) in leaves grown under PSII-light (a, b) and PSI-light (c, d) and measured using PSII-light (a, c) and PSI-light (b, d). Excitation energy distribution properties of leaves are adjusted depending on growth light. GL: growth light, ML: measuring light."
+  "Fig. 2  Conceptual diagrams of effects of excitation energy distribution between photosystems (PSII and PSI) on photosynthetic electron transport rate (ETR). Figure shows electron flow (white lines) and energy flow (black lines) in leaves grown under PSII-light (a, b) and PSI-light (c, d) and measured using PSII-light (a, c) and PSI-light (b, d). Excitation energy distribution properties of leaves are adjusted depending on growth light. GL: growth light, ML: measuring light."
 
 CapInteract <-
   "Fig. 3  Conceptual diagram of photosynthetic electron transport rates per absorbed photons by leaves grown under PSII-light (PSII-leaves) and PSI-light (PSI-leaves) in response to the PSII/PSI-bised level of measuring light."

### 2016-08-14 Header.Rmd
誤字脱字程度。タイトルに悩みつつ 3098wordsでとりあえず。

@@
 output:
-  pdf_document:
-    latex_engine: xelatex
+#   pdf_document:
+#     latex_engine: xelatex
+#     fig_caption: TRUE
+# fontsize: 20pt
+# geometry: margin=1.2in
+  html_document:
+    toc: TRUE
+    depth: 3
+    theme: sandstone
+    self_contained: TRUE
     fig_caption: TRUE
-fontsize: 20pt
-geometry: margin=1.2in
-  # html_document:
-  #   toc: TRUE
-  #   depth: 3
-  #   theme: sandstone
-  #   self_contained: TRUE
-  #   fig_caption: TRUE
-  # word_document:
-  #   toc: FALSE
-  #   fig_caption: TRUE
+  word_document:
+    toc: FALSE
+    fig_caption: TRUE
 ---
@@
   The *P*~n~ should be measured under *in situ* conditions, depending on the purpose of the study.
-  For studies focusing on plant growth after measurements, *P*~n~ should be measured under the SPD of light that the plant will be subjected to.
+  For prospective studies focusing on plant growth after measurements, *P*~n~ should be measured under the SPD of light that the plant will be subjected to.
   In retrospective studies aiming to elucidate the causes of differences among experimental groups, measurements should be made under the SPDs of the lights the plants were grown under.

### 2016-08-14 Main.Rmd
誤字脱字程度。タイトルに悩みつつ 3098wordsでとりあえず。

@@
   Light with a given SPD is sometimes categorized as either PSII- or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI [e.g.
-@Chow_et_al1990PNAS; @Melis1991BBA; @Pfannschmidt_et_al2001JBC; @Fan_et_al2007BBA; @Dietzel_et_al2008FJ; @Pfannschmidt_et_al2009AB; @Dietzel_et_al2011PC; @Hogewoning_et_al2012PC].
+@Chow_et_al1990PNAS; @Melis1991BBA; @Pfannschmidt_et_al2001JBC; @Dietzel_et_al2008FJ; @Pfannschmidt_et_al2009AB; @Dietzel_et_al2011PC; @Hogewoning_et_al2012PC].
 
@@
 @Kozai2007POP], the measurements should be made under sunlight because the plants will be transferred to a greenhouse and cultivated under sunlight.
-  However, the measurements under sunlight may be less reliable because of fluctations in the incident PPFD.
+  However, the measurements under sunlight may be less reliable because of fluctuations in the incident PPFD.
   In such cases, SPD-controllable light sources might be helpful [e.g.
@@
   Therefore, the obtained results must be discussed in relation to the SPD of the measuring light.
-  Photosynthesis should be evaluated under *in situ* conditions or multi-pattern SPDs of measuring light so that the evaluation is not biased by the interaction between the SPDs of the growth and measureing lights.
+  Photosynthesis should be evaluated under *in situ* conditions or multi-pattern SPDs of measuring light so that the evaluation is not biased by the interaction between the SPDs of the growth and measuring lights.
   Imitating the various SPDs of light incident on the leaf for *in situ* evaluation might be difficult or impossible for technical reasons.
@@
 
-  We thank Dr Sander W. Hogewoning (Plant Lighting B.V., the Netherlands) for providing data of absorpbance spectra of photosystems.
+  We thank Dr Sander W. Hogewoning (Plant Lighting B.V., the Netherlands) for providing data of absorbance spectra of photosystems.
   This work was supported by JSPS KAKENHI Grant Number 26·9372.

### 2016-08-14 caption.R

@@ -5,7 +5,7 @@ CapETRs <-
   "Fig. 2  Conceptual diagrams of effects of excitation energy distribution between photosystems (PSII and PSI) on photosynthetic electron transport rate (ETR). Figure shows electron flow (white lines) and energy flow (black lines) in leaves grown under PSII-light (a, b) and PSI-light (c, d) and measured using PSII-light (a, c) and PSI-light (b, d). Excitation energy distribution properties of leaves are adjusted depending on growth light. GL: growth light, ML: measuring light."
 
 CapInteract <-
-  "Fig. 3  Conceptual diagram of photosynthetic electron transport rates per absorbed photons by leaves grown under PSII-light (PSII-leaves) and PSI-light (PSI-leaves) in response to the PSII/PSI-bised level of measuring light."
+  "Fig. 3  Conceptual diagram of photosynthetic electron transport rates per absorbed photons by leaves grown under PSII-light (PSII-leaves) and PSI-light (PSI-leaves) in response to the PSII/PSI-biased level of measuring light."
 
 CapSPD <-
   'Fig. 4  Spectral photon flux density distributions of light provided by (a) fluorescent lamp (FL; FPL55EX-N^1^); metal halide lamp (MH; M220FCELS-W/BUD^1^); high-pressure sodium lamp (HPS; NH220FLS^1^), (b) blue (B; HBL3-3S55-LE^2^), red (R; SRK3-3A80-LE^2^), far-red (FR; L735-36AU^3^), and white (W; NSPW310DS^4^) light-emitting diodes, and (c) incident and leaf-transmitted sunlight. Distributions at a photon flux density of 100 µmol m^--2^ s^--1^ within 400--750 nm are shown. Grey shading indicates far-red waveband (700--750 nm). Distribution of sunlight is from International Electrotechnical Commission Standard 60904–3 [@IEC2007]. Distribution of leaf-transmitted sunlight was calculated from that of incident sunlight and transmittance spectrum of cucumber leaf (Murakami et al. 2016).<br>^1^IWASAKI ELECTRIC CO., LTD, Tokyo, Japan; ^2^Tricon Co., Shimane, Japan; ^3^Epitex Inc., Kyoto, Japan; ^4^Nichia Chemical Industries Ltd., Tokushima, Japan.'

### 2016-08-16 Header.Rmd
3172 words. KF, RMのコメントを反映。

@@
 ---
-title: "A basis for selecting the spectral photon flux density distribution of light for measuring leaf photosynthetic rates in light quality response studies"
+title: "A basis for selecting light spectral distribution for evaluating photosynthetic rates of leaves grown under different light spectral distributions"
 author: "Keach Murakami^1\\*^, Ryo Matsuda^1^, Kazuhiro Fujiwara^1^"
@@
 
-  The spectral photon flux density distributions (SPDs) of light during growth and for measurements do not only directly affect the net photosynthetic rate (*P*~n~), but also interacts on it.
+  The spectral photon flux density distributions of light during growth and for measurements do not only directly affect the net photosynthetic rate (*P*~n~).
+  Moreover, 
   This paper summarizes a plausible mechanism of the interaction, some situations in which the interaction should be considered, and recommendations for selecting appropriate measuring light to evaluate photosynthesis.
   The *P*~n~ should be measured under *in situ* conditions, depending on the purpose of the study.
-  For prospective studies focusing on plant growth after measurements, *P*~n~ should be measured under the SPD of light that the plant will be subjected to.
+  For studies focusing on the evaluation of plant growth after measurements, *P*~n~ should be measured under the SPD of light that the plant will be subjected to.
   In retrospective studies aiming to elucidate the causes of differences among experimental groups, measurements should be made under the SPDs of the lights the plants were grown under.
   In descriptive studies, *P*~n~ should be evaluated under several SPDs of measuring light to understand the general photosynthetic characteristics of the leaves.
-  The *P*~n~ under a single-pattern SPD of measuring light is only one aspect of the photosynthetic characteristics of a leaf.
+  The *P*~n~ under a single spectral distribution of measuring light is only one aspect of the photosynthetic characteristics of a leaf.
   The obtained results must be discussed in relation to the SPD of measuring light so as not to make biased evaluations.
@@
 PSII: photosystem II,
-SPD: relative spectral PFD distribution
 

### 2016-08-16 Main.Rmd
3172 words. KF, RMのコメントを反映。

@@
   In agricultural and horticultural studies, the effectiveness of treatments is sometimes discussed based on the measured photosynthetic rates and calculated indices.
-  Therefore, accurate measurements of photosynthetic rates are essential.
+  To examine the research questions appropriately, the *P*~n~ should be evaluated .
 
-  A number of studies have reported that the relative spectral photon-flux-density (PFD) distribution (SPD) of light used for   measurement (i.e.
+  A number of studies have reported that the relative spectral photon flux density (PFD) distribution of light used for measurement (i.e.
 measuring light or actinic light) affects leaf net photosynthetic rates (*P*~n~) [e.g.
 @McCree1972AM; @Inada1976PCP].
-  To eliminate this direct effect from the comparison, *P*~n~ is usually measured under a common SPD of measuring light irrespective of leaf growth conditions in agricultural and horticultural studies.
+  To eliminate this direct effect from the comparison, *P*~n~ is usually measured under a common relative spectral PFD distribution of measuring light irrespective of leaf growth conditions in agricultural and horticultural studies.
   One of the most widely-used measuring lights is a mixture of blue and red light (BR-light) provided by light-emitting diodes (LEDs) installed in commercial photosynthesis analysis systems (e.g.
 LI6400 and LI6400XT, LI-COR Inc., Lincoln, NE; GFS-3000, Heinz Walz GmbH, Effeltrich, Germany).
-  The use of artificial light sources enables precise control of the photosynthetic PFD (PPFD) and SPD incident on the leaf, and therefore, ensures reproducibility and reliability among experiments.
+  The use of artificial light sources enables precise control of the spectral PFD distribution on the leaf, and therefore, ensures reproducibility and reliability among experiments.
 
-  @Walters2005JXB noted that photosynthetic rates measured with a SPD of light different from that of the growth light do not necessarily reflect the functioning of photosynthesis under the actual growth conditions.
+  @Walters2005JXB noted that photosynthetic rates measured with a spectral PFD distribution of light different from that of the growth light do not necessarily reflect the functioning of photosynthesis under the actual growth conditions.
   Indeed, we have experimentally demonstrated this problem in *P*~n~ measurements in our recent study [@Murakami_et_al2016PP].
-  In that experiment, cucumber seedlings were grown under white LED without and with supplemental far-red (FR) LED light (W and WFR, respectively), and the *P*~n~ of the leaves was subsequently compared under BR-light and under light with a SPD resembling that of sunlight (‘artificial’ sunlight).
+  In that experiment, cucumber seedlings were grown under white LED without and with supplemental far-red (FR) LED light (W and WFR, respectively), and the *P*~n~ of the leaves was subsequently compared under BR-light and under light with a relative spectral PFD distribution approximating to that of sunlight (‘artificial’ sunlight).
   The *P*~n~ of W-grown-leaves was greater than that of WFR-grown-leaves under BR-light, while the rates were comparable under the artificial sunlight [@Murakami_et_al2016PP].
@@
 
-  The effect of the SPD of growth light on *P*~n~ depends on the SPD of measuring light.
-  In other words, the interaction between the SPDs of growth light and measuring light affect the *P*~n~ of a leaf.
+  The effect of the relative spectral PFD distribution of growth light on *P*~n~ depends on the relative spectral PFD distribution of measuring light.
+  In other words, the interaction between the relative spectral PFD distributions of growth light and measuring light affect the *P*~n~ of a leaf.
   In this short article, we describe a plausible mechanism for this interaction, based on the excitation energy distribution balance between the photosystems.
@@
   Several mechanisms other than the excitation balance, such as stomatal responses [@Shimazaki_et_al2007AnnRev], photoinhibition [@Zavafer_et_al2015JPP], and vertical PFD profile within a leaf [@Terashima_et_al2009PCP] affect photosynthesis via the SPD of measuring light.
-  Although these subjects are not discussed in this article, several cited articles are available for these topics.
+  Although these subjects are not discussed in this article, the cited articles are available for these topics.
 
@@
 
-  Fundamental knowledge about photosynthetic electron transport is required to understand the mechanism of the interaction.
+  We first summarize the physiological basis of photosynthetic electron transport, which is required to understand the mechanism of the interaction.
   Light energy absorbed by a leaf drives photosynthetic electron transport, O~2~ evolution, and CO~2~ uptake.
@@
 
-  The two photosystems---PSII and PSI---represent different spectral light absorption distributions due to their different compositions of binding pigments, mainly chl *a* and chl *b*.
-  Within the chlorophyll (chl) absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [Fig.
+  The two photosystems---PSII and PSI---represent different spectral distributions of light absorption due to their different compositions of binding pigments, mainly chl *a* and chl *b*.
+  Within the chlorophyll (chl) absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited compared with PSII [Fig.
 1; @Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
@@
 1; @Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
-  These wavelength dependencies of the excitation balance between PSII and PSI determine the excitation energy distribution (EED) under a given SPD of light.
+  These wavelength dependencies of the excitation balance between PSII and PSI determine **the excitation energy distribution (EED)** under a given relative spectral PFD distribution of light.
   Light with a given SPD is sometimes categorized as either PSII- or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI [e.g.
@@
 
-  Because the photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) through the thylakoid membrane is limited by the slowest step (Fig. 2).
+  Because the photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) is limited by the slowest step (Fig. 2).
   When there is excess excitation energy at PSII (i.e. under PSII-light), the smaller amount of excitation energy distributed to PSI results in lower photochemical reaction rates at PSI than at PSII.
-  This shortage in the EED to PSI limits the ETR, thereby leading to lower photochemical quantum yield of PSII and balaced ETR between PSII and PSI (Fig. 2C).
+  This shortage in the EED to PSI limits the ETR, thereby leading to the reduction of photochemical quantum yield of PSII and balaced ETR between PSII and PSI (Fig. 2C).
   When PSI absorbs excess excitation energy (i.e. under PSI-light), the excitation energy distributed to PSII limits the ETR and lowers the yield of PSI (Fig. 2B).
   In both cases, the excess energy is dissipated mainly as heat and fluorescence.
-  Consequently, the entire photosynthetic quantum yield---ETR per absorbed photons by the leaf---becomes smaller.
+  **Consequently, the entire photosynthetic quantum yield---ETR per absorbed photons by the leaf---becomes smaller.**
   Therefore, balancing the EED between PSII and PSI is essential for plants to retain a high photosynthetic quantum yield.
-  Imbalanced excitation between the photosystems is supposed to damage leaves by generating reactive oxygen species, which cause oxidative damage to chloroplast components [for reviews, see @Asada1999AnnRev; @Asada2006PP].
+  **for a long period of time** Imbalanced excitation between the photosystems is supposed to damage leaves by generating reactive oxygen species, which cause oxidative damage to chloroplast components [for reviews, see @Asada1999AnnRev; @Asada2006PP].
 
-  Apparently, the EED at a given SPD of light is also affected by the composition of the thylakoid components, especially the stoichiometry between PSII and PSI.
-  The stoichiometry appears to adjust to the SPD of the growth light.
-  Under PSII-light, the relative amount of the reaction center complex of PSII to that of PSI in leaves decreases; conversely, under PSI-light, the relative amount increases to achieve a balance [e.g.
+  Apparently, the EED at a given relative spectral PFD distribution of light is also affected by the composition of the thylakoid components, especially the stoichiometry between PSII and PSI.
+  The stoichiometry appears to adjust to the spectral PFD distribution of the growth light.
+  Under PSII-light, the relative amount of the reaction center complex of PSII to that of PSI in leaves decreases; conversely, under PSI-light, the relative amount increases to achieve a balance **time scale** [e.g.
 @Melis1991BBA; @Pfannschmidt_et_al1999Nature].
@@
   The categories of light, that is, ‘PSII-light’ and ‘PSI-light’, are defined for a given leaf on a relative scale, not an absolute scale.
-  For instance, the SPD of light that is evenly absorbed by PSII and PSI in PSII-light-grown leaves (Fig. 2A), can overexcite PSII in PSI-light-grown leaves (Fig. 2C).
+  For instance, the relative spectral PFD distribution of light that is evenly absorbed by PSII and PSI in PSII-light-grown leaves (Fig. 2A), can overexcite PSII in PSI-light-grown leaves (Fig. 2C).
   Therefore, the terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context.
@@
   The SPD of growth light affects the EED properties of a leaf.
-  This modifies the ETR responses, and therefore the *P*~n~, to the SPD of measuring light.
-  Thus, the SPDs of growth light and measuring light not only directly affect the *P*~n~, but also indirectly affect it through their interaction.
+  This modifies the responses of ETR, and therefore that of *P*~n~, to the relative spectral PFD distribution of measuring light.
+  Thus, the SPDs of growth light and measuring light not only directly affect the *P*~n~, but also indirectly affect it through the interaction between the growth and the measuring light.
   This expected interaction has been reported in several studies [@Chow_et_al1990PNAS; @Walters_Horton1995aPlanta; @Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
-  In their pioneering study, @Chow_et_al1990PNAS grew *Pisum sativum* plants under light provided by cool-white fluorescent lamps with yellow Plexiglas (PSII-light) and incandescent bulbs with red Plexiglas (PSI-light) and measured the photosynthetic quantum yield of O~2~ evolution---O~2~ evolution rate per absorbed photons by the leaf---under the PSII- and PSI-lights reciprocally.
-  When measured under PSII-light, the yield was higher in the PSII-light-grown leaves; when measured under PSI-light, the yield was higher in the PSI-light-grown leaves.
-  Similar trends in the photosynthetic quantum yield of O~2~ evolution [in *Arabidopsis thaliana*; @Walters_Horton1995aPlanta], in the photosynthetic quantum yield of CO~2~ uptake [in *Cucumis sativus*; @Hogewoning_et_al2012PC], and in *P*~n~ [in *C.
-sativus*, see also Introduction; @Murakami_et_al2016PP] were observed.
+  In their pioneering research, @Chow_et_al1990PNAS grew *Pisum sativum* plants under light provided by cool-white fluorescent lamps with yellow Plexiglas (PSII-light) and incandescent bulbs with red Plexiglas (PSI-light) and measured the photosynthetic quantum yield of O~2~ evolution---O~2~ evolution rate per absorbed photons by the leaf---under the PSII- and PSI-lights reciprocally.
+  When measured under PSII-light, the yield was higher in the PSII-light-grown leaves than in the PSI-light-grown leaves; when measured under PSI-light, in contrast, the yield was higher in the PSI-light-grown leaves.
+  Similar trends were observed for the photosynthetic quantum yield of O~2~ evolution [in *Arabidopsis thaliana*; @Walters_Horton1995aPlanta], the photosynthetic quantum yield of CO~2~ uptake [in *Cucumis sativus*; @Hogewoning_et_al2012PC], and *P*~n~ [in *C.
+sativus*, see also Introduction; @Murakami_et_al2016PP].
 
@@
   It is expected that a leaf will perform a higher ETR per absorbed photons by the leaf under measuring light with a PSII/PSI-biased level similar to that of the growth light (Fig. 3).
-  When leaves grown under different SPDs of light are compared and evaluated under a specific SPD of measuring light, the results will inevitably be biased depending on the SPD of the measuring light.
+  When leaves grown under different spectral PFD distributions of light are compared and evaluated under measuring light with a specific relative spectral PFD distribution, therefore, the results will inevitably be biased depending on the SPD of the measuring light.
 
@@
 
-  The interaction may have a considerable impact on *P*~n~, especially when it is measured under low PPFDs and/or high CO~2~ concentrations, where the ETR is a limiting factor for photosynthetic CO~2~ fixation [@vonCaemmerer_Farquhar1981Planta].
+  The interaction may have a considerable impact on *P*~n~, especially when measured under low PPFDs and/or high CO~2~ concentrations, where the ETR is a limiting factor for photosynthetic CO~2~ fixation [@vonCaemmerer_Farquhar1981Planta].
   Under such conditions, any bias in the ETR is directly reflected in *P*~n~.
@@
 
-  The mechanisms of how EED properties adapt to SPD have not yet been fully elucidated [see @Murakami_et_al2016PP].
-  Considering the sensitive adjustments of photosystem stoichiometry in response to the SPD of growth light [e.g.
+  The mechanisms of how EED properties adapt to SPD have not yet been fully elucidated as discussed in @Murakami_et_al2016PP.
+  Considering that the photosystem stoichiometry is sensitive to the SPD of growth light [e.g.
 @Walters_Horton1995aPlanta], the interaction should always be taken into account whenever the *P*~n~ and related indices are compared among leaves grown under different SPDs of light.
@@
 
-  Several studies published over the last decade have investigated the effects of the SPD of the growth light on plant growth and photosynthesis [e.g.
+  Many studies published over the last decade have investigated the effects of the SPD of the growth light on plant growth and photosynthesis [e.g.
 @Matsuda_et_al2004PCP; @Matsuda_et_al2007SSPN; @Matsuda_et_al2008PCP; @Hogewoning_et_al2010aJXB; @Hogewoning_et_al2010bJXB; @Hogewoning_et_al2012PC; @Shibuya_et_al2015BP; @Trouwborst_et_al2016EEB].
-  Growth light provided by most artificial light sources contains little FR light.
+  **Growth light provided by most artificial light sources contains little FR light.**
   In general, fluorescent lamps, metal halide lamps, high-pressure sodium lamps, and blue, red, and white LEDs used for assimilation lighting all emit typical PSII-light (Fig. 4).
@@
 
-  Such biases can also occur when evaluating the vertical profiles of leaf photosynthetic characteristics of plants cultivated in greenhouses.
-  While leaves in the upper layers are acclimated to sunlight, those in the lower layers are acclimated to light that has penetrated through the upper leaves.
-  Due to the higher transmittance in the FR waveband of a leaf, the transmitted light incident on lower leaves contains a relatively greater proportion of FR light (Fig. 4) and is therefore PSI-light.
+  Such biases can also occur when evaluating the vertical profiles of photosynthetic characteristics of individual leaves for **close** plants canopy.
+  While leaves in the upper layers are acclimated to sunlight **unshaded**, those in the lower layers are acclimated to sunlight that has penetrated through the upper leaves.
+  Due to the higher transmittance for FR light of a leaf, the transmitted light incident on lower leaves contains a relatively greater proportion of FR light (Fig. 4) and is therefore PSI-light.
   Consequently, when measured using BR-light, the *P*~n~ of upper leaves might be overestimated while that of lower leaves might be underestimated.
@@
   Ideally, photosynthetic rates and related indices should be measured under *in situ* conditions.
-  In prospective studies focusing on plant growth after measurements, the measurements should be made under the SPD of light that the plant will be subjected to.
-  For instance, when evaluating plants grown under artificial lighting that will be transplanted [e.g.
-@Kozai2007POP], the measurements should be made under sunlight because the plants will be transferred to a greenhouse and cultivated under sunlight.
-  However, the measurements under sunlight may be less reliable because of fluctuations in the incident PPFD.
-  In such cases, SPD-controllable light sources might be helpful [e.g.
-@Yano_Fujiwara2012PM; @Fujiwara_et_al2013Proc] to make *in situ* evaluations under PPFD-stable conditions and to ensure reproducibility and reliability of the results.
+  In prospective studies focusing on plant growth after measurements, the measurements should be made under relative spectral PFD distribution of light to which the plant will be subjected.
+  For instance, when evaluating transplants grown under artificial lighting [e.g.
+@Kozai2007POP], the measurements should be made under sunlight because the plants will be transferred to a greenhouse or an open field and cultivated under sunlight.
+  However, the measurements under actual sunlight may be less reliable because of short-term fluctuations and diurnal change in the spectral distributions [].
+  **In such cases, SPD-controllable light sources might be helpful [e.g.
+@Fujiwara_et_al2013Proc] to make *in situ* evaluations under PPFD-stable conditions and to ensure reproducibility and reliability of the results.**
   In retrospective studies that aim to explain differences among experimental groups, the measurements should be made under the SPDs of light that the plants received during the treatments.
-  For instance, when differences in dry weight between plants grown under white LEDs and those grown under fluorescent lamps are analyzed and *P*~n~ is used as an explanatory variable, the measurements should be made using the white LEDs for the plants grown under white LEDs and using the fluorescent lamps for those grown under fluorescent lamps.
+  For instance, when differences in dry weight between plants grown under white LEDs and those grown under white fluorescent lamps are analyzed and *P*~n~ is used as an explanatory variable, the measurements should be made using the LEDs for the plants grown under white LEDs and using the fluorescent lamps for those grown under white fluorescent lamps.
   In both prospective and retrospective studies, these simple *in situ* measurements will eliminate the problems caused by the interaction between the growth and the measuring light.
 
-  On the other hand, in descriptive studies that hardly make assumption about the *in situ* conditions, *P*~n~ measurements should be made under several SPDs of light including PSII- and PSI-light.
-  It is better for researchers to report on the ‘general’ characteristics of the leaves in these studies.
+  **On the other hand, in descriptive studies that hardly make assumption about the *in situ* conditions, *P*~n~ measurements should be made under several SPDs of light including PSII- and PSI-light.**
+  It is better for researchers to report the ‘general’ characteristics of the leaves in these studies.
   Therefore, the interaction should be tested so as not to make biased evaluations.
   If there is any interaction, the results should be descriptively reported and should not be generalized.
-  When the measurements are made only under a single-pattern of SPD of measuring light because there is no other option, the light source must be described in the materials and methods section so that the reader knows the SPD.
+  When the measurements are made only under a single of SPD of measuring light because there is no other option, **detailed information of the light source (e.g.
+Model ID)** must be described in the materials and methods section so that the reader knows the SPD.
 
@@
 
-  The *P*~n~ under a single-pattern SPD of measuring light is only one aspect of the photosynthetic characteristics of a leaf.
-  Therefore, the obtained results must be discussed in relation to the SPD of the measuring light.
-  Photosynthesis should be evaluated under *in situ* conditions or multi-pattern SPDs of measuring light so that the evaluation is not biased by the interaction between the SPDs of the growth and measuring lights.
+  The *P*~n~ under a single spectral PFD distribution of measuring light is only one aspect of the photosynthetic characteristics of a leaf.
+  Therefore, the obtained results must be discussed in relation to relative spectral distributions of the growth and measuring light.
+  Photosynthesis should be evaluated under *in situ* conditions or several SPDs of measuring light so that the evaluation is not biased by the interaction between the spectral distributions of the growth and measuring lights.
   Imitating the various SPDs of light incident on the leaf for *in situ* evaluation might be difficult or impossible for technical reasons.
-  In addition, measuring the *P*~n~ under multi-pattern SPDs is time-, resource-, and labor-consuming.
+  In addition, measuring the *P*~n~ under several SPDs is time-, resource-, and labor-consuming.
   Although these two approaches might not always be used to evaluate leaf *P*~n~, the interaction should always be considered to make circumspect conclusions.

### 2016-08-17 Main.Rmd
修正を進める。妥協できるレベルまでは仕上がり。3329 words

@@
   The photosynthetic rate is one of the most important and fundamental aspects for plant growth.
-  In many studies this rate is measured, evaluated, and compared among the leaves of plants cultivated under different conditions.
+  In many researches this rate is measured, evaluated, and compared among the leaves of plants cultivated under different conditions.
   The measured rates are also used to calculate other photosynthesis-related indices, such as photosynthetic light-, water-, and nitrogen-use efficiencies.
-  In agricultural and horticultural studies, the effectiveness of treatments is sometimes discussed based on the measured photosynthetic rates and calculated indices.
-  To examine the research questions appropriately, the *P*~n~ should be evaluated .
+  In agricultural and horticultural researches, the effectiveness of treatments is sometimes discussed based on the measured photosynthetic rates and calculated indices.
+  In these researches, the *P*~n~ should be measured appropriately so that researcher can answer the research questions.
 
-  A number of studies have reported that the relative spectral photon flux density (PFD) distribution of light used for measurement (i.e.
+  A number of researches have reported that the relative spectral photon flux density (PFD) distribution of light used for measurement (i.e.
 measuring light or actinic light) affects leaf net photosynthetic rates (*P*~n~) [e.g.
 @McCree1972AM; @Inada1976PCP].
-  To eliminate this direct effect from the comparison, *P*~n~ is usually measured under a common relative spectral PFD distribution of measuring light irrespective of leaf growth conditions in agricultural and horticultural studies.
+  To eliminate this direct effect from the comparison, *P*~n~ is usually measured under a common spectral distribution of measuring light irrespective of leaf growth conditions in agricultural and horticultural researches.
   One of the most widely-used measuring lights is a mixture of blue and red light (BR-light) provided by light-emitting diodes (LEDs) installed in commercial photosynthesis analysis systems (e.g.
-LI6400 and LI6400XT, LI-COR Inc., Lincoln, NE; GFS-3000, Heinz Walz GmbH, Effeltrich, Germany).
+LI6400XT, LI-COR Inc., Lincoln, NE; GFS-3000, Heinz Walz GmbH, Effeltrich, Germany).
   The use of artificial light sources enables precise control of the spectral PFD distribution on the leaf, and therefore, ensures reproducibility and reliability among experiments.
 
-  @Walters2005JXB noted that photosynthetic rates measured with a spectral PFD distribution of light different from that of the growth light do not necessarily reflect the functioning of photosynthesis under the actual growth conditions.
-  Indeed, we have experimentally demonstrated this problem in *P*~n~ measurements in our recent study [@Murakami_et_al2016PP].
-  In that experiment, cucumber seedlings were grown under white LED without and with supplemental far-red (FR) LED light (W and WFR, respectively), and the *P*~n~ of the leaves was subsequently compared under BR-light and under light with a relative spectral PFD distribution approximating to that of sunlight (‘artificial’ sunlight).
+  @Walters2005JXB noted that photosynthetic rates measured with a relative spectral distribution of light different from that of the growth light do not necessarily reflect the functioning of photosynthesis under the actual growth conditions.
+  Indeed, we have demonstrated this problem in *P*~n~ measurements in our recent experiment [@Murakami_et_al2016PP].
+  In that experiment, cucumber seedlings were grown under white LED without and with supplemental far-red (FR) LED light (W and WFR, respectively), and the *P*~n~ of the leaves was subsequently compared under BR-light and under light with a relative spectral distribution approximating to that of sunlight (‘artificial’ sunlight).
   The *P*~n~ of W-grown-leaves was greater than that of WFR-grown-leaves under BR-light, while the rates were comparable under the artificial sunlight [@Murakami_et_al2016PP].
@@
 
-  The effect of the relative spectral PFD distribution of growth light on *P*~n~ depends on the relative spectral PFD distribution of measuring light.
-  In other words, the interaction between the relative spectral PFD distributions of growth light and measuring light affect the *P*~n~ of a leaf.
+  The effect of the relative spectral distribution of growth light on *P*~n~ depends on the distribution of measuring light.
+  In other words, the interaction between the relative spectral distributions of growth light and measuring light affect the *P*~n~ of a leaf.
   In this short article, we describe a plausible mechanism for this interaction, based on the excitation energy distribution balance between the photosystems.
@@
 1; @Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
-  These wavelength dependencies of the excitation balance between PSII and PSI determine **the excitation energy distribution (EED)** under a given relative spectral PFD distribution of light.
-  Light with a given SPD is sometimes categorized as either PSII- or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI [e.g.
+  These wavelength dependencies of the excitation balance between PSII and PSI determine the excitation energy distribution (EED)---the fraction of the excitation energy distributed to PSII (or PSI) to that absorbed by the leaf or by the photosystems---under a given relative spectral PFD distribution of light.
+
+  For instance, ETR can be estimated by a following eauations originated from @Genty_et_al1989BBA,  
+  ETR = PFD × α~leaf~ × β~leaf~ × *Y*~II~,  
+  ETR = PFD × α~PS~ × β~PS~ × *Y*~II~,  
+  where α~leaf~ (frequently assumed to be 0.84) and α~PS~ are absorptances of the leaf and the photosystems, β~leaf~ (frequently assumed to be 0.50) and β~PS~ are EEDs to PSII on the basises of the absorptions by the leaf and by the photosystems, and *Y*~II~ (also known as Φ~PSII~, *F*~q~'/*F*~m~', or Δ*F*/*F*~m~') is a photochemical quantum yield of PSII obtained from chl fluorescence measurement.
+  Although β~leaf~ is frequently assumed to be 0.50, it is not always valid as mentioned above.
+  Lights with different relative spectral distributions are sometimes categorized as PSII- or PSI-light based on the β~PS~ approximated from their spectra and the spectrum of excitation balance (i.e.
+Fig.
+1)---mainly judged by the PFD in the FR waveband [e.g.
 @Chow_et_al1990PNAS; @Melis1991BBA; @Pfannschmidt_et_al2001JBC; @Dietzel_et_al2008FJ; @Pfannschmidt_et_al2009AB; @Dietzel_et_al2011PC; @Hogewoning_et_al2012PC].
@@
   Because the photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) is limited by the slowest step (Fig. 2).
-  When there is excess excitation energy at PSII (i.e. under PSII-light), the smaller amount of excitation energy distributed to PSI results in lower photochemical reaction rates at PSI than at PSII.
-  This shortage in the EED to PSI limits the ETR, thereby leading to the reduction of photochemical quantum yield of PSII and balaced ETR between PSII and PSI (Fig. 2C).
+  When there is excess excitation energy at PSII (i.e. under PSII-light), the smaller amount of excitation energy distributed to PSI results in lower potential ETR at PSI than at PSII.
+  In this case, the smaller potential ETR at PSI limits the bulk ETR and PSII represents a smaller ETR than the potential that by decreasing the photochemical quantum yield (Fig. 2C).
+  <!-- This shortage in the EED to PSI limits the bulk ETR so that ETR between PSII and PSI balances. -->
+  <!-- In this case, PSII represents a smaller photochemical quantum yield compared to its maximum value. -->
   When PSI absorbs excess excitation energy (i.e. under PSI-light), the excitation energy distributed to PSII limits the ETR and lowers the yield of PSI (Fig. 2B).
-  In both cases, the excess energy is dissipated mainly as heat and fluorescence.
-  **Consequently, the entire photosynthetic quantum yield---ETR per absorbed photons by the leaf---becomes smaller.**
+  In both cases, the excess energy is dissipated mainly as heat, thereby leading to a lower photosynthetic quantum yield---ETR per absorbed photons---than that under light with balanced EED for the leaf.
   Therefore, balancing the EED between PSII and PSI is essential for plants to retain a high photosynthetic quantum yield.
-  **for a long period of time** Imbalanced excitation between the photosystems is supposed to damage leaves by generating reactive oxygen species, which cause oxidative damage to chloroplast components [for reviews, see @Asada1999AnnRev; @Asada2006PP].
+  Prolonged imbalances in the EED are supposed to damage leaves by generating reactive oxygen species, which cause oxidative damage to chloroplast components [for reviews, see @Asada1999AnnRev; @Asada2006PP].
 
@@
   The stoichiometry appears to adjust to the spectral PFD distribution of the growth light.
-  Under PSII-light, the relative amount of the reaction center complex of PSII to that of PSI in leaves decreases; conversely, under PSI-light, the relative amount increases to achieve a balance **time scale** [e.g.
+  Under PSII-light, the relative amount of the reaction center complex of PSII to that of PSI in leaves decreases; conversely, under PSI-light, the relative amount increases to achieve a balance [e.g.
 @Melis1991BBA; @Pfannschmidt_et_al1999Nature].
@@
   The categories of light, that is, ‘PSII-light’ and ‘PSI-light’, are defined for a given leaf on a relative scale, not an absolute scale.
-  For instance, the relative spectral PFD distribution of light that is evenly absorbed by PSII and PSI in PSII-light-grown leaves (Fig. 2A), can overexcite PSII in PSI-light-grown leaves (Fig. 2C).
-  Therefore, the terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context.
+  For instance, the relative spectral PFD distribution of light that is evenly absorbed by PSII and PSI in PSII-light-grown leaves (i.e.
+β~PS~ = 0.5; Fig.
+2A), can overexcite PSII in PSI-light-grown leaves (i.e.
+β~PS~ > 0.5; Fig.
+2C).
+  Therefore, the terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context in connection to the given leaf.
   In the short term within an hour, an imbalance in the EED is, at least partly, relieved by the reversible allocation of the light-harvesting antenna complexes of PSII (LHCII) between PSII and PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].
@@
   Thus, the SPDs of growth light and measuring light not only directly affect the *P*~n~, but also indirectly affect it through the interaction between the growth and the measuring light.
-  This expected interaction has been reported in several studies [@Chow_et_al1990PNAS; @Walters_Horton1995aPlanta; @Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
+  This expected interaction has been reported in several researches [@Chow_et_al1990PNAS; @Walters_Horton1995aPlanta; @Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
   In their pioneering research, @Chow_et_al1990PNAS grew *Pisum sativum* plants under light provided by cool-white fluorescent lamps with yellow Plexiglas (PSII-light) and incandescent bulbs with red Plexiglas (PSI-light) and measured the photosynthetic quantum yield of O~2~ evolution---O~2~ evolution rate per absorbed photons by the leaf---under the PSII- and PSI-lights reciprocally.
@@
 @Walters_Horton1995aPlanta], the interaction should always be taken into account whenever the *P*~n~ and related indices are compared among leaves grown under different SPDs of light.
-  Particular attention should be paid to the effects of the interaction on *P*~n~, at least when the measured leaves are expected to represent different EED properties.
+  Particular attention should be paid to the effects of the interaction on *P*~n~, at least when the measured leaves are expected to represent different EED properties, as described below.
 
@@
 @Matsuda_et_al2004PCP; @Matsuda_et_al2007SSPN; @Matsuda_et_al2008PCP; @Hogewoning_et_al2010aJXB; @Hogewoning_et_al2010bJXB; @Hogewoning_et_al2012PC; @Shibuya_et_al2015BP; @Trouwborst_et_al2016EEB].
-  **Growth light provided by most artificial light sources contains little FR light.**
-  In general, fluorescent lamps, metal halide lamps, high-pressure sodium lamps, and blue, red, and white LEDs used for assimilation lighting all emit typical PSII-light (Fig. 4).
+  Most light sources used for promoting photosynthetic and growth rates, such as fluorescent lamps, metal halide lamps, high-pressure sodium lamps, and blue, red, and white LEDs, emit light containing little PFD in the FR waveband (i.e.
+PSII-light; Fig.
+4).
   This is because FR light is hardly ‘photosynthetically active’ and promotes excessive stem elongation.
@@
 
-  Such biases can also occur when evaluating the vertical profiles of photosynthetic characteristics of individual leaves for **close** plants canopy.
-  While leaves in the upper layers are acclimated to sunlight **unshaded**, those in the lower layers are acclimated to sunlight that has penetrated through the upper leaves.
+  Such biases can also occur when evaluating the vertical profiles of photosynthetic characteristics of individual leaves of plants grown in a closed canopy.
+  While leaves in the upper layers are acclimated to sunlight, those in the lower layers are acclimated to sunlight that has penetrated through the upper leaves.
   Due to the higher transmittance for FR light of a leaf, the transmitted light incident on lower leaves contains a relatively greater proportion of FR light (Fig. 4) and is therefore PSI-light.
@@
   Ideally, photosynthetic rates and related indices should be measured under *in situ* conditions.
-  In prospective studies focusing on plant growth after measurements, the measurements should be made under relative spectral PFD distribution of light to which the plant will be subjected.
+  In prospective studies focusing on plant growth after measurements, the measurements should be made under the spectral PFD distribution of light to which the plant will be subjected.
   For instance, when evaluating transplants grown under artificial lighting [e.g.
 @Kozai2007POP], the measurements should be made under sunlight because the plants will be transferred to a greenhouse or an open field and cultivated under sunlight.
-  However, the measurements under actual sunlight may be less reliable because of short-term fluctuations and diurnal change in the spectral distributions [].
-  **In such cases, SPD-controllable light sources might be helpful [e.g.
-@Fujiwara_et_al2013Proc] to make *in situ* evaluations under PPFD-stable conditions and to ensure reproducibility and reliability of the results.**
+  However, the measurements under actual sunlight may be less reliable because of the short-term fluctuations and diurnal changes in the spectral distributions [].
+  The use of artificial light sources approximating *in situ* light [e.g. @Fujiwara_et_al2013Proc] is necessary to make reproducible and reliable *in situ* evaluations.
   In retrospective studies that aim to explain differences among experimental groups, the measurements should be made under the SPDs of light that the plants received during the treatments.
@@
 
-  **On the other hand, in descriptive studies that hardly make assumption about the *in situ* conditions, *P*~n~ measurements should be made under several SPDs of light including PSII- and PSI-light.**
+  On the other hand, in descriptive studies that hardly make assumption about the *in situ* conditions (i.e.
+fundamental researches), *P*~n~ measurements should be made under several SPDs of light including PSII- and PSI-light.
   It is better for researchers to report the ‘general’ characteristics of the leaves in these studies.
@@
   If there is any interaction, the results should be descriptively reported and should not be generalized.
-  When the measurements are made only under a single of SPD of measuring light because there is no other option, **detailed information of the light source (e.g.
-Model ID)** must be described in the materials and methods section so that the reader knows the SPD.
+  When the measurements are made only under a single of SPD of measuring light because there is no other option, detailed information on the light source (e.g.
+model number) must be described in the materials and methods section so that the reader knows the SPD.
 
@@
 
-  The *P*~n~ under a single spectral PFD distribution of measuring light is only one aspect of the photosynthetic characteristics of a leaf.
-  Therefore, the obtained results must be discussed in relation to relative spectral distributions of the growth and measuring light.
-  Photosynthesis should be evaluated under *in situ* conditions or several SPDs of measuring light so that the evaluation is not biased by the interaction between the spectral distributions of the growth and measuring lights.
-  Imitating the various SPDs of light incident on the leaf for *in situ* evaluation might be difficult or impossible for technical reasons.
-  In addition, measuring the *P*~n~ under several SPDs is time-, resource-, and labor-consuming.
+  The *P*~n~ under a relative spectral PFD distribution of measuring light is only one aspect of the photosynthetic characteristics of a leaf.
+  Therefore, the obtained results must be discussed in relation to the relative spectral distributions of the growth and measuring lights.
+  Photosynthesis should be evaluated under *in situ* conditions or several spectral distributions of measuring light so that the evaluation is not biased by the interaction between the spectral distributions of the growth and measuring lights.
+  Imitating the various spectral distributions of light incident on the leaf for *in situ* evaluation might be difficult or impossible for technical reasons.
+  In addition, measuring the *P*~n~ under several spectral distributions is time-, resource-, and labor-consuming.
   Although these two approaches might not always be used to evaluate leaf *P*~n~, the interaction should always be considered to make circumspect conclusions.

### 2016-08-18 Header.Rmd
3363 words おおづめ

@@
 **Abstract**
-
-  The spectral photon flux density distributions of light during growth and for measurements do not only directly affect the net photosynthetic rate (*P*~n~).
-  Moreover, 
+  Relative spectral distributions of light during growth and for measurements do not only directly affect the net photosynthetic rate (*P*~n~), but also indirectly affect it through the interaction between the distributions of the growth and the measuring light.
   This paper summarizes a plausible mechanism of the interaction, some situations in which the interaction should be considered, and recommendations for selecting appropriate measuring light to evaluate photosynthesis.
-  The *P*~n~ should be measured under *in situ* conditions, depending on the purpose of the study.
-  For studies focusing on the evaluation of plant growth after measurements, *P*~n~ should be measured under the SPD of light that the plant will be subjected to.
-  In retrospective studies aiming to elucidate the causes of differences among experimental groups, measurements should be made under the SPDs of the lights the plants were grown under.
-  In descriptive studies, *P*~n~ should be evaluated under several SPDs of measuring light to understand the general photosynthetic characteristics of the leaves.
+  In agricultural and horticultural studies, the *P*~n~ should be measured under *in situ* conditions, depending on the purpose of the study.
+  For prospective studies focusing on the evaluation of plant growth after measurements, *P*~n~ should be measured under the spectral distribution of light to which the plant will be subjected.
+  In retrospective studies aiming to elucidate the causes of differences in growth brought about by the different growth conditions, measurements should be made under the spectral distributions of the lights under which the plants were grown.
   The *P*~n~ under a single spectral distribution of measuring light is only one aspect of the photosynthetic characteristics of a leaf.
-  The obtained results must be discussed in relation to the SPD of measuring light so as not to make biased evaluations.
+  The obtained results must be discussed in relation to the spectral distribution of measuring light so as not to make biased evaluations.
 

### 2016-08-18 Main.Rmd
3363 words おおづめ

@@
   The photosynthetic rate is one of the most important and fundamental aspects for plant growth.
-  In many researches this rate is measured, evaluated, and compared among the leaves of plants cultivated under different conditions.
+  In many studies this rate is measured, evaluated, and compared among the leaves of plants cultivated under different conditions.
   The measured rates are also used to calculate other photosynthesis-related indices, such as photosynthetic light-, water-, and nitrogen-use efficiencies.
   In agricultural and horticultural researches, the effectiveness of treatments is sometimes discussed based on the measured photosynthetic rates and calculated indices.
-  In these researches, the *P*~n~ should be measured appropriately so that researcher can answer the research questions.
 
@@
 @McCree1972AM; @Inada1976PCP].
-  To eliminate this direct effect from the comparison, *P*~n~ is usually measured under a common spectral distribution of measuring light irrespective of leaf growth conditions in agricultural and horticultural researches.
+  To eliminate this direct effect from the comparison, *P*~n~ is usually measured under a common spectral distribution of measuring light irrespective of leaf growth conditions in agricultural and horticultural studies
   One of the most widely-used measuring lights is a mixture of blue and red light (BR-light) provided by light-emitting diodes (LEDs) installed in commercial photosynthesis analysis systems (e.g.
 LI6400XT, LI-COR Inc., Lincoln, NE; GFS-3000, Heinz Walz GmbH, Effeltrich, Germany).
-  The use of artificial light sources enables precise control of the spectral PFD distribution on the leaf, and therefore, ensures reproducibility and reliability among experiments.
+  The use of artificial light sources enables precise control of the spectral distribution of measuring light on the leaf, and therefore, ensures reproducibility and reliability among experiments.
 
@@
   We then suggest situations in which the interaction should be particularly considered.
-  We also discuss good practice for selecting measuring light with an appropriate SPD for *P*~n~ measurements.
-  Several mechanisms other than the excitation balance, such as stomatal responses [@Shimazaki_et_al2007AnnRev], photoinhibition [@Zavafer_et_al2015JPP], and vertical PFD profile within a leaf [@Terashima_et_al2009PCP] affect photosynthesis via the SPD of measuring light.
+  We also discuss good practice for selecting measuring light with appropriate relative spectral distributions for *P*~n~ measurements.
+  Several mechanisms other than the excitation balance, such as stomatal responses [@Shimazaki_et_al2007AnnRev], photoinactivation [@Zavafer_et_al2015JPP], and vertical PFD profile within a leaf [@Terashima_et_al2009PCP] affect photosynthesis via the relative spectral distribution of measuring light.
   Although these subjects are not discussed in this article, the cited articles are available for these topics.
@@
 1; @Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
-  These wavelength dependencies of the excitation balance between PSII and PSI determine the excitation energy distribution (EED)---the fraction of the excitation energy distributed to PSII (or PSI) to that absorbed by the leaf or by the photosystems---under a given relative spectral PFD distribution of light.
-
-  For instance, ETR can be estimated by a following eauations originated from @Genty_et_al1989BBA,  
+  These wavelength dependencies of the excitation balance between PSII and PSI determine the excitation energy distribution (EED)---the fraction of the excitation energy distributed to PSII (or PSI) to that absorbed by the leaf or by the photosystems---under a given relative spectral distribution of light.
+  The idea of EED is adopted in the widely-accepted equations for ETR estimation originated from @Genty_et_al1989BBA,  
   ETR = PFD × α~leaf~ × β~leaf~ × *Y*~II~,  
   ETR = PFD × α~PS~ × β~PS~ × *Y*~II~,  
-  where α~leaf~ (frequently assumed to be 0.84) and α~PS~ are absorptances of the leaf and the photosystems, β~leaf~ (frequently assumed to be 0.50) and β~PS~ are EEDs to PSII on the basises of the absorptions by the leaf and by the photosystems, and *Y*~II~ (also known as Φ~PSII~, *F*~q~'/*F*~m~', or Δ*F*/*F*~m~') is a photochemical quantum yield of PSII obtained from chl fluorescence measurement.
+  where α~leaf~ (frequently assumed to be 0.84) and α~PS~ are absorptances of the leaf and the photosystems, β~leaf~ (frequently assumed to be 0.50) and β~PS~ are EEDs to PSII on the bases of the absorptions by the leaf and by the photosystems, and *Y*~II~ (also known as Φ~PSII~, *F*~q~'/*F*~m~', or Δ*F*/*F*~m~') is a photochemical quantum yield of PSII obtained from chl fluorescence measurement.
   Although β~leaf~ is frequently assumed to be 0.50, it is not always valid as mentioned above.
-  Lights with different relative spectral distributions are sometimes categorized as PSII- or PSI-light based on the β~PS~ approximated from their spectra and the spectrum of excitation balance (i.e.
+  Lights with different spectral distributions are sometimes categorized into PSII- and PSI-light based on the β~PS~ approximated from their relative spectral distributions and the spectrum of excitation balance (i.e.
 Fig.
-1)---mainly judged by the PFD in the FR waveband [e.g.
+1)---mainly judged by the proportions of PFDs in the FR waveband [e.g.
 @Chow_et_al1990PNAS; @Melis1991BBA; @Pfannschmidt_et_al2001JBC; @Dietzel_et_al2008FJ; @Pfannschmidt_et_al2009AB; @Dietzel_et_al2011PC; @Hogewoning_et_al2012PC].
@@
 
-  Apparently, the EED at a given relative spectral PFD distribution of light is also affected by the composition of the thylakoid components, especially the stoichiometry between PSII and PSI.
+  Apparently, the EED at a given relative spectral distribution of light is affected by the composition of the thylakoid components, especially the stoichiometry between PSII and PSI.
   The stoichiometry appears to adjust to the spectral PFD distribution of the growth light.
-  Under PSII-light, the relative amount of the reaction center complex of PSII to that of PSI in leaves decreases; conversely, under PSI-light, the relative amount increases to achieve a balance [e.g.
+  When growth light was changed from PSII-light to PSI-light, the relative amount of the reaction center complex of PSII to that of PSI in leaves increases; conversely, when changed from PSI-light to PSII-light, the relative amount decreases [e.g.
 @Melis1991BBA; @Pfannschmidt_et_al1999Nature].
-  These adjustments in the EED properties might help the leaves to maintain a high photosynthetic quantum yield under different growth lights [@Chow_et_al1990PNAS].
-  As a result of these adjustments in the EED properties of a leaf, the spectrum of excitation balance (Fig. 1) differs depending on the SPD of the growth light.
-  The categories of light, that is, ‘PSII-light’ and ‘PSI-light’, are defined for a given leaf on a relative scale, not an absolute scale.
-  For instance, the relative spectral PFD distribution of light that is evenly absorbed by PSII and PSI in PSII-light-grown leaves (i.e.
+  These adjustments in the EED properties help the leaves to maintain a high photosynthetic quantum yield under different growth lights [@Chow_et_al1990PNAS].
+  As a result of these adjustments in the EED properties of a leaf, the spectrum of excitation balance (Fig. 1) differs depending on the relative spectral distribution of the growth light.
+  Note that the categories of light, that is, ‘PSII-light’ and ‘PSI-light’, are defined for a given leaf on a relative scale, not an absolute scale.
+  For instance, a relative spectral distribution of light that is evenly absorbed by PSII and PSI in PSII-light-grown leaves (i.e.
 β~PS~ = 0.5; Fig.
@@
 2C).
-  Therefore, the terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context in connection to the given leaf.
-  In the short term within an hour, an imbalance in the EED is, at least partly, relieved by the reversible allocation of the light-harvesting antenna complexes of PSII (LHCII) between PSII and PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].
+  In the short term within an hour, an imbalance in the EED is, at least partly, relieved by the reversible allocation of the light-harvesting antenna complexes of PSII between PSII and PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].
   Although a slight imbalance in the EED might be compensated for by state transitions, the long-term adjustments in the EED properties are thought to occur when state transitions are insufficient to counterbalance the uneven EED [@Dietzel_et_al2008FJ].
 
-  The SPD of growth light affects the EED properties of a leaf.
+  The relative spectral distribution of growth light affects the EED properties of a leaf.
   This modifies the responses of ETR, and therefore that of *P*~n~, to the relative spectral PFD distribution of measuring light.
-  Thus, the SPDs of growth light and measuring light not only directly affect the *P*~n~, but also indirectly affect it through the interaction between the growth and the measuring light.
+  Thus, the relative spectral distributions of growth light and measuring light do not only directly affect the *P*~n~, but also indirectly affect it through the interaction between the distributions of the growth and the measuring lights.
   This expected interaction has been reported in several researches [@Chow_et_al1990PNAS; @Walters_Horton1995aPlanta; @Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
@@
   It is expected that a leaf will perform a higher ETR per absorbed photons by the leaf under measuring light with a PSII/PSI-biased level similar to that of the growth light (Fig. 3).
-  When leaves grown under different spectral PFD distributions of light are compared and evaluated under measuring light with a specific relative spectral PFD distribution, therefore, the results will inevitably be biased depending on the SPD of the measuring light.
+  When leaves grown under different spectral distributions of light are compared and evaluated under measuring light with a specific distribution, therefore, the results will inevitably be biased depending on the selecting of the measuring light.
 
@@
 
-  The mechanisms of how EED properties adapt to SPD have not yet been fully elucidated as discussed in @Murakami_et_al2016PP.
-  Considering that the photosystem stoichiometry is sensitive to the SPD of growth light [e.g.
-@Walters_Horton1995aPlanta], the interaction should always be taken into account whenever the *P*~n~ and related indices are compared among leaves grown under different SPDs of light.
+  The mechanisms of how EED properties adapt to relative spectral distributions of growth light have not yet been fully elucidated as discussed in @Murakami_et_al2016PP.
+  Considering that the photosystem stoichiometry is sensitive to the relative spectral distribution of growth light [e.g.
+@Walters_Horton1995aPlanta], the interaction should always be taken into account whenever the *P*~n~ and related indices are compared among leaves grown with different relative spectral distributions.
   Particular attention should be paid to the effects of the interaction on *P*~n~, at least when the measured leaves are expected to represent different EED properties, as described below.
 
-  Many studies published over the last decade have investigated the effects of the SPD of the growth light on plant growth and photosynthesis [e.g.
+  Many studies published over the last decade have investigated the effects of the relative spectral distribution of the growth light on plant growth and photosynthesis [e.g.
 @Matsuda_et_al2004PCP; @Matsuda_et_al2007SSPN; @Matsuda_et_al2008PCP; @Hogewoning_et_al2010aJXB; @Hogewoning_et_al2010bJXB; @Hogewoning_et_al2012PC; @Shibuya_et_al2015BP; @Trouwborst_et_al2016EEB].
@@
 4).
-  This is because FR light is hardly ‘photosynthetically active’ and promotes excessive stem elongation.
+  This is because FR light is hardly ‘photosynthetically active’ and causes excessive stem elongation.
   However, several recent papers have suggested the significance of supplemental FR light on plant growth and development [for a review, see @Demotes-Mainard_et_al2016EEB].
-  Since FR light overexcites PSI, leaves grown under PSII-light with supplemental FR light are more similar to PSI-leaves in terms of their EED properties, compared with leaves of plants grown without supplemental FR light.
+  Since FR light overexcites PSI, leaves grown under PSII-light with supplemental FR light may be more similar to PSI-leaves in terms of their EED properties, compared with leaves of plants grown without supplemental FR light.
   Therefore, comparing the *P*~n~ of leaves of plants grown with and without supplemental FR light using BR-light as the measuring light might lead to a biased evaluation because of the interaction, as demonstrated in our recent report [@Murakami_et_al2016PP].
 
-  Such biases can also occur when evaluating the vertical profiles of photosynthetic characteristics of individual leaves of plants grown in a closed canopy.
+  Such biases can also occur when evaluating the vertical profiles of photosynthetic characteristics of individual leaves of plants grown in closed canopy.
   While leaves in the upper layers are acclimated to sunlight, those in the lower layers are acclimated to sunlight that has penetrated through the upper leaves.
-  Due to the higher transmittance for FR light of a leaf, the transmitted light incident on lower leaves contains a relatively greater proportion of FR light (Fig. 4) and is therefore PSI-light.
+  Due to the higher transmittance in the FR waveband of a leaf, the transmitted light incident on lower leaves contains a relatively greater proportion of PFD in the FR waveband (Fig.
+4) and is therefore PSI-light.
   Consequently, when measured using BR-light, the *P*~n~ of upper leaves might be overestimated while that of lower leaves might be underestimated.
 
-# Selecting appropriate SPDs of measuring light for evaluating photosynthetic rates
+# Selecting appropriate relative spectral distributions of measuring light for evaluating photosynthetic rates
 
   Ideally, photosynthetic rates and related indices should be measured under *in situ* conditions.
-  In prospective studies focusing on plant growth after measurements, the measurements should be made under the spectral PFD distribution of light to which the plant will be subjected.
+  In prospective studies focusing on plant growth after measurements, the measurements should be made under the spectral distribution of light to which the plant will be subjected.
   For instance, when evaluating transplants grown under artificial lighting [e.g.
 @Kozai2007POP], the measurements should be made under sunlight because the plants will be transferred to a greenhouse or an open field and cultivated under sunlight.
-  However, the measurements under actual sunlight may be less reliable because of the short-term fluctuations and diurnal changes in the spectral distributions [].
-  The use of artificial light sources approximating *in situ* light [e.g. @Fujiwara_et_al2013Proc] is necessary to make reproducible and reliable *in situ* evaluations.
-  In retrospective studies that aim to explain differences among experimental groups, the measurements should be made under the SPDs of light that the plants received during the treatments.
-  For instance, when differences in dry weight between plants grown under white LEDs and those grown under white fluorescent lamps are analyzed and *P*~n~ is used as an explanatory variable, the measurements should be made using the LEDs for the plants grown under white LEDs and using the fluorescent lamps for those grown under white fluorescent lamps.
-  In both prospective and retrospective studies, these simple *in situ* measurements will eliminate the problems caused by the interaction between the growth and the measuring light.
+  However, the measurements under actual sunlight may be less reliable because of the short-term fluctuations and diurnal changes in the spectral distributions.
+  In this case, therefore, the use of artificial light sources, which provide light with relative spectral distributions approximating to that of sunlight [e.g.
+@Fujiwara_et_al2013Proc], may be necessary to make comparable, reproducible and reliable *in situ* evaluations.
+  In retrospective studies that aim to explain differences in growth brought about by the different growth conditions, the measurements should be made under the spectral distributions of light that the plants received during the treatments.
+  For instance, when differences in dry weight between plants grown under white LEDs and those grown under white fluorescent lamps are analyzed and *P*~n~ is used as an explanatory variable, the measurements should be made using the white LEDs for the plants grown under the LEDs and using the white fluorescent lamps for those grown under the fluorescent lamps.
+  In both prospective and retrospective studies, these simple *in situ* measurements will eliminate the problems caused by the interaction between the growth and the measuring lights.
 
   On the other hand, in descriptive studies that hardly make assumption about the *in situ* conditions (i.e.
-fundamental researches), *P*~n~ measurements should be made under several SPDs of light including PSII- and PSI-light.
-  It is better for researchers to report the ‘general’ characteristics of the leaves in these studies.
+fundamental studies), *P*~n~ measurements should be made under several relative spectral distributions of light including PSII- and PSI-light.
+  It is better for researchers to report the ‘general’ photosynthetic characteristics of the leaves in these studies.
   Therefore, the interaction should be tested so as not to make biased evaluations.
   If there is any interaction, the results should be descriptively reported and should not be generalized.
-  When the measurements are made only under a single of SPD of measuring light because there is no other option, detailed information on the light source (e.g.
-model number) must be described in the materials and methods section so that the reader knows the SPD.
+  When the measurements are made only under a single spectral distribution of measuring light because there is no other option, detailed information on the light source (e.g.
+model number) must be described in the materials and methods section so that the reader knows the spectral distribution.
 
@@
   Therefore, the obtained results must be discussed in relation to the relative spectral distributions of the growth and measuring lights.
-  Photosynthesis should be evaluated under *in situ* conditions or several spectral distributions of measuring light so that the evaluation is not biased by the interaction between the spectral distributions of the growth and measuring lights.
+  Photosynthesis should be evaluated under *in situ* light or several relative spectral distributions of light so that the evaluation is not biased by the interaction between the spectral distributions of the growth and measuring lights.
   Imitating the various spectral distributions of light incident on the leaf for *in situ* evaluation might be difficult or impossible for technical reasons.

### 2016-08-19 Header.Rmd
SWHに原稿を送付

@@
 ---
-title: "A basis for selecting light spectral distribution for evaluating photosynthetic rates of leaves grown under different light spectral distributions"
+title: "A basis for selecting light spectral distribution for evaluating leaf photosynthetic rates of plants grown under different light spectral distributions"
 author: "Keach Murakami^1\\*^, Ryo Matsuda^1^, Kazuhiro Fujiwara^1^"
@@
     fig_caption: TRUE
-  word_document:
-    toc: FALSE
-    fig_caption: TRUE
+  # word_document:
+  #   toc: FALSE
+  #   fig_caption: TRUE
 ---
@@
 
-e-mail: keach.murakami@gmail.com
+Mail: keach.murakami@gmail.com
+
+Running title: the spectral distribution for evaluating leaf photosynthesis
 
@@
   The obtained results must be discussed in relation to the spectral distribution of measuring light so as not to make biased evaluations.
-
-------
 
@@
 
-------
+**Keywords**  
+Excitation energy distribution, Light quality, Photosystems, PSII, PSI
 

### 2016-08-19 Main.Rmd
SWHに原稿を送付

@@
 @McCree1972AM; @Inada1976PCP].
-  To eliminate this direct effect from the comparison, *P*~n~ is usually measured under a common spectral distribution of measuring light irrespective of leaf growth conditions in agricultural and horticultural studies
+  To eliminate this direct effect from the comparison, *P*~n~ is usually measured under a common spectral distribution of measuring light irrespective of growth conditions in agricultural and horticultural studies.
   One of the most widely-used measuring lights is a mixture of blue and red light (BR-light) provided by light-emitting diodes (LEDs) installed in commercial photosynthesis analysis systems (e.g.
-LI6400XT, LI-COR Inc., Lincoln, NE; GFS-3000, Heinz Walz GmbH, Effeltrich, Germany).
+LI6400XT, LI-COR Inc., Lincoln, NE; GFS-3000, US, Heinz Walz GmbH, Effeltrich, Germany).
   The use of artificial light sources enables precise control of the spectral distribution of measuring light on the leaf, and therefore, ensures reproducibility and reliability among experiments.
@@
   The *P*~n~ of W-grown-leaves was greater than that of WFR-grown-leaves under BR-light, while the rates were comparable under the artificial sunlight [@Murakami_et_al2016PP].
-  Based on the results obtained from measurement under BR-light, the prospective leaf photosynthetic rate of WFR-grown-plants may be evaluated to be smaller than that of W-grown-plants, despite the comparable rates under sunlight.
+  Based on the results obtained from measurement under BR-light, the prospective leaf photosynthetic rate (i.e.
+leaf photosynthetic rates after the measurements) of WFR-grown-plants may be evaluated to be smaller than that of W-grown-plants, despite the comparable rates under sunlight.
 
@@
   We then suggest situations in which the interaction should be particularly considered.
-  We also discuss good practice for selecting measuring light with appropriate relative spectral distributions for *P*~n~ measurements.
+  We also discuss good practice for selecting measuring light with appropriate relative spectral distributions for *P*~n~ evaluations.
   Several mechanisms other than the excitation balance, such as stomatal responses [@Shimazaki_et_al2007AnnRev], photoinactivation [@Zavafer_et_al2015JPP], and vertical PFD profile within a leaf [@Terashima_et_al2009PCP] affect photosynthesis via the relative spectral distribution of measuring light.
@@
 
-  The two photosystems---PSII and PSI---represent different spectral distributions of light absorption due to their different compositions of binding pigments, mainly chl *a* and chl *b*.
-  Within the chlorophyll (chl) absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited compared with PSII [Fig.
+  The two photosystems---PSII and PSI---represent different spectral distributions of light absorption due to their different compositions of binding pigments, mainly chloropyhll (chl) *a* and chl *b*.
+  Within the chl absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited compared with PSII [Fig.
 1; @Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
@@
   These wavelength dependencies of the excitation balance between PSII and PSI determine the excitation energy distribution (EED)---the fraction of the excitation energy distributed to PSII (or PSI) to that absorbed by the leaf or by the photosystems---under a given relative spectral distribution of light.
-  The idea of EED is adopted in the widely-accepted equations for ETR estimation originated from @Genty_et_al1989BBA,  
+  The idea of EED is adopted in the following equations for ETR estimation originated from @Genty_et_al1989BBA,  
   ETR = PFD × α~leaf~ × β~leaf~ × *Y*~II~,  
@@
   Because the photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) is limited by the slowest step (Fig. 2).
-  When there is excess excitation energy at PSII (i.e. under PSII-light), the smaller amount of excitation energy distributed to PSI results in lower potential ETR at PSI than at PSII.
+  When there is excess excitation energy at PSII (i.e. under PSII-light), the smaller amount of excitation energy distributed to PSI results in lower potential ETR at PSI than that at PSII.
   In this case, the smaller potential ETR at PSI limits the bulk ETR and PSII represents a smaller ETR than the potential that by decreasing the photochemical quantum yield (Fig. 2C).
@@
   When PSI absorbs excess excitation energy (i.e. under PSI-light), the excitation energy distributed to PSII limits the ETR and lowers the yield of PSI (Fig. 2B).
-  In both cases, the excess energy is dissipated mainly as heat, thereby leading to a lower photosynthetic quantum yield---ETR per absorbed photons---than that under light with balanced EED for the leaf.
+  In both cases, the excess energy is dissipated mainly as heat, thereby leading to a lower photosynthetic quantum yield---ETR per absorbed photons by the photosystems---than that under light with suitable EED for the leaf.
   Therefore, balancing the EED between PSII and PSI is essential for plants to retain a high photosynthetic quantum yield.
@@
   Apparently, the EED at a given relative spectral distribution of light is affected by the composition of the thylakoid components, especially the stoichiometry between PSII and PSI.
-  The stoichiometry appears to adjust to the spectral PFD distribution of the growth light.
+  The stoichiometry appears to adjust to the relative spectral distribution of the growth light.
   When growth light was changed from PSII-light to PSI-light, the relative amount of the reaction center complex of PSII to that of PSI in leaves increases; conversely, when changed from PSI-light to PSII-light, the relative amount decreases [e.g.
 @Melis1991BBA; @Pfannschmidt_et_al1999Nature].
-  These adjustments in the EED properties help the leaves to maintain a high photosynthetic quantum yield under different growth lights [@Chow_et_al1990PNAS].
+  These adjustments in the EED properties help the leaves to maintain a high photosynthetic quantum yield under growth conditions [@Chow_et_al1990PNAS].
   As a result of these adjustments in the EED properties of a leaf, the spectrum of excitation balance (Fig. 1) differs depending on the relative spectral distribution of the growth light.
@@
   These reports suggested that the EED properties of a leaf might be tuned to the PSII/PSI-biased level of growth light.
-  It is expected that a leaf will perform a higher ETR per absorbed photons by the leaf under measuring light with a PSII/PSI-biased level similar to that of the growth light (Fig. 3).
+  It is expected that a leaf will perform a higher ETR per absorbed photons by the photosystems under measuring light with a PSII/PSI-biased level similar to that of the growth light (Fig. 3).
   When leaves grown under different spectral distributions of light are compared and evaluated under measuring light with a specific distribution, therefore, the results will inevitably be biased depending on the selecting of the measuring light.
@@
 @Walters_Horton1995aPlanta], the interaction should always be taken into account whenever the *P*~n~ and related indices are compared among leaves grown with different relative spectral distributions.
-  Particular attention should be paid to the effects of the interaction on *P*~n~, at least when the measured leaves are expected to represent different EED properties, as described below.
+  Particular attention should be paid to the effects of the interaction on *P*~n~, at least when the evaluated leaves are expected to represent different EED properties, as described below.
 
@@
 
-  Ideally, photosynthetic rates and related indices should be measured under *in situ* conditions.
-  In prospective studies focusing on plant growth after measurements, the measurements should be made under the spectral distribution of light to which the plant will be subjected.
+  Ideally, photosynthetic rates and related indices should be evaluated under *in situ* conditions.
+  In prospective studies focusing on plant growth after measurements, the evaluations should be made under the spectral distribution of light to which the plant will be subjected.
   For instance, when evaluating transplants grown under artificial lighting [e.g.
@@
   For instance, when differences in dry weight between plants grown under white LEDs and those grown under white fluorescent lamps are analyzed and *P*~n~ is used as an explanatory variable, the measurements should be made using the white LEDs for the plants grown under the LEDs and using the white fluorescent lamps for those grown under the fluorescent lamps.
-  In both prospective and retrospective studies, these simple *in situ* measurements will eliminate the problems caused by the interaction between the growth and the measuring lights.
+  In both prospective and retrospective studies, these simple *in situ* evaluations will eliminate the problems caused by the interaction between the growth and the measuring lights.
 
   On the other hand, in descriptive studies that hardly make assumption about the *in situ* conditions (i.e.
-fundamental studies), *P*~n~ measurements should be made under several relative spectral distributions of light including PSII- and PSI-light.
+fundamental studies), *P*~n~ evaluations should be made under several relative spectral distributions of light including PSII- and PSI-light.
   It is better for researchers to report the ‘general’ photosynthetic characteristics of the leaves in these studies.
@@
 
-```{r EED, eval = evalFig}
-library(EBImage)
-which_mean <- function(x) x %>% which %>% mean
-Join_by <- function(x, y) join(x, y, by = "wavelength")
-
-  Hoge_PSII <- readImage("~/Dropbox/Publish/2016PgEstimate/Data/Hoge_PSII.png")
-  Hoge_PSI <- readImage("~/Dropbox/Publish/2016PgEstimate/Data/Hoge_PSI.png")
-
-  Abs_PSII <-
-    (Hoge_PSII[, , 1] < .8 & Hoge_PSII[, , 3] > .8) %>%
-    .@.Data %>%
-    data.frame %>%
-    t %>%
-    aaply(.margins = 2, .fun = which_mean) %>%
-    data.frame(wavelength = seq(400, 800, by = 1), abs = (dim(Hoge_PSII)[2] - .)) %>%
-    select(wavelength, PSII = abs)
-
-  Abs_PSI <-
-    (Hoge_PSI[, , 1] > .8 & Hoge_PSI[, , 3] < .8) %>%
-    .@.Data %>%
-    data.frame %>%
-    t %>%
-    aaply(.margins = 2, .fun = which_mean) %>%
-    data.frame(wavelength = seq(400, 800, by = 1), abs = (dim(Hoge_PSI)[2] - .)) %>%
-    select(wavelength, PSI = abs)
-
-Mole_abs <-
-  Reduce(Join_by, list(Abs_PSII, Abs_PSI)) %>%
-  filter(wavelength %% 1 == 0) %>%
-  na.omit
-
-EED_dat <-
-  Mole_abs %>%
-  transmute(
-    wavelength,
-    AlltoPSII = PSII / (1.5 * PSI + PSII)
-  )
-
-EEDs <-
-  EED_dat %>%
-    mutate(All2_for = c(tail(EED_dat$AlltoPSII, -1), 0),
-           All2_back = c(0, head(EED_dat$AlltoPSII, -1)),
-           AlltoPSII = (AlltoPSII + All2_for + All2_back) / 3) %>% # get moving average
-    filter(wavelength > 400)  %>%
-    replace_na(list(AlltoPSII = 0)) %>%
-    ggplot(aes(x = wavelength, y = AlltoPSII)) +
-    theme_thesis(base_family = "serif", base_size = base_size) +
-    geom_hline(yintercept = 0.5, col = "grey50", linetype = 3) +
-    gg_x(c(380, 770)) +
-    # geom_ribbon(aes(ymin = AlltoPSII_max, ymax = AlltoPSII_min), col = "grey50") +
-    geom_line() +
-    scale_y_continuous(labels = c("0    ", "0.25", "0.50", "0.75", "1.00"),
-                       breaks = c(0, 0.25, 0.5, 0.75, 1),
-                       limits = c(-.005, 1.005),
-                       expand = c(0, 0)) +
-    xlab("Wavelength [nm]") + ylab("Fraction of the excitation energy distributed to PSII")
-```
-
-```{r InteractionPict, eval = evalFig}
-
-X_div <- 101
-X_range <- seq(0, 1, length.out = X_div)
-x_breaks <- c(0.2, 0.4, 0.65)
-
-InteractionDat <-
-  data_frame(X = rep(X_range, times = 2),
-           ETR = c(sqrt(dbeta(X_range, 4.5, 3.5)) * 1.1, sqrt(dbeta(X_range, 3, 5))),
-           Trtm = rep(c("PSII-leaves", "PSI-leaves"), each = X_div))
-
-InteractionLabel <-
-  InteractionDat %>%
-  group_by(Trtm) %>%
-  summarise(ETR = max(ETR)) %>%
-  left_join(., InteractionDat, by = c("Trtm", "ETR"))
-
-InteractionPoint <-
-  InteractionDat %>%
-  filter(X %in% x_breaks)
-
-InteractionText <-
-  InteractionDat %>%
-  filter(X %in% x_breaks) %>%
-  mutate(labels = c("far-red LED light", "Sunlight", "blue + red LED light", rep("", length(x_breaks)))) %>%
-  mutate(ETR = c(0.1, 0.1, 0.1, numeric(length(x_breaks))))
-
-InteractionView <-
-  InteractionDat %>%
-  ggplot(aes(X, ETR, linetype = Trtm, fill = Trtm, group = Trtm)) +
-  theme_thesis(base_family = "serif", base_size = base_size) +
-  geom_vline(aes(xintercept = x_breaks[1]), linetype = 3, size = .75, col = "grey") +
-  geom_vline(aes(xintercept = x_breaks[2]), linetype = 3, size = .75, col = "grey") +
-  geom_vline(aes(xintercept = x_breaks[3]), linetype = 3, size = .75, col = "grey") +
-  geom_line() +
-  geom_point(data = InteractionPoint, col = "black", size = 3, shape = 21) +
-  geom_text(data = InteractionLabel, aes(x = X, y = ETR, label = Trtm), vjust = -1, family = "serif", size = Annotate_size) +
-  geom_text(data = InteractionText, aes(label = labels), vjust = 1, family = "serif", size = Annotate_size) +
-  scale_fill_manual(values = c("white", "black")) +
-  scale_linetype_manual(values = c(2, 1)) +
-  scale_x_continuous(breaks = c(0.07, 0.92),
-                     limits = c(0.05, 0.95),
-                     labels = c("PSI-biased", "PSII-biased")) +
-  scale_y_continuous(breaks = NULL,
-                     limits = c(-0.05, 2.05)) +
-  xlab("PSII/PSI-biased level of measuring light") +
-  ylab("Relative electron transport rate")
-
-```
-
-```{r Spectra, eval = evalFig}
-
-# set integrate ranges
-PFD_integrate_min <- 350
-PFD_integrate_max <- 750
-
-IntegratePFD <- 100
-
-panel_names <- c("(a)", "(b)", "(c)")
-
-FL_Ocean_raw <-
-  fread("~/Dropbox/materials/SPD_FL.csv") %>%
-  transmute(wavelength = `Wavelength[nm]`, value = FL) %>%
-  na.omit
-
-FL_Ocean_PFD <-
-  smooth.spline(FL_Ocean_raw$wavelength, FL_Ocean_raw$value) %>%
-    predict(., seq(PFD_integrate_min, PFD_integrate_max)) %>%
-    .$y %>%
-  sum
-
-FL_Ocean <-
-  FL_Ocean_raw %>%
-  mutate(value = value * 100 / FL_Ocean_PFD, variable = "FL")
-
-HPS_Ocean_raw <-
-  fread("~/Dropbox/materials/SPD_HPS.txt", skip = 50, nrow = 2000) %>%
-  rename(wavelength = V1, value = V2)
-
-HPS_Ocean_PFD <-
-  smooth.spline(HPS_Ocean_raw$wavelength, HPS_Ocean_raw$value) %>%
-    predict(., seq(PFD_integrate_min, PFD_integrate_max)) %>%
-    .$y %>%
-  sum
-
-HPS_Ocean <-
-  HPS_Ocean_raw %>%
-  mutate(value = value * 100 / HPS_Ocean_PFD, variable = "HPS")
-
-MH_Ocean_raw <-
-  fread("~/Dropbox/materials/SPD_MH.txt", skip = 50, nrow = 2000) %>%
-  rename(wavelength = V1, value = V2)
-
-MH_Ocean_PFD <-
-  smooth.spline(MH_Ocean_raw$wavelength, MH_Ocean_raw$value) %>%
-    predict(., seq(PFD_integrate_min, PFD_integrate_max)) %>%
-    .$y %>%
-  sum
-
-MH_Ocean <-
-  MH_Ocean_raw %>%
-  mutate(value = value * 100 / MH_Ocean_PFD, variable = "MH")
-
-OceanSPDs <-
-  bind_rows(FL_Ocean, HPS_Ocean, MH_Ocean) %>%
-  mutate(panel = panel_names[1])
-
-Absorptances <-
-  fread("~/Dropbox/materials/SpectrumCucumber.csv") %>%
-  filter(Trtm %in% c("W", "WFR", "FL")) %>%
-  mutate(wavelength = as.numeric(wavelength)) %>%
-  filter(variable == "absorption", Trtm == "W")
-
-# Sun: JIS C8904-3
-Sun <-
-  fread("~/Dropbox/materials/Sunlight_JIS.csv") %>%
-  setnames(c("wavelength", "Sunlight")) %>%
-  left_join(., Absorptances, by = "wavelength") %>%
-  transmute(wavelength, Sun = Sunlight, Shade = Sunlight * (100 - ave), Absorptance = ave)
-
-LEDs <-
-  fread("~/Dropbox/materials/SPD_FL.csv") %>%
-  transmute(wavelength = `Wavelength[nm]`, W, FR, B = B_HL, R = R_SR) %>%
-  SPDnorm(from = 350, to = 750, integratedPFD = IntegratePFD) %>%
-  gather(variable, value, -wavelength) %>%
-  mutate(panel = panel_names[2]) %>%
-  na.omit
-
-SPD_labels <-
-  data_frame(variable = c("FL", "MH", "HPS", "B", "R", "FR", "W", "Sun", "Shade"),
-             wavelength = c(435, 520, 570, 448, 660, 735, 460, 450, 700),
-             value = c(2.2, .6, 3, 4, 4.2, 3.8, 1.3, 0.6, 2),
-             label = c("FL", "MH", "HPS", "B", "R", "FR", "W", "Sunlight", "Leaf-transmitted sunlight"),
-             panel = rep(panel_names,  c(3, 4, 2)))
-
-SPD_panel <-
-  data_frame(variable = "FL",
-           wavelength = 400, value = 4,
-           label = letters[1:3],
-           panel = rep(panel_names))
-
-SPDs <-
-  Sun %>%
-  SPDnorm(from = 350, to = 750, integratedPFD = IntegratePFD) %>%
-  select(-Absorptance) %>%
-  gather(variable, value, -wavelength) %>%
-  mutate(panel = panel_names[3]) %>%
-  bind_rows(., OceanSPDs, LEDs) %>%
-  filter(between(wavelength, 380, 820)) %>%
-  ggplot(aes(x = wavelength, y = value, group = variable, col = variable, linetype = variable)) +
-  theme_thesis(base_family = "serif", base_size = base_size) +
-  geom_rect(aes(xmin = 700, xmax = 750, ymin = 0, ymax = +Inf), fill = "grey90", col = NA) +
-  geom_line() +
-  geom_text(data = SPD_labels, aes(x = wavelength, y = value, label = label), family = "serif", size = Annotate_size) +
-  geom_text(data = SPD_panel, col = "black", aes(label = panel), family = "serif", size = Annotate_size * .8) +
-  scale_linetype_manual(values = c(1, 1, 3, 2, 4, 2, 2, 1, 4)) +
-  scale_color_manual(values = c("blue", "black", "darkred", "orange", "purple", "red", "grey25", "black", "black")) +
-  facet_grid(panel ~ .) +
-  gg_xy(c(380, 820, -.01, 4.5)) +
-  xlab("Wavelength [nm]") + ylab(u_SPFD("Spectral photon flux density"))
+```{r, eval = evalFig}
+source("./FigMake.R")
 ```

### 2016-08-19 FigMake.R

@@ -1,0 +1,228 @@
+#-------------- EED balance spectrum
+
+if (1 == 1){
+library(EBImage)
+which_mean <- function(x) x %>% which %>% mean
+Join_by <- function(x, y) join(x, y, by = "wavelength")
+
+Hoge_PSII <- readImage("~/Dropbox/Publish/2016PgEstimate/Data/Hoge_PSII.png")
+Hoge_PSI <- readImage("~/Dropbox/Publish/2016PgEstimate/Data/Hoge_PSI.png")
+
+Abs_PSII <-
+  (Hoge_PSII[, , 1] < .8 & Hoge_PSII[, , 3] > .8) %>%
+  .@.Data %>%
+  data.frame %>%
+  t %>%
+  aaply(.margins = 2, .fun = which_mean) %>%
+  data.frame(wavelength = seq(400, 800, by = 1), abs = (dim(Hoge_PSII)[2] - .)) %>%
+  select(wavelength, PSII = abs)
+
+Abs_PSI <-
+  (Hoge_PSI[, , 1] > .8 & Hoge_PSI[, , 3] < .8) %>%
+  .@.Data %>%
+  data.frame %>%
+  t %>%
+  aaply(.margins = 2, .fun = which_mean) %>%
+  data.frame(wavelength = seq(400, 800, by = 1), abs = (dim(Hoge_PSI)[2] - .)) %>%
+  select(wavelength, PSI = abs)
+
+Mole_abs <-
+  Reduce(Join_by, list(Abs_PSII, Abs_PSI)) %>%
+  filter(wavelength %% 1 == 0) %>%
+  na.omit
+}
+
+# Mole_abs <-
+#   xlsx::read.xlsx("~/Dropbox/materials/Hogewoning_et_al.2012_Data.xlsx", sheetIndex = 2, startRow = 2) %>%
+#   select(wavelength = 1, PSII = 2, PSI = 4) %>%
+#   arrange(wavelength)
+#   
+EED_dat <-
+  Mole_abs %>%
+  transmute(
+    wavelength,
+    AlltoPSII = PSII / (1.2* PSI + PSII)
+  )
+
+EEDs <-
+  EED_dat %>%
+  mutate(All2_for = c(tail(EED_dat$AlltoPSII, -1), 0),
+         All2_back = c(0, head(EED_dat$AlltoPSII, -1)),
[…]

### 2016-08-19 caption.R

@@ -1,11 +1,11 @@
 CapEED <-
-  "Fig. 1  Typical excitation balance between photosystems in response to wavelength of measuring light. Spectrum was calculated from absorbance spectra of PSII and PSI complexes in solvent (Hogewoning et al. 2012)."
+  "Fig. 1  Typical excitation balance between photosystems in response to wavelength of measuring light. Spectrum was calculated from absorbance spectra of PSII and PSI complexes in solvent (Hogewoning et al. 2012) with a little modifications. The spectrum is adjusted so that the excitation energy distributed to PSII under red LED light matches a quantified value (55%, unpublished data)."
 
 CapETRs <-
-  "Fig. 2  Conceptual diagrams of effects of excitation energy distribution between photosystems (PSII and PSI) on photosynthetic electron transport rate (ETR). Figure shows electron flow (white lines) and energy flow (black lines) in leaves grown under PSII-light (a, b) and PSI-light (c, d) and measured using PSII-light (a, c) and PSI-light (b, d). Excitation energy distribution properties of leaves are adjusted depending on growth light. GL: growth light, ML: measuring light."
+  "Fig. 2  Conceptual diagrams of effects of excitation energy distribution between photosystems (PSII and PSI) on photosynthetic electron transport rate (ETR). Electron transport is driven by photochemical reactions at reaction centers (gears) consuming the distributed excitation energy. Figure shows electron flow (white lines) and energy flow (black lines) in leaves grown under PSII-light (a, b) and PSI-light (c, d) and measured using PSII-light (a, c) and PSI-light (b, d). Excitation energy distribution properties of leaves are adjusted depending on growth light. GL: growth light, ML: measuring light."
 
 CapInteract <-
-  "Fig. 3  Conceptual diagram of photosynthetic electron transport rates per absorbed photons by leaves grown under PSII-light (PSII-leaves) and PSI-light (PSI-leaves) in response to the PSII/PSI-biased level of measuring light."
+  "Fig. 3  Conceptual diagram of photosynthetic electron transport rates per absorbed photons by the photosystems of leaves grown under PSII-light (PSII-leaves) and PSI-light (PSI-leaves) in response to the PSII/PSI-biased level of measuring light."
 
 CapSPD <-
[…]

### 2016-08-22 Header.Rmd
RM修正。完了3427 words SWHからの許可待ちで終わり。

@@
 #     fig_caption: TRUE
-# fontsize: 20pt
-# geometry: margin=1.2in
   html_document:
@@
 **Abstract**  
-  Relative spectral distributions of light during growth and for measurements do not only directly affect the net photosynthetic rate (*P*~n~), but also indirectly affect it through the interaction between the distributions of the growth and the measuring light.
+  Relative spectral distributions of light during growth and for measurements do not only directly affect the net photosynthetic rate (*P*~n~), but also indirectly affect it through the interaction between the distributions of the lights.
   This paper summarizes a plausible mechanism of the interaction, some situations in which the interaction should be considered, and recommendations for selecting appropriate measuring light to evaluate photosynthesis.

### 2016-08-22 Main.Rmd
RM修正。完了3427 words SWHからの許可待ちで終わり。

@@
   One of the most widely-used measuring lights is a mixture of blue and red light (BR-light) provided by light-emitting diodes (LEDs) installed in commercial photosynthesis analysis systems (e.g.
-LI6400XT, LI-COR Inc., Lincoln, NE; GFS-3000, US, Heinz Walz GmbH, Effeltrich, Germany).
+LI-6400, LI-COR Inc., Lincoln, NE, USA; GFS-3000, Heinz Walz GmbH, Effeltrich, Germany).
   The use of artificial light sources enables precise control of the spectral distribution of measuring light on the leaf, and therefore, ensures reproducibility and reliability among experiments.
@@
 1; @Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
-  These wavelength dependencies of the excitation balance between PSII and PSI determine the excitation energy distribution (EED)---the fraction of the excitation energy distributed to PSII (or PSI) to that absorbed by the leaf or by the photosystems---under a given relative spectral distribution of light.
+  These wavelength dependencies of the excitation balance between PSII and PSI determine the excitation energy distribution (EED)---the fraction of the excitation energy distributed to PSII (or PSI) to that absorbed by the leaf or by the both photosystems---under a given relative spectral distribution of light.
   The idea of EED is adopted in the following equations for ETR estimation originated from @Genty_et_al1989BBA,  
@@
   ETR = PFD × α~PS~ × β~PS~ × *Y*~II~,  
-  where α~leaf~ (frequently assumed to be 0.84) and α~PS~ are absorptances of the leaf and the photosystems, β~leaf~ (frequently assumed to be 0.50) and β~PS~ are EEDs to PSII on the bases of the absorptions by the leaf and by the photosystems, and *Y*~II~ (also known as Φ~PSII~, *F*~q~'/*F*~m~', or Δ*F*/*F*~m~') is a photochemical quantum yield of PSII obtained from chl fluorescence measurement.
+  where α~leaf~ (frequently assumed to be 0.84) and α~PS~ are absorptances of the leaf and the photosystems, β~leaf~ (frequently assumed to be 0.50) and β~PS~ are EEDs to PSII on the basis of the absorptions by the leaf and by the photosystems, and *Y*~II~ (also known as Φ~PSII~, *F*~q~'/*F*~m~', or Δ*F*/*F*~m~') is a photochemical quantum yield of PSII obtained from chl fluorescence measurement.
   Although β~leaf~ is frequently assumed to be 0.50, it is not always valid as mentioned above.
-  Lights with different spectral distributions are sometimes categorized into PSII- and PSI-light based on the β~PS~ approximated from their relative spectral distributions and the spectrum of excitation balance (i.e.
-Fig.
-1)---mainly judged by the proportions of PFDs in the FR waveband [e.g.
+  Lights with different spectral distributions are sometimes categorized into PSII- and PSI-light based on the β~PS~ approximated from their relative spectral distributions and the spectrum of excitation balance (Fig.
+1)---mainly judged by the proportions of PFD in the FR waveband [e.g.
 @Chow_et_al1990PNAS; @Melis1991BBA; @Pfannschmidt_et_al2001JBC; @Dietzel_et_al2008FJ; @Pfannschmidt_et_al2009AB; @Dietzel_et_al2011PC; @Hogewoning_et_al2012PC].
@@
   When there is excess excitation energy at PSII (i.e. under PSII-light), the smaller amount of excitation energy distributed to PSI results in lower potential ETR at PSI than that at PSII.
-  In this case, the smaller potential ETR at PSI limits the bulk ETR and PSII represents a smaller ETR than the potential that by decreasing the photochemical quantum yield (Fig. 2C).
+  In this case, the smaller potential ETR at PSI limits the bulk ETR and PSII represents a smaller ETR than the potential by decreasing the photochemical quantum yield (Fig. 2C).
   <!-- This shortage in the EED to PSI limits the bulk ETR so that ETR between PSII and PSI balances. -->
@@
   Therefore, balancing the EED between PSII and PSI is essential for plants to retain a high photosynthetic quantum yield.
-  Prolonged imbalances in the EED are supposed to damage leaves by generating reactive oxygen species, which cause oxidative damage to chloroplast components [for reviews, see @Asada1999AnnRev; @Asada2006PP].
+  Prolonged exposure to light with an imbalanced EED is supposed to damage leaves by generating reactive oxygen species, which cause oxidative damage to chloroplast components [for reviews, see @Asada1999AnnRev; @Asada2006PP].
 
@@
   For instance, a relative spectral distribution of light that is evenly absorbed by PSII and PSI in PSII-light-grown leaves (i.e.
-β~PS~ = 0.5; Fig.
+β~PS~ ~ 0.5; Fig.
 2A), can overexcite PSII in PSI-light-grown leaves (i.e.
@@
   The relative spectral distribution of growth light affects the EED properties of a leaf.
-  This modifies the responses of ETR, and therefore that of *P*~n~, to the relative spectral PFD distribution of measuring light.
-  Thus, the relative spectral distributions of growth light and measuring light do not only directly affect the *P*~n~, but also indirectly affect it through the interaction between the distributions of the growth and the measuring lights.
+  This modifies the response of ETR, and therefore that of *P*~n~, to the relative spectral distribution of measuring light.
+  Thus, the relative spectral distributions of growth light and measuring light do not only directly affect the *P*~n~, but also indirectly affect it through the interaction between the distributions of the lights.
   This expected interaction has been reported in several researches [@Chow_et_al1990PNAS; @Walters_Horton1995aPlanta; @Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
@@
   It is expected that a leaf will perform a higher ETR per absorbed photons by the photosystems under measuring light with a PSII/PSI-biased level similar to that of the growth light (Fig. 3).
-  When leaves grown under different spectral distributions of light are compared and evaluated under measuring light with a specific distribution, therefore, the results will inevitably be biased depending on the selecting of the measuring light.
+  When leaves grown under different spectral distributions of light are compared and evaluated under measuring light with a specific distribution, therefore, the results will inevitably be biased depending on the selection of the measuring light.
 
@@
 @Matsuda_et_al2004PCP; @Matsuda_et_al2007SSPN; @Matsuda_et_al2008PCP; @Hogewoning_et_al2010aJXB; @Hogewoning_et_al2010bJXB; @Hogewoning_et_al2012PC; @Shibuya_et_al2015BP; @Trouwborst_et_al2016EEB].
-  Most light sources used for promoting photosynthetic and growth rates, such as fluorescent lamps, metal halide lamps, high-pressure sodium lamps, and blue, red, and white LEDs, emit light containing little PFD in the FR waveband (i.e.
+  Most light sources used for providing growth light, such as fluorescent lamps, metal halide lamps, high-pressure sodium lamps, and blue, red, and white LEDs, emit light containing little PFD in the FR waveband (i.e.
 PSII-light; Fig.
 4).
-  This is because FR light is hardly ‘photosynthetically active’ and causes excessive stem elongation.
+  This is primarily because FR light is hardly ‘photosynthetically active’ and causes excessive stem elongation.
   However, several recent papers have suggested the significance of supplemental FR light on plant growth and development [for a review, see @Demotes-Mainard_et_al2016EEB].
@@
   On the other hand, in descriptive studies that hardly make assumption about the *in situ* conditions (i.e.
-fundamental studies), *P*~n~ evaluations should be made under several relative spectral distributions of light including PSII- and PSI-light.
+fundamental physiological studies), *P*~n~ evaluations should be made under several relative spectral distributions of light including PSII- and PSI-light.
   It is better for researchers to report the ‘general’ photosynthetic characteristics of the leaves in these studies.
@@
   When the measurements are made only under a single spectral distribution of measuring light because there is no other option, detailed information on the light source (e.g.
-model number) must be described in the materials and methods section so that the reader knows the spectral distribution.
+model number) must be described in the materials and methods section so that the readers know the spectral distribution.
 
@@
 ```
+
+```{r, eval = evalFig, html.cap = CapSPD}
+SPDs_grey
+# pdf("./Figs/SPDs.pdf", family = "Times", width = 3.15, height = 4)
+#   InteractionView + theme_thesis(base_size = 5)
+# dev.off()
+```

### 2016-08-22 FigMake.R

@@ -41,7 +41,7 @@ EED_dat <-
   Mole_abs %>%
   transmute(
     wavelength,
-    AlltoPSII = PSII / (1.2* PSI + PSII)
+    AlltoPSII = PSII / (1.5* PSI + PSII)
   )
 
 EEDs <-
@@ -215,14 +215,33 @@ SPDs <-
   mutate(panel = panel_names[3]) %>%
   bind_rows(., OceanSPDs, LEDs) %>%
   filter(between(wavelength, 380, 820)) %>%
-  ggplot(aes(x = wavelength, y = value, group = variable, col = variable, linetype = variable)) +
+  ggplot(aes(x = wavelength, y = value, group = variable, col = variable)) +
   theme_thesis(base_family = "serif", base_size = base_size) +
   geom_rect(aes(xmin = 700, xmax = 750, ymin = 0, ymax = +Inf), fill = "grey90", col = NA) +
   geom_line() +
   geom_text(data = SPD_labels, aes(x = wavelength, y = value, label = label), family = "serif", size = Annotate_size) +
   geom_text(data = SPD_panel, col = "black", aes(label = panel), family = "serif", size = Annotate_size * .8) +
-  scale_linetype_manual(values = c(1, 1, 3, 2, 4, 2, 2, 1, 4)) +
-  scale_color_manual(values = c("blue", "black", "darkred", "orange", "purple", "red", "grey25", "black", "black")) +
+  scale_color_manual(values = c("blue", "black", "darkred", "orange", "purple", "red", "grey60", "black", "black")) +
+  facet_grid(panel ~ .) +
+  gg_xy(c(380, 820, -.01, 4.5)) +
+  xlab("Wavelength [nm]") + ylab(u_SPFD("Spectral photon flux density"))
+
+
+SPDs_grey <-
+  Sun %>%
+  SPDnorm(from = 350, to = 750, integratedPFD = IntegratePFD) %>%
+  select(-Absorptance) %>%
+  gather(variable, value, -wavelength) %>%
+  mutate(panel = panel_names[3]) %>%
+  bind_rows(., OceanSPDs, LEDs) %>%
+  filter(between(wavelength, 380, 820)) %>%
+  ggplot(aes(x = wavelength, y = value, group = variable, linetype = variable)) +
+  theme_thesis(base_family = "serif", base_size = base_size) +
[…]

### 2016-08-22 caption.R

@@ -1,5 +1,5 @@
 CapEED <-
-  "Fig. 1  Typical excitation balance between photosystems in response to wavelength of measuring light. Spectrum was calculated from absorbance spectra of PSII and PSI complexes in solvent (Hogewoning et al. 2012) with a little modifications. The spectrum is adjusted so that the excitation energy distributed to PSII under red LED light matches a quantified value (55%, unpublished data)."
+  "Fig. 1  Typical excitation balance between photosystems in response to wavelength of measuring light. Spectrum was calculated from absorbance spectra of PSII and PSI complexes in solvent (Hogewoning et al. 2012). The spectrum is adjusted so that the excitation energy distributed to PSII under red LED light matches a quantified value (55%, unpublished data)."
 
 CapETRs <-
   "Fig. 2  Conceptual diagrams of effects of excitation energy distribution between photosystems (PSII and PSI) on photosynthetic electron transport rate (ETR). Electron transport is driven by photochemical reactions at reaction centers (gears) consuming the distributed excitation energy. Figure shows electron flow (white lines) and energy flow (black lines) in leaves grown under PSII-light (a, b) and PSI-light (c, d) and measured using PSII-light (a, c) and PSI-light (b, d). Excitation energy distribution properties of leaves are adjusted depending on growth light. GL: growth light, ML: measuring light."

### 2016-08-24 Main.Rmd
AcknowledgementにEWを追加。

@@
   In this case, the smaller potential ETR at PSI limits the bulk ETR and PSII represents a smaller ETR than the potential by decreasing the photochemical quantum yield (Fig. 2C).
-  <!-- This shortage in the EED to PSI limits the bulk ETR so that ETR between PSII and PSI balances. -->
-  <!-- In this case, PSII represents a smaller photochemical quantum yield compared to its maximum value. -->
   When PSI absorbs excess excitation energy (i.e. under PSI-light), the excitation energy distributed to PSII limits the ETR and lowers the yield of PSI (Fig. 2B).
@@
 
-**Acknowledgements**
-
-  We thank Dr Sander W. Hogewoning (Plant Lighting B.V., the Netherlands) for providing data of absorbance spectra of photosystems.
-  This work was supported by JSPS KAKENHI Grant Number 26·9372.
-
 ```{r, eval = evalFig}

### 2016-08-26 Header.Rmd
AcknowledgementにEWを追加。
no message

@@
 #     fig_caption: TRUE
-  html_document:
-    toc: TRUE
-    depth: 3
-    theme: sandstone
-    self_contained: TRUE
+  # html_document:
+  #   toc: TRUE
+  #   depth: 3
+  #   theme: sandstone
+  #   self_contained: TRUE
+  #   fig_caption: TRUE
+  word_document:
+    toc: FALSE
   fig_caption: TRUE
-  # word_document:
-  #   toc: FALSE
-    # fig_caption: TRUE
 ---
@@
 
+**Acknowledgements**
+
+  We thank Dr. Sander W. Hogewoning (Plant Lighting B.V., The Netherlands) and Dr. Emilie Wientjes (Wageningen University, The Netherlands) for providing data of absorbance spectra of photosystems.
+  This work was supported by JSPS KAKENHI Grant Number 26·9372.
+
 # References

### 2016-08-26 FigMake.R

@@ -1,73 +1,3 @@
-#-------------- EED balance spectrum
-
-if (1 == 1){
-library(EBImage)
-which_mean <- function(x) x %>% which %>% mean
-Join_by <- function(x, y) join(x, y, by = "wavelength")
-
-Hoge_PSII <- readImage("~/Dropbox/Publish/2016PgEstimate/Data/Hoge_PSII.png")
-Hoge_PSI <- readImage("~/Dropbox/Publish/2016PgEstimate/Data/Hoge_PSI.png")
-
-Abs_PSII <-
-  (Hoge_PSII[, , 1] < .8 & Hoge_PSII[, , 3] > .8) %>%
-  .@.Data %>%
-  data.frame %>%
-  t %>%
-  aaply(.margins = 2, .fun = which_mean) %>%
-  data.frame(wavelength = seq(400, 800, by = 1), abs = (dim(Hoge_PSII)[2] - .)) %>%
-  select(wavelength, PSII = abs)
-
-Abs_PSI <-
-  (Hoge_PSI[, , 1] > .8 & Hoge_PSI[, , 3] < .8) %>%
-  .@.Data %>%
-  data.frame %>%
-  t %>%
-  aaply(.margins = 2, .fun = which_mean) %>%
-  data.frame(wavelength = seq(400, 800, by = 1), abs = (dim(Hoge_PSI)[2] - .)) %>%
-  select(wavelength, PSI = abs)
-
-Mole_abs <-
-  Reduce(Join_by, list(Abs_PSII, Abs_PSI)) %>%
-  filter(wavelength %% 1 == 0) %>%
-  na.omit
-}
-
-# Mole_abs <-
-#   xlsx::read.xlsx("~/Dropbox/materials/Hogewoning_et_al.2012_Data.xlsx", sheetIndex = 2, startRow = 2) %>%
-#   select(wavelength = 1, PSII = 2, PSI = 4) %>%
-#   arrange(wavelength)
-#   
-EED_dat <-
-  Mole_abs %>%
-  transmute(
-    wavelength,
-    AlltoPSII = PSII / (1.5* PSI + PSII)
-  )
-
-EEDs <-
-  EED_dat %>%
-  mutate(All2_for = c(tail(EED_dat$AlltoPSII, -1), 0),
-         All2_back = c(0, head(EED_dat$AlltoPSII, -1)),
[…]

### 2016-10-02 Rebuttal.Rmd
査読対応

---
header-includes:
  - \setmainfont{Times New Roman}
  - \usepackage{zxjatype} # 日本語を使うためのパッケージ
  - \setjamainfont{Hiragino Kaku Gothic Pro} # 日本語フォントの指定
  - \usepackage{lscape} # 図を回転するためのパッケージ
  - \newcommand{\blandscape}{\begin{landscape}} # 図回転用のbegin command
  - \newcommand{\elandscape}{\end{landscape}} # 図回転用のend command
  - \usepackage{setspace} # 行間の調節ためのパッケージ
  - \newcommand{\bdoublespace}{\begin{spacing}{1.5}} # 行間を広げるbegin command
  - \newcommand{\edoublespace}{\end{spacing}{}} # 行間を広げるbegin command

output:
  pdf_document:
    latex_engine: xelatex
---

\bdoublespace

安武 大輔 先生

  迅速な編集対応をありがとうございます。
  査読者のおふたりの速やかな対応にも感謝いたします。
  以下に査読者のコメントに対する対応を記載いたします。
  原稿中の変更箇所は赤文字で示しております。
  ご確認くださるよう、よろしくお願いいたします。

村上 貴一

------

[Editor's Comments]

指摘事項は多いですが、できる範囲の対応で結構ですので、
論文をより良いものにするために活用して下さい。

[Reviewer(s)' Comments]
Reviewer: 1

#### 小さな変更

  投稿時にはIn pressだった論文が出版され、掲載巻号・ページが確定したため、修正しました (line 315)。

#### 査読者#1への返答

Comments to the Author  
審査の言語は英語を希望されていたが、本査読者は日本人であり、審査の速さや誤解などを招かぬよう日本語で記述させていただいた。ご理解いただけると幸いである。  
本論文は、異なる光スペクトルで育てられた植物の光合成速度を測る場合の光源のスペクトル選定についての注意喚起を促している。とりわけ、単色光に赤外光を含むか含まないかの実験処理区を設定した場合には、葉の中でPSIIとPSIに関連するタンパク質などの組成が変化している可能性があるため、PSIIに吸収されやすい光で光合成を測定するか、あるいはPSIに吸収されやすい光で光合成を測定するかで得られる測定結果（大小関係）が異なってしまうことを理論的に説明している。関連する文献などよく読みこまれており、説明も分かりやすいと感じる。光合成と光質を扱う研究者への啓発論文となっており、興味深い。本誌への掲載に値すると思うが、その前に気になる点を挙げる。可能な限りそれらに応えてほしいと思う次第である。

１．著者らの以前の実験で、キュウリ苗を白色LEDで育成するときにFRを入れるか入れないかの処理区が設定され、それらの光合成能力を評価するために赤青LEDを光源としてLI-6400でガス交換速度が測られた。その後、疑似太陽光で測定が繰り返され、LEDで認められた光合成の大小関係が疑似太陽光ではその差がなくなっていると述べられている。このとき、測定値は何％ずれていたのか、記述する必要があると感じる。たとえば、処理区間におけるLEDで測定された光合成速度の差が５％なのか２０％以上あるのか、その程度によって印象が異なるからである。Fig3の曲線ではその差を随分と増幅したように描かれているが、基本的には数値が入っていない。仮に５％ほどしか差がないと考える。それが疑似太陽光でほぼ互角の光合成速度となったとする。多くの場合、その程度であれば、もともと栽培時の光質処理によって光合成速度は変わらないと、問題なく評価するであろう。しかし、それが２０％や３０％にもなるのであれば、著者らの意見に納得するであろう。  
ちなみに、成長と合わせて考える場合、葉面積あたりの正味光合成速度で成長の差を議論できないのは多くの場合でありえる。（作物系の雑誌では国内外を問わず問題視されてきた過去がある。）成長には葉の展開、角度などの形態形成も直接的に影響を与えるからである。FRはダイレクトに細胞伸長を誘導する光であることも考慮に入れる必要があるだろう。そのため、測定波長による光合成速度の測定誤差はどの程度となるのか、その点は重要でないかと思われる。なお、著者らは論文としてアクセプトされているようだが、本誌を読むだけでもそのことが分かるように書かれている必要がある。

> 試験区間差に関する記述を追加しました (line 75--77)。
> 引用文献に記載されているため、論文としてアクセプトされていることは明確であると判断します。

２．上記キュウリ苗の実験において、栽培光中の可視光に対してFRは何割ほど入っているのか、また、そのFR割合はPS II/PS Iの量比を変化させているとなぜ判断できるのか、その根拠となる論文を引用する必要あり。本来ならば、著者らのグループもPSII/PSI比を化学的に示す必要がある。

> FRの割合に関する記述を追加しました (line 72)。
> PSII/PSI量比が光エネルギー分配の調節に重要であると考えられていますが、その他の機構が関与している可能性があります (追記箇所: line 191--192)。
> 本論文では、光エネルギー分配の調節の原因をPSII/PSI量比に限定せずに議論しております。

３．本論文がLI-6400のLED測定光源がある意味、使えない光源、と判断している、と受け取られても仕方ない面がある。ライカ社にとっては、気分のいいものではないと思われる。ライカのLED光源は、どのような測定で有効と考えられるか、そのようなケースがあるのであれば簡単でよいので記述したほうが良いと考える（もし、今のテキストに記述されていたなら、査読者の読み取り不足です）。

> 「使えない光源だ」と判断しています。
> 強いて上げれば、広く標準的に使われているため、他の研究との比較が容易なことです。
> ただし、多くの研究でこれらの光源を標準的に利用することは系統的なバイアスを強調するため、避けるべきです。
> したがって、テキストに同光源が有益な条件は記述しておりません。

４．PSIIに偏向した光（例えば、赤、赤青光）で栽培されたとき、測定光がＰＳＩに吸収の高い光であった場合に過誤が生じやすいとのことであるが、大気CO2分圧下で光飽和条件下の場合、電子伝達速度が律速にならない場合も過誤が起きるのだろうか？PSIに吸収されやすい光であっても、それより短い波長の光が十分に強く当たっていれば、PSIIとPSIは飽和し、PSIに偏向された測定光であっても光合成速度（電子伝達速度）のポテンシャルは取れるのではないだろうか？この意見が違っていれば、そのような誤解が生じないようなテキストの工夫をお願いしたい。テキストにあったように光が不足する条件（電子伝達速度が律速）では、生じる可能性大、であることは理解できた。光飽和、弱光などのような場合分けをもっと明確にしてもいいと思う。

> 光飽和 (高PFD・低CO2濃度) 条件での交互作用に関する記述を追加しました (line 179--186)。

細かな指摘  
１．Abstractをもっと具体的に記述したほうがよい。今回、本文を読む前に読ませていただいたが、抽象的な表現が多いため、最初はアブストラクトだけでは内容がわからなかった。本文を読んだ後では理解できたが。PSIIやPSIの吸収しやすい光で育てられた場合、PSII/PSI比が変わる可能性があるので、測定光がPSIIに偏向した光、PSIに偏向した光、で測定すると、波長に依存して過小評価あるいは過大評価がおきる、などの本文を反映した具体的な記述を入れるべきである。

> 修正しました (line 9--21)。

２．P4L79この記述には引用が必要

> 引用文献を追加し、記述を修正しました (line 104--105, 278-289)。

３．P5L102,104など
Fig.2中の各パネルとそのキャプションのアルファベットはa～ｄの小文字であるが、本文はA～Ｄの大文字である。統一すべき。

> 修正しました (line 128, 130, 147)。

４．Fig. 2について
Fig2dに関する記述がないように見受けられた。掲載された図の説明は全て行うべきであるため、加筆すべき（もしあったなら査読者の間違いであり、お詫びする）。  
分配されるエネルギの大小を黒線の太さで示していると思うのだが、bとcの図について、途中から細い矢印が始まる箇所はここで合っていますか？分配されるまでは太い線、利用できるのは細い線ならば、逆三角形の桶にはいるまでは太い線のまま？桶を通過後細い線になるのでは？とも思った。この図に関しては、テキストかキャプションでさらなる解説が必要と感ずる。例えば、桶の大きさが何を反映しているか、などの記述。

> Fig2b,dを比較した記述を追加しました (line 147--149)。
> Fig2の矢印を修正し、キャプションに記述を追加しました (line 353--354)。

#### Response to Reviewer #2:

Reviewer: 2

Comments to the Author  
Gneral comments  
This paper indicates the importance of the spectral properties of measuring lights for photosynthesis, offering useful information to readers of the journal.
I basically agree with authors’ argument. However, I think the lack of quantitative data lowers the usefulness of this paper. Readers want to know how much Pn can change with the light spectral distribution under the same intensity conditions to decide which types of light for measurement to be used. If possible, show some values (e.g., xx% increase) as examples.
“Interaction” is used thoroughly as a key term, please use “interaction” properly (see specific comment #1)

Specific comments  
1. Line 11 “the interaction between the distributions of the lights”
What does this phase mean? “interaction” is a process by which two or more things affect each other. Does one light distribution affect another light distribution?

> We rephrased the some “interaction” to “statistical interaction” (line 11, 88).
> We used the term “interaction” as a statistical term throughout the manuscript.

2. Explain equations (Line 87-88) in more detail. Does upper “ETR” differ from lower “ETR”
ETR is first used in Line 86 not in 98.

> The two ETRs are the same.
> We corrected the equation (line 113) and the abbreviated point (line 111).

3. Please clarify the definition of PSI-light and PSII-light?
Is there neutral light?

> We added description on the definition (line 122--123).
> “Neutral light” exists depending on the leaf as mentioned in the manuscript (line 144--149).

4. Figure 1 is very informative. Please clarify how to calculate it in detail.
Is “typical” correct?  Is “example” better?

> We added some description (line 345-346).
> As similar spectrum was drawn in several earlier papers, the shown spectrum may be “typical”.

5. What is “potential ETR at PSI or PSII” in Line 100?

> The following sentence describes the meaning of “potential” (line 126--128).

6. Is Figure 3 based on the quantitative data? Does the shape or height of the peaks in curves have meanings?  I think this figure is not necessary.

> The figure is conceptual diagram, and not based on the quantative data.
> For simplicity, the peaks were made to be the same height.
> Although we agree with you that this figure is not “necessary”, it will help the readers to understand the discussion.

7. What is “relative spectral distribution”? What is the difference from “spectral distribution”? Why did you use not “relative spectral distribution” but “spectral distribution” in Fig.4?

> We added description on the “relative spectral distribution” (line 59).
> “Spectral distribution” consists of two factors; PFD---integral of the “spectral distribution”---and light quality---the “relative spectral distribution”.
> Fig.4 shows the “spectral distributions” because they are more informative than the “relative spectral distributions”.

\edoublespace

### 2016-10-02 Header.Rmd
査読対応

@@
   Relative spectral distributions of light during growth and for measurements do not only directly affect the net photosynthetic rate (*P*~n~), but also indirectly affect it through the interaction between the distributions of the lights.
-  This paper summarizes a plausible mechanism of the interaction, some situations in which the interaction should be considered, and recommendations for selecting appropriate measuring light to evaluate photosynthesis.
-  In agricultural and horticultural studies, the *P*~n~ should be measured under *in situ* conditions, depending on the purpose of the study.
-  For prospective studies focusing on the evaluation of plant growth after measurements, *P*~n~ should be measured under the spectral distribution of light to which the plant will be subjected.
-  In retrospective studies aiming to elucidate the causes of differences in growth brought about by the different growth conditions, measurements should be made under the spectral distributions of the lights under which the plants were grown.
+  This paper summarizes a plausible mechanism of the statistical interaction, some situations in which the interaction should be considered, and recommendations for selecting appropriate measuring light to evaluate photosynthesis.
+  A leaf grows to adjust excitation energy distribution balance between the photosystems in response to the relative spectral distribution of growth light.
+This adjustment modifies the response of Pn to the relative spectral distribution of measuring light.
+  Therefore, evaluating *P*~n~ of leaves of plants grown under different relative spectral distributions of growth light with single spectral distribution of measuring light leads to over/underestimation of the *P*~n~.
   The *P*~n~ under a single spectral distribution of measuring light is only one aspect of the photosynthetic characteristics of a leaf.
 The obtained results must be discussed in relation to the spectral distribution of measuring light so as not to make biased evaluations.
+  In agricultural and horticultural studies, the *P*~n~ should be evaluated under appropriate measuring light, depending on the purpose of the study.
 

### 2016-10-02 CI_calc.R

@@ -1,0 +1,27 @@
+# Analyze Confidence interval
+
+library(xlsx)
+Pn_dat <-
+  read.xlsx("~/Dropbox/Publish/Done!/2015Cucumber_PhysiolPlant/data.xlsx", sheetName = "RawPn")
+
+Pn_0 <-
+  Pn_dat %>%
+  select(GL = Growth.light,
+         ML = Measuring.light,
+         Trtm, ave) %>%
+  filter(GL %in% c("W", "WFr"),
+         ML %in% c("BR_LED", "sunlight"),
+         Trtm == "LowLight.Ca40.Pn") %>%
+  select(-Trtm)
+
+Pn_0 %>%
+  arrange(ML, GL) %>%
+  filter(., ML == "BR_LED") %>%
+  {t.test(.[1:3, 3], .[4:6, 3])} %>%
+  print
+
+Pn_0 %>%
+  arrange(ML, GL) %>%
+  filter(., ML != "BR_LED") %>%
+  {t.test(.[1:3, 3], .[4:6, 3])} %>%
+  print

### 2016-10-02 FigMake.R

@@ -1,12 +1,12 @@
 #----------------------- two curves plot
 X_div <- 101
 X_range <- seq(0, 1, length.out = X_div)
-x_breaks <- c(0.2, 0.4, 0.65)
+x_breaks <- c(0.2, 0.48, 0.75)
 
 
 InteractionDat <-
   data_frame(X = rep(X_range, times = 2),
-             ETR = c(sqrt(dbeta(X_range, 4.5, 3.5)) * 1.1, sqrt(dbeta(X_range, 3, 5))),
+             ETR = c(sqrt(dbeta(X_range, 4, 2.7)), sqrt(dbeta(X_range, 2.7, 4))),
              Trtm = rep(c("PSII-leaves", "PSI-leaves"), each = X_div))
 
 InteractionLabel <-
@@ -22,7 +22,7 @@ InteractionPoint <-
 InteractionText <-
   InteractionDat %>%
   filter(X %in% x_breaks) %>%
-  mutate(labels = c("far-red LED light", "Sunlight", "blue + red LED light", rep("", length(x_breaks)))) %>%
+  mutate(labels = c("far-red LED light", "Sunlight", "blue+red LED light", rep("", length(x_breaks)))) %>%
   mutate(ETR = c(0.1, 0.1, 0.1, numeric(length(x_breaks))))
 
 InteractionView <-

### 2016-10-03 Rebuttal.Rmd
おもにwordで直し。3768 wordsでFin。

@@
     latex_engine: xelatex
+
 ---
 
+\large
 \bdoublespace
@@
 
-  投稿時にはIn pressだった論文が出版され、掲載巻号・ページが確定したため、修正しました (line 315)。
+  投稿時にはIn pressだった論文が出版され、掲載巻号・ページが確定したため、修正しました (line 299)。
 
@@
 
-> 試験区間差に関する記述を追加しました (line 75--77)。
-> 引用文献に記載されているため、論文としてアクセプトされていることは明確であると判断します。
+> 以前の実験では、試験区間差は赤青LED光下で36%、疑似太陽光下で-3%でした。
+> 光合成評価時に無視できない効果の大きさだと考えます。
+> 各試験区の実測値・試験区間差に関する記述を追加しました (line 51--56)。
 
@@
 
-> FRの割合に関する記述を追加しました (line 72)。
-> PSII/PSI量比が光エネルギー分配の調節に重要であると考えられていますが、その他の機構が関与している可能性があります (追記箇所: line 191--192)。
+> FRの割合に関する記述を追加しました (line 49)。
+> PSII/PSI量比が光エネルギー分配の調節に重要であると考えられますが、その他の機構が関与している可能性があります。
 > 本論文では、光エネルギー分配の調節の原因をPSII/PSI量比に限定せずに議論しております。
+> 本文を修正し、その旨を明確にしました (line 174--175)。
 
@@
 > 「使えない光源だ」と判断しています。
-> 強いて上げれば、広く標準的に使われているため、他の研究との比較が容易なことです。
+> 強いて上げれば、広く標準的に使われているため、他の研究との比較が容易なことが利点です。
 > ただし、多くの研究でこれらの光源を標準的に利用することは系統的なバイアスを強調するため、避けるべきです。
@@
 
-> 光飽和 (高PFD・低CO2濃度) 条件での交互作用に関する記述を追加しました (line 179--186)。
+> 筆者らも、光飽和条件下では、交互作用に起因した評価のずれの問題は生じないことを予想しておりました。
+> しかし、実際には、光飽和条件 (PPFD: 1200 µmol m^--2^ s^--1^・葉内CO~2~濃度: 20 Pa) 下においても交互作用が検出されました。
+> その原因は明確ではありませんが、いずれかの光化学系を過剰に励起させるような光を高PPFDで照射したことで、光阻害が生じたのではないか、と考えております。
+> 以上の記述を追加しました (line 160--169)。
 
@@
 
-> 修正しました (line 9--21)。
+> ご指摘に従い、具体的な記述が多くなるよう修正しました (line 9--21)。
 
@@
 
-> 引用文献を追加し、記述を修正しました (line 104--105, 278-289)。
+> 引用文献を追加し、記述を修正しました (line 83--84, 261-262)。
 
@@
 
-> 修正しました (line 128, 130, 147)。
+> 修正しました (line 108, 110, 127)。
 
@@
 
-> Fig2b,dを比較した記述を追加しました (line 147--149)。
-> Fig2の矢印を修正し、キャプションに記述を追加しました (line 353--354)。
+> Fig2b,dを比較した記述を追加しました (line 128--129)。
+> Fig2の矢印を修正し、キャプションに記述を追加しました (line 337--338)。
 
@@
 Specific comments
-1. Line 11 “the interaction between the distributions of the lights”
+
+###### 1. Line 11 “the interaction between the distributions of the lights”
 What does this phase mean? “interaction” is a process by which two or more things affect each other. Does one light distribution affect another light distribution?
 
-> We rephrased the some “interaction” to “statistical interaction” (line 11, 88).
 > We used the term “interaction” as a statistical term throughout the manuscript.
+> We rephrased some “interaction” to “statistical interaction” (line 11, 61, 234).
 
-2. Explain equations (Line 87-88) in more detail. Does upper “ETR” differ from lower “ETR”
+###### 2. Explain equations (Line 87-88) in more detail. Does upper “ETR” differ from lower “ETR”
 ETR is first used in Line 86 not in 98.
@@
 > The two ETRs are the same.
-> We corrected the equation (line 113) and the abbreviated point (line 111).
+> We corrected the equation (line 92) and the abbreviated point (line 90, 104).
 
-3. Please clarify the definition of PSI-light and PSII-light?
+###### 3. Please clarify the definition of PSI-light and PSII-light?
 Is there neutral light?
 
-> We added description on the definition (line 122--123).
+> We added description on the definition (line 101--103).
 > “Neutral light” exists depending on the leaf as mentioned in the manuscript (line 144--149).
 
-4. Figure 1 is very informative. Please clarify how to calculate it in detail.
+###### 4. Figure 1 is very informative. Please clarify how to calculate it in detail.
 Is “typical” correct?  Is “example” better?
 
-> We added some description (line 345-346).
-> As similar spectrum was drawn in several earlier papers, the shown spectrum may be “typical”.
+> We added some description (line 329-330), although readers must read the cited paper for complete understanding.
+> As similar spectrum was drawn in several earlier papers (e.g. Evans 1986, Hogewoning et al. 2012, Wientjes et al. 2013, Laisk et al. 2014), the shown spectrum may be “typical”.
 
-5. What is “potential ETR at PSI or PSII” in Line 100?
+###### 5. What is “potential ETR at PSI or PSII” in Line 100?
 
-> The following sentence describes the meaning of “potential” (line 126--128).
+> The potential ETR is a product of the distributed excitation energy to and the maximum photochemical yield of PSII (or PSI).
+> The following sentence was rephrased so that the meaning of “potential” becomes clear (line 107--108).
 
-6. Is Figure 3 based on the quantitative data? Does the shape or height of the peaks in curves have meanings?  I think this figure is not necessary.
+###### 6. Is Figure 3 based on the quantitative data? Does the shape or height of the peaks in curves have meanings?  I think this figure is not necessary.
 
@@
 
-7. What is “relative spectral distribution”? What is the difference from “spectral distribution”? Why did you use not “relative spectral distribution” but “spectral distribution” in Fig.4?
+###### 7. What is “relative spectral distribution”? What is the difference from “spectral distribution”? Why did you use not “relative spectral distribution” but “spectral distribution” in Fig.4?
 
-> We added description on the “relative spectral distribution” (line 59).
-> “Spectral distribution” consists of two factors; PFD---integral of the “spectral distribution”---and light quality---the “relative spectral distribution”.
+> Relative spectral distribution is normalized spectral distributions usually by the peak value.
+> We added description on the “relative spectral distribution” (line 35-36).
 > Fig.4 shows the “spectral distributions” because they are more informative than the “relative spectral distributions”.

### 2016-10-03 CI_calc.R

@@ -25,3 +25,8 @@ Pn_0 %>%
   filter(., ML != "BR_LED") %>%
   {t.test(.[1:3, 3], .[4:6, 3])} %>%
   print
+
+Pn_0 %>%
+  group_by(GL, ML) %>%
+  summarise(mean = round(mean(ave), 1), se = round(se(ave), 1)) %>%
+  arrange(ML)

### 2016-10-18 Revised_ED1/Rebuttal.Rmd
4752 words

--- 2016-10-03 Rebuttal.Rmd
@@
 
-  投稿時にはIn pressだった論文が出版され、掲載巻号・ページが確定したため、修正しました (line 299)。
+  投稿時にはIn pressだった論文が出版され、掲載巻号・ページが確定したため、修正しました (line 300)。
 
@@
 > 光合成評価時に無視できない効果の大きさだと考えます。
-> 各試験区の実測値・試験区間差に関する記述を追加しました (line 51--56)。
+> 各試験区の実測値・試験区間差に関する記述を追加しました (line 52--57)。
 
@@
 
-> FRの割合に関する記述を追加しました (line 49)。
+> FRの割合に関する記述を追加しました (line 50)。
 > PSII/PSI量比が光エネルギー分配の調節に重要であると考えられますが、その他の機構が関与している可能性があります。
 > 本論文では、光エネルギー分配の調節の原因をPSII/PSI量比に限定せずに議論しております。
-> 本文を修正し、その旨を明確にしました (line 174--175)。
+> 本文を修正し、その旨を明確にしました (line 175--176)。
 
@@
 > その原因は明確ではありませんが、いずれかの光化学系を過剰に励起させるような光を高PPFDで照射したことで、光阻害が生じたのではないか、と考えております。
-> 以上の記述を追加しました (line 160--169)。
+> 以上の記述を追加しました (line 161--170)。
 
@@
 
-> ご指摘に従い、具体的な記述が多くなるよう修正しました (line 9--21)。
+> ご指摘に従い、具体的な記述が多くなるよう修正しました (line 9--22)。
 
@@
 
-> 引用文献を追加し、記述を修正しました (line 83--84, 261-262)。
+> 引用文献を追加し、記述を修正しました (line 84--85, 262-263)。
 
@@
 
-> 修正しました (line 108, 110, 127)。
+> 修正しました (line 109, 111, 128)。
 
@@
 
-> Fig2b,dを比較した記述を追加しました (line 128--129)。
-> Fig2の矢印を修正し、キャプションに記述を追加しました (line 337--338)。
+> Fig2b,dを比較した記述を追加しました (line 129--130)。
+> Fig2の矢印を修正し、キャプションに記述を追加しました (line 338--339)。
 
@@
 > We used the term “interaction” as a statistical term throughout the manuscript.
-> We rephrased some “interaction” to “statistical interaction” (line 11, 61, 234).
+> We rephrased some “interaction” to “statistical interaction” (line 11, 62, 235).
 
@@
 > The two ETRs are the same.
-> We corrected the equation (line 92) and the abbreviated point (line 90, 104).
+> We corrected the equation (line 92) and the abbreviated point (line 91, 105).
 
@@
 
-> We added description on the definition (line 101--103).
-> “Neutral light” exists depending on the leaf as mentioned in the manuscript (line 144--149).
+> We added description on the definition (line 102--104).
+> “Neutral light” exists depending on the leaf as mentioned in the manuscript (line 145--150).
 
@@
 
-> We added some description (line 329-330), although readers must read the cited paper for complete understanding.
+> We added some description (line 330--331), although readers must read the cited paper for complete understanding.
 > As similar spectrum was drawn in several earlier papers (e.g. Evans 1986, Hogewoning et al. 2012, Wientjes et al. 2013, Laisk et al. 2014), the shown spectrum may be “typical”.
@@
 > The potential ETR is a product of the distributed excitation energy to and the maximum photochemical yield of PSII (or PSI).
-> The following sentence was rephrased so that the meaning of “potential” becomes clear (line 107--108).
+> The following sentence was rephrased so that the meaning of “potential” becomes clear (line 108--109).
 
@@
 > Relative spectral distribution is normalized spectral distributions usually by the peak value.
-> We added description on the “relative spectral distribution” (line 35-36).
+> We added description on the “relative spectral distribution” (line 36--37).
 > Fig.4 shows the “spectral distributions” because they are more informative than the “relative spectral distributions”.
